### 2014-04-08 cosmic_voids.tex
Initializing repository

\documentclass[a4,useAMS,usenatbib,usegraphicx]{latex/mn2e} 
%\documentclass{latex/emulateapj} 
%External Packages and personalized macros
\include{latex/macros}

\begin{document}

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{The place of the local group in the cosmic web}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

\maketitle

\begin{abstract}

We present here a study about the influence of the environment on the
local group (LG) of galaxies in the context of $\Lambda$CDM. In this study
we use a large volume high resolution N-body cosmological simulation 
(Bolshoi) along with the most recent methods to quantify the cosmic web 
(T-web, V-web schemes); furthermore we propose a novel approximation, base
upon the minimization of the mean density of void regions, to determinate 
the optimal threshold value $\lambda_{th}$, which have been treated until 
now as a free parameter. 
Following the recent work of Courtois et al. (2013), where was 
found that the LG is located near to a large void, we also perform an 
extensive study of voids, applying a FOF algorithm to find void regions 
and performing an analysis of their shape based upon the reduced inertia 
tensor.
Using the recent observations that constrain the tangential velocity of
M31 with respect to the Milky Way (MW), the previously established radial 
velocity, the estimated masses of dark halos, along with some criteria
to guarantee the gravitational isolation of these systems (Forero-Romero
et al. 2013-1), we select a set of halo pairs as a candidate sample 
of LG-like systems in the Bolshoi simulation. 
We look for possible biases and correlations between the environment 
properties of each LG-like system and its kinematic and formation 
properties. Among our main result we find \SRKED{[summarize our results 
here!]}.

\end{abstract}

\begin{keywords}
Cosmology: large-scale Structure of Universe, 
galaxies: star formation - line: formation
\end{keywords}

%=========================================================================
%		PAPER CONTENT
%=========================================================================

%*************************************************************************
\section{Introduction}
\label{sec:introduction}
%*************************************************************************

The spatial distribution of galaxies describes a web-like pattern, the 
so-called cosmic web. Today it is understood that such configuration is 
driven by gravitational instabilities. ...

The study of the influence of the cosmic web on galaxy properties start 
with the seminal work of Dressler \SRKED{[reference here]} and extends to 
recent works using large observational surveys that look for signatures of 
the web into the evolution of galaxy populations. With the advention of 
more detailed observations and sophisticated computational models it is 
now within our reach to understand what physical processes dominate.

This makes  that the mass assembly history of a galaxy is deeply connected 
with its  position in the cosmic web. There is an extensive body of 
literature on the effects of the web environment on the observable 
properties of galaxies.

This environmental study is also of paramount importance to understand the 
formation of our Galaxy. In our local neighborhood, the observations of 
dwarf galaxies around the Milky Way (MW) and the Andromeda galaxy (M31) 
show filamentary and disk-like patterns that can be linked to a 
preferential infall direction, very likely connected with the cosmic web 
where the Local Group (LG) of galaxies is embedded.

In this paper we quantify the velocity shear environment of DM halo pairs
representative of the principal members of the Local Group (LG), the Milky
Way (MW) and Andromeda galaxy (M31). We perform this study in an 
unconstrained cosmological simulation from random phases in the initial 
conditions, and unlike previous works, where were used constrained 
cosmological simulations which have been setup as to reproduce the large 
scale structure of the local universe, we use directly observational 
measurements of the kinematics properties of the local group \SRKED{
[Reference here]} in order to build faithful samples of LG-like systems.

We pay special attention to the correlation of the present velocity shear 
environment with the assembly and the kinematics properties of the pairs. 
The motivation to have that focus is that it has been previously shown 
that the LG present in three different realizations of the constrained 
simulations have assembly histories biased towards early formation times 
and absence of major mergers (ratio 1:10) in the last $10$ Gyr. In the 
case of the kinematic properties, recent observational constrains to the 
galactocentric tangential velocity of M31 has enabled to establish how 
typical is the LG in a cosmological context \SRKED{[reference to 
Forero-Romero et.al 2013-1]}, that is why we focus here how a specific kind 
of host environment biases these kinematics properties.

%*************************************************************************
\section{The Simulation}
\label{sec:the_simulation}
%*************************************************************************

As it was previously mentioned, we use an unconstrained cosmological 
simulation, the Bolshoi simulation, to identify the possible large scale 
environment of the Local Group. This is a similar approach to the one already 
used by \SRKED{[reference here]}.

The Bolshoi simulation follows the non-linear evolution of a dark matter 
density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
particles. The cosmological parameters in the simulation are 
$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
dimensionless Hubble parameter, spectral index of primordial density 
perturbations and normalization for the power spectrum. The mass of each 
particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.

%-------------------------------------------------------------------------
\subsection{Halos and Merger Trees}
\label{subsec:halos_merger_trees}
%-------------------------------------------------------------------------

We identify halos with two algorithms, the Friends-of-Friends \SRKED{
[reference here]} algorithm and the Bound Density Maximum algorithm. The 
constructed catalogues also provide the basis for the mass aggregation 
history studies. We also include in the catalogues information about the 
substructure.

All the results presented here must be interpreted in term of host halos, 
without any information of the substructure. In particular the merger of 
two FOF halos corresponds to the epoch of first overlap, and not to the 
fusion and/or disruption of an accreted sub-halo with a dominant halo.

The linking length is $b=0.17$ times the mean inter-particle separation. 
All objects with 20 particles or more are considered a bona fide halo and 
are included in the construction of the merger tree, this corresponds to a 
minimum halo mass of $M_{\rm min}=2.70\times 10^{9}$\hMsun in the Bolshoi 
simulation.

The halo identification for the simulation was done for XX snapshots in 
the redshift range $0<z<7$ more or less evenly spaced in look-back time.

%*************************************************************************
\section{Algorithms to quantify the cosmic web}
\label{sec:algorithms_cosmic_web}
%*************************************************************************

%-------------------------------------------------------------------------
\subsection{The tidal web (T-web)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

The first algorithm  we use to identify the cosmic web is based upon the
diagonalization of the tidal tensor, defined as the Hessian of a 
normalized gravitational potential

%.........................................................................
%Tidal Tensor
\begin{equation}
T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}}
\end{equation}
%.........................................................................
where the physical gravitational potential has been rescaled by a factor 
$4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
equation

%.........................................................................
%Poisson
\begin{equation}
\nabla^2\phi = \delta,
\end{equation}
%.........................................................................
where $\bar{\rho}$ is the average density in the Universe, $G$ is the 
gravitational constant and $\delta$ is the dimensionless matter 
overdensity.

%-------------------------------------------------------------------------
\subsection{The velocity  web (V-web)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

We also use a kinematical method to define the cosmic-web environment in 
the simulation. The method has been thoroughly described in XXX and 
applied to study the shape and spin alignment in the Bolshoi simulation 
here XX. We refer the reader to these papers to find a detailed 
description of the algorithm, its limitations and capabilities. Here we 
summarize the most relevant points for the discussion.

The V-web method for environment finding is based on the local shear 
tensor calculated from the smoothed DM velocity field in the simulation.
The central quantity is the following dimensionless quantity

%.........................................................................
%V-Web Definition
\eq{V_web}
{
\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}}
}
%.........................................................................
where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
the comoving velocity and position, respectively. $\Sigma_{\alpha\beta}$ 
can be represented by a $3\times 3$ symmetric matrix with real values,
that ensures that is possible to diagonalize and obtain three real 
eigenvalues $\lambda_{1} > \lambda_{2}>\lambda_3$ whose sum (the trace of
$\Sigma_{\alpha\beta}$) is proportional to the divergence of the local 
velocity field smoothed on the physical scale ${\mathcal R}$.

The relative strength of the three eigenvalues with respect to a threshold
value $\lambda_{th}$ allows for the local classification of the matter 
distribution into four web types: voids, sheets, filaments and peaks, 
which correspond to regions with 3, 2, 1 or 0 eigenvalues with values 
larger than $\lambda_{th}$. Below we shall discuss a novel approach to 
define an adequate threshold value based on the visual impression of void
regions, furthermore we study other possible values based on other visual
features of the cosmic web.

%-------------------------------------------------------------------------
\subsection{The cosmic web in Bolshoi}
\label{subsec:web_in_simulations}
%-------------------------------------------------------------------------

Both established schemes to quantify the cosmic web depend on continuous 
and smooth physical quantities, as the peculiar velocity field and the 
density field. In order to calculate the necessary tensors, a discretization
of the simulation volume is performed, so all the properties are reduced 
to single values associated to discrete cells. According to this, we divide 
the overall volume into $(256)^3$ cells, so each cell has an associated 
comoving cubic volume of $0.98 \mbox{ Mpc h}^{-1}$. Finally, in order to 
reduce possible effects due to the discretization process, a gaussian 
softening is performed between neighbour cells.

Once defined the numerical details about the classification schemes, we 
shall analyse the dependence on the threshold value $\lambda_{th}$ for each 
one. In Figure \ref{fig:mean_density} we show the variation of the mean 
density parameter $\delta$ with the threshold value for cells marked as one 
of the two more dominant types of environment (voids and sheets).

%.........................................................................
%FIGURE 1: Mean density for each environment
\begin{flushleft}
\begin{figure}
\centering

  \includegraphics[trim = 0mm 0mm 12mm 5mm, clip, keepaspectratio=true,
  width=0.35\textheight]{./figures/cell_types_density.pdf}

  \captionof{figure}{\small Mean density parameter for each one of the 
  defined environments according to the chosen $\lambda_{th}$ value and 
  for both classification schemes. Tweb (green lines) and Vweb (blue 
  lines). The mean density parameter is calculated by averaging all the 
  values  of the cells determined as a certain type of environment 
  according to its eigenvalues. The optimal parameters found are 
  $\lambda_{opt}^{T}=0.326$ and $\lambda_{opt}^{V}=0.188$.}

  \label{fig:mean_density}
  \vspace{0.1 cm}

\end{figure}
\end{flushleft}
%.........................................................................

As was previously established by \SRKED{Hoffman et al. (2012)} and as 
can be seen in Figure \ref{fig:mean_density}, the behaviour of the 
V-web scheme is significantly more sensible to variations of the 
$\lambda_{th}$ value compared with the T-web scheme; nevertheless, the 
behaviour of the mean density parameter for voids, sheets and filaments, 
are qualitatively quite similar for the two schemes, increasing with the 
value of $\lambda_{th}$. Although we shall focus our analysis on voids 
because they are completely dominant in the visual impression of the 
cosmic web, an analogous analysis might be performed for other type of 
environments.

On cosmic scales, the presence of highly non-linear structures implies the 
existence of very vast regions with density lower than the mean 
cosmological value due to the mass conservation. That is why the visual 
impression of the cosmic web should be necessarily dominated by these 
under-dense regions. Keeping that in mind, our novel proposal is based upon
the correct quantification of these regions, so the optimal threshold 
value must be chosen such that: sheet regions do not invade real void 
regions (in such case, the mean density parameter of sheet regions would 
become negative) and void regions do not invade real sheet and filament 
regions (in such case, the mean density parameter of void regions would 
increase due to the contribution of over-dense regions). Thus, the optimal 
value is simply where the mean density parameter of sheet regions is 
null. According to this, we obtain the next optimal threshold values 
for the T-web and the V-web respectively, $\lambda_{opt}^T = 0.326$ and 
$\lambda_{opt}^V = 0.188$. To verify our analysis, we show in Figure 
\ref{fig:visual_impression} the visual impression for each defined critical 
value, and as can be seen, the chosen values reproduce properly the 
expected impression according to the density field.

%.........................................................................
%FIGURE 2: Visual impresion
\begin{flushleft}
\begin{figure*}
\begin{center}

  \includegraphics[trim = 42mm 15mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
  \includegraphics[trim = 42mm 15mm 37mm 10mm, clip, keepaspectratio=true,
  width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}

  \captionof{figure}{\small Visual impression of the density field (left 
  panels), and of each classification scheme with the $\lambda_{th}$ values 
  obtained by our criteria (others panels). Our color convention for each 
  environment is (white) - void, (light gray) - sheet, (gray) - filament, 
  (black) - knot. For each web scheme, it has been used the previously 
  established optimal threshold as a reference value, so plots are done 
  with the next values $\lambda_{th} = 0.0$, $\lambda_{th} = 
  \lambda_{opt}/2$, $\lambda_{th} = \lambda_{opt}$ and $\lambda_{th} = 
  2\lambda_{opt}$.}

  \label{fig:visual_impression}
  \vspace{0.1 cm}

\end{center}
\end{figure*}
\end{flushleft}
%.........................................................................

Our classification scheme may be thought as a refinement of the recent 
schemes, where the threshold value is used to taking as a free parameter, 
based on the classic methods, where the classification is performed 
based on a cut off of the density field directly \SRKED{[references here]}.
So we make use of the objectivity achieved by the analysis of the mean 
density, but keeping all the environmental information provided by the
tensorial schemes instead of the poor description provided by the density 
field.

%-------------------------------------------------------------------------
\subsection{Method to find void regions}
\label{subsec:method_voids}
%-------------------------------------------------------------------------

Following the recent growing interest in studying galaxy formation in 
low-density regions, we use a method based on a FOF-like algorithm to 
find extended regions of voids. To achieve this, we build the input 
catalogue for the FOF method with the coordinate of the center of every 
cell marked as void according to the web classification scheme adopted, 
furthermore we set an adequate linking length to connect even diagonal 
neighbour cells.

Following the work of \SRKED{Forero-Romero et al. 2008}, we also perform a 
percolation analysis in order to select the best threshold parameter that
reduces percolation in cells, thereby accounting for physical bulk void 
regions. In Figure \ref{fig:percolation_analysis} we show the obtained 
result of our percolation analysis for both web schemes. In both cases, it 
can be noticed that the volume of the largest void region is minimized and 
the volume distribution of voids is relatively flat at $\lambda_{th} = 0.0$, 
what means percolation is completely reduced for this threshold value. So, 
in spite of the previously established $\lambda_{th}$ optimal values for 
each scheme, we shall use $\lambda_{th} = 0.0$ just for the detection of 
bulk void regions. Moreover, due to the domination of the large scale 
visual impression by voids, it is inevitable the presence of the 
percolation phenomenon, so the current chosen threshold value for 
percolation is justified because though voids are necessarily connected 
among them, we are just interested in detecting bulk regions.

%.........................................................................
%FIGURE 3: Percolation analysis
\begin{flushleft}
\begin{figure*}
\begin{center}

  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_regions_percolation.pdf}
  \includegraphics[trim = 0mm 00mm 00mm 00mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_regions_volume.pdf}

  \captionof{figure}{\small Percolation analysis of void regions for 
  different $\lambda_{th}$ values and for both defined classification 
  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
  volume and the number of voids detected according to the threshold value 
  $\lambda_{th}$ (left panels). Size distribution histogram of void cells
  using the threshold value $\lambda_{th} = 0.0$ for both schemes 
  (right panel).}

  \label{fig:percolation_analysis}
  \vspace{0.1 cm}

\end{center}
\end{figure*}
\end{flushleft}
%.........................................................................

Next, we shall calculate the reduced inertia tensor of each void region 
in order to determinate their principal directions of inertia and analyse 
the size-shape distribution of voids.

%.........................................................................
%Reduced inertia tensor
\eq{ReducedIntertia}
{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
%.........................................................................
where $l$ is an index associated to each cell of to the current region, 
$i$ and $j$ indexes run over each spatial direction and finally 
$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$, all 
positions are measured from the respective center of mass of the region.

%.........................................................................
%FIGURE 4: Distribution of eigenvalues of the inertia tensor
\begin{flushleft}
\begin{figure}
\begin{center}

  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb}
  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Vweb}

  \captionof{figure}{\small Histogram of eigenvalue ratio $\tau_1/\tau_2$
  vs $\tau_2/\tau_3$ for the inertia tensor of void regions. T-web 
  (upper panel) and V-web (lower panel). Number of cells per 
  region in 2D histograms are indicated by the respective colour bar. 
  Upper ($\tau_1/\tau_2$) and right ($\tau_2/\tau_3$) panels of each 
  figure shows a normalized histogram of each ratio parameter. The 
  adopted division for quantify the morphology of void regions is not
  well justified, it should be understood as a fuzzy and continuous 
  limit, done just for illustrative purposes.}

  \label{fig:distro_inertia}
  \vspace{0.1 cm}

\end{center}
\end{figure}
\end{flushleft}
%.........................................................................

The eigenvalues of the reduced inertia tensor, i.e. the principal moments
of inertia, are used to quantify the shape of void regions. They are 
denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$, where we rather 
calculate histograms for these ratio quantities instead of each single 
value in order to avoid using an arbitrary normalization. For both schemes, 
it can be noticed that the shape-distribution is completely spread out, 
thereby indicating a non-preferred geometry of void regions, which is in 
agreement with the well established highly anisotropy of matter flows
associated to this type of region \SRKED{[reference here]}. Because of 
that, we shall look for possible alignments between the plane of rotation 
of halo pairs and the principal directions of inertia of the nearest void 
regions.

%*************************************************************************
\section{Defining Samples}
\label{section:Def_Samples}
%*************************************************************************

In order to establish an adequate set of criteria to define a LG-like 
sample in unconstrained simulations, we proceed from the the general dark 
halo catalogues, constructed using the FOF scheme with a linking length of 
$b=0.17$ and the Bound Density Maxima (BDM) scheme for halos with an 
associated overdensity value of $200$ times the critical density 
(\SRKED{[references here]}). These samples are defined over all the Bolshoi 
simulation and will be referred as General Halos samples, \GHFOF and 
\GHBDM respectively\footnote{For each sample defined, there will be a FOF 
sample and a BDM sample in order to have robust results}. To be consistent 
with the mass range observationally determined of halos that host disk-form 
galaxies, we select halos in the mass range $7\times10^{11} < M_{h}/\hMsun 
< 7\times 10^{12}$, referred here as Individual Halos (\texttt{IH}) samples.

As a primal approach to define gravitational bounded halo pairs we select 
halos within the \texttt{IH} sample that satisfied to be the closest to 
each other. They constitute the Pairs (\texttt{P}) sample. To maintain the 
consistency with previous works regarding algorithms used for LG selection 
(\SRKED{[references here]}), we define here the next list of conditions 
that have to fulfil a pair system in order to belong to the Isolated Pairs 
(\texttt{IP}) sample. All these considerations are based upon the relative 
dynamics of the Milky Way and M31, and its isolation from massive 
structures:

%.........................................................................
%Isolated pairs criteria
\begin{enumerate}

\item{With respect to each halo, there cannot be any other halo within the 
mass range $7\times10^{11} < M_{h}/\hMsun < 7\times 10^{12}$ closer than 
its partner. It means that there cannot be ambiguity on the identity of
the pair members.}

\item{The relative radial velocity between the two halos must be 
negative.}

\item{The distance between the center of the two halos must be less than 
$1.0$\hMpc.}

\item{The distance to any halo more massive than any of the pair members 
cannot be less than $3$\hMpc.}

\item{The distance to cluster-like halos with masses larger than 
$7\times10^{13}$ \hMsun must be larger than $4$\hMpc.}
\end{enumerate}
%.........................................................................

Following the previous criteria established by Forero-Romero et al. 2013-1,
we define a more reduced sample, the Reduced Isolated Pairs sample 
(\texttt{RIP}), as pairs that fulfil the next two extra criteria :

%.........................................................................
%Reduced Isolated pairs criteria
\begin{enumerate}

\item{The separation between the center of mass of the halos is in the 
range $700-800$kpc.}

\item{The total mass of the two halos is in the range 
$1-4\times 10^{12}/\hMsun$.}

\end{enumerate}
%.........................................................................

Finally in Table \ref{tab:Samples_Size} shows the sizes of all defined 
samples.

%.........................................................................
%Table of sizes of each sample defined in Bolshoi
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{l  r  r} \hline\hline
	\textbf{Sample}					&\textbf{FOF}&\textbf{BDM} \\ \hline
	General Halos (\texttt{GH}) 	& 432000	 & 404432  \\ 
	Individual Halos (\texttt{IH}) 	& 65109		 & 61165  \\ 
	Pairs (\texttt{P}) 	 			& 17115		 & 15981  \\ 
	Isolated Pairs (\texttt{IP})	& 1249		 & 1647  \\ 
	Reduced Isolated Pairs (\texttt{RIP})& 138	 & 116  \\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}

  \label{tab:Samples_Size}

\end{center}
\end{flushleft}
\end{table}
%.........................................................................

%.........................................................................
%FIGURE 5: Distribution of eigenvalues of the web schemes
\begin{flushleft}
\begin{figure*}
\begin{center}

  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/eigen1_dist_Tweb}
  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/eigen2_dist_Tweb}
  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/eigen3_dist_Tweb}

  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/eigen1_dist_Vweb}
  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/eigen2_dist_Vweb}
  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/eigen3_dist_Vweb}

  \captionof{figure}{\small Distributions of eigenvalues for each defined
  scheme. T-web (upper panels) and V-web (lower panels). In each figure is
  calculated the distributions of eigenvalues for the volume cells of the 
  simulation (black lines), evaluating the respective tensor on the 
  geometric center of the cell. This is also done for \texttt{IP} 
  (continuous lines) and \texttt{RIP} (dashed lines) samples (both BDM 
  (red) and FOF (blue)), but the tensors are evaluated on the cell which 
  contains the center of mass of the halo pair. The vertical dashed line
  corresponds to the optimal threshold value $\lambda_{opt}$ for each 
  scheme respectively.}

  \label{fig:distro_cosmicweb}
  \vspace{0.1 cm}

\end{center}
\end{figure*}
\end{flushleft}
%.........................................................................

It can also be noticed that both schemes used to detect halos in the 
simulation are practically equivalent regarding the size of each sample.

%*************************************************************************
\section{Finding the Environment of the Local Group}
\label{sec:LGEnvironment}
%*************************************************************************

Once defined all samples, we shall proceed to quantify the environment
by using two different approaches. The first one is by applying the 
tensorial schemes defined in Section \ref{sec:algorithms_cosmic_web} 
and then, calculating the local eigenvalues associated to each halo or halo 
pair and the respective fractional anisotropy index (\SRKED{[reference 
here]}). The second approach is complementary to the first one, and 
consists in calculating the relative distance of each halo or halo pair to 
the nearest void regions, thereby allowing linking the influence of bulk 
voids to physical properties of the samples.

%-------------------------------------------------------------------------
\subsection{Tensorial Schemes}
\label{subsec:tensorial_schemes}
%-------------------------------------------------------------------------

The advantage of using the tensorial schemes (T-web and V-web) defined in
Section \ref{sec:algorithms_cosmic_web}, lies in quantifying all the local 
structure of the environment of halos and pair halos just from kinematic 
and dynamic properties of the matter distribution, like the density and 
velocity fields. Next, we shall calculate the distributions of each 
eigenvalue for the two defined web schemes and for the \texttt{GH}, 
\texttt{IP} and \texttt{RIP} samples. In Figure \ref{fig:distro_cosmicweb} 
is shown the obtained results, where it can be noticed that there is a 
significant bias in the distribution of halo pairs respect to volume cells. 
Furthermore, choosing the previously established optimal threshold value 
$\lambda_{opt}$ for each web scheme, Table \ref{tab:OccupationFractions} 
is built. In this has been listed the occupation fractions for the volume 
cells of the simulation and for each sample defined in the previous Section 
\ref{section:Def_Samples}.

As it was mentioned, the selection of an optimal threshold value for each 
web scheme, according to our proposed method based upon the mean density, 
is just an approximation which reproduces properly the visual impression 
of the cosmic web, so Table \ref{tab:OccupationFractions} must not be 
interpreted rigorously. Those occupation values must be thought just as a 
comparative illustration in order to understand possible bias between the 
defined samples and the overall matter distribution of the simulation. For 
instance, for the T-web scheme, the occupation fraction associated to the 
\texttt{RIP} sample is greater in filaments than sheet regions, what 
should not be interpreted as \texttt{RIP} systems lie in filaments, but 
those systems lie preferentially in higher density and stronger non-linear 
regions.

An expected result obtained from Figure \ref{fig:distro_cosmicweb} is 
the equivalence between both halos detection schemes, regarding the 
obtained distribution of eigenvalues for all samples, and even for both 
web schemes. This along with the results shown in Table 
\ref{tab:Samples_Size} allow to conclude that both halos detection schemes 
reproduce reliable halos samples with similar spatial distribution since 
the occupation values of each sample are approximately equal. Regarding 
the differences between both web classification schemes, from the 
distribution of the web eigenvalues associated to volume cells, shown in 
Figure \ref{fig:distro_cosmicweb}, it is clear that each scheme quantify 
the structure of the cosmic web in very different ways, what can be 
explained by how each scheme is built. The T-web is built based upon the 
gravitational potential, thereby retaining bulk features of the cosmic web 
because of the long-range nature of the potential, whereas the V-web 
scheme, based upon the peculiar velocity field, describes better the very 
local structure of the cosmic environment. All of this causes that
strong non-linear regions, like filaments and knots, are poorly described 
by the T-web, being less spread out than the V-web. Now, due to the weak 
gravitational correlation and specially low-rate matter flows in low 
density zones, like voids, those regions are also less spread out in the 
V-web scheme. It should be noticed that these conclusions were done 
independently on the chosen threshold value, and they hold for a 
reasonable range of values (see Figure \ref{fig:visual_impression}).

%.........................................................................
%Table of 
\begin{table}[H]
\begin{flushleft}
\begin{center}
  \begin{tabular}{l  r  r  r  r}
  	&&\textbf{T-web}&&\\\hline\hline
	\textbf{Region}	&\textbf{void}&\textbf{sheet}&\textbf{filament}&\textbf{knot}	\\\hline
	Cells			&	60.6\%	  &		29.1\%	 &		9.7\%	   &	0.7\%		\\
	&&&&\\	
	\GHFOF			& 	12.1\%	  &		35.9\%	 &		43.3\%	   &	8.7\%		\\
	\GHBDM			&	9.7\%	  &		31.9\%	 &		44.2\%	   &	14.2\%		\\
	&&&&\\	
	\IPFOF			&	0.1\%	  &		6.1\%	 &		63.3\%	   &	30.5\%		\\
	\IPBDM			&	0.1\%	  &		3.0\%	 &		53.3\%	   &	43.6\%		\\
	&&&&\\
	\RIPFOF			&	0.0\%	  &		5.1\%	 &		88.4\%	   &	6.5\%		\\
	\RIPBDM			&	0.0\%	  &		3.4\%	 &		85.3\%	   &	11.2\%		\\\hline\hline
	&&&&\\
  	&&\textbf{V-web}&&\\\hline\hline
	\textbf{Region}	&\textbf{void}&\textbf{sheet}&\textbf{filament}&\textbf{knot}	\\\hline
	Cells			&	49.3\%	  &		38.3\%	 &		11.3\%	   &	1.1\%		\\
	&&&&\\
	\GHFOF			&	22.7\%	  &		44.3\%	 &		29.3\%	   &	3.7\%		\\
	\GHBDM			&	20.7\%	  &		43.6\%	 &		31.6\%	   &	4.2\%		\\
	&&&&\\
	\IPFOF			&	13.3\%	  &		63.6\%	 &		23.1\%	   &	0.1\%		\\
	\IPBDM			&	10.7\%	  &		60.1\%	 &		28.4\%	   &	0.8\%		\\
	&&&&\\
	\RIPFOF			&	20.3\%	  &		68.1\%	 &		11.6\%	   &	0.0\%		\\
	\RIPBDM			&	13.8\%	  &		69.0\%	 &		17.2\%	   &	0.0\%		\\\hline\hline
  \end{tabular}  
  \captionof{table}{\small Occupation fractions for each one of the defined
  samples and for all the volume cells of the simulation, and for each one 
  of the occupied type of environment selected by both web schemes.}

  \label{tab:OccupationFractions}

\end{center}
\end{flushleft}
\end{table}
%.........................................................................

Once established the expected characteristics of each web scheme, we shall 
proceed to analyse the more likely environment of LG-like systems under 
the selection criteria defined in Section \ref{section:Def_Samples}. An
interesting issue to be taken into account before, it is the push and pull
situation produced by the closeness criteria between the halos of each 
pair, and the gravitational isolation criteria. Correlation between the 
cosmic environment and the abundance and masses of individual galaxies has 
been well studied (\SRKED{[references here]}), finding more massive 
galaxies and high abundances in strongly non-linear and high density 
regions of the cosmic web. This is in agreement with the closeness 
criteria, which allows to find more pair systems in high density regions, 
but it is against the isolation criteria, where a high abundance affects
the imposed gravitational isolation and biases the likely host environment
towards low density regions. Because of that, it makes no clear 
how to assign a priori type of environment to LG-like systems, making this 
study necessary.

When we adopt the T-web scheme, an important bias is found for the 
\texttt{RIP} sample compared with the \texttt{IP}, whereas the latter 
also follows a different distribution than the \texttt{GH} sample. 
According to Table \ref{tab:OccupationFractions}, \texttt{RIP} systems 
appears to lie in highly non-linear regions preferentially, with $\sim 85\%
-90\%$ lying in filament-like regions, and $\sim 15\%-10\%$ distributed in 
sheet-like and knot-like regions\footnote{Note we rather use sheet-like, 
filament-like, ... regions instead of sheet, filament, ... regions in 
order to not classify a priori each type of region according to the 
optimal threshold value.}. \texttt{IP} systems lie in even higher 
non-linear regions than \texttt{RIP} systems, with $\sim 30\% - 45\%$ of 
them distributed in knot-like, $\sim 63\% - 53\%$ in filament-like and the 
remainder distributed mainly in sheet-like regions.

Now, using the V-web scheme, there is also found a bias between the 
environmental distribution of \texttt{RIP} and \texttt{IP} systems, but it 
is less clear than the T-web case. Furthermore, the occupation fractions 
are quite different to the T-web scheme. For instance, \texttt{RIP} 
systems lie mainly in sheet-like regions, with $\sim 68\% - 69\%$ of them 
found in this type of region, $\sim 20\% - 14\%$ in voids and $\sim 12\% - 
17\%$ in filament-like regions. Whereas there are $\sim 60\% - 63\%$ of
\texttt{IP} systems in sheet-like regions, $\sim 28\% - 23\%$ in 
filament-like, $\sim 10\% - 13\%$ in voids and remainder in knot-like
regions. All of this shows effectively a minor bias respect to that found
in the T-web, what might be explained because of the different physical 
origin of each scheme.

%-------------------------------------------------------------------------
\subsection{Fractional anisotropy}
\label{subsec:fractional_anisotropy}
%-------------------------------------------------------------------------

In order to overcome and standardize differences between the two web 
schemes, we shall calculate the fractional anisotropy for each sample, 
with the normalization given by (\SRKED{[reference here]}).

%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} } }
%.........................................................................
where the eigenvalues can be taken from any of the two web schemes. This 
index, such as it is defined, allows quantifying the local anisotropy 
degree of the cosmological environment, where $FA=0$ corresponds to highly
isotropic regions and $FA=1$ the opposite case, completely anisotropic 
regions. Although there does not exist a perfect correspondence between 
certain range of the fractional anisotropy and each one of the above defined
type of environment, there is an insight about what characteristics should 
have a cell volume according to its $FA$ value. Following the analysis 
performed by (\SRKED{[reference here]}), we shall assign low values of the 
fractional anisotropic to the most symmetric and isotropic regions, 
knot-like, due to their collapse in all directions. Low-middle values are 
assigned to sheet-like regions whereas high-middle values to filament-like 
regions, which indicates the complex dynamics of these types of environment. 
Finally, high values ($FA \lesssim 1$) of the fractional anisotropy would
correspond to the most highly anisotropic type of environment, voids. That
is because their expansion rate in each direction can take very different 
values, thereby shaping highly amorphous regions, as was concluded 
by mean of the shape-distribution previously performed over bulk voids.

%.........................................................................
%FIGURE 6: Distribution of fractional anisotropy
\begin{flushleft}
\begin{figure}
\begin{center}

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/fractional_anisotrpy_Tweb}
  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/fractional_anisotrpy_Vweb}

  \captionof{figure}{\small Cumulative distribution of the fractional 
  anisotropy for each web scheme. T-web (upper panel) and V-web (lower 
  panel). Distributions for each sample are also calculated, \texttt{GH} 
  sample (black lines), \texttt{IP} sample (blue lines) and \texttt{RIP} 
  sample (red lines). In order to compare each halo scheme, we also 
  calculate distributions for each one, FOF (dashed lines) and BDM 
  (continuous lines). }

  \label{fig:fractional_anisotropy}
  \vspace{0.1 cm}

\end{center}
\end{figure}
\end{flushleft}
%.........................................................................

Figure \ref{fig:fractional_anisotropy} shows the normed cumulative 
histograms of the fractional anisotropy for each sample. The first 
characteristic that can be noticed is the high similitude between both web
schemes, allowing inferring that the fractional anisotropy is effectively
an efficient way to overcome differences between the web schemes, and 
thereby allowing obtaining more robust conclusions. Regarding possible 
differences between each sample, now it is clearer the existing bias 
between \texttt{RIP} and \texttt{IP} systems, even for both web schemes. 
In spite of all halos of the simulation are distributed mainly over middle 
to high anisotropic regions like voids and sheet-like regions, 
\texttt{RIP} and \texttt{IP} systems lie preferentially in more isotropic 
and non-linear regions than \texttt{GH}. Although \texttt{RIP} systems 
appear to lie in slightly less isotropic regions. This can be explained 
because of the mass cut-off and the established range of relative 
distances as extra criterion for selecting the \texttt{RIP} sample, thus 
indicating a first possible environmental correlation. These conclusions 
reinforce the results obtained in previous Subsection 
\ref{subsec:tensorial_schemes}, showing the complementary character of the 
fractional anisotropy.

Returning back to the discussion about the quantification of the 
environment leaded by the fractional anisotropy, due to its fuzzy 
character, it is not possible to assign a well-defined type of environment 
to each sample. While this may be thought as a disadvantage of the method, 
actually the real character of the cosmological matter distribution is 
also fuzzy, where any attempt to establish well-defined type of regions 
depends necessarily on free parameters like the threshold value 
$\lambda_{th}$, which has little or no physical motivation. So 
independence of free parameters is indeed an advantage of quantifying 
through the fractional anisotropy index.

%-------------------------------------------------------------------------
\subsection{The neighbourhood of voids}
\label{subsec:neighbourhood_voids}
%-------------------------------------------------------------------------

In Subsection \ref{subsec:method_voids} we quantified bulk void regions 
by using a FOF-like scheme. Our second approach to quantify the 
cosmological environment of LG-like systems involves taking distances to 
the nearest void regions in order to establish possible environmental 
effects related with the closeness, the size and the geometry of these 
bulk voids.

In Figure \ref{fig:voids2samples} we calculate histograms of the distance 
to the nearest void cell that belongs to the nearest bulk void region from 
each one of the systems of each defined sample, and the volume size of 
such bulk region. A first interesting feature found in this figure is the 
correlation between distance and volume, where the closer a pair system is 
to the nearest void, the larger is the volume of such void, and thus for
both web schemes. This correlation is followed by all the samples, even 
the \texttt{GH} and \texttt{P} samples, thereby indicating this is a 
general feature of the matter distribution. A possible interpretation of 
this result comes with the process of structure formation itself and the 
way in which the web schemes classify the cosmic web. Bulk voids with very 
extensive volumes are expected to be the lowest density regions of the 
cosmic web due to all their matter content is being dragged by highly 
non-linear and high density neighbour regions, such as filaments and knots. 
This also implies that such high density neighbour regions are very close 
to the limits of the void, with well-defined boundaries according to the 
web schemes. In the case of voids with smaller volumes, their associated 
mean densities are expected to be greater than the previous case, which 
means it is difficult to establish a cut-off between sheet and void cells, 
where such transition is rather fuzzy. Actually, most of these small 
volume void regions are the result of a fragmentation process produced 
along sheet-void boundaries of the cosmic web. This effect can be 
appreciated in Figure \ref{fig:visual_impression}, specially for the V-web 
scheme with the optimal parameter.

%.........................................................................
%FIGURE 7: Distribution of size and distance to void regions respect to 
%each sample
\begin{flushleft}
\begin{figure}
\begin{center}

  \includegraphics[trim = 0mm 9mm 1mm 0mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_statistics_samples_BDM_Tweb}
  \includegraphics[trim = 0mm 9mm 1mm 0mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_statistics_samples_BDM_Vweb}

  \captionof{figure}{\small Histograms of the distance and the volume of
  the nearest bulk void to each system of the \texttt{IP} (background 
  histogram) and \texttt{RIP} (scatter plot) samples for BDM catalogue. 
  Gray colorbar indicates the number of \texttt{IP} systems in each bin, 
  whereas hot colorbar indicates the FA of the host cell of \texttt{RIP} 
  systems. Both web classification schemes has been used, Tweb (upper 
  panel) and V-web (lower panel). Upper and right panels of each figure
  indicate normed histograms of each single property for the \texttt{IP}
  sample.}

  \label{fig:voids2samples}
  \vspace{0.1 cm}

\end{center}
\end{figure}
\end{flushleft}
%.........................................................................

As was found in Subsection \ref{subsec:tensorial_schemes} (Table 
\ref{tab:OccupationFractions}), \texttt{IP} and \texttt{RIP} systems are 
found to lie specially into high density (low anisotropy) regions. 
Therefore, and according to the previous analysis, structures embedded 
into such regions are also expected to be close to large volume volume 
voids, while it is less likely to find pair systems close to small volume
voids. In Figure \ref{fig:voids2samples} is also performed an analysis 
of the fractional anisotropy of \texttt{RIP} systems. For the V-web scheme, 
it can be noticed that \texttt{RIP} systems embedded into low anisotropy 
regions (black, dark red and red dots) are specially distributed over the 
peak of the underlying distribution, i.e., around large volume voids and 
close distances. While \texttt{RIP} systems in higher FA values (yellow 
and white dots) are completely spread out over all possible volumes and 
distances, though following the underlying correlation. For the T-web 
scheme it is less clear this result, being any FA value equally likely in 
any zone of the distribution, nevertheless a slight overabundance of low 
to middle FA values over the peak of the distribution. A completely 
analogous analysis has been performed for FOF halos, finding equivalent
results for both web schemes.

Although previous conclusions are interesting, distances and volumes in 
this context are little meaningless because of the arbitrary origin of the 
threshold value $\lambda_{th}$, set in Subsection \ref{subsec:method_voids} 
to minimize the percolation phenomenon. Therefore, those conclusions 
should be taken as an insight of a possible underlying effect, which needs 
more robust statistics (larger simulations) in order to have more 
definitive conclusions. Hence, this approach is just useful to quantify 
possible biases of the distance and volume distributions between pair 
samples. However, in next sections it will be useful in the frame of the 
analysis of correlations with several physical properties.

%*************************************************************************
\section{Influence of the environment on LG-like systems}
\label{sec:influence_environment_LG}
%*************************************************************************

Once defined the general features of the preferred environment of 
\texttt{IP} and \texttt{RIP} systems, next step is to look for possible 
environmental effects on all physical properties of these systems. Firstly, 
we shall study effects on kinematic properties of pair systems, i.e. total 
mass and mass ratio, radial and tangential velocities, specific angular 
momentum and specific mechanical energy, and the reduced spin parameter. 
After, we look for effects on the history of each system, so we shall 
analyse all the parameters of the MAH (Mass Assembly History) of each pair, 
i.e., the last major merger, the formation time and the assembly time. 
Finally, we quantify different possible alignments of pairs regarding 
characteristic directions of the environment, like the eigenvectors of the 
web scheme and the principal directions of inertia of the nearest void 
region.

Based on the results of Section \ref{sec:LGEnvironment}, our strategy 
consists in using the fractional anisotropy, the distance and the volume 
of the nearest bulk void region in order to detect and quantify any 
possible bias on each one of the analysed properties produced by the 
features of the host environment. Furthermore, as two web schemes have
proven to be equivalent regarding the fractional anisotropy and the 
statistics of void regions, we shall consider in this section only the 
T-web scheme. Analogously for the halos detection schemes, we only 
consider here the BDM catalogue.

%-------------------------------------------------------------------------
\subsection{Bias induced on kinematic and dynamics properties}
\label{subsec:bias_kinematic}
%-------------------------------------------------------------------------

%.........................................................................
%FIGURE 8: Distribution of size and distance to void regions respect to 
%each sample
\begin{flushleft}
\begin{figure*}
\begin{center}

  \includegraphics[trim = 0mm 7mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.60\textheight]{./bench/codes/plot}

  \captionof{figure}{\small Histograms of the distance and the volume of
  the nearest bulk void to each system of the \texttt{IP} (background 
  histogram) and \texttt{RIP} (scatter plot) samples for BDM catalogue. 
  Gray colorbar indicates the number of \texttt{IP} systems in each bin, 
  whereas hot colorbar indicates the FA of the host cell of \texttt{RIP} 
  systems. Both web classification schemes has been used, Tweb (upper 
  panel) and V-web (lower panel). Upper and right panels of each figure
  indicate normed histograms of each single property for the \texttt{IP}
  sample.}

  \label{fig:correlation_kinematics_properties}\ref{fig
  \vspace{0.1 cm}

\end{center}
\end{figure*}
\end{flushleft}
%.........................................................................

%.........................................................................
%Table of extreme values of each quintile of the environmental properties
\begin{table*}
\begin{flushleft}
\begin{center}
  \begin{tabular}{l | c  c  c} \hline\hline
									&		&	\textbf{Property}	 & \\ \hline
\textbf{Quintile}	& \textbf{Fractional} & \textbf{Distance to the} &	\textbf{Equivalent spherical radius}	      \\
& \textbf{Anisotropy} & \textbf{nearest void [Mpc $\bds{h^{-1}}$]} &	\textbf{of the nearest void [Mpc $\bds{h^{-1}}$]} \\ \hline
Q1		&	$  0.0\ -\ 0.366$  &	$0.086\ -\ 1.018$	&  	$0.606\ -\ 2.072$  \\
Q2		&	$0.366\ -\ 0.468$  &	$1.018\ -\ 2.444$	&  	$2.072\ -\ 5.777$  \\
Q3		&	$0.468\ -\ 0.575$  &	$2.444\ -\ 4.072$ 	&  	$5.777\ -\ 12.074$  \\
Q4		&	$0.575\ -\ 0.703$  &	$4.072\ -\ 6.151$ 	&  	$12.074\ -\ 27.618$  \\
Q5		&	$0.703\ -\ 1.0$    &	$6.151\ -\ 15.224$ 	&  	$27.618\ -\ 42.271$  \\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small Size of each sample defined in the Bolshoi 
  simulation and for each of the two schemes used to detect halos (FOF 
  and BDM).}

  \label{tab:Samples_Size}

\end{center}
\end{flushleft}
\end{table*}
%.........................................................................

Our Local Group of galaxies is certainly the most and best known 
large-scale structure of the universe, including the knowledge of a set of
kinematic properties, that due to their mechanical nature, are easily 
testable by dark matter simulations like Bolshoi. The first of these 
properties that we analyse in this section is the total mass of the pair 
systems.

Although there are not good enough estimates of each single mass 
of the host halos of the Milky Way and M31 galaxies, there is a dynamical 
estimate of their overall mass \SRKED{[Reference here]} compatible with the 
selection criteria defined for selecting the \texttt{RIP} samples.

In Figure \ref{fig:totalmass_FA} we calculate the distribution of 
\texttt{IP} and \texttt{RIP} samples with regards to the total mass of 
each pair and the fractional anisotropy index of the host cell. In order
to make clearer any possible correlation between these properties, in the
right panel we compute individual histograms for systems selected according 
to defined mass ranges.

... Radial vs. tangential velocities

... Angular Momentum

... Total Mechanical energy.

... Reduced Spin

%-------------------------------------------------------------------------
\subsection{Bias induced on the Mass Assembly Histories}
\label{subsec:bias_MAH}
%-------------------------------------------------------------------------

... Last major merger. Formation Time. Assembly Time.

%-------------------------------------------------------------------------
\subsection{Pair Alignment with the Cosmic Web}
\label{subsec:alignment_cosmic_web}
%-------------------------------------------------------------------------

... Separation.

... Relative velocity.

... Angular Momentum.

%*************************************************************************
\section{Conclusions}
\label{sec:conclusions}
%*************************************************************************

%*************************************************************************
\section*{Acknowledgments}  
%*************************************************************************

\bibliographystyle{mn2e}
\bibliography{references}

%.........................................................................
\end{document}

### 2014-04-08 cosmic_voids.tex
New structure

@@
 %=========================================================================
-\title{The place of the local group in the cosmic web}
+\title{Analysis of bulk void regions}
 \author[S. Bustamante and J.E. Forero-Romero]{
@@
 \begin{abstract}
-
-We present here a study about the influence of the environment on the
-local group (LG) of galaxies in the context of $\Lambda$CDM. In this study
-we use a large volume high resolution N-body cosmological simulation 
-(Bolshoi) along with the most recent methods to quantify the cosmic web 
-(T-web, V-web schemes); furthermore we propose a novel approximation, base
-upon the minimization of the mean density of void regions, to determinate 
-the optimal threshold value $\lambda_{th}$, which have been treated until 
-now as a free parameter. 
-Following the recent work of Courtois et al. (2013), where was 
-found that the LG is located near to a large void, we also perform an 
-extensive study of voids, applying a FOF algorithm to find void regions 
-and performing an analysis of their shape based upon the reduced inertia 
-tensor.
-Using the recent observations that constrain the tangential velocity of
-M31 with respect to the Milky Way (MW), the previously established radial 
-velocity, the estimated masses of dark halos, along with some criteria
-to guarantee the gravitational isolation of these systems (Forero-Romero
-et al. 2013-1), we select a set of halo pairs as a candidate sample 
-of LG-like systems in the Bolshoi simulation. 
-We look for possible biases and correlations between the environment 
-properties of each LG-like system and its kinematic and formation 
-properties. Among our main result we find \SRKED{[summarize our results 
-here!]}.
 
@@
 %*************************************************************************
-\section{Defining Samples}
-\label{section:Def_Samples}
-%*************************************************************************
-
-In order to establish an adequate set of criteria to define a LG-like 
-sample in unconstrained simulations, we proceed from the the general dark 
-halo catalogues, constructed using the FOF scheme with a linking length of 
-$b=0.17$ and the Bound Density Maxima (BDM) scheme for halos with an 
-associated overdensity value of $200$ times the critical density 
-(\SRKED{[references here]}). These samples are defined over all the Bolshoi 
-simulation and will be referred as General Halos samples, \GHFOF and 
-\GHBDM respectively\footnote{For each sample defined, there will be a FOF 
-sample and a BDM sample in order to have robust results}. To be consistent 
-with the mass range observationally determined of halos that host disk-form 
-galaxies, we select halos in the mass range $7\times10^{11} < M_{h}/\hMsun 
-< 7\times 10^{12}$, referred here as Individual Halos (\texttt{IH}) samples.
-
-As a primal approach to define gravitational bounded halo pairs we select 
-halos within the \texttt{IH} sample that satisfied to be the closest to 
-each other. They constitute the Pairs (\texttt{P}) sample. To maintain the 
-consistency with previous works regarding algorithms used for LG selection 
-(\SRKED{[references here]}), we define here the next list of conditions 
-that have to fulfil a pair system in order to belong to the Isolated Pairs 
-(\texttt{IP}) sample. All these considerations are based upon the relative 
-dynamics of the Milky Way and M31, and its isolation from massive 
-structures:
-
-%.........................................................................
-%Isolated pairs criteria
-\begin{enumerate}
-
-\item{With respect to each halo, there cannot be any other halo within the 
-mass range $7\times10^{11} < M_{h}/\hMsun < 7\times 10^{12}$ closer than 
-its partner. It means that there cannot be ambiguity on the identity of
-the pair members.}
-
-\item{The relative radial velocity between the two halos must be 
-negative.}
-
-\item{The distance between the center of the two halos must be less than 
-$1.0$\hMpc.}
-
-\item{The distance to any halo more massive than any of the pair members 
-cannot be less than $3$\hMpc.}
-
-\item{The distance to cluster-like halos with masses larger than 
-$7\times10^{13}$ \hMsun must be larger than $4$\hMpc.}
-\end{enumerate}
-%.........................................................................
-
-Following the previous criteria established by Forero-Romero et al. 2013-1,
-we define a more reduced sample, the Reduced Isolated Pairs sample 
-(\texttt{RIP}), as pairs that fulfil the next two extra criteria :
-
-%.........................................................................
-%Reduced Isolated pairs criteria
-\begin{enumerate}
-
-\item{The separation between the center of mass of the halos is in the 
-range $700-800$kpc.}
-
-\item{The total mass of the two halos is in the range 
-$1-4\times 10^{12}/\hMsun$.}
-
-\end{enumerate}
-%.........................................................................
-
-Finally in Table \ref{tab:Samples_Size} shows the sizes of all defined 
-samples.
-
-%.........................................................................
-%Table of sizes of each sample defined in Bolshoi
-\begin{table}[h]
-\begin{flushleft}
-\begin{center}
-  \begin{tabular}{l  r  r} \hline\hline
-	\textbf{Sample}					&\textbf{FOF}&\textbf{BDM} \\ \hline
-	General Halos (\texttt{GH}) 	& 432000	 & 404432  \\ 
-	Individual Halos (\texttt{IH}) 	& 65109		 & 61165  \\ 
-	Pairs (\texttt{P}) 	 			& 17115		 & 15981  \\ 
-	Isolated Pairs (\texttt{IP})	& 1249		 & 1647  \\ 
-	Reduced Isolated Pairs (\texttt{RIP})& 138	 & 116  \\ \hline\hline
-  \end{tabular}  
-  \captionof{table}{\small Size of each sample defined in the Bolshoi 
-  simulation and for each of the two schemes used to detect halos (FOF 
-  and BDM).}
-
-  \label{tab:Samples_Size}
-
-\end{center}
-\end{flushleft}
-\end{table}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 5: Distribution of eigenvalues of the web schemes
-\begin{flushleft}
-\begin{figure*}
-\begin{center}
-
-  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/eigen1_dist_Tweb}
-  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/eigen2_dist_Tweb}
-  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/eigen3_dist_Tweb}
-
-  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/eigen1_dist_Vweb}
-  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/eigen2_dist_Vweb}
-  \includegraphics[trim = 3mm 0mm 10mm 8mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/eigen3_dist_Vweb}
-
-  \captionof{figure}{\small Distributions of eigenvalues for each defined
-  scheme. T-web (upper panels) and V-web (lower panels). In each figure is
-  calculated the distributions of eigenvalues for the volume cells of the 
-  simulation (black lines), evaluating the respective tensor on the 
-  geometric center of the cell. This is also done for \texttt{IP} 
-  (continuous lines) and \texttt{RIP} (dashed lines) samples (both BDM 
-  (red) and FOF (blue)), but the tensors are evaluated on the cell which 
-  contains the center of mass of the halo pair. The vertical dashed line
-  corresponds to the optimal threshold value $\lambda_{opt}$ for each 
-  scheme respectively.}
-
-  \label{fig:distro_cosmicweb}
-  \vspace{0.1 cm}
-
-\end{center}
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-It can also be noticed that both schemes used to detect halos in the 
-simulation are practically equivalent regarding the size of each sample.
-
-%*************************************************************************
-\section{Finding the Environment of the Local Group}
-\label{sec:LGEnvironment}
-%*************************************************************************
-
-Once defined all samples, we shall proceed to quantify the environment
-by using two different approaches. The first one is by applying the 
-tensorial schemes defined in Section \ref{sec:algorithms_cosmic_web} 
-and then, calculating the local eigenvalues associated to each halo or halo 
-pair and the respective fractional anisotropy index (\SRKED{[reference 
-here]}). The second approach is complementary to the first one, and 
-consists in calculating the relative distance of each halo or halo pair to 
-the nearest void regions, thereby allowing linking the influence of bulk 
-voids to physical properties of the samples.
-
-%-------------------------------------------------------------------------
-\subsection{Tensorial Schemes}
-\label{subsec:tensorial_schemes}
-%-------------------------------------------------------------------------
-
-The advantage of using the tensorial schemes (T-web and V-web) defined in
-Section \ref{sec:algorithms_cosmic_web}, lies in quantifying all the local 
-structure of the environment of halos and pair halos just from kinematic 
-and dynamic properties of the matter distribution, like the density and 
-velocity fields. Next, we shall calculate the distributions of each 
-eigenvalue for the two defined web schemes and for the \texttt{GH}, 
-\texttt{IP} and \texttt{RIP} samples. In Figure \ref{fig:distro_cosmicweb} 
-is shown the obtained results, where it can be noticed that there is a 
-significant bias in the distribution of halo pairs respect to volume cells. 
-Furthermore, choosing the previously established optimal threshold value 
-$\lambda_{opt}$ for each web scheme, Table \ref{tab:OccupationFractions} 
-is built. In this has been listed the occupation fractions for the volume 
-cells of the simulation and for each sample defined in the previous Section 
-\ref{section:Def_Samples}.
-
-As it was mentioned, the selection of an optimal threshold value for each 
-web scheme, according to our proposed method based upon the mean density, 
-is just an approximation which reproduces properly the visual impression 
-of the cosmic web, so Table \ref{tab:OccupationFractions} must not be 
-interpreted rigorously. Those occupation values must be thought just as a 
-comparative illustration in order to understand possible bias between the 
-defined samples and the overall matter distribution of the simulation. For 
-instance, for the T-web scheme, the occupation fraction associated to the 
-\texttt{RIP} sample is greater in filaments than sheet regions, what 
-should not be interpreted as \texttt{RIP} systems lie in filaments, but 
-those systems lie preferentially in higher density and stronger non-linear 
-regions.
-
-An expected result obtained from Figure \ref{fig:distro_cosmicweb} is 
-the equivalence between both halos detection schemes, regarding the 
-obtained distribution of eigenvalues for all samples, and even for both 
-web schemes. This along with the results shown in Table 
-\ref{tab:Samples_Size} allow to conclude that both halos detection schemes 
-reproduce reliable halos samples with similar spatial distribution since 
-the occupation values of each sample are approximately equal. Regarding 
-the differences between both web classification schemes, from the 
-distribution of the web eigenvalues associated to volume cells, shown in 
-Figure \ref{fig:distro_cosmicweb}, it is clear that each scheme quantify 
-the structure of the cosmic web in very different ways, what can be 
-explained by how each scheme is built. The T-web is built based upon the 
-gravitational potential, thereby retaining bulk features of the cosmic web 
-because of the long-range nature of the potential, whereas the V-web 
-scheme, based upon the peculiar velocity field, describes better the very 
-local structure of the cosmic environment. All of this causes that
-strong non-linear regions, like filaments and knots, are poorly described 
-by the T-web, being less spread out than the V-web. Now, due to the weak 
-gravitational correlation and specially low-rate matter flows in low 
-density zones, like voids, those regions are also less spread out in the 
-V-web scheme. It should be noticed that these conclusions were done 
-independently on the chosen threshold value, and they hold for a 
-reasonable range of values (see Figure \ref{fig:visual_impression}).
-
-%.........................................................................
-%Table of 
-\begin{table}[H]
-\begin{flushleft}
-\begin{center}
-  \begin{tabular}{l  r  r  r  r}
-  	&&\textbf{T-web}&&\\\hline\hline
-	\textbf{Region}	&\textbf{void}&\textbf{sheet}&\textbf{filament}&\textbf{knot}	\\\hline
-	Cells			&	60.6\%	  &		29.1\%	 &		9.7\%	   &	0.7\%		\\
-	&&&&\\	
-	\GHFOF			& 	12.1\%	  &		35.9\%	 &		43.3\%	   &	8.7\%		\\
-	\GHBDM			&	9.7\%	  &		31.9\%	 &		44.2\%	   &	14.2\%		\\
-	&&&&\\	
-	\IPFOF			&	0.1\%	  &		6.1\%	 &		63.3\%	   &	30.5\%		\\
-	\IPBDM			&	0.1\%	  &		3.0\%	 &		53.3\%	   &	43.6\%		\\
-	&&&&\\
-	\RIPFOF			&	0.0\%	  &		5.1\%	 &		88.4\%	   &	6.5\%		\\
-	\RIPBDM			&	0.0\%	  &		3.4\%	 &		85.3\%	   &	11.2\%		\\\hline\hline
-	&&&&\\
-  	&&\textbf{V-web}&&\\\hline\hline
-	\textbf{Region}	&\textbf{void}&\textbf{sheet}&\textbf{filament}&\textbf{knot}	\\\hline
-	Cells			&	49.3\%	  &		38.3\%	 &		11.3\%	   &	1.1\%		\\
-	&&&&\\
-	\GHFOF			&	22.7\%	  &		44.3\%	 &		29.3\%	   &	3.7\%		\\
-	\GHBDM			&	20.7\%	  &		43.6\%	 &		31.6\%	   &	4.2\%		\\
-	&&&&\\
-	\IPFOF			&	13.3\%	  &		63.6\%	 &		23.1\%	   &	0.1\%		\\
-	\IPBDM			&	10.7\%	  &		60.1\%	 &		28.4\%	   &	0.8\%		\\
-	&&&&\\
-	\RIPFOF			&	20.3\%	  &		68.1\%	 &		11.6\%	   &	0.0\%		\\
-	\RIPBDM			&	13.8\%	  &		69.0\%	 &		17.2\%	   &	0.0\%		\\\hline\hline
-  \end{tabular}  
-  \captionof{table}{\small Occupation fractions for each one of the defined
-  samples and for all the volume cells of the simulation, and for each one 
-  of the occupied type of environment selected by both web schemes.}
-
-  \label{tab:OccupationFractions}
-
-\end{center}
-\end{flushleft}
-\end{table}
-%.........................................................................
-
-Once established the expected characteristics of each web scheme, we shall 
-proceed to analyse the more likely environment of LG-like systems under 
-the selection criteria defined in Section \ref{section:Def_Samples}. An
-interesting issue to be taken into account before, it is the push and pull
-situation produced by the closeness criteria between the halos of each 
-pair, and the gravitational isolation criteria. Correlation between the 
-cosmic environment and the abundance and masses of individual galaxies has 
-been well studied (\SRKED{[references here]}), finding more massive 
-galaxies and high abundances in strongly non-linear and high density 
-regions of the cosmic web. This is in agreement with the closeness 
-criteria, which allows to find more pair systems in high density regions, 
-but it is against the isolation criteria, where a high abundance affects
-the imposed gravitational isolation and biases the likely host environment
-towards low density regions. Because of that, it makes no clear 
-how to assign a priori type of environment to LG-like systems, making this 
-study necessary.
-
-When we adopt the T-web scheme, an important bias is found for the 
-\texttt{RIP} sample compared with the \texttt{IP}, whereas the latter 
-also follows a different distribution than the \texttt{GH} sample. 
-According to Table \ref{tab:OccupationFractions}, \texttt{RIP} systems 
-appears to lie in highly non-linear regions preferentially, with $\sim 85\%
--90\%$ lying in filament-like regions, and $\sim 15\%-10\%$ distributed in 
-sheet-like and knot-like regions\footnote{Note we rather use sheet-like, 
-filament-like, ... regions instead of sheet, filament, ... regions in 
-order to not classify a priori each type of region according to the 
-optimal threshold value.}. \texttt{IP} systems lie in even higher 
-non-linear regions than \texttt{RIP} systems, with $\sim 30\% - 45\%$ of 
-them distributed in knot-like, $\sim 63\% - 53\%$ in filament-like and the 
-remainder distributed mainly in sheet-like regions.
-
-Now, using the V-web scheme, there is also found a bias between the 
-environmental distribution of \texttt{RIP} and \texttt{IP} systems, but it 
-is less clear than the T-web case. Furthermore, the occupation fractions 
-are quite different to the T-web scheme. For instance, \texttt{RIP} 
-systems lie mainly in sheet-like regions, with $\sim 68\% - 69\%$ of them 
-found in this type of region, $\sim 20\% - 14\%$ in voids and $\sim 12\% - 
-17\%$ in filament-like regions. Whereas there are $\sim 60\% - 63\%$ of
-\texttt{IP} systems in sheet-like regions, $\sim 28\% - 23\%$ in 
-filament-like, $\sim 10\% - 13\%$ in voids and remainder in knot-like
-regions. All of this shows effectively a minor bias respect to that found
-in the T-web, what might be explained because of the different physical 
-origin of each scheme.
-
-%-------------------------------------------------------------------------
-\subsection{Fractional anisotropy}
-\label{subsec:fractional_anisotropy}
-%-------------------------------------------------------------------------
-
-In order to overcome and standardize differences between the two web 
-schemes, we shall calculate the fractional anisotropy for each sample, 
-with the normalization given by (\SRKED{[reference here]}).
-
-%.........................................................................
-%Fractional anisotropy
-\eq{fractional_anisotropy}
-{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
-(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
-\lambda_2^2 + \lambda_3^2} } }
-%.........................................................................
-where the eigenvalues can be taken from any of the two web schemes. This 
-index, such as it is defined, allows quantifying the local anisotropy 
-degree of the cosmological environment, where $FA=0$ corresponds to highly
-isotropic regions and $FA=1$ the opposite case, completely anisotropic 
-regions. Although there does not exist a perfect correspondence between 
-certain range of the fractional anisotropy and each one of the above defined
-type of environment, there is an insight about what characteristics should 
-have a cell volume according to its $FA$ value. Following the analysis 
-performed by (\SRKED{[reference here]}), we shall assign low values of the 
-fractional anisotropic to the most symmetric and isotropic regions, 
-knot-like, due to their collapse in all directions. Low-middle values are 
-assigned to sheet-like regions whereas high-middle values to filament-like 
-regions, which indicates the complex dynamics of these types of environment. 
-Finally, high values ($FA \lesssim 1$) of the fractional anisotropy would
-correspond to the most highly anisotropic type of environment, voids. That
-is because their expansion rate in each direction can take very different 
-values, thereby shaping highly amorphous regions, as was concluded 
-by mean of the shape-distribution previously performed over bulk voids.
-
-%.........................................................................
-%FIGURE 6: Distribution of fractional anisotropy
-\begin{flushleft}
-\begin{figure}
-\begin{center}
-
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/fractional_anisotrpy_Tweb}
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/fractional_anisotrpy_Vweb}
-
-  \captionof{figure}{\small Cumulative distribution of the fractional 
-  anisotropy for each web scheme. T-web (upper panel) and V-web (lower 
-  panel). Distributions for each sample are also calculated, \texttt{GH} 
-  sample (black lines), \texttt{IP} sample (blue lines) and \texttt{RIP} 
-  sample (red lines). In order to compare each halo scheme, we also 
-  calculate distributions for each one, FOF (dashed lines) and BDM 
-  (continuous lines). }
-
-  \label{fig:fractional_anisotropy}
-  \vspace{0.1 cm}
-
-\end{center}
-\end{figure}
-\end{flushleft}
-%.........................................................................
-
-Figure \ref{fig:fractional_anisotropy} shows the normed cumulative 
-histograms of the fractional anisotropy for each sample. The first 
-characteristic that can be noticed is the high similitude between both web
-schemes, allowing inferring that the fractional anisotropy is effectively
-an efficient way to overcome differences between the web schemes, and 
-thereby allowing obtaining more robust conclusions. Regarding possible 
-differences between each sample, now it is clearer the existing bias 
-between \texttt{RIP} and \texttt{IP} systems, even for both web schemes. 
-In spite of all halos of the simulation are distributed mainly over middle 
-to high anisotropic regions like voids and sheet-like regions, 
-\texttt{RIP} and \texttt{IP} systems lie preferentially in more isotropic 
-and non-linear regions than \texttt{GH}. Although \texttt{RIP} systems 
-appear to lie in slightly less isotropic regions. This can be explained 
-because of the mass cut-off and the established range of relative 
-distances as extra criterion for selecting the \texttt{RIP} sample, thus 
-indicating a first possible environmental correlation. These conclusions 
-reinforce the results obtained in previous Subsection 
-\ref{subsec:tensorial_schemes}, showing the complementary character of the 
-fractional anisotropy.
-
-Returning back to the discussion about the quantification of the 
-environment leaded by the fractional anisotropy, due to its fuzzy 
-character, it is not possible to assign a well-defined type of environment 
-to each sample. While this may be thought as a disadvantage of the method, 
-actually the real character of the cosmological matter distribution is 
-also fuzzy, where any attempt to establish well-defined type of regions 
-depends necessarily on free parameters like the threshold value 
-$\lambda_{th}$, which has little or no physical motivation. So 
-independence of free parameters is indeed an advantage of quantifying 
-through the fractional anisotropy index.
-
-%-------------------------------------------------------------------------
-\subsection{The neighbourhood of voids}
-\label{subsec:neighbourhood_voids}
-%-------------------------------------------------------------------------
-
-In Subsection \ref{subsec:method_voids} we quantified bulk void regions 
-by using a FOF-like scheme. Our second approach to quantify the 
-cosmological environment of LG-like systems involves taking distances to 
-the nearest void regions in order to establish possible environmental 
-effects related with the closeness, the size and the geometry of these 
-bulk voids.
-
-In Figure \ref{fig:voids2samples} we calculate histograms of the distance 
-to the nearest void cell that belongs to the nearest bulk void region from 
-each one of the systems of each defined sample, and the volume size of 
-such bulk region. A first interesting feature found in this figure is the 
-correlation between distance and volume, where the closer a pair system is 
-to the nearest void, the larger is the volume of such void, and thus for
-both web schemes. This correlation is followed by all the samples, even 
-the \texttt{GH} and \texttt{P} samples, thereby indicating this is a 
-general feature of the matter distribution. A possible interpretation of 
-this result comes with the process of structure formation itself and the 
-way in which the web schemes classify the cosmic web. Bulk voids with very 
-extensive volumes are expected to be the lowest density regions of the 
-cosmic web due to all their matter content is being dragged by highly 
-non-linear and high density neighbour regions, such as filaments and knots. 
-This also implies that such high density neighbour regions are very close 
-to the limits of the void, with well-defined boundaries according to the 
-web schemes. In the case of voids with smaller volumes, their associated 
-mean densities are expected to be greater than the previous case, which 
-means it is difficult to establish a cut-off between sheet and void cells, 
-where such transition is rather fuzzy. Actually, most of these small 
-volume void regions are the result of a fragmentation process produced 
-along sheet-void boundaries of the cosmic web. This effect can be 
-appreciated in Figure \ref{fig:visual_impression}, specially for the V-web 
-scheme with the optimal parameter.
-
-%.........................................................................
-%FIGURE 7: Distribution of size and distance to void regions respect to 
-%each sample
-\begin{flushleft}
-\begin{figure}
-\begin{center}
-
-  \includegraphics[trim = 0mm 9mm 1mm 0mm, clip, keepaspectratio=true,
-  width=0.36\textheight]{./figures/voids_statistics_samples_BDM_Tweb}
-  \includegraphics[trim = 0mm 9mm 1mm 0mm, clip, keepaspectratio=true,
-  width=0.36\textheight]{./figures/voids_statistics_samples_BDM_Vweb}
-
-  \captionof{figure}{\small Histograms of the distance and the volume of
-  the nearest bulk void to each system of the \texttt{IP} (background 
-  histogram) and \texttt{RIP} (scatter plot) samples for BDM catalogue. 
-  Gray colorbar indicates the number of \texttt{IP} systems in each bin, 
-  whereas hot colorbar indicates the FA of the host cell of \texttt{RIP} 
-  systems. Both web classification schemes has been used, Tweb (upper 
-  panel) and V-web (lower panel). Upper and right panels of each figure
-  indicate normed histograms of each single property for the \texttt{IP}
-  sample.}
-
-  \label{fig:voids2samples}
-  \vspace{0.1 cm}
-
-\end{center}
-\end{figure}
-\end{flushleft}
-%.........................................................................
-
-As was found in Subsection \ref{subsec:tensorial_schemes} (Table 
-\ref{tab:OccupationFractions}), \texttt{IP} and \texttt{RIP} systems are 
-found to lie specially into high density (low anisotropy) regions. 
-Therefore, and according to the previous analysis, structures embedded 
-into such regions are also expected to be close to large volume volume 
-voids, while it is less likely to find pair systems close to small volume
-voids. In Figure \ref{fig:voids2samples} is also performed an analysis 
-of the fractional anisotropy of \texttt{RIP} systems. For the V-web scheme, 
-it can be noticed that \texttt{RIP} systems embedded into low anisotropy 
-regions (black, dark red and red dots) are specially distributed over the 
-peak of the underlying distribution, i.e., around large volume voids and 
-close distances. While \texttt{RIP} systems in higher FA values (yellow 
-and white dots) are completely spread out over all possible volumes and 
-distances, though following the underlying correlation. For the T-web 
-scheme it is less clear this result, being any FA value equally likely in 
-any zone of the distribution, nevertheless a slight overabundance of low 
-to middle FA values over the peak of the distribution. A completely 
-analogous analysis has been performed for FOF halos, finding equivalent
-results for both web schemes.
-
-Although previous conclusions are interesting, distances and volumes in 
-this context are little meaningless because of the arbitrary origin of the 
-threshold value $\lambda_{th}$, set in Subsection \ref{subsec:method_voids} 
-to minimize the percolation phenomenon. Therefore, those conclusions 
-should be taken as an insight of a possible underlying effect, which needs 
-more robust statistics (larger simulations) in order to have more 
-definitive conclusions. Hence, this approach is just useful to quantify 
-possible biases of the distance and volume distributions between pair 
-samples. However, in next sections it will be useful in the frame of the 
-analysis of correlations with several physical properties.
-
-%*************************************************************************
-\section{Influence of the environment on LG-like systems}
-\label{sec:influence_environment_LG}
-%*************************************************************************
-
-Once defined the general features of the preferred environment of 
-\texttt{IP} and \texttt{RIP} systems, next step is to look for possible 
-environmental effects on all physical properties of these systems. Firstly, 
-we shall study effects on kinematic properties of pair systems, i.e. total 
-mass and mass ratio, radial and tangential velocities, specific angular 
-momentum and specific mechanical energy, and the reduced spin parameter. 
-After, we look for effects on the history of each system, so we shall 
-analyse all the parameters of the MAH (Mass Assembly History) of each pair, 
-i.e., the last major merger, the formation time and the assembly time. 
-Finally, we quantify different possible alignments of pairs regarding 
-characteristic directions of the environment, like the eigenvectors of the 
-web scheme and the principal directions of inertia of the nearest void 
-region.
-
-Based on the results of Section \ref{sec:LGEnvironment}, our strategy 
-consists in using the fractional anisotropy, the distance and the volume 
-of the nearest bulk void region in order to detect and quantify any 
-possible bias on each one of the analysed properties produced by the 
-features of the host environment. Furthermore, as two web schemes have
-proven to be equivalent regarding the fractional anisotropy and the 
-statistics of void regions, we shall consider in this section only the 
-T-web scheme. Analogously for the halos detection schemes, we only 
-consider here the BDM catalogue.
-
-%-------------------------------------------------------------------------
-\subsection{Bias induced on kinematic and dynamics properties}
-\label{subsec:bias_kinematic}
-%-------------------------------------------------------------------------
-
-%.........................................................................
-%FIGURE 8: Distribution of size and distance to void regions respect to 
-%each sample
-\begin{flushleft}
-\begin{figure*}
-\begin{center}
-
-  \includegraphics[trim = 0mm 7mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.60\textheight]{./bench/codes/plot}
-
-  \captionof{figure}{\small Histograms of the distance and the volume of
-  the nearest bulk void to each system of the \texttt{IP} (background 
-  histogram) and \texttt{RIP} (scatter plot) samples for BDM catalogue. 
-  Gray colorbar indicates the number of \texttt{IP} systems in each bin, 
-  whereas hot colorbar indicates the FA of the host cell of \texttt{RIP} 
-  systems. Both web classification schemes has been used, Tweb (upper 
-  panel) and V-web (lower panel). Upper and right panels of each figure
-  indicate normed histograms of each single property for the \texttt{IP}
-  sample.}
-
-  \label{fig:correlation_kinematics_properties}\ref{fig
-  \vspace{0.1 cm}
-
-\end{center}
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%Table of extreme values of each quintile of the environmental properties
-\begin{table*}
-\begin{flushleft}
-\begin{center}
-  \begin{tabular}{l | c  c  c} \hline\hline
-									&		&	\textbf{Property}	 & \\ \hline
-\textbf{Quintile}	& \textbf{Fractional} & \textbf{Distance to the} &	\textbf{Equivalent spherical radius}	      \\
-& \textbf{Anisotropy} & \textbf{nearest void [Mpc $\bds{h^{-1}}$]} &	\textbf{of the nearest void [Mpc $\bds{h^{-1}}$]} \\ \hline
-Q1		&	$  0.0\ -\ 0.366$  &	$0.086\ -\ 1.018$	&  	$0.606\ -\ 2.072$  \\
-Q2		&	$0.366\ -\ 0.468$  &	$1.018\ -\ 2.444$	&  	$2.072\ -\ 5.777$  \\
-Q3		&	$0.468\ -\ 0.575$  &	$2.444\ -\ 4.072$ 	&  	$5.777\ -\ 12.074$  \\
-Q4		&	$0.575\ -\ 0.703$  &	$4.072\ -\ 6.151$ 	&  	$12.074\ -\ 27.618$  \\
-Q5		&	$0.703\ -\ 1.0$    &	$6.151\ -\ 15.224$ 	&  	$27.618\ -\ 42.271$  \\ \hline\hline
-  \end{tabular}  
-  \captionof{table}{\small Size of each sample defined in the Bolshoi 
-  simulation and for each of the two schemes used to detect halos (FOF 
-  and BDM).}
-
-  \label{tab:Samples_Size}
-
-\end{center}
-\end{flushleft}
-\end{table*}
-%.........................................................................
-
-Our Local Group of galaxies is certainly the most and best known 
-large-scale structure of the universe, including the knowledge of a set of
-kinematic properties, that due to their mechanical nature, are easily 
-testable by dark matter simulations like Bolshoi. The first of these 
-properties that we analyse in this section is the total mass of the pair 
-systems.
-
-Although there are not good enough estimates of each single mass 
-of the host halos of the Milky Way and M31 galaxies, there is a dynamical 
-estimate of their overall mass \SRKED{[Reference here]} compatible with the 
-selection criteria defined for selecting the \texttt{RIP} samples.
-
-In Figure \ref{fig:totalmass_FA} we calculate the distribution of 
-\texttt{IP} and \texttt{RIP} samples with regards to the total mass of 
-each pair and the fractional anisotropy index of the host cell. In order
-to make clearer any possible correlation between these properties, in the
-right panel we compute individual histograms for systems selected according 
-to defined mass ranges.
-
-... Radial vs. tangential velocities
-
-... Angular Momentum
-
-... Total Mechanical energy.
-
-... Reduced Spin
-
-%-------------------------------------------------------------------------
-\subsection{Bias induced on the Mass Assembly Histories}
-\label{subsec:bias_MAH}
-%-------------------------------------------------------------------------
-
-... Last major merger. Formation Time. Assembly Time.
-
-%-------------------------------------------------------------------------
-\subsection{Pair Alignment with the Cosmic Web}
-\label{subsec:alignment_cosmic_web}
-%-------------------------------------------------------------------------
-
-... Separation.
-
-... Relative velocity.
-
-... Angular Momentum.
-
-%*************************************************************************
 \section{Conclusions}

### 2014-04-08 bench/codes/Density_Regions.c

@@ -1,0 +1,181 @@
+#include <stdio.h>
+#include <stdlib.h>
+#define FLOAT1 float
+#define FLOAT2 double
+#define NMAX 1000
+
+//USAGE  Density_Regions.out <EIG_Filename> <DELTA_Filename> <Min_Lambda> <Max_Lambda> <N_Lambda> <Out_Filename>
+
+int main(int argc, char **argv)
+{    
+    FILE *in, *out_corr;
+    FLOAT1 *eigen1, *eigen2, *eigen3;
+    FLOAT2 *delta;
+    int *environment;
+    char filename[100];
+    
+    FLOAT1 Lambda_min, Lambda_max, Lambda;
+    int j, k, N_thr, eig;
+    float Nrho[NMAX][4];
+    int Nreg[NMAX][4];
+    
+    //Grid variables===============================================================================
+    int dumb;
+    char line[30];
+    long long i;
+    int n_x, n_y, n_z;
+    int n_nodes;
+    long long n_total;
+    float dx, dy, dz, x_0, y_0, z_0;
+    //=============================================================================================
+    
+   
+    //PARAMETERS===================================================================================
+    //Number of divisions in Lambda_th array
+    N_thr = atoi( argv[5] );     
+    //Minim Lambda_th
+    Lambda_min = atof( argv[3] );
+    //Maxim Lambda_th
+    Lambda_max = atof( argv[4] );
+    //=============================================================================================
+        
+        
+    //LOADING EIGENVALUES==========================================================================
+    for( eig=0; eig<3; eig++ ){
+        //filename of current eigenvalue
+ 	sprintf(filename, "%s_%d", argv[1], eig + 1);
+	if(!(in=fopen(filename, "r"))){
+	    fprintf(stderr, "Problem opening file %s\n", filename);
+	    exit(1);}
+	fread(&dumb,sizeof(int),1,in);
+	fread(line,sizeof(char)*30,1,in);
[…]

### 2014-04-08 bench/codes/Lambda_Histograms.c

@@ -1,0 +1,172 @@
+#include <stdio.h>
+#include <stdlib.h>
+#define FLOAT1 float
+#define NMAX1 1000
+#define NMAX2 10000
+
+//Usage  Lambda_Histogram.out <eig_filename> <size of 2D hist> <size of 1D hist> <Lambda range> <Histogram Type>
+// Histogram Type
+//	0	L1
+//	1	L2
+//	2	L3
+//	3	L1 - L2
+//	4	L1 - L3
+
+int main(int argc, char **argv)
+{   
+    FILE *in, *out_count;
+    FLOAT1 *eigen1, *eigen2, *eigen3;
+    char filename[100];
+    float Lambda_ex, L1, L2, L3;
+    
+    int l, m, n, N_2C, N_1C, eig, l2, m2, n2;
+    int count13[NMAX1][NMAX1], count12[NMAX1][NMAX1];
+    int countL1[NMAX2], countL2[NMAX2], countL3[NMAX2];
+
+    
+    //Grid variables===============================================================================
+    int dumb;
+    char line[30];
+    long long i;
+    int n_x, n_y, n_z;
+    int n_nodes;
+    long long n_total;
+    float dx, dy, dz, x_0, y_0, z_0;
+    //=============================================================================================
+    
+    
+    //PARAMETERS===================================================================================
+    //Number of divisions in Lambda count
+    N_2C = atoi( argv[2] );     
+    N_1C = atoi( argv[3] );     
+    //Lambdas Range
+    Lambda_ex = atof( argv[4] );
+    //=============================================================================================
+        
+        
+    //LOADING EIGENVALUES==========================================================================
+    for( eig=0; eig<3; eig++ ){
+        //filename of current eigenvalue
+ 	sprintf(filename, "%s_%d", argv[1], eig + 1);
+	if(!(in=fopen(filename, "r"))){
[…]

### 2014-04-08 bench/codes/Lambda_Histograms_Variance.c

@@ -1,0 +1,178 @@
+#include <stdio.h>
+#include <stdlib.h>
+#define FLOAT1 float
+#define NMAX1 100
+#define NMAX2 1000
+
+//Usage  Lambda_Histograms_Variance.out 
+//   	 <eig_filename> <size of 1D hist> <Lambda range> <N_div> <Histogram Type>
+// Histogram Type
+//	0	L1
+//	1	L2
+//	2	L3
+
+int main(int argc, char **argv)
+{   
+    FILE *in, *out_count;
+    FLOAT1 *eigen1, *eigen2, *eigen3;
+    char filename[100];
+    float Lambda_ex, L1, L2, L3;
+    
+    int l, m, n, N_1C, eig;
+    int ii, jj, kk, octx, octy, octz, oct_id, N_div;
+    int countL1[NMAX2][NMAX1], countL2[NMAX2][NMAX1], countL3[NMAX2][NMAX1];
+
+    
+    //Grid variables===============================================================================
+    int dumb;
+    char line[30];
+    long long i;
+    int n_x, n_y, n_z;
+    int n_nodes;
+    long long n_total;
+    float dx, dy, dz, x_0, y_0, z_0;
+    //=============================================================================================
+    
+    
+    //PARAMETERS===================================================================================
+    //Number of divisions of simulation
+    N_div = atoi( argv[4] );     
+    //Number of divisions in Lambda count
+    N_1C = atoi( argv[2] );     
+    //Lambdas Range
+    Lambda_ex = atof( argv[3] );
+    //=============================================================================================
+        
+        
+    //LOADING EIGENVALUES==========================================================================
+    for( eig=0; eig<3; eig++ ){
+        //filename of current eigenvalue
+ 	sprintf(filename, "%s_%d", argv[1], eig + 1);
+	if(!(in=fopen(filename, "r"))){
+	    fprintf(stderr, "Problem opening file %s\n", filename);
[…]

### 2014-04-08 bench/codes/_Head.py

@@ -1,0 +1,562 @@
+#==================================================================================================
+#			HEADERS
+#==================================================================================================
+from __future__ import division
+from struct import *
+import numpy as np
+import sys
+import matplotlib
+import os
+import matplotlib.pyplot as plt
+from pylab import *
+import scipy.integrate as integ
+import scipy.interpolate as interp
+import matplotlib.gridspec as gridspec
+from matplotlib.patches import Ellipse
+from matplotlib.ticker import NullFormatter
+
+
+#==================================================================================================
+#			VARIABLES
+#==================================================================================================
+#Global Fold
+foldglobal = '../../../ThesisProyect/data/'
+#Fold of the Void Finder code
+void_finder_fold = '../../../Void_Finder/'
+
+
+#==================================================================================================
+#			FUNCTIONS
+#==================================================================================================
+
+#..................................................................................................
+#Cutting Halos in X axe
+#..................................................................................................
+def CutHaloX( X, thick, datos, plot=True, color='black' ):
+    #Initial data
+    ncol = len(datos)		#Number of columns
+    nrow = len(datos[0])	#Number of rows
+    Box_lenght = np.max( tuple(datos[1])+tuple(datos[2])+tuple(datos[3]) )#h^-1 Mpc
+
+    
+    #Sorting in x axe
+    argx = list( np.argsort( datos[1] ) )
+    for i in xrange(0, ncol):
+	datos[i] = datos[i][argx]
+    
+    if X<=thick:
+	i_star = 0
+    else:
+	i_star = int(Box_lenght/(X - thick))
+    
+    i1 = 0
+    i2 = -1
+    for i in xrange(i_star,nrow):
+	if datos[1][i] >= X and i1==0:
+	    i1 = i
[…]

### 2014-04-08 bench/codes/cosmicweb_visual_impresion.py

@@ -1,0 +1,137 @@
+#cosmicweb_visual_impresion.py
+#
+#This code perform a graphic scheme of the visual impresion for a defined cutting off of Bolshoi
+#simulation, using the density field and the two environment classification schemes
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+folds = ["BOLSHOI/"]
+#Labels of graphs
+labels = ["BOLSHOI"]
+#Box lenght
+Box_L = [250]
+#Number of sections
+N_sec = [256]
+#Web scheme
+web = 'Vweb'
+#Values to evaluate lambda_th
+#Lambda_ths = [ 0, 0.326/2.0, 0.326, 2*0.326 ]
+Lambda_ths = [ 0, 0.188/2.0, 0.188, 2*0.188 ]
+#Smooth parameter
+smooth = '_s1'
+#Coordinate to cut (1 -- X, 2 -- Y, 3 -- Z)
+axe = 1
+#Cut
+Cut = 10
+
+#Colors
+my_cmapC = plt.cm.get_cmap('gray')
+my_cmap4 = plt.cm.get_cmap('gray', 4)
+
+#==================================================================================================
+#			PLOTING EACH CLUES SIMULATION AND RESPECTIVE LG
+#==================================================================================================
+'''
+FIGURE SCHEME
+-------------------
+|  1  |  2  |  3  |
+-------------------
+'''
+
+N_sim = len( folds )
+ax = np.zeros( (3, N_sim) )
+
+i_fold = 0
+plt.figure( figsize=(16,4*N_sim) )
+
+for fold in folds:
+    #Extent
+    extent = [0, Box_L[i_fold], 0, Box_L[i_fold]]
+
+    #Loading Density filename
+    delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,fold,N_sec[i_fold],smooth)
+    #Loading Vweb filename
[…]

### 2014-04-08 bench/codes/regions_mean_density.py

@@ -1,0 +1,90 @@
+#regions_mean_density.py
+#
+#This code calculates the mean density (dark matter density) in different zones (void, sheet, 
+#filament, knot) in order to define the best value to reproduce the visual impression of the cosmic 
+#web.
+#Usage: regions_mean_density.py <BDM or FOF>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+#folds = ["BOLSHOI/","CLUES/10909/","CLUES/16953/","CLUES/2710/"]
+folds = ["BOLSHOI/"]
+#Number of sections
+#N_sec = [256,64,64,64]
+N_sec = [256]
+#Smooth parameter
+smooth = '_s1'
+#Catalog Scheme
+catalog = sys.argv[1]
+#Web Scheme
+webs = ['Vweb', 'Tweb']
+#Styles
+color = ['blue','green']
+
+#N Lambda
+N_l = 100
+#Lambdas Extremes
+L_min = 0
+L_max = 2
+
+
+#==================================================================================================
+#			CONSTRUCTING REGIONS VOLUME
+#==================================================================================================
+
+N_sim = len(folds)
+
+plt.figure( figsize=(6.0,4) )
+i_web = 0
+for web in webs:
+    i_fold = 0
+    for fold in folds:
+	print fold, web
+	
+	#Loading eigenvalues
+	eigV_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,fold,web,N_sec[i_fold],smooth)
+	#Loading density
+	delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,fold,N_sec[i_fold],smooth)
+	#Loading environment properties of halos
+	eig = np.transpose(np.loadtxt('%s%s%s/%d/E_GH%s_%s.dat'%(foldglobal,fold,web,N_sec[i_fold],smooth,catalog)))
+
+	#Calculating mean densities associated to differents kind of regions
+	regs = Counts( eigV_filename, delta_filename, L_min, L_max, N_l )
+	print 'Mean density of regions for %s: done!'%(fold)
+	
+	#Lambda_th array
[…]

### 2014-04-08 bench/codes/void_FOF_regions.py

@@ -1,0 +1,67 @@
+#void_FOF_regions.py
+#
+#This code calculate the dependece of the volume of the largest region with the threshold value,
+#furthermore, the number of voids.
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+#folds = ["BOLSHOI/","CLUES/10909/","CLUES/16953/","CLUES/2710/"]
+folds = ["BOLSHOI/"]
+#Number of sections
+#N_sec = [256,64,64,64]
+N_sec = [256]
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+webs = ['Vweb', 'Tweb'] 
+
+#Lambda values
+Lambda_th = np.arange( 0, 1.0, 0.01 )
+
+#==================================================================================================
+#			CONSTRUCTING REGIONS VOLUME
+#==================================================================================================
+
+N_sim = len(folds)
+
+plt.figure( figsize=(5,2*4) )
+for web in webs:
+    i_fold = 0
+    for fold in folds:
+	print fold, web
+	
+	N_voids = []
+	Vol_1void = []
+	
+	for lamb in Lambda_th:
+	    void_regs = np.transpose(np.loadtxt("%s/%s/%s/%d/voids%s/voids_%1.2f/void_regions.dat"%\
+	    (foldglobal, fold, web, N_sec[i_fold], smooth, lamb )))
+	    
+	    N_voids.append( void_regs[0,-1] )
+	    Vol_1void.append( void_regs[1,0]/np.sum(1.0*void_regs[1]) )
+	    
+	plt.subplot( 2,1,1 )
+	plt.plot( Lambda_th, N_voids/N_voids[0], '-', linewidth = 2, label="%s"%(web) )
+	
+	plt.subplot( 2,1,2 )
+	plt.plot( Lambda_th, Vol_1void , '-', linewidth = 2 )
+    
+    
+plt.subplot( 2,1,1 )
+plt.grid()
+plt.ylabel( "Number of voids $N/N_0$" )
+plt.xlabel( "$\lambda_{th}$" )
+plt.legend(fancybox = True, shadow = True)
+
+plt.subplot( 2,1,2 )
+plt.grid()
+plt.ylabel( "Largest void volume  $V/V_{all}$" )
+plt.xlabel( "$\lambda_{th}$" )
+
+plt.show()

### 2014-04-08 bench/codes/void_inertia_distribution.py

@@ -1,0 +1,131 @@
+#void_intertia_tensor.py
+#
+#This code computes distributions of the eigenvalues of the reduced intertia tensor of each void 
+#region found by the FOF scheme. The eigenvalues were sorted such as Lambda1 < Lambda2 < Lambda3.
+#Here it will be calculated non-integrated and normed distributions of Lambda1/Lambda2 and 
+#Lambda1/Lambda3 in order to determinate the shape of void regions.
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+folds = ["BOLSHOI/"]
+#Number of sections
+N_sec = [256]
+#Box lenght [Mpc]
+L_box = [250.]
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+web = 'Tweb'
+#Lambda_th
+Lambda_th = 0.0
+#Nbins of each histogram
+Nbins = 10
+
+#==================================================================================================
+#			COMPUTING EIGENVALUES AND BUILDING THE INERTIA TENSOR
+#==================================================================================================
+
+i_fold = 0
+N_sim = len(folds)
+
+#no labels
+nullfmt = NullFormatter()
+
+#definitions for the axes
+left, width = 0.1, 0.65
+bottom_v, height = 0.1, 0.65
+bottom_h = left_h = left+width+0.02
+
+rect_hist2D = [left, bottom_v, width, height]
+rect_histx = [left, bottom_h, 1.335*width, 0.2]
+rect_histy = [left_h, bottom_v, 0.2, height]
+
+#start with a rectangular Figure
+plt.figure(1, figsize=(8,8))
+
+axHist2D = plt.axes(rect_hist2D)
+axHistx = plt.axes(rect_histx)
+axHisty = plt.axes(rect_histy)
+
+#no labels
+axHistx.xaxis.set_major_formatter(nullfmt)
+axHisty.yaxis.set_major_formatter(nullfmt)
+
+
+for fold in folds:
+    print fold
+    
+    
[…]

### 2014-04-08 bench/codes/void_matrix_builder.c

@@ -1,0 +1,104 @@
+#include <stdio.h>
+#include <stdlib.h>
+#define FLOAT1 float
+#define NMAX 1000
+
+//USAGE void_matrix_builder.out <EIG_Filename> <Lambda_th> <Out_Filename>
+
+int main(int argc, char **argv)
+{    
+    FILE *in, *out;
+    FLOAT1 *eigen1, *eigen2, *eigen3;
+    char filename[100];
+    
+    FLOAT1 Lambda_th;
+    int regiont_type, eig;
+    
+    //Grid variables===============================================================================
+    int dumb;
+    char line[30];
+    long long i;
+    int n_x, n_y, n_z;
+    int n_nodes;
+    long long n_total;
+    float dx, dy, dz, x_0, y_0, z_0;
+    //=============================================================================================
+    
+   
+    //PARAMETERS===================================================================================
+    //Lambda_th
+    Lambda_th = atof( argv[2] );
+    //=============================================================================================
+        
+        
+    //LOADING EIGENVALUES==========================================================================
+    for( eig=0; eig<3; eig++ ){
+        //filename of current eigenvalue
+ 	sprintf(filename, "%s_%d", argv[1], eig + 1);
+	if(!(in=fopen(filename, "r"))){
+	    fprintf(stderr, "Problem opening file %s\n", filename);
+	    exit(1);}
+	fread(&dumb,sizeof(int),1,in);
+	fread(line,sizeof(char)*30,1,in);
+	fread(&dumb,sizeof(int),1,in);
+	fread(&dumb,sizeof(int),1,in);
+	fread(&n_x,sizeof(int),1,in);    
+	fread(&n_y,sizeof(int),1,in);    
+	fread(&n_z,sizeof(int),1,in);    
+	fread(&n_nodes,sizeof(int),1,in);    
+	fread(&x_0,sizeof(float),1,in);    
+	fread(&y_0,sizeof(float),1,in);    
+	fread(&z_0,sizeof(float),1,in);    
+	fread(&dx,sizeof(float),1,in);    
+	fread(&dy,sizeof(float),1,in);    
+	fread(&dz,sizeof(float),1,in);    
+	fread(&dumb,sizeof(int),1,in);
+	n_total = n_x * n_y * n_z;
[…]

### 2014-04-08 bench/codes/void_volume_regions.py

@@ -1,0 +1,67 @@
+#void_volume_regions.py
+#
+#This code calculate an histogram of volumes for every found void region for the given lambda_th 
+#value
+#Usage void_volume_regions.py
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+folds = ["BOLSHOI/"]
+#Number of sections
+N_sec = [256]
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+webs = ['Vweb', 'Tweb'] 
+
+#Lambda value
+Lambda_th = 0.0
+
+#==================================================================================================
+#			CONSTRUCTING REGIONS VOLUME
+#==================================================================================================
+
+N_sim = len(folds)
+
+fig = plt.figure( figsize=(6,6) )
+ax1 = fig.add_subplot(111)
+ax2 = ax1.twiny()
+
+tick_locations = np.array( [0,1,2,3,4,5,6] )
+#Function to build the second axe
+def tick_function(X):
+    return ((10**X*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
+
+for web in webs:
+    i_fold = 0
+    for fold in folds:
+	print fold, web
+		
+	void_regs = np.transpose(np.loadtxt("%s/%s/%s/%d/voids%s/voids_%1.2f/void_regions.dat"%\
+	(foldglobal, fold, web, N_sec[i_fold], smooth, Lambda_th )))
+	    	    	
+	ax1.hist( np.log10(void_regs[1]) , bins=30, linewidth = 3,\
+	label = "%s"%(web), normed = True, histtype = 'step', cumulative = False   )
+    
+
+#Axe 1    
+ax1.grid()
+ax1.set_ylabel( "Normed distribution" )
+ax1.set_xlabel( "Comoving volume $\log_{10}[ (0.98$ Mpc $h^{-1} )^{-3} ]$" )
+ax1.legend(fancybox = True, shadow = True)
+
+#Axe 2
+ax2.set_xticks( tick_locations )
+tick_label = []
+for tick in tick_locations:
+    tick_label.append( "%1.2f"%tick_function(tick) )
+ax2.set_xticklabels( tick_label )
+ax2.set_xlabel( "Equivalent spherical comoving radius Mpc $h^{-1}$" )
+
+plt.show()

### 2014-04-18 cosmic_voids.tex
Updating paper structure
Figures and analysis of fraction of halos in each environment

@@
 
-The study of the influence of the cosmic web on galaxy properties start 
-with the seminal work of Dressler \SRKED{[reference here]} and extends to 
-recent works using large observational surveys that look for signatures of 
-the web into the evolution of galaxy populations. With the advention of 
-more detailed observations and sophisticated computational models it is 
-now within our reach to understand what physical processes dominate.
-
-This makes  that the mass assembly history of a galaxy is deeply connected 
-with its  position in the cosmic web. There is an extensive body of 
-literature on the effects of the web environment on the observable 
-properties of galaxies.
-
-This environmental study is also of paramount importance to understand the 
-formation of our Galaxy. In our local neighborhood, the observations of 
-dwarf galaxies around the Milky Way (MW) and the Andromeda galaxy (M31) 
-show filamentary and disk-like patterns that can be linked to a 
-preferential infall direction, very likely connected with the cosmic web 
-where the Local Group (LG) of galaxies is embedded.
-
-In this paper we quantify the velocity shear environment of DM halo pairs
-representative of the principal members of the Local Group (LG), the Milky
-Way (MW) and Andromeda galaxy (M31). We perform this study in an 
-unconstrained cosmological simulation from random phases in the initial 
-conditions, and unlike previous works, where were used constrained 
-cosmological simulations which have been setup as to reproduce the large 
-scale structure of the local universe, we use directly observational 
-measurements of the kinematics properties of the local group \SRKED{
-[Reference here]} in order to build faithful samples of LG-like systems.
-
-We pay special attention to the correlation of the present velocity shear 
-environment with the assembly and the kinematics properties of the pairs. 
-The motivation to have that focus is that it has been previously shown 
-that the LG present in three different realizations of the constrained 
-simulations have assembly histories biased towards early formation times 
-and absence of major mergers (ratio 1:10) in the last $10$ Gyr. In the 
-case of the kinematic properties, recent observational constrains to the 
-galactocentric tangential velocity of M31 has enabled to establish how 
-typical is the LG in a cosmological context \SRKED{[reference to 
-Forero-Romero et.al 2013-1]}, that is why we focus here how a specific kind 
-of host environment biases these kinematics properties.
+Relevant information about previous works and current state of the art.
 
@@
 particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
-
-%-------------------------------------------------------------------------
-\subsection{Halos and Merger Trees}
-\label{subsec:halos_merger_trees}
-%-------------------------------------------------------------------------
-
 We identify halos with two algorithms, the Friends-of-Friends \SRKED{
-[reference here]} algorithm and the Bound Density Maximum algorithm. The 
-constructed catalogues also provide the basis for the mass aggregation 
-history studies. We also include in the catalogues information about the 
-substructure.
-
-All the results presented here must be interpreted in term of host halos, 
-without any information of the substructure. In particular the merger of 
-two FOF halos corresponds to the epoch of first overlap, and not to the 
-fusion and/or disruption of an accreted sub-halo with a dominant halo.
-
-The linking length is $b=0.17$ times the mean inter-particle separation. 
-All objects with 20 particles or more are considered a bona fide halo and 
-are included in the construction of the merger tree, this corresponds to a 
-minimum halo mass of $M_{\rm min}=2.70\times 10^{9}$\hMsun in the Bolshoi 
-simulation.
-
-The halo identification for the simulation was done for XX snapshots in 
-the redshift range $0<z<7$ more or less evenly spaced in look-back time.
+[reference here]} algorithm and the Bound Density Maximum algorithm.
 
@@
 Both established schemes to quantify the cosmic web depend on continuous 
-and smooth physical quantities, as the peculiar velocity field and the 
-density field. In order to calculate the necessary tensors, a discretization
-of the simulation volume is performed, so all the properties are reduced 
-to single values associated to discrete cells. According to this, we divide 
-the overall volume into $(256)^3$ cells, so each cell has an associated 
-comoving cubic volume of $0.98 \mbox{ Mpc h}^{-1}$. Finally, in order to 
-reduce possible effects due to the discretization process, a gaussian 
-softening is performed between neighbour cells.
+and smooth physical quantities, i.e the peculiar velocity field and the 
+density field. To calculate these quantities, a discretization over the 
+volume of the simulation is performed, so all the properties are reduced 
+to single values associated to discrete cells. According to this, we 
+divide the overall volume into $(256)^3$ cells, so each cell has an 
+associated comoving cubic volume of $0.98 \mbox{ Mpc h}^{-1}$. Finally, in 
+order to reduce possible effects due to the discretization process, a 
+gaussian softening is performed between neighbour cells.
 
-Once defined the numerical details about the classification schemes, we 
-shall analyse the dependence on the threshold value $\lambda_{th}$ for each 
-one. In Figure \ref{fig:mean_density} we show the variation of the mean 
-density parameter $\delta$ with the threshold value for cells marked as one 
-of the two more dominant types of environment (voids and sheets).
-
-%.........................................................................
-%FIGURE 1: Mean density for each environment
-\begin{flushleft}
-\begin{figure}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 12mm 5mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{./figures/cell_types_density.pdf}
-
-  \captionof{figure}{\small Mean density parameter for each one of the 
-  defined environments according to the chosen $\lambda_{th}$ value and 
-  for both classification schemes. Tweb (green lines) and Vweb (blue 
-  lines). The mean density parameter is calculated by averaging all the 
-  values  of the cells determined as a certain type of environment 
-  according to its eigenvalues. The optimal parameters found are 
-  $\lambda_{opt}^{T}=0.326$ and $\lambda_{opt}^{V}=0.188$.}
-
-  \label{fig:mean_density}
-  \vspace{0.1 cm}
-
-\end{figure}
-\end{flushleft}
-%.........................................................................
+Once defined the numerical details about both classification schemes, we
+shall analyse the dependence on the threshold value $\lambda_{th}$ for 
+each one. In Figure \ref{fig:median_density} we calculate the median 
+contrast density for cells catalogued in each one of the types of 
+environment with respect to the threshold value, where filled regions 
+correspond to quartiles $Q_1$ and $Q_3$ of the samples, i.e. half of the 
+cells are mapped within such regions. Moreover, we calculate fraction of
+halos within each one of the defined environments based upon the FOF 
+catalogue of the simulation.
 
 As was previously established by \SRKED{Hoffman et al. (2012)} and as 
-can be seen in Figure \ref{fig:mean_density}, the behaviour of the 
+can be seen in Figure \ref{fig:median_density}, the behaviour of the 
 V-web scheme is significantly more sensible to variations of the 
-$\lambda_{th}$ value compared with the T-web scheme; nevertheless, the 
-behaviour of the mean density parameter for voids, sheets and filaments, 
-are qualitatively quite similar for the two schemes, increasing with the 
-value of $\lambda_{th}$. Although we shall focus our analysis on voids 
-because they are completely dominant in the visual impression of the 
-cosmic web, an analogous analysis might be performed for other type of 
-environments.
+$\lambda_{th}$ value compared with the T-web scheme. Furthermore, taking
+into account the physical origin of the T-web scheme, based upon the 
+Hessian matrix, environments catalogued through this scheme have a 
+well-differentiate density value for all \lth range, whereas for the V-web 
+case, all regions are overlapped, specially for high \lth values and for 
+high density regions, being more confuse to discern a typical density for 
+each type of environment. This could be explained appealing to the 
+kinematic rather than dynamic origin of the V-web, which is based upon the 
+velocity shear tensor, and implying that the correspondence between 
+density and peculiar velocity is less trivial for high density regions, 
+what it is precisely expected for the non-linear regime.
 
@@
 expected impression according to the density field.
+
+Our classification scheme may be thought as a refinement of the recent 
+schemes, where the threshold value is used to taking as a free parameter, 
+based on the classic methods, where the classification is performed 
+based on a cut off of the density field directly \SRKED{[references here]}.
+So we make use of the objectivity achieved by the analysis of the mean 
+density, but keeping all the environmental information provided by the
+tensorial schemes instead of the poor description provided by the density 
+field.
+
+%*************************************************************************
+\section{Finding bulk voids}
+\label{sec:bulk_voids}
+%*************************************************************************
+
+Following the recent growing interest in studying galaxy formation in 
+low-density regions, we use a method based on a FOF-like algorithm to 
+find extended regions of voids. To achieve this, we build the input 
+catalogue for the FOF method with the coordinate of the center of every 
+cell marked as void according to the web classification scheme adopted, 
+furthermore we set an adequate linking length to connect even diagonal 
+neighbour cells.
+
+Following the work of \SRKED{Forero-Romero et al. 2008}, we also perform a 
+percolation analysis in order to select the best threshold parameter that
+reduces percolation in cells, thereby accounting for physical bulk void 
+regions. In Figure \ref{fig:percolation_analysis} we show the obtained 
+result of our percolation analysis for both web schemes. In both cases, it 
+can be noticed that the volume of the largest void region is minimized and 
+the volume distribution of voids is relatively flat at $\lambda_{th} = 0.0$, 
+what means percolation is completely reduced for this threshold value. So, 
+in spite of the previously established $\lambda_{th}$ optimal values for 
+each scheme, we shall use $\lambda_{th} = 0.0$ just for the detection of 
+bulk void regions. Moreover, due to the domination of the large scale 
+visual impression by voids, it is inevitable the presence of the 
+percolation phenomenon, so the current chosen threshold value for 
+percolation is justified because though voids are necessarily connected 
+among them, we are just interested in detecting bulk regions.
+
+Next, we shall calculate the reduced inertia tensor of each void region 
+in order to determinate their principal directions of inertia and analyse 
+the size-shape distribution of voids.
+
+%.........................................................................
+%Reduced inertia tensor
+\eq{ReducedIntertia}
+{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
+%.........................................................................
+where $l$ is an index associated to each cell of to the current region, 
+$i$ and $j$ indexes run over each spatial direction and finally 
+$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$, all 
+positions are measured from the respective center of mass of the region.
+
+The eigenvalues of the reduced inertia tensor, i.e. the principal moments
+of inertia, are used to quantify the shape of void regions. They are 
+denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
+\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
+distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$, where we rather 
+calculate histograms for these ratio quantities instead of each single 
+value in order to avoid using an arbitrary normalization. For both schemes, 
+it can be noticed that the shape-distribution is completely spread out, 
+thereby indicating a non-preferred geometry of void regions, which is in 
+agreement with the well established highly anisotropy of matter flows
+associated to this type of region \SRKED{[reference here]}. Because of 
+that, we shall look for possible alignments between the plane of rotation 
+of halo pairs and the principal directions of inertia of the nearest void 
+regions.
+
+%*************************************************************************
+\section{Statistics of voids and influence over dark matter halos}
+\label{sec:statistics}
+%*************************************************************************
+
+%*************************************************************************
+\section{Conclusions}
+\label{sec:conclusions}
+%*************************************************************************
+
+%*************************************************************************
+\section*{Acknowledgments}  
+%*************************************************************************
+
+\bibliographystyle{mn2e}
+\bibliography{references}
+
+%.........................................................................
+%FIGURE 1: Median density for each environment
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/median_environments_densities_Tweb.pdf}
+  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/median_environments_densities_Vweb.pdf}
+  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}
+  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}
+
+  \captionof{figure}{\small Mean density parameter for each one of the 
+  defined environments according to the chosen $\lambda_{th}$ value and 
+  for both classification schemes. Tweb (green lines) and Vweb (blue 
+  lines). The mean density parameter is calculated by averaging all the 
+  values  of the cells determined as a certain type of environment 
+  according to its eigenvalues. The optimal parameters found are 
+  $\lambda_{opt}^{T}=0.326$ and $\lambda_{opt}^{V}=0.188$.}
+
+  \label{fig:median_density}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
 
@@
 
-Our classification scheme may be thought as a refinement of the recent 
-schemes, where the threshold value is used to taking as a free parameter, 
-based on the classic methods, where the classification is performed 
-based on a cut off of the density field directly \SRKED{[references here]}.
-So we make use of the objectivity achieved by the analysis of the mean 
-density, but keeping all the environmental information provided by the
-tensorial schemes instead of the poor description provided by the density 
-field.
-
-%-------------------------------------------------------------------------
-\subsection{Method to find void regions}
-\label{subsec:method_voids}
-%-------------------------------------------------------------------------
-
-Following the recent growing interest in studying galaxy formation in 
-low-density regions, we use a method based on a FOF-like algorithm to 
-find extended regions of voids. To achieve this, we build the input 
-catalogue for the FOF method with the coordinate of the center of every 
-cell marked as void according to the web classification scheme adopted, 
-furthermore we set an adequate linking length to connect even diagonal 
-neighbour cells.
-
-Following the work of \SRKED{Forero-Romero et al. 2008}, we also perform a 
-percolation analysis in order to select the best threshold parameter that
-reduces percolation in cells, thereby accounting for physical bulk void 
-regions. In Figure \ref{fig:percolation_analysis} we show the obtained 
-result of our percolation analysis for both web schemes. In both cases, it 
-can be noticed that the volume of the largest void region is minimized and 
-the volume distribution of voids is relatively flat at $\lambda_{th} = 0.0$, 
-what means percolation is completely reduced for this threshold value. So, 
-in spite of the previously established $\lambda_{th}$ optimal values for 
-each scheme, we shall use $\lambda_{th} = 0.0$ just for the detection of 
-bulk void regions. Moreover, due to the domination of the large scale 
-visual impression by voids, it is inevitable the presence of the 
-percolation phenomenon, so the current chosen threshold value for 
-percolation is justified because though voids are necessarily connected 
-among them, we are just interested in detecting bulk regions.
-
 %.........................................................................
@@
 %.........................................................................
-
-Next, we shall calculate the reduced inertia tensor of each void region 
-in order to determinate their principal directions of inertia and analyse 
-the size-shape distribution of voids.
-
-%.........................................................................
-%Reduced inertia tensor
-\eq{ReducedIntertia}
-{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
-%.........................................................................
-where $l$ is an index associated to each cell of to the current region, 
-$i$ and $j$ indexes run over each spatial direction and finally 
-$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$, all 
-positions are measured from the respective center of mass of the region.
 
@@
 
-The eigenvalues of the reduced inertia tensor, i.e. the principal moments
-of inertia, are used to quantify the shape of void regions. They are 
-denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
-\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
-distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$, where we rather 
-calculate histograms for these ratio quantities instead of each single 
-value in order to avoid using an arbitrary normalization. For both schemes, 
-it can be noticed that the shape-distribution is completely spread out, 
-thereby indicating a non-preferred geometry of void regions, which is in 
-agreement with the well established highly anisotropy of matter flows
-associated to this type of region \SRKED{[reference here]}. Because of 
-that, we shall look for possible alignments between the plane of rotation 
-of halo pairs and the principal directions of inertia of the nearest void 
-regions.
-
-%*************************************************************************
-\section{Conclusions}
-\label{sec:conclusions}
-%*************************************************************************
-
-%*************************************************************************
-\section*{Acknowledgments}  
-%*************************************************************************
-
-\bibliographystyle{mn2e}
-\bibliography{references}
-
 %.........................................................................

### 2014-04-18 bench/codes_analysis/_Head.py

@@ -14,6 +14,7 @@ import scipy.interpolate as interp
 import matplotlib.gridspec as gridspec
 from matplotlib.patches import Ellipse
 from matplotlib.ticker import NullFormatter
+plt.close('all')
 
 
 #==================================================================================================
@@ -25,6 +26,8 @@ foldglobal = '../../../CosmicData/'
 void_finder_fold = '../../../Void_Finder/'
 #Fold to store data of figures
 data_figures_fold = '../data_figures/'
+#Fold to store figures
+figures_fold = '../../figures/'
 
 
 #==================================================================================================

### 2014-04-18 bench/codes_analysis/halos_histograms_regions.py

@@ -1,0 +1,68 @@
+#halos_histogram_region.py
+#
+#This code calculates histograms of number of dark matter halos for each type of region, sweeping
+#several lambda threshols values
+#Usage: halos_histogram_region.py <BDM or FOF>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Halo Scheme
+catalog = sys.argv[1]
+#Web Scheme
+webs = ['Vweb', 'Tweb']
+#Styles
+color = ['blue','green']
+
+#N Lambda
+N_l = 100
+#Lambdas extremes values
+L_min = 0
+L_max = 1
+#Lambda array
+Lambda = np.linspace(L_min, L_max, N_l)
+
+
+#==================================================================================================
+#			CONSTRUCTING HISTOGRAMS
+#==================================================================================================
+i_web = 0
+for web in webs:
+    #Number of dark matter halos per region
+    Numb_GH = np.zeros( (N_l,5) )
+    print simulation, web
+    
+    #Loading eigenvalues
+    eigV = np.loadtxt('%s%s%s/%d/E_GH%s_%s.dat'%(foldglobal,simulation,web,N_sec,smooth,catalog))
+
+    for i_l in xrange( N_l ):
+	lamb = Lambda[i_l]
+	#Storing lambda value
+	Numb_GH[i_l,0] = lamb
+	#Halos in Voids
+	bool_v = (eigV[:,1] <= lamb)*(eigV[:,2] <= lamb)*(eigV[:,3] <= lamb)
+	Numb_GH[i_l,1] = len( eigV[bool_v,0] )/(1.0*len( eigV ))
+	#Halos in Sheets
+	bool_s = (eigV[:,1] > lamb)*(eigV[:,2] <= lamb)*(eigV[:,3] <= lamb)
+	Numb_GH[i_l,2] = len( eigV[bool_s,0] )/(1.0*len( eigV ))
+	#Halos in Filaments
[…]

### 2014-04-18 bench/codes_analysis/void_geometric_center.py

@@ -24,7 +24,7 @@ web = sys.argv[1]
 #Lambda_th
 Lambda_th = float(sys.argv[2])
 #Cutt of respect to the number of cells
-N_cut = 8
+N_cut = 0
 
 #==================================================================================================
 #			COMPUTING GEOMETRIC CENTER OF VOIDS

### 2014-04-18 bench/codes_analysis/void_inertia_tensor.py

@@ -1,0 +1,123 @@
+#void_intertia_tensor.py
+#
+#This code computes the reduced intertia tensor of each void region found by the FOF scheme. For 
+#each region is also computed the associated eigenvalues and the principal directions of inertia 
+#in order to quantify the shape of those regions.
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+folds = ["BOLSHOI/"]
+#Number of sections
+N_sec = [256]
+#Box lenght [Mpc]
+L_box = [250.]
+#Smooth parameter
+smooth = '_s1'
+#Catalog Scheme
+catalog = 'FOF'
+#Web Scheme
+web = 'Vweb'
+#Lambda_th
+Lambda_th = 0.0
+#Cutt of respect to the number of cells
+N_cut = 8
+
+#==================================================================================================
+#			COMPUTING EIGENVALUES AND BUILDING THE INERTIA TENSOR
+#==================================================================================================
+
+i_fold = 0
+N_sim = len(folds)
+
+for fold in folds:
+    print fold
+    
+    #Loading the file with all the information about each region
+    voids = np.transpose( np.loadtxt( "%s/%s/%s/%d/voids%s/voids_%1.2f/void_regions.dat"%\
+    (foldglobal, fold, web, N_sec[i_fold], smooth, Lambda_th )))
+    
+    #Calculating eigenvalues and principal directions of inertia
+    Eigenvalues = []
+    Eigenvector = []
+    #Sweeping through the regions
+    for i_void in voids[0]:
+	sys.stdout.write( " In region:\t%d\r" %(int(i_void)) )
+	sys.stdout.flush()
+
+	#Loading cells of the current region
+	region = np.transpose( np.loadtxt( "%s/%s/%s/%d/voids%s/voids_%1.2f/void_%d.dat"%\
+	(foldglobal, fold, web, N_sec[i_fold], smooth, Lambda_th, int(i_void) )))
+      
[…]

### 2014-04-18 bench/codes_figures/halos_fraction.py

@@ -1,0 +1,58 @@
+#halos_fraction.py
+#
+#This code calculates plots of fraction of halos in each one of the defined environments for a 
+#range od threshold values
+#Usage: halos_fraction.py <Vweb or Tweb> <BDM or FOF> <show(0) or save(1)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+web = sys.argv[1]
+#Catalogue
+catalogue = sys.argv[2]
+#Colors
+colors = [ 'green', 'blue', 'red', 'gray' ]
+
+#==================================================================================================
+#Fraction of halos in each environment
+#==================================================================================================
+
+plt.figure( figsize=(5,5) )
+
+#Loading file of number fractions
+numbers = np.loadtxt( '%shalos_count_regions_%s_%s.dat'%(data_figures_fold,catalogue,web) )
+#Plotting 
+plt.plot( numbers[:,0], numbers[:,1], linewidth = 2, label='voids', color = colors[0] )
+plt.plot( numbers[:,0], numbers[:,2], linewidth = 2, label='sheets', color = colors[1] )
+plt.plot( numbers[:,0], numbers[:,3], linewidth = 2, label='filaments', color = colors[2] )
+plt.plot( numbers[:,0], numbers[:,4], linewidth = 2, label='knots', color = colors[3] )
+plt.grid(1)
+plt.ylabel( 'Fraction of halos', fontsize = 12 )
+plt.xlabel( '$\lambda_{th}$', fontsize = 12 )
+plt.xlim( (0,1) )
+plt.ylim( (0,1) )
+plt.title( '%s %s'%(web, catalogue) )
+plt.legend( loc='upper left', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
+#Lambda_th line
+if web == 'Tweb':
+    lamb_opt = 0.36
+elif web == 'Vweb':
+    lamb_opt = 0.202
+plt.vlines( lamb_opt, 0, 1, linestyle = '--', color = 'blue', linewidth = 2 )
+plt.text( lamb_opt + 0.01, 0.6, '$\lambda_{opt}$', fontsize = 15, color='blue' )
[…]

### 2014-04-18 bench/codes_figures/median_density_histograms.py

@@ -1,0 +1,55 @@
+#median_density_histogram.py
+#
+#This code plots histograms of median density for all type regions according to Lambda_thr values
+#Usage: median_density_histogram.py <Vweb or Tweb>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+web = sys.argv[1]
+#Colors and labels
+colors = [ 'green', 'blue', 'red', 'gray' ]
+labels = [ 'voids', 'sheets', 'filaments', 'knots' ]
+
+#==================================================================================================
+#Median contrast density
+#==================================================================================================
+#Loading file of quartiles
+names_quartiles = []
+names_quartiles.append('%svoids_delta_hist/%s/quartiles.dat'%(data_figures_fold,web) )
+names_quartiles.append( '%ssheets_delta_hist/%s/quartiles.dat'%(data_figures_fold,web) )
+names_quartiles.append( '%sfilaments_delta_hist/%s/quartiles.dat'%(data_figures_fold,web) )
+names_quartiles.append( '%sknots_delta_hist/%s/quartiles.dat'%(data_figures_fold,web) )
+
+
+plt.figure( figsize=(5,5) )
+#Median contrast density for each region
+for i in xrange(4):
+    #plt.subplot( 1,4,i+1 )
+    quartiles = np.loadtxt( names_quartiles[i] )
+    quartiles[:,[1,2,3]] = np.log( quartiles[:,[1,2,3]] + 1.0 )
+    plt.fill_between( quartiles[:,0], quartiles[:,1], quartiles[:,3], color = colors[i], alpha = 0.3 )
+    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i], linewidth = 1 )
+    plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i], linewidth = 2, label = labels[i] )
+    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i], linewidth = 1 )
+    
+#Plot format
+plt.hlines( 0, 1, 0, linestyle='--', linewidth = 2 )
+plt.grid(1)
[…]

### 2014-04-20 cosmic_voids.tex
Analysis of optimal lambda_th based upon the fraction of halos

@@
 shall analyse the dependence on the threshold value $\lambda_{th}$ for 
-each one. In Figure \ref{fig:median_density} we calculate the median 
-contrast density for cells catalogued in each one of the types of 
-environment with respect to the threshold value, where filled regions 
-correspond to quartiles $Q_1$ and $Q_3$ of the samples, i.e. half of the 
-cells are mapped within such regions. Moreover, we calculate fraction of
-halos within each one of the defined environments based upon the FOF 
-catalogue of the simulation.
+each one. For this, we shall use the distribution of dark matter halos as 
+tracer of the underlying matter field in order to be more consistent with
+available observational data. In Figure \ref{fig:halos_fractions} we 
+calculate fractions of halos within each one of the defined environments 
+based upon the FOF catalogue of the simulation and for an extensive \lth 
+range. Then we look for some key feature that could indicated us a 
+possible optimal value of the \lth value. One first step forward our quest 
+is the behaviour of the V-web scheme compared with the T-web. As was 
+previously established by \SRKED{Hoffman et al. (2012)} and as can be seen 
+in Figure \ref{fig:halos_fractions}, V-web scheme is significantly more 
+sensible to variations of the $\lambda_{th}$ value, since all fractions of
+halos for the V-web change significantly in the range $[0,0.4]$, whereas, 
+for the T-web scheme, fractions change smoothly throughout all \lth range 
+covered. From this, it is then expected that the optimal \lth value for the 
+V-web scheme is less than the T-web value.
 
-As was previously established by \SRKED{Hoffman et al. (2012)} and as 
-can be seen in Figure \ref{fig:median_density}, the behaviour of the 
-V-web scheme is significantly more sensible to variations of the 
-$\lambda_{th}$ value compared with the T-web scheme. Furthermore, taking
-into account the physical origin of the T-web scheme, based upon the 
-Hessian matrix, environments catalogued through this scheme have a 
-well-differentiate density value for all \lth range, whereas for the V-web 
-case, all regions are overlapped, specially for high \lth values and for 
-high density regions, being more confuse to discern a typical density for 
-each type of environment. This could be explained appealing to the 
-kinematic rather than dynamic origin of the V-web, which is based upon the 
-velocity shear tensor, and implying that the correspondence between 
-density and peculiar velocity is less trivial for high density regions, 
-what it is precisely expected for the non-linear regime.
-
-On cosmic scales, the presence of highly non-linear structures implies the 
-existence of very vast regions with density lower than the mean 
-cosmological value due to the mass conservation. That is why the visual 
-impression of the cosmic web should be necessarily dominated by these 
-under-dense regions. Keeping that in mind, our novel proposal is based upon
-the correct quantification of these regions, so the optimal threshold 
-value must be chosen such that: sheet regions do not invade real void 
-regions (in such case, the mean density parameter of sheet regions would 
-become negative) and void regions do not invade real sheet and filament 
-regions (in such case, the mean density parameter of void regions would 
-increase due to the contribution of over-dense regions). Thus, the optimal 
-value is simply where the mean density parameter of sheet regions is 
-null. According to this, we obtain the next optimal threshold values 
-for the T-web and the V-web respectively, $\lambda_{opt}^T = 0.326$ and 
-$\lambda_{opt}^V = 0.188$. To verify our analysis, we show in Figure 
-\ref{fig:visual_impression} the visual impression for each defined critical 
-value, and as can be seen, the chosen values reproduce properly the 
-expected impression according to the density field.
-
-Our classification scheme may be thought as a refinement of the recent 
-schemes, where the threshold value is used to taking as a free parameter, 
-based on the classic methods, where the classification is performed 
-based on a cut off of the density field directly \SRKED{[references here]}.
-So we make use of the objectivity achieved by the analysis of the mean 
-density, but keeping all the environmental information provided by the
-tensorial schemes instead of the poor description provided by the density 
-field.
+The more notorious characteristic of Figure \ref{fig:halos_fractions} is
+the behaviour of the fraction of halos within sheet regions for both web 
+schemes, increasing until a local maximum, and then decreasing. The 
+increasing or decreasing rate of the fraction of halos for some region 
+could be interpreted as a measure of the degree of non-linearity of such 
+region for some specific \lth value. For example, filaments and knots, 
+that are the most non-linear regions of the universe, have a negative rate 
+for all covered \lth range. In the case of voids, the situation is 
+completely opposite, where fractions of halos increase in everywhere. If 
+we think in terms of the underlying matter field of the cosmic web, \lth 
+is just a cutting parameter between high non-linear regions (filament and 
+knots) and low non-linear (voids and sheets). Furthermore, if we take into 
+account that dark matter halos are much more likely to form in high 
+non-linear regions, it is expected the obtained behaviour of fractions of 
+halos for voids, filaments and knots as we increase the \lth value. 
+However, the behaviour of the fraction of halos in sheets is less clear,
+increasing for low \lth values (like voids) and decreasing for higher \lth 
+values (like filaments and knots). This indicates us the transitional 
+character of sheet regions in the cosmic web. Our proposal here is to 
+select as optimal \lth the value where the fraction of sheets reaches a
+local maximum, so sheets are completely taken as intermediate transitional 
+and neutral zones regarding the degree of non-linearity. According to this,
+we find for the T-web scheme a optimal value $\lambda_{opt}^T = 0.36$ and
+for the V-web scheme $\lambda_{opt}^V = 0.20$. In figure 
+\ref{fig:visual_impression} we show the visual impression of the cosmic 
+web along with the density field for different \lth values including the 
+optimal values.
 
@@
 %.........................................................................
-%FIGURE 1: Median density for each environment
+%FIGURE 1: Fraction of halos in each environment
 \begin{flushleft}
-\begin{figure*}
+\begin{figure}
 \centering
@@
   \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/median_environments_densities_Tweb.pdf}
-  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/median_environments_densities_Vweb.pdf}
-  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
   width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}
+
   \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
@@
 
-  \label{fig:median_density}
+  \label{fig:halos_fractions}
   \vspace{0.1 cm}
 
-\end{figure*}
+\end{figure}
 \end{flushleft}
@@
 %.........................................................................
-%FIGURE 2: Visual impresion
+%FIGURE 2: Visual impression of the cosmic web
 \begin{flushleft}
 \begin{figure*}
-\begin{center}
+\centering
 
@@
   panels), and of each classification scheme with the $\lambda_{th}$ values 
-  obtained by our criteria (others panels). Our color convention for each 
+  obtained by our criteria (others panels). The color convention for each 
   environment is (white) - void, (light gray) - sheet, (gray) - filament, 
@@
 
-\end{center}
 \end{figure*}
@@
 
-%.........................................................................
-%FIGURE 3: Percolation analysis
-\begin{flushleft}
-\begin{figure*}
-\begin{center}
-
-  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_regions_percolation.pdf}
-  \includegraphics[trim = 0mm 00mm 00mm 00mm, clip, keepaspectratio=true,
-  width=0.36\textheight]{./figures/voids_regions_volume.pdf}
-
-  \captionof{figure}{\small Percolation analysis of void regions for 
-  different $\lambda_{th}$ values and for both defined classification 
-  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
-  volume and the number of voids detected according to the threshold value 
-  $\lambda_{th}$ (left panels). Size distribution histogram of void cells
-  using the threshold value $\lambda_{th} = 0.0$ for both schemes 
-  (right panel).}
-
-  \label{fig:percolation_analysis}
-  \vspace{0.1 cm}
-
-\end{center}
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 4: Distribution of eigenvalues of the inertia tensor
-\begin{flushleft}
-\begin{figure}
-\begin{center}
-
-  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
-  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb}
-  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
-  width=0.36\textheight]{./figures/voids_inertia_tensor_Vweb}
-
-  \captionof{figure}{\small Histogram of eigenvalue ratio $\tau_1/\tau_2$
-  vs $\tau_2/\tau_3$ for the inertia tensor of void regions. T-web 
-  (upper panel) and V-web (lower panel). Number of cells per 
-  region in 2D histograms are indicated by the respective colour bar. 
-  Upper ($\tau_1/\tau_2$) and right ($\tau_2/\tau_3$) panels of each 
-  figure shows a normalized histogram of each ratio parameter. The 
-  adopted division for quantify the morphology of void regions is not
-  well justified, it should be understood as a fuzzy and continuous 
-  limit, done just for illustrative purposes.}
-
-  \label{fig:distro_inertia}
-  \vspace{0.1 cm}
-
-\end{center}
-\end{figure}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
 \end{document}

### 2014-04-20 bench/codes_figures/cosmicweb_visual_impresion.py

@@ -2,6 +2,7 @@
 #
 #This code perform a graphic scheme of the visual impresion for a defined cutting off of Bolshoi
 #simulation, using the density field and the two environment classification schemes
+#Usage cosmicweb_visual_impresion.py <Vweb or Tweb> <show(0) or save(1)>
 #
 #by: Sebastian Bustamante
 
@@ -11,18 +12,21 @@ execfile('_Head.py')
 #			PARAMETERS
 #==================================================================================================
 #Simulation
-folds = ["BOLSHOI/"]
+simulation = "BOLSHOI/"
 #Labels of graphs
-labels = ["BOLSHOI"]
+labels = "BOLSHOI"
 #Box lenght
-Box_L = [250]
+Box_L = 250
 #Number of sections
-N_sec = [256]
+N_sec = 256
 #Web scheme
-web = 'Vweb'
+web = sys.argv[1]
 #Values to evaluate lambda_th
-#Lambda_ths = [ 0, 0.326/2.0, 0.326, 2*0.326 ]
-Lambda_ths = [ 0, 0.188/2.0, 0.188, 2*0.188 ]
+if web == 'Tweb':
+    Lambda_opt = 0.36
+if web == 'Vweb':
+    Lambda_opt = 0.20
+Lambda_ths = [ 0, Lambda_opt/2.0, Lambda_opt, 2*Lambda_opt ]
 #Smooth parameter
 smooth = '_s1'
 #Coordinate to cut (1 -- X, 2 -- Y, 3 -- Z)
@@ -35,7 +39,7 @@ my_cmapC = plt.cm.get_cmap('gray')
 my_cmap4 = plt.cm.get_cmap('gray', 4)
 
 #==================================================================================================
-#			PLOTING EACH CLUES SIMULATION AND RESPECTIVE LG
+#			PLOTING WEB SCHEME AND DENSITY FIELD FOR SIMULATION
 #==================================================================================================
 '''
 FIGURE SCHEME
@@ -43,95 +47,71 @@ FIGURE SCHEME
 |  1  |  2  |  3  |
 -------------------
 '''
[…]

### 2014-04-20 cosmic_voids.tex
Analysis of distributions of mass and peculiar velocity of dark matter halos

@@
 and neutral zones regarding the degree of non-linearity. According to this,
-we find for the T-web scheme a optimal value $\lambda_{opt}^T = 0.36$ and
+we find for the T-web scheme an optimal value $\lambda_{opt}^T = 0.36$ and
 for the V-web scheme $\lambda_{opt}^V = 0.20$. In figure 
@@
 web along with the density field for different \lth values including the 
-optimal values.
+optimal values. It can be noticed that the optimal values found reproduce 
+well the visual impression.
+
+As we have taken halos as tracers of the cosmic web, we analyse 
+distributions of mass and peculiar velocity in order to assign typical 
+values to each type of environment. In figure 
+\ref{fig:typical_mass_velocity} we calculate both distributions for web 
+schemes and using the FOF catalogue of the simulation. Thick lines 
+correspond to the median of the distribution and filled regions limited by
+dashed lines correspond to quartiles $Q_1$ and $Q_3$, it means, $50\%$ of
+all halos are within such regions for every \lth value and for each type of
+environment. We rather use median and quartiles as measure of dispersion 
+because there are some very unusual and extreme values that makes the usual
+analysis based upon means and standard deviations less reliable.
+
+A first interesting feature of Figure  \ref{fig:typical_mass_velocity} is 
+the median mass for each region. In the case of the T-web, although 
+dispersions of the distribution of mass for each environment are 
+considerably overlapped each other, the median value is very 
+well-differentiated among types of environment, indicating that it is 
+possible to assign typical values of mass to each region, and being 
+consistent with expectations, where low mass halos are typical in voids 
+until high mass halos in knots. For the case of the V-web scheme, all
+medians and dispersions are completely overlapped, specially for values 
+grater than the optimal \lth value, indicating that it is not possible to
+assign typical mass ranges to each environment as quantified by this 
+scheme. For peculiar velocities, this situation is opposite, where V-web
+scheme is much more adequate to assign typical distributions of velocity
+to each environment. Although T-web also makes a differentiation in the 
+distributions of velocity, this is very slight compared with the V-web 
+case. These results can be explained by appealing the physical origin of 
+each web scheme. As T-web is based upon the Hessian matrix of the potential
+field, it is expected all quantities related to the potential, like density
+field and distribution of halos mass, are well-differentiated among each 
+region, while for the V-web scheme, based upon the shear velocity tensor, 
+all dynamical quantities, as the peculiar velocity field and the 
+distribution of halos velocity are alike expected to be 
+well-differentiated among regions as quantified by this scheme.
+
+Finally, we also calculate typical distributions of the density and 
+peculiar velocity fields in each type of environment, obtaining completely 
+analogous results. Furthermore, we also use a BDM catalogue of the 
+simulation, obtaining very similar conclusions.
 
@@
 
-  \captionof{figure}{\small Mean density parameter for each one of the 
-  defined environments according to the chosen $\lambda_{th}$ value and 
-  for both classification schemes. Tweb (green lines) and Vweb (blue 
-  lines). The mean density parameter is calculated by averaging all the 
-  values  of the cells determined as a certain type of environment 
-  according to its eigenvalues. The optimal parameters found are 
-  $\lambda_{opt}^{T}=0.326$ and $\lambda_{opt}^{V}=0.188$.}
+  \captionof{figure}{\small Fractions of halos embedded in each one of 
+  the defined environments according to the \lth value. T-web scheme 
+  (upper panel) and V-web scheme (lower panel). The optimal parameters 
+  found are $\lambda_{opt}^{T}=0.36$ and $\lambda_{opt}^{V}=0.20$.}
 
@@
 
-  \includegraphics[trim = 42mm 15mm 37mm 10mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
   width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
-  \includegraphics[trim = 42mm 15mm 37mm 10mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
   width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}
@@
 
+%.........................................................................
+%FIGURE 3: Typical mass and pecular velocity
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Tweb.pdf}
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Vweb.pdf}
+
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Tweb.pdf}
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Vweb.pdf}
+
+  \captionof{figure}{\small Distribution of masses of dark matter halos
+  according the region where they are embedded for both web schemes 
+  (upper panels) and of peculiar velocity (lower| panels).}
+
+  \label{fig:typical_mass_velocity}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
 \end{document}

### 2014-04-20 bench/codes_figures/halos_typical_mass.py

@@ -29,7 +29,7 @@ labels = [ 'voids', 'sheets', 'filaments', 'knots' ]
 #Typical halo mass for each environment
 #==================================================================================================
 #Colors
-plt.figure( figsize=(5,5) )
+plt.figure( figsize=(5.8,5) )
 
 #Loading files with quartiles
 quartiles = np.loadtxt( '%shalos_masses_%s_%s.dat'%(data_figures_fold,catalogue,web) )

### 2014-04-20 bench/codes_figures/halos_typical_velocity.py

@@ -28,8 +28,7 @@ labels = [ 'voids', 'sheets', 'filaments', 'knots' ]
 #==================================================================================================
 #Typical halo peculiar velocity for each environment
 #==================================================================================================
-#Colors
-plt.figure( figsize=(5,5) )
+plt.figure( figsize=(5.8,5) )
 
 #Loading files with quartiles
 quartiles = np.loadtxt( '%shalos_velocities_%s_%s.dat'%(data_figures_fold,catalogue,web) )
@@ -76,7 +75,7 @@ plt.ylabel( '$|\\vec v_{pec}\ |$ $1\\times10^2$ km s$^{-1}$', fontsize = 12 )
 plt.xlabel( '$\lambda_{th}$', fontsize = 12)
 plt.xlim( (0,1) )
 plt.ylim( (2,12) )
-plt.legend( loc='upper left', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
+plt.legend( loc='upper right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
 plt.title('%s %s'%(web, catalogue), fontweight="bold" )   
 
 if sys.argv[3] == '1':

### 2014-04-21 cosmic_voids.tex
Figures and analysis of histogram of volumes for bulk voids, for lambda_th = 0 and lambda_th = optimal.

@@
 for the T-web scheme, fractions change smoothly throughout all \lth range 
-covered. From this, it is then expected that the optimal \lth value for the 
-V-web scheme is less than the T-web value.
+covered. From this, it is then expected that the optimal \lth value for 
+the V-web scheme is less than the T-web value.
 
@@
 dashed lines correspond to quartiles $Q_1$ and $Q_3$, it means, $50\%$ of
-all halos are within such regions for every \lth value and for each type of
-environment. We rather use median and quartiles as measure of dispersion 
-because there are some very unusual and extreme values that makes the usual
-analysis based upon means and standard deviations less reliable.
+all halos are within such regions for every \lth value and for each type 
+of environment. We rather use median and quartiles as measure of 
+dispersion because there are some very unusual and extreme values that 
+makes the usual analysis based upon means and standard deviations less 
+reliable.
 
@@
 case. These results can be explained by appealing the physical origin of 
-each web scheme. As T-web is based upon the Hessian matrix of the potential
-field, it is expected all quantities related to the potential, like density
-field and distribution of halos mass, are well-differentiated among each 
-region, while for the V-web scheme, based upon the shear velocity tensor, 
-all dynamical quantities, as the peculiar velocity field and the 
-distribution of halos velocity are alike expected to be 
+each web scheme. As T-web is based upon the Hessian matrix of the 
+potential field, it is expected all quantities related to the potential, 
+like density field and distribution of halos mass, are well-differentiated 
+among each region, while for the V-web scheme, based upon the shear 
+velocity tensor, all dynamical quantities, as the peculiar velocity field 
+and the distribution of halos velocity are alike expected to be 
 well-differentiated among regions as quantified by this scheme.
@@
 
+%-------------------------------------------------------------------------
+\subsection{FOF void finder}
+\label{subsec:fof_finder}
+%-------------------------------------------------------------------------
+
 Following the recent growing interest in studying galaxy formation in 
-low-density regions, we use a method based on a FOF-like algorithm to 
-find extended regions of voids. To achieve this, we build the input 
+low-density regions as cosmological tests, we propose an scheme to find 
+bulk voids by using the two defined web schemes. Initially, we explore a 
+first simple method based on a FOF-like algorithm, where we build an input 
 catalogue for the FOF method with the coordinate of the center of every 
 cell marked as void according to the web classification scheme adopted, 
-furthermore we set an adequate linking length to connect even diagonal 
-neighbour cells.
+setting a linking length to connect diagonal neighbour cells.
 
@@
 percolation analysis in order to select the best threshold parameter that
-reduces percolation in cells, thereby accounting for physical bulk void 
-regions. In Figure \ref{fig:percolation_analysis} we show the obtained 
-result of our percolation analysis for both web schemes. In both cases, it 
-can be noticed that the volume of the largest void region is minimized and 
-the volume distribution of voids is relatively flat at $\lambda_{th} = 0.0$, 
-what means percolation is completely reduced for this threshold value. So, 
-in spite of the previously established $\lambda_{th}$ optimal values for 
-each scheme, we shall use $\lambda_{th} = 0.0$ just for the detection of 
-bulk void regions. Moreover, due to the domination of the large scale 
-visual impression by voids, it is inevitable the presence of the 
-percolation phenomenon, so the current chosen threshold value for 
-percolation is justified because though voids are necessarily connected 
-among them, we are just interested in detecting bulk regions.
-
-Next, we shall calculate the reduced inertia tensor of each void region 
-in order to determinate their principal directions of inertia and analyse 
-the size-shape distribution of voids.
-
-%.........................................................................
-%Reduced inertia tensor
-\eq{ReducedIntertia}
-{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
-%.........................................................................
-where $l$ is an index associated to each cell of to the current region, 
-$i$ and $j$ indexes run over each spatial direction and finally 
-$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$, all 
-positions are measured from the respective center of mass of the region.
-
-The eigenvalues of the reduced inertia tensor, i.e. the principal moments
-of inertia, are used to quantify the shape of void regions. They are 
-denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
-\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
-distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$, where we rather 
-calculate histograms for these ratio quantities instead of each single 
-value in order to avoid using an arbitrary normalization. For both schemes, 
-it can be noticed that the shape-distribution is completely spread out, 
-thereby indicating a non-preferred geometry of void regions, which is in 
-agreement with the well established highly anisotropy of matter flows
-associated to this type of region \SRKED{[reference here]}. Because of 
-that, we shall look for possible alignments between the plane of rotation 
-of halo pairs and the principal directions of inertia of the nearest void 
-regions.
+reduces percolation in cells. In Figure \ref{fig:percolation_analysis_FOF}
+we show the obtained result of our percolation analysis for both web 
+schemes. In both cases, it can be noticed that the volume of the largest 
+void region is minimized at $\lambda_{th} = 0.0$, what means the 
+percolation is completely reduced for this threshold value. However, 
+according to our previous analysis, such value does not reproduce the
+visual appearance of the cosmic web, so it is out of consideration.
 
@@
   according the region where they are embedded for both web schemes 
-  (upper panels) and of peculiar velocity (lower| panels).}
+  (upper panels) and of peculiar velocity (lower panels).}
 
@@
 
+%.........................................................................
+%FIGURE 4: Percolation analysis for FOF void finder
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/voids_regions_percolation_FOF.pdf}
+
+  \captionof{figure}{\small Percolation analysis of bulk void found by using
+  FOF void finder algorithm. It is swept an extensive \lth range for both web
+  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
+  volume (lower panel) and the number of bulk voids found (upper panel).}
+
+  \label{fig:percolation_analysis_FOF}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 5: Percolation analysis for FOF void finder
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
+  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}
+
+  \captionof{figure}{\small Percolation analysis of bulk void found by using
+  FOF void finder algorithm. It is swept an extensive \lth range for both web
+  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
+  volume (lower panel) and the number of bulk voids found (upper panel).}
+
+  \label{fig:volume_distributions}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
 \end{document}

### 2014-04-21 bench/codes_figures/void_FOF_regions.py

@@ -2,6 +2,7 @@
 #
 #This code calculate the dependece of the volume of the largest region with the threshold value,
 #furthermore, the number of voids.
+#Usage void_FOF_regions.py <show(0) or save(1)>
 #
 #by: Sebastian Bustamante
 
@@ -17,7 +18,9 @@ N_sec = 256
 #Smooth parameter
 smooth = '_s1'
 #Web Scheme
-webs = ['Vweb', 'Tweb'] 
+webs = ['Tweb', 'Vweb'] 
+#Colors
+colors = ['green', 'blue']
 
 #Lambda values
 Lambda_th = np.arange( 0, 1.0, 0.01 )
@@ -26,7 +29,8 @@ Lambda_th = np.arange( 0, 1.0, 0.01 )
 #			CONSTRUCTING REGIONS VOLUME
 #==================================================================================================
 
-plt.figure( figsize=(5,2*4) )
+plt.figure( figsize=(5,10) )
+i_web = 0
 for web in webs:
     print simulation, web
     
@@ -40,12 +44,29 @@ for web in webs:
 	N_voids.append( void_regs[0,-1] )
 	Vol_1void.append( void_regs[1,0]/np.sum(1.0*void_regs[1]) )
 	
+    #Number of voids
     plt.subplot( 2,1,1 )
-    plt.plot( Lambda_th, N_voids/N_voids[0], '-', linewidth = 2, label="%s"%(web) )
+    plt.plot( Lambda_th, N_voids/N_voids[0], '-', linewidth = 2, label="%s"%(web), color = colors[i_web] )
+    if web == 'Tweb':
+	lamb_opt = 0.36
+    elif web == 'Vweb':
+	lamb_opt = 0.202
+    plt.vlines( lamb_opt, 0, 2.5, linestyle = '--', color = colors[i_web], linewidth = 2 )
+    plt.text( lamb_opt + 0.02, 2.5*.5, '$\lambda_{opt}^{%s}$'%(web[0]), fontsize = 12, color = colors[i_web] )
+    plt.ylim( (0,2.5) )
     
+    #Largest volume
     plt.subplot( 2,1,2 )
-    plt.plot( Lambda_th, Vol_1void , '-', linewidth = 2 )
+    plt.plot( Lambda_th, Vol_1void , '-', linewidth = 2, color = colors[i_web] )
+    if web == 'Tweb':
[…]

### 2014-04-21 bench/codes_figures/void_volume_regions.py

@@ -2,7 +2,7 @@
 #
 #This code calculate an histogram of volumes for every found void region for the given lambda_th 
 #value
-#Usage void_volume_regions.py
+#Usage void_volume_regions.py <lambda_th=0.0(0) or lambda_th=optimal(1)> <show(0) or save(1)>
 #
 #by: Sebastian Bustamante
 
@@ -21,13 +21,16 @@ smooth = '_s1'
 webs = ['Vweb', 'Tweb'] 
 
 #Lambda value
-Lambda_th = 0.0
+if sys.argv[1] == '0':
+    Lambda_th = [ 0.0, 0.0 ]
+if sys.argv[1] == '1':
+    Lambda_th = [ 0.20, 0.36 ]
 
 #==================================================================================================
 #			CONSTRUCTING REGIONS VOLUME
 #==================================================================================================
 
-fig = plt.figure( figsize=(6,6) )
+fig = plt.figure( figsize=(5,5) )
 ax1 = fig.add_subplot(111)
 ax2 = ax1.twiny()
 
@@ -36,14 +39,17 @@ tick_locations = np.array( [0,1,2,3,4,5,6] )
 def tick_function(X):
     return ((10**X*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
 
+i_web = 0
 for web in webs:
     print simulation, web
 	    
     void_regs = np.transpose(np.loadtxt("%s/%s/%s/%d/voids%s/voids_%1.2f/void_regions.dat"%\
-    (foldglobal, simulation, web, N_sec, smooth, Lambda_th )))
-		    
-    ax1.hist( np.log10(void_regs[1]) , bins=30, linewidth = 3,\
-    label = "%s"%(web), normed = True, histtype = 'step', cumulative = False   )
+    (foldglobal, simulation, web, N_sec, smooth, Lambda_th[i_web] )))
+
+    hist1d = np.histogram( np.log10(void_regs[1]) , bins=20, normed=False	 )
+    
+    ax1.semilogy( hist1d[1][:-1], hist1d[0], linewidth = 3, label = "%s"%(web))
+    i_web += 1
     
 
 #Axe 1    
@@ -51,6 +57,7 @@ ax1.grid()
 ax1.set_ylabel( "Normed distribution" )
[…]

### 2014-04-25 cosmic_voids.tex
Analysis of shape of voids

@@
 tracer of the underlying matter field in order to be more consistent with
-available observational data. In Figure \ref{fig:halos_fractions} we 
+available observational data. In the figure \ref{fig:halos_fractions} we 
 calculate fractions of halos within each one of the defined environments 
@@
 previously established by \SRKED{Hoffman et al. (2012)} and as can be seen 
-in Figure \ref{fig:halos_fractions}, V-web scheme is significantly more 
+in the figure \ref{fig:halos_fractions}, V-web scheme is significantly more
 sensible to variations of the $\lambda_{th}$ value, since all fractions of
@@
 
-The more notorious characteristic of Figure \ref{fig:halos_fractions} is
-the behaviour of the fraction of halos within sheet regions for both web 
-schemes, increasing until a local maximum, and then decreasing. The 
+The more notorious characteristic of the figure \ref{fig:halos_fractions} 
+is the behaviour of the fraction of halos within sheet regions for both 
+web schemes, increasing until a local maximum, and then decreasing. The 
 increasing or decreasing rate of the fraction of halos for some region 
@@
 we find for the T-web scheme an optimal value $\lambda_{opt}^T = 0.36$ and
-for the V-web scheme $\lambda_{opt}^V = 0.20$. In figure 
+for the V-web scheme $\lambda_{opt}^V = 0.20$. In the figure 
 \ref{fig:visual_impression} we show the visual impression of the cosmic 
@@
 distributions of mass and peculiar velocity in order to assign typical 
-values to each type of environment. In figure 
+values to each type of environment. In the figure 
 \ref{fig:typical_mass_velocity} we calculate both distributions for web 
@@
 
-A first interesting feature of Figure  \ref{fig:typical_mass_velocity} is 
-the median mass for each region. In the case of the T-web, although 
+A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
+is the median mass for each region. In the case of the T-web, although 
 dispersions of the distribution of mass for each environment are 
@@
 
+Following the recent growing interest in studying galaxy formation in 
+low-density regions as cosmological tests, we use a simple method based on 
+a FOF-like algorithm, where we build an input catalogue for the FOF method
+with the coordinate of the center of every cell marked as void according 
+to the web classification scheme adopted, setting a linking length to 
+connect diagonal neighbour cells. Then, following the work of 
+\SRKED{Forero-Romero et al. 2008}, we perform a percolation analysis in 
+order to select the best threshold parameter that reduces percolation in 
+cells.
+
+In figure \ref{fig:percolation_analysis_FOF} we show the result of our 
+percolation analysis for both web schemes. In both cases, it can be 
+noticed that the volume of the largest void region in the lower panel is 
+minimized at $\lambda_{th} = 0$, what means that percolation is completely 
+reduced for this threshold value. Regarding the number of voids, shown in 
+the upper panel, the T-web scheme presents a expected behaviour, where the 
+number of voids decreases with \lth as the largest void absorbs minor 
+voids through percolation. For the V-web scheme, there is an anomaly 
+around the optimal \lth value, where there is a considerable increment of 
+the number of voids. In the figure \ref{fig:volume_distributions}, we 
+calculate a distribution function of the volume of voids. First for 
+$\lambda_{th}=0.0$ in the upper panel, where both schemes present similar 
+distributions, although voids in the V-web scheme are slight biased 
+towards middle volume, with a lower abundance for low volume regions than 
+voids in the T-web scheme. Secondly, in the lower panel of this figure, we 
+compute the same distribution of volumes for the optimal parameter 
+previously established for both schemes. Here, it can be noticed a 
+significant over-abundance of low volume voids for the V-web scheme 
+compared with the T-web. As it was above-mentioned from the figure 
+\ref{fig:typical_mass_velocity}, the \lth value can be associated, at 
+least indirectly, to an increase of the threshold value of the peculiar 
+velocity field, in the case of the V-web, or the density field for the 
+T-web. Therefore, the over-abundance of low volume voids for the V-web 
+implies high fluctuations in the peculiar velocity field, while the 
+density field is more robust. In the same plot, it can be noticed a lack 
+of high volume voids, what is also due to percolation, since high volume 
+voids are absorbed by the largest void.
+
+In the light of the previous results, we choose a threshold parameter 
+$\lambda_{th} = 0$ for all subsequent analysis of voids in order to avoid
+percolation and high fluctuations of the V-web scheme. In spite of this 
+value is quite different to the previously established optimal threshold
+for each scheme, bulk voids for $\lambda_{th} = 0$ are expected to be 
+the central cores of bulk voids at higher threshold values, assuming that 
+percolation could be reduced. Therefore, global properties of voids are 
+expected to maintain for $\lambda_{th} = 0$.
+
+%*************************************************************************
+\section{Properties of voids}
+\label{sec:properties}
+%*************************************************************************
+
+Once defined the proper scheme to classify bulk voids in the simulation,
+we proceed to analyse their physical properties, like the inertia values,
+the density and peculiar velocities profiles as calculated over the grid 
+and profiles of number of halos.
+
 %-------------------------------------------------------------------------
-\subsection{FOF void finder}
-\label{subsec:fof_finder}
+\subsection{Shape of voids}
+\label{subsec:shape_voids}
 %-------------------------------------------------------------------------
 
-Following the recent growing interest in studying galaxy formation in 
-low-density regions as cosmological tests, we propose an scheme to find 
-bulk voids by using the two defined web schemes. Initially, we explore a 
-first simple method based on a FOF-like algorithm, where we build an input 
-catalogue for the FOF method with the coordinate of the center of every 
-cell marked as void according to the web classification scheme adopted, 
-setting a linking length to connect diagonal neighbour cells.
+Quantifying the shape of voids is gaining importance due to cosmological 
+tests such as the Alcock-Paczynski test \SRKED{Sutter, et.al (2012)}, so 
+we compute here the reduced inertia tensor through the next expression in 
+order to determine shape distributions of bulk voids.
 
-Following the work of \SRKED{Forero-Romero et al. 2008}, we also perform a
-percolation analysis in order to select the best threshold parameter that
-reduces percolation in cells. In Figure \ref{fig:percolation_analysis_FOF}
-we show the obtained result of our percolation analysis for both web 
-schemes. In both cases, it can be noticed that the volume of the largest 
-void region is minimized at $\lambda_{th} = 0.0$, what means the 
-percolation is completely reduced for this threshold value. However, 
-according to our previous analysis, such value does not reproduce the
-visual appearance of the cosmic web, so it is out of consideration.
+%.........................................................................
+%Reduced inertia tensor
+\eq{ReducedIntertia}
+{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
+%.........................................................................
+where $l$ is an index associated to each cell of the current region, 
+$i$ and $j$ indexes run over each spatial direction and finally 
+$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$. All 
+positions are measured from the respective geometric center of each void.
 
-%*************************************************************************
-\section{Statistics of voids and influence over dark matter halos}
-\label{sec:statistics}
-%*************************************************************************
+The eigenvalues of the reduced inertia tensor, i.e. the principal moments
+of inertia, are used to quantify the shape of each bulk void. They are 
+denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
+\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
+distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$ for voids larger 
+than 8 cells in order to avoid statistic fluctuations due to small regions.
+We rather calculate histograms for these ratio quantities instead of each 
+single value in order to avoid using an arbitrary normalization. For both 
+schemes, it can be noticed that the shape distribution is completely 
+spread out, thereby indicating a non-preferred geometry of void regions, 
+which is in agreement with the well established high anisotropy of matter 
+flows associated to this type of region.
+
+For a better quantification, we also perform a classification of the shape 
+of voids by setting a threshold in the analysed ratio quantities. An 
+anisotropic or tri-axial shape correspond to voids where $\tau_1/\tau_2 < 
+0.7$ and $\tau_2/\tau_3 < 0.7$, where there is not any symmetry among the
+principal directions. We find about $57.2\% \sim 61.0\%$ of total voids 
+consistent with this shape, for the T-web and V-web respectively. A 
+pancake or quasi-oblate shape is associated to voids where $\tau_1/\tau_2 
+< 0.7$ and $\tau_2/\tau_3 > 0.7$. We found $13.1\% \sim 17.9\%$ of 
+consistent voids. Filamentary or quasi-prolate voids satisfy $\tau_1/\tau_2 
+> 0.7$ and $\tau_2/\tau_3 < 0.7$, with $25.4\% \sim 18.1\%$ of all voids.
+Finally, isotropic or quasi-spheric voids are found when $\tau_1/\tau_2 
+> 0.7$ and $\tau_2/\tau_3 > 0.7$, with $4.2\% \sim 3.1\%$ of total voids 
+compatible with this shape. The threshold value of $0.7$ adopted here for
+the ratios of the moments of inertia is just for illustrative purposes, 
+where such distinction is rather fuzzy and continuous. However, the 
+previous analysis allows us to conclude that voids are quite asymmetric 
+structures.
+
+%-------------------------------------------------------------------------
+\subsection{Density profile of voids}
+\label{subsec:density_voids}
+%-------------------------------------------------------------------------
 
@@
 \begin{flushleft}
-\begin{figure}
+\begin{figure*}
 \centering
@@
 
-\end{figure}
+\end{figure*}
 \end{flushleft}
@@
 %.........................................................................
-%FIGURE 5: Percolation analysis for FOF void finder
+%FIGURE 5: Volume functions of voids for null threshold and optimal threshold
 \begin{flushleft}
@@
   \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
+  width=0.24\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
   \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}
+  width=0.24\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}
 
-  \captionof{figure}{\small Percolation analysis of bulk void found by using
-  FOF void finder algorithm. It is swept an extensive \lth range for both web
-  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
-  volume (lower panel) and the number of bulk voids found (upper panel).}
+  \captionof{figure}{\small Volume functions of voids for both web schemes.
+  In the upper panel is shown the results for the catalogue generated at
+  $\lambda_{th} = 0.0$, while in the lower panel for the catalogue at 
+  $\lambda_{th} = \lambda_{opt}$.}
 
@@
 
+%.........................................................................
+%FIGURE 6: Distribution of eigenvalues of the inertia tensor
+\begin{flushleft}
+\begin{figure*}
+\begin{center}
+
+  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
+  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb}
+  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
+  width=0.36\textheight]{./figures/voids_inertia_tensor_Vweb}
+
+  \captionof{figure}{\small Histogram of eigenvalue ratio $\tau_1/\tau_2$
+  vs $\tau_2/\tau_3$ for the inertia tensor of void regions. T-web 
+  (upper panel) and V-web (lower panel). Number of cells per 
+  region in 2D histograms are indicated by the respective colour bar. 
+  Upper ($\tau_1/\tau_2$) and right ($\tau_2/\tau_3$) panels of each 
+  figure shows a normalized histogram of each ratio parameter. The 
+  adopted division for quantify the morphology of void regions is not
+  well justified, it should be understood as a fuzzy and continuous 
+  limit, done just for illustrative purposes.}
+
+  \label{fig:distro_inertia}
+  \vspace{0.1 cm}
+
+\end{center}
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
 \end{document}

### 2014-04-28 bench/codes_analysis/Density_L1_Correlation.c
Code to calculate correspondece between fractional anisotropy and Lambda_th

@@ -1,0 +1,173 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#define FLOAT1 float
+#define FLOAT2 double
+#define NMAX1 1000
+
+//Usage  Density_L3_Correlation.out <eig_filename> <delta_filename> <Lambda min> <Lambda max> 
+// 				    <number of lambda bins> <delta min> <delta max> <number of delta bins>
+
+int main(int argc, char **argv)
+{   
+    FILE *in, *out_count;
+    FLOAT1 *eigen1, *eigen2, *eigen3;
+    FLOAT2 *delta;
+    char filename[100];
+    int eig;
+    
+    float lambda_min, lambda_max, delta_min, delta_max;
+    int N_delta, N_lambda, i_lm, i_delta;
+    float count[NMAX1][NMAX1];
+    float lamb, lamb_f;
+    double delta_f, delta_i;
+    
+    //Grid variables===============================================================================
+    int dumb;
+    char line[30];
+    long long i;
+    int n_x, n_y, n_z;
+    int n_nodes;
+    long long n_total;
+    float dx, dy, dz, x_0, y_0, z_0;
+    //=============================================================================================
+    
+    
+    //PARAMETERS===================================================================================
+    //Lambdas Range
+    lambda_min = atof( argv[3] );
+    lambda_max = atof( argv[4] );
+    //Number of divisions in Lambda
+    N_lambda = atoi( argv[5] );
+    //Delta Range
+    delta_min = atof( argv[6] );
+    delta_max = atof( argv[7] );
+    //Number of divisions in delta
+    N_delta = atoi( argv[8] );
+    //=============================================================================================
+        
+        
+    //LOADING EIGENVALUES==========================================================================
+    for( eig=0; eig<3; eig++ ){
+        //filename of current eigenvalue
+ 	sprintf(filename, "%s_%d", argv[1], eig + 1);
[…]

### 2014-04-28 bench/codes_analysis/FA_L1_correlation.py

@@ -1,0 +1,77 @@
+#FA_L1_correlation.py
+#
+#This code builds a matrix of correlations regarding FA and lambda_1 value
+#Usage: FA_L1_correlation.py <Tweb or Vweb>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+web = sys.argv[1]
+#Lambda_min
+Lambda_min = -1
+#Lambda_max
+Lambda_max = 1
+#N lambda
+N_lamb = 100
+#FA_min
+FA_min = 0
+#FA_max
+FA_max = 1.0
+#N FA
+N_FA = 200
+
+#Arrays
+Lambda = np.linspace( Lambda_min, Lambda_max, N_lamb )
+FA = np.linspace( FA_min, FA_max, N_FA )
+
+#==================================================================================================
+#			CONSTRUCTING MEDIANS OF FA REGARDING LAMBDA_1
+#==================================================================================================
+
+print simulation
+
+#Loading eigenvalues
+eigV_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
+
+
+#Building the matrix      
+FA_L1 = FA_lambda1_correlation( eigV_filename, Lambda_min, Lambda_max, N_lamb, FA_min, FA_max, N_FA )
+
+#Initializing counters
+Quartiles = np.zeros( (N_lamb,3) )
+for i_l in xrange( N_lamb ):
+      FA_L1[i_l,:] = np.cumsum( FA_L1[i_l,:] )
+      FA_L1[i_l,:] /= FA_L1[i_l,-1]
+      median = True
+      Q1 = True
+      Q3 = True
+      for i_fa in xrange( N_FA ):
+	  #Finding Median
+	  if FA_L1[i_l,i_fa] > 0.5 and median:
+	      median = False
+	      Quartiles[i_l,1] = FA[i_fa]
+	  #Finding Q1
+	  if FA_L1[i_l,i_fa] > 0.25 and Q1:
+	      Q1 = False
+	      Quartiles[i_l,0] = FA[i_fa]
[…]

### 2014-04-28 bench/codes_analysis/_Head.py

@@ -462,6 +462,25 @@ def void_matrix_builder( filename_eig, Lambda_th, N, outname ):
     #datos = datos.reshape( (N, N, N) )
     return 0
     
+#..................................................................................................
+#FA anisotropy correlator
+#..................................................................................................
+def FA_lambda1_correlation( filename_eig, lamb_min, lamb_max, N_lam, FA_min, FA_max, N_FA ):
+    os.system( "./FA_L1_Correlation.out %s %f %f %d %f %f %d"%
+    ( filename_eig, lamb_min, lamb_max, N_lam, FA_min, FA_max, N_FA ) )
+    datos = np.loadtxt( "temp.tmp" )
+    os.system( "rm temp.tmp" )
+    return datos
+
+#..................................................................................................
+#Density correlator
+#..................................................................................................
+def density_lambda1_correlation( filename_eig, delta_file, lamb_min, lamb_max, N_lam, lambda_min, lambda_max, N_lambda ):
+    os.system( "./Density_L1_Correlation.out %s %s %f %f %d %f %f %d"%
+    ( filename_eig, delta_file, lamb_min, lamb_max, N_lam, lambda_min, lambda_max, N_lambda ) )
+    datos = np.loadtxt( "temp.tmp" )
+    #os.system( "rm temp.tmp" )
+    return datos
 
 #..................................................................................................
 #Void Finder

### 2014-04-28 bench/codes_analysis/density_L1_correlation.py

@@ -1,0 +1,79 @@
+#density_L1_correlation.py
+#
+#This code builds a matrix of correlations regarding density field and lambda_1 value
+#Usage: density_L1_correlation.py <Tweb or Vweb>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+web = sys.argv[1]
+#Lambda_min
+Lambda_min = -1
+#Lambda_max
+Lambda_max = 1
+#N lambda
+N_lamb = 100
+#Delta_min
+delta_min = -1.0
+#Delta_max
+delta_max = 1.0
+#N delta
+N_delta = 200
+
+#Arrays
+Lambda = np.linspace( Lambda_min, Lambda_max, N_lamb )
+delta = np.linspace( delta_min, delta_max, N_delta )
+
+#==================================================================================================
+#			CONSTRUCTING MEDIANS OF DENSITY REGARDING LAMBDA_1
+#==================================================================================================
+
+print simulation
+
+#Loading eigenvalues
+eigV_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
+
+#Loading density
+delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,simulation,N_sec,smooth)
+
+#Building the matrix      
+delta_L1 = density_lambda1_correlation( eigV_filename, delta_filename, Lambda_min, Lambda_max, N_lamb, delta_min, delta_max, N_delta )
+
+#Initializing counters
+Quartiles = np.zeros( (N_lamb,3) )
+for i_l in xrange( N_lamb ):
+      delta_L1[i_l,:] = np.cumsum( delta_L1[i_l,:] )
+      delta_L1[i_l,:] /= delta_L1[i_l,-1]
+      median = True
+      Q1 = True
+      Q3 = True
+      for i_fa in xrange( N_delta ):
+	  #Finding Median
+	  if delta_L1[i_l,i_fa] > 0.5 and median:
+	      median = False
[…]

### 2014-04-28 time-machine/cosmic_voids(24-04-14).tex
time machine

--- 2014-04-21 cosmic_voids.tex
@@
 
-%-------------------------------------------------------------------------
-\subsection{FOF void finder}
-\label{subsec:fof_finder}
-%-------------------------------------------------------------------------
-
 Following the recent growing interest in studying galaxy formation in 
@@
 percolation analysis in order to select the best threshold parameter that
-reduces percolation in cells. In Figure \ref{fig:percolation_analysis_FOF}
-we show the obtained result of our percolation analysis for both web 
-schemes. In both cases, it can be noticed that the volume of the largest 
-void region is minimized at $\lambda_{th} = 0.0$, what means the 
-percolation is completely reduced for this threshold value. However, 
-according to our previous analysis, such value does not reproduce the
-visual appearance of the cosmic web, so it is out of consideration.
+reduces percolation in cells. In the left panels of the figure 
+\ref{fig:percolation_analysis_FOF} we show the result of our percolation 
+analysis for both web schemes. In both cases, it can be noticed that the 
+volume of the largest void region is minimized at $\lambda_{th} = 0.0$, 
+what means that percolation is completely reduced for this threshold 
+value. However, according to our previous analysis, such value does not 
+reproduce the visual appearance of the cosmic web, so it is out of 
+consideration.
 
@@
   width=0.25\textheight]{./figures/voids_regions_percolation_FOF.pdf}
+  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/voids_regions_percolation_LAY.pdf}
 
@@
   \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
+  width=0.24\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
   \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}
+  width=0.24\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}
+  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_regions_volume_LAY_opt.pdf}
 

### 2014-04-28 time-machine/cosmic_voids(28-04-14).tex
time machine

--- 2014-04-25 cosmic_voids.tex
@@
 Quantifying the shape of voids is gaining importance due to cosmological 
-tests such as the Alcock-Paczynski test \SRKED{Sutter, et.al (2012)}, so 
+tests such as the Alcock-Paczynski test \SRKED{[Sutter, et.al (2012)]}, so 
 we compute here the reduced inertia tensor through the next expression in 
@@
 %-------------------------------------------------------------------------
+
+Describing the density profiles of voids is quite important in order to 
+compare and match simulation with observational surveys, allowing possible
+constrains for different cosmology models \SRKED{[Hamaous, et.al 2014]}. 
+Here, and taking into account the previous results, we rather use an 
+ellipsoidal approximation to describe and fit the shape of bulk voids, so 
+we use the next ellipsoidal radial coordinate to describe density profiles.
+
+%.........................................................................
+%Ellipsoidal radial coordinate
+\eq{radial_coordinate}
+{
+r^2 = \frac{x^2}{\tau_1^2} + \frac{y^2}{\tau_2^2} + \frac{z^2}{\tau_3^2},
+\ \ \ \ 0\leq r \leq 1
+}
+%.........................................................................
+where we take the principal moments of inertia $\{\tau_i \}$ as the 
+lengths of the principal axes of the ellipsoid and each one of the 
+cartesian coordinates as measured in the rotated frame of each void.
+
+We use the same analytic density profile that \SRKED{[Hamaous, et.al 2014]} 
+to fit the numerical density profiles of our voids.
+
+%.........................................................................
+%Density profile
+\eq{density_profile}
+{
+\delta_v(r) = \delta_c\frac{1-(r/r_s)^\alpha}{1+(r/r_v)^\beta}
+}
+%.........................................................................
 

### 2014-04-29 cosmic_voids.tex
Analysis of FA field slides

--- 2014-04-21 cosmic_voids.tex
@@
 tracer of the underlying matter field in order to be more consistent with
-available observational data. In Figure \ref{fig:halos_fractions} we 
-calculate fractions of halos within each one of the defined environments 
-based upon the FOF catalogue of the simulation and for an extensive \lth 
-range. Then we look for some key feature that could indicated us a 
-possible optimal value of the \lth value. One first step forward our quest 
-is the behaviour of the V-web scheme compared with the T-web. As was 
-previously established by \SRKED{Hoffman et al. (2012)} and as can be seen 
-in Figure \ref{fig:halos_fractions}, V-web scheme is significantly more 
-sensible to variations of the $\lambda_{th}$ value, since all fractions of
-halos for the V-web change significantly in the range $[0,0.4]$, whereas, 
-for the T-web scheme, fractions change smoothly throughout all \lth range 
-covered. From this, it is then expected that the optimal \lth value for 
-the V-web scheme is less than the T-web value.
+available observational data. First, we analyse distributions of mass and 
+peculiar velocity in order to assign typical values to each type of 
+environment. In the figure \ref{fig:typical_mass_velocity} we calculate 
+both distributions for web schemes and using the FOF catalogue of the 
+simulation. Thick lines correspond to the median of the distribution and 
+filled regions limited by dashed lines correspond to quartiles $Q_1$ and 
+$Q_3$, it means, $50\%$ of all halos are within such regions for every 
+\lth value and for each type of environment. We rather use median and 
+quartiles as measure of dispersion because there are some very unusual and 
+extreme values that makes the usual analysis based upon means and standard 
+deviations less reliable.
 
-The more notorious characteristic of Figure \ref{fig:halos_fractions} is
-the behaviour of the fraction of halos within sheet regions for both web 
-schemes, increasing until a local maximum, and then decreasing. The 
-increasing or decreasing rate of the fraction of halos for some region 
-could be interpreted as a measure of the degree of non-linearity of such 
-region for some specific \lth value. For example, filaments and knots, 
-that are the most non-linear regions of the universe, have a negative rate
-for all covered \lth range. In the case of voids, the situation is 
-completely opposite, where fractions of halos increase in everywhere. If 
-we think in terms of the underlying matter field of the cosmic web, \lth 
-is just a cutting parameter between high non-linear regions (filament and 
-knots) and low non-linear (voids and sheets). Furthermore, if we take into 
-account that dark matter halos are much more likely to form in high 
-non-linear regions, it is expected the obtained behaviour of fractions of 
-halos for voids, filaments and knots as we increase the \lth value. 
-However, the behaviour of the fraction of halos in sheets is less clear,
-increasing for low \lth values (like voids) and decreasing for higher \lth 
-values (like filaments and knots). This indicates us the transitional 
-character of sheet regions in the cosmic web. Our proposal here is to 
-select as optimal \lth the value where the fraction of sheets reaches a
-local maximum, so sheets are completely taken as intermediate transitional 
-and neutral zones regarding the degree of non-linearity. According to this,
-we find for the T-web scheme an optimal value $\lambda_{opt}^T = 0.36$ and
-for the V-web scheme $\lambda_{opt}^V = 0.20$. In figure 
-\ref{fig:visual_impression} we show the visual impression of the cosmic 
-web along with the density field for different \lth values including the 
-optimal values. It can be noticed that the optimal values found reproduce 
-well the visual impression.
-
-As we have taken halos as tracers of the cosmic web, we analyse 
-distributions of mass and peculiar velocity in order to assign typical 
-values to each type of environment. In figure 
-\ref{fig:typical_mass_velocity} we calculate both distributions for web 
-schemes and using the FOF catalogue of the simulation. Thick lines 
-correspond to the median of the distribution and filled regions limited by
-dashed lines correspond to quartiles $Q_1$ and $Q_3$, it means, $50\%$ of
-all halos are within such regions for every \lth value and for each type 
-of environment. We rather use median and quartiles as measure of 
-dispersion because there are some very unusual and extreme values that 
-makes the usual analysis based upon means and standard deviations less 
-reliable.
-
-A first interesting feature of Figure  \ref{fig:typical_mass_velocity} is 
-the median mass for each region. In the case of the T-web, although 
+A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
+is the median mass for each region. In the case of the T-web, although 
 dispersions of the distribution of mass for each environment are 
@@
 Finally, we also calculate typical distributions of the density and 
-peculiar velocity fields in each type of environment, obtaining completely
-analogous results. Furthermore, we also use a BDM catalogue of the 
-simulation, obtaining very similar conclusions.
+peculiar velocity fields on the volume cells associated to each type of 
+environment, obtaining completely analogous results. Furthermore, we use a 
+BDM catalogue of the simulation as well, obtaining very similar conclusions.
 
@@
 
+According to the recent growing interest in studying galaxy formation in 
+low-density regions as cosmological tests, classifying void regions is 
+becoming an important task in cosmology. Most of those classification 
+schemes for voids in cosmological simulations are based upon the density 
+field, setting a cut off value below which some region becomes a void 
+\SRKED{[references]}. Some more advanced classification schemes are based 
+on Voronoi tessellations applied over the tracer particles of the 
+simulation in order to compute the density field. Then, through a watershed 
+transform, a hierarchy of void regions are found \SRKED{[references, 
+ZOBOV algorithm]}.
+
+As has been established \SRKED{[references]}, both schemes presented in
+the previous section (V-web and T-web) for classifying the cosmic web 
+present many advantages compared with classification schemes based
+completely upon the density field, e.g. a more robust description of the
+dynamic a kinematic of the cosmic web, a more reliable quantification of 
+the visual impression, among others. With the aim of exploiting all of 
+these advantages, we propose here a novel approach to classify voids in
+cosmological simulations based entirely on the web schemes.
+
+The original version of the T-web scheme \SRKED{[reference, Hahn]} was not
+successful at reproducing the visual impression of the cosmic web, 
+however, with the introduction of a threshold parameter \SRKED{[reference, 
+Forero-Romero]}, this scheme, and even the V-web \SRKED{[reference, 
+Hoffman]}, improved enormously. As this free parameter controls the visual 
+impression provided by each scheme, phenomenons like percolation depends 
+on it as well. Percolation is one of the key features of the structure of 
+void regions, indicating how voids are merged among them, and how they 
+permeate all the cosmic web.
+
+In order to overcome the percolation of voids in our classification scheme,
+we introduce the fractional anisotropy as defined in \SRKED{[reference, 
+Libeskind]}.
+
+%.........................................................................
+%Fractional anisotropy
+\eq{fractional_anisotropy}
+{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
+(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
+\lambda_2^2 + \lambda_3^2} } }
+%.........................................................................
+where the eigenvalues are taken from any of the two web schemes. This 
+index, such as it is defined, allows quantifying the local anisotropy 
+degree of the cosmological environment, where $FA=0$ corresponds to highly
+isotropic regions and $FA=1$ anisotropic ones.
+
+In the figure \ref{fig:FA_field} we calculate the FA field over the 
+simulation for both web schemes. The first interesting feature of this
+figure is the degeneration presented for knots and central regions of 
+voids, where both of them exhibit low to middle values of the FA, 
+indicating a high isotropy regarding the physical property quantified by 
+each web scheme, i.e. the density field for the T-web and the peculiar 
+velocity for the V-web. For the T-web, the FA field around knots presents 
+a very narrow distribution, whereas for the V-web the same distribution is
+more spread. This can be explained appealing to the low dispersion of the 
+density field with respect to the peculiar velocity in highly non-linear 
+regions like knots. For more linear regions like voids, the behaviour of 
+the FA field is quite similar between both schemes, what is consistent 
+with the equivalence of the T-web and the V-web in the linear regime 
+\SRKED{[reference, Hoffman]}.
+
+According to the classification scheme adopted for the cosmological 
+environment, voids are regions where 
+$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$, this implies that
+the boundaries of void regions are controlled completely by the $\lambda_1$
+eigenvalue of the web scheme and the threshold value. Therefore, as we 
+increase the threshold value $\lambda_th$, all voids grow up progressively 
+through contours of $\lambda_3$ field until certain critical value where 
+voids are very large so the visual impression is no longer reliable.
+
+%*************************************************************************
+\section{Properties of voids}
+\label{sec:properties}
+%*************************************************************************
+
+Once defined the proper scheme to classify bulk voids in the simulation,
+we proceed to analyse their physical properties, like the inertia values,
+the density and peculiar velocities profiles as calculated over the grid 
+and profiles of number of halos.
+
 %-------------------------------------------------------------------------
-\subsection{FOF void finder}
-\label{subsec:fof_finder}
+\subsection{Shape of voids}
+\label{subsec:shape_voids}
 %-------------------------------------------------------------------------
 
-Following the recent growing interest in studying galaxy formation in 
-low-density regions as cosmological tests, we propose an scheme to find 
-bulk voids by using the two defined web schemes. Initially, we explore a 
-first simple method based on a FOF-like algorithm, where we build an input 
-catalogue for the FOF method with the coordinate of the center of every 
-cell marked as void according to the web classification scheme adopted, 
-setting a linking length to connect diagonal neighbour cells.
+Quantifying the shape of voids is gaining importance due to cosmological 
+tests such as the Alcock-Paczynski test \SRKED{[Sutter, et.al (2012)]}, so 
+we compute here the reduced inertia tensor through the next expression in 
+order to determine shape distributions of bulk voids.
 
-Following the work of \SRKED{Forero-Romero et al. 2008}, we also perform a
-percolation analysis in order to select the best threshold parameter that
-reduces percolation in cells. In Figure \ref{fig:percolation_analysis_FOF}
-we show the obtained result of our percolation analysis for both web 
-schemes. In both cases, it can be noticed that the volume of the largest 
-void region is minimized at $\lambda_{th} = 0.0$, what means the 
-percolation is completely reduced for this threshold value. However, 
-according to our previous analysis, such value does not reproduce the
-visual appearance of the cosmic web, so it is out of consideration.
+%.........................................................................
+%Reduced inertia tensor
+\eq{ReducedIntertia}
+{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
+%.........................................................................
+where $l$ is an index associated to each cell of the current region, 
+$i$ and $j$ indexes run over each spatial direction and finally 
+$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$. All 
+positions are measured from the respective geometric center of each void.
 
-%*************************************************************************
-\section{Statistics of voids and influence over dark matter halos}
-\label{sec:statistics}
-%*************************************************************************
+The eigenvalues of the reduced inertia tensor, i.e. the principal moments
+of inertia, are used to quantify the shape of each bulk void. They are 
+denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
+\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
+distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$ for voids larger 
+than 8 cells in order to avoid statistic fluctuations due to small regions.
+We rather calculate histograms for these ratio quantities instead of each 
+single value in order to avoid using an arbitrary normalization. For both 
+schemes, it can be noticed that the shape distribution is completely 
+spread out, thereby indicating a non-preferred geometry of void regions, 
+which is in agreement with the well established high anisotropy of matter 
+flows associated to this type of region.
+
+For a better quantification, we also perform a classification of the shape 
+of voids by setting a threshold in the analysed ratio quantities. An 
+anisotropic or tri-axial shape correspond to voids where $\tau_1/\tau_2 < 
+0.7$ and $\tau_2/\tau_3 < 0.7$, where there is not any symmetry among the
+principal directions. We find about $57.2\% \sim 61.0\%$ of total voids 
+consistent with this shape, for the T-web and V-web respectively. A 
+pancake or quasi-oblate shape is associated to voids where $\tau_1/\tau_2 
+< 0.7$ and $\tau_2/\tau_3 > 0.7$. We found $13.1\% \sim 17.9\%$ of 
+consistent voids. Filamentary or quasi-prolate voids satisfy $\tau_1/\tau_2 
+> 0.7$ and $\tau_2/\tau_3 < 0.7$, with $25.4\% \sim 18.1\%$ of all voids.
+Finally, isotropic or quasi-spheric voids are found when $\tau_1/\tau_2 
+> 0.7$ and $\tau_2/\tau_3 > 0.7$, with $4.2\% \sim 3.1\%$ of total voids 
+compatible with this shape. The threshold value of $0.7$ adopted here for
+the ratios of the moments of inertia is just for illustrative purposes, 
+where such distinction is rather fuzzy and continuous. However, the 
+previous analysis allows us to conclude that voids are quite asymmetric 
+structures.
+
+%-------------------------------------------------------------------------
+\subsection{Density profile of voids}
+\label{subsec:density_voids}
+%-------------------------------------------------------------------------
+
+Describing the density profiles of voids is quite important in order to 
+compare and match simulation with observational surveys, allowing possible
+constrains for different cosmology models \SRKED{[Hamaous, et.al 2014]}. 
+Here, and taking into account the previous results, we rather use an 
+ellipsoidal approximation to describe and fit the shape of bulk voids, so 
+we use the next ellipsoidal radial coordinate to describe density profiles.
+
+%.........................................................................
+%Ellipsoidal radial coordinate
+\eq{radial_coordinate}
+{
+r^2 = \frac{x^2}{\tau_1^2} + \frac{y^2}{\tau_2^2} + \frac{z^2}{\tau_3^2},
+\ \ \ \ 0\leq r \leq 1
+}
+%.........................................................................
+where we take the principal moments of inertia $\{\tau_i \}$ as the 
+lengths of the principal axes of the ellipsoid and each one of the 
+cartesian coordinates as measured in the rotated frame of each void.
+
+We use the same analytic density profile that \SRKED{[Hamaous, et.al 2014]} 
+to fit the numerical density profiles of our voids.
+
+%.........................................................................
+%Density profile
+\eq{density_profile}
+{
+\delta_v(r) = \delta_c\frac{1-(r/r_s)^\alpha}{1+(r/r_v)^\beta}
+}
+%.........................................................................
 
@@
 %.........................................................................
-%FIGURE 1: Fraction of halos in each environment
-\begin{flushleft}
-\begin{figure}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}
-
-  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}
-
-  \captionof{figure}{\small Fractions of halos embedded in each one of 
-  the defined environments according to the \lth value. T-web scheme 
-  (upper panel) and V-web scheme (lower panel). The optimal parameters 
-  found are $\lambda_{opt}^{T}=0.36$ and $\lambda_{opt}^{V}=0.20$.}
-
-  \label{fig:halos_fractions}
-  \vspace{0.1 cm}
-
-\end{figure}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 2: Visual impression of the cosmic web
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
-  width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
-  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
-  width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}
-
-  \captionof{figure}{\small Visual impression of the density field (left 
-  panels), and of each classification scheme with the $\lambda_{th}$ values 
-  obtained by our criteria (others panels). The color convention for each 
-  environment is (white) - void, (light gray) - sheet, (gray) - filament, 
-  (black) - knot. For each web scheme, it has been used the previously 
-  established optimal threshold as a reference value, so plots are done 
-  with the next values $\lambda_{th} = 0.0$, $\lambda_{th} = 
-  \lambda_{opt}/2$, $\lambda_{th} = \lambda_{opt}$ and $\lambda_{th} = 
-  2\lambda_{opt}$.}
-
-  \label{fig:visual_impression}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 3: Typical mass and pecular velocity
+%FIGURE 1: Typical mass and pecular velocity
 \begin{flushleft}
@@
   according the region where they are embedded for both web schemes 
-  (upper panels) and of peculiar velocity (lower panels).}
+  (upper panels) and of peculiar velocity (lower panels). It can be 
+  noticed that the T-web scheme selects different mass ranges according
+  to the environment, while the V-web scheme is better selecting ranges
+  of peculiar velocity of the dark matter halos. This can be understood
+  taking into account the physical origin of each web scheme.}
 
@@
 %.........................................................................
-%FIGURE 4: Percolation analysis for FOF void finder
+%FIGURE 2: Typical mass and pecular velocity
 \begin{flushleft}
@@
 
-  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_regions_percolation_FOF.pdf}
+  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
+  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb(null).pdf}
 
-  \captionof{figure}{\small Percolation analysis of bulk void found by using
-  FOF void finder algorithm. It is swept an extensive \lth range for both web
-  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
-  volume (lower panel) and the number of bulk voids found (upper panel).}
+  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
+  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb(null).pdf}
 
-  \label{fig:percolation_analysis_FOF}
-  \vspace{0.1 cm}
+  \captionof{figure}{\small In left panels is shown the visual impression 
+  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
+  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
+  defined type of environments, where voids corresponds to white zones, 
+  sheets to gray, filaments to dark gray and finally knots to black regions. 
+  In the right panels is shown the fractional anisotropy field for the same 
+  slide of the simulation and for each web schemes, where black regions 
+  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
+  degeneration of low values of FA for knots and central regions of voids, 
+  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
+  and highly planar sheets.}
 
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 5: Percolation analysis for FOF void finder
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
-  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}
-
-  \captionof{figure}{\small Percolation analysis of bulk void found by using
-  FOF void finder algorithm. It is swept an extensive \lth range for both web
-  schemes. T-web (blue lines) and  V-web (green lines). Plot of the largest 
-  volume (lower panel) and the number of bulk voids found (upper panel).}
-
-  \label{fig:volume_distributions}
+  \label{fig:FA_field}
   \vspace{0.1 cm}

### 2014-04-30 bench/codes_analysis/FA_L1_correlation.py
Modifying codes to include a larger range of Lambda_1 for density and FA correlations

@@ -21,9 +21,9 @@ web = sys.argv[1]
 #Lambda_min
 Lambda_min = -1
 #Lambda_max
-Lambda_max = 1
+Lambda_max = 2
 #N lambda
-N_lamb = 100
+N_lamb = 200
 #FA_min
 FA_min = 0
 #FA_max
@@ -49,29 +49,30 @@ eigV_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
 FA_L1 = FA_lambda1_correlation( eigV_filename, Lambda_min, Lambda_max, N_lamb, FA_min, FA_max, N_FA )
 
 #Initializing counters
-Quartiles = np.zeros( (N_lamb,3) )
+Quartiles = np.zeros( (N_lamb,4) )
 for i_l in xrange( N_lamb ):
       FA_L1[i_l,:] = np.cumsum( FA_L1[i_l,:] )
       FA_L1[i_l,:] /= FA_L1[i_l,-1]
       median = True
       Q1 = True
       Q3 = True
+      Quartiles[i_l,0] = Lambda[i_l]
       for i_fa in xrange( N_FA ):
 	  #Finding Median
 	  if FA_L1[i_l,i_fa] > 0.5 and median:
 	      median = False
-	      Quartiles[i_l,1] = FA[i_fa]
+	      Quartiles[i_l,2] = FA[i_fa]
 	  #Finding Q1
 	  if FA_L1[i_l,i_fa] > 0.25 and Q1:
 	      Q1 = False
-	      Quartiles[i_l,0] = FA[i_fa]
+	      Quartiles[i_l,1] = FA[i_fa]
 	  #Finding Q3
 	  if FA_L1[i_l,i_fa] > 0.75 and Q3:
 	      Q3 = False
-	      Quartiles[i_l,2] = FA[i_fa]
+	      Quartiles[i_l,3] = FA[i_fa]
 
 np.savetxt( '%sFA_L1_%s.dat'%(data_figures_fold,web), Quartiles )
 
-plt.fill_between( Lambda, Quartiles[:,0], Quartiles[:,2], alpha = 0.5 )
-plt.plot( Lambda, Quartiles[:,1], "-" )
+plt.fill_between( Lambda, Quartiles[:,1], Quartiles[:,3], alpha = 0.5 )
+plt.plot( Lambda, Quartiles[:,2], "-" )
 plt.show()

### 2014-04-30 bench/codes_analysis/density_L1_correlation.py

@@ -21,9 +21,9 @@ web = sys.argv[1]
 #Lambda_min
 Lambda_min = -1
 #Lambda_max
-Lambda_max = 1
+Lambda_max = 2
 #N lambda
-N_lamb = 100
+N_lamb = 200
 #Delta_min
 delta_min = -1.0
 #Delta_max
@@ -51,29 +51,30 @@ delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,simulation,N_sec,smooth)
 delta_L1 = density_lambda1_correlation( eigV_filename, delta_filename, Lambda_min, Lambda_max, N_lamb, delta_min, delta_max, N_delta )
 
 #Initializing counters
-Quartiles = np.zeros( (N_lamb,3) )
+Quartiles = np.zeros( (N_lamb,4) )
 for i_l in xrange( N_lamb ):
       delta_L1[i_l,:] = np.cumsum( delta_L1[i_l,:] )
       delta_L1[i_l,:] /= delta_L1[i_l,-1]
       median = True
       Q1 = True
       Q3 = True
+      Quartiles[i_l,0] = Lambda[i_l]
       for i_fa in xrange( N_delta ):
 	  #Finding Median
 	  if delta_L1[i_l,i_fa] > 0.5 and median:
 	      median = False
-	      Quartiles[i_l,1] = delta[i_fa]
+	      Quartiles[i_l,2] = delta[i_fa]
 	  #Finding Q1
 	  if delta_L1[i_l,i_fa] > 0.25 and Q1:
 	      Q1 = False
-	      Quartiles[i_l,0] = delta[i_fa]
+	      Quartiles[i_l,1] = delta[i_fa]
 	  #Finding Q3
 	  if delta_L1[i_l,i_fa] > 0.75 and Q3:
 	      Q3 = False
-	      Quartiles[i_l,2] = delta[i_fa]
+	      Quartiles[i_l,3] = delta[i_fa]
 
 np.savetxt( '%sdelta_L1_%s.dat'%(data_figures_fold,web), Quartiles )
 
-plt.fill_between( Lambda, Quartiles[:,0], Quartiles[:,2], alpha = 0.5 )
-plt.plot( Lambda, Quartiles[:,1], "-" )
+plt.fill_between( Lambda, Quartiles[:,1], Quartiles[:,3], alpha = 0.5 )
+plt.plot( Lambda, Quartiles[:,2], "-" )
 plt.show()

### 2014-04-30 bench/codes_figures/FA_L1_correlation.py

@@ -1,0 +1,66 @@
+#FA_L1_correlation.py
+#
+#This code plots the correlation between the fractional anisotropy and the eigenvalue L1 of each 
+#web scheme
+#Usage: FA_L1_correlation.py <show(0) or save(1)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+webs = ['Tweb', 'Vweb']
+#Colors and labels
+colors = [ 'red', 'blue' ]
+
+#==================================================================================================
+#Typical halo mass for each environment
+#==================================================================================================
+#Colors
+plt.figure( figsize=(5.8,5) )
+
+i_web = 0
+for web in webs:
+    #Loading files with quartiles
+    quartiles = np.loadtxt( '%sFA_L1_%s.dat'%(data_figures_fold,web) )
+
+    #Quartiles regions-------
+    plt.fill_between( quartiles[:,0], quartiles[:,1], quartiles[:,3], color = colors[i_web], alpha = 0.2 )
+    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = '--' )
+    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = '--' )
+
+    #Medians-----------------
+    plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i_web], linewidth = 3, label = web )
+    
+    plt.grid(1)
+    plt.ylabel( 'FA', fontsize = 12 )
+    plt.xlabel( '$\lambda_{3}$', fontsize = 12)
+    plt.xlim( (-0.3,2) )
+    plt.ylim( (0,1) )
+    plt.legend( loc='lower right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
+    #Lambda_th line
+    if web == 'Tweb':
+	lamb_opt = 0.36
+    elif web == 'Vweb':
+	lamb_opt = 0.202
[…]

### 2014-04-30 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -26,7 +26,7 @@ if web == 'Tweb':
     Lambda_opt = 0.36
 if web == 'Vweb':
     Lambda_opt = 0.20
-#Lambda_opt = 0
+Lambda_opt = 0
 #Smooth parameter
 smooth = '_s1'
 #Coordinate to cut (1 -- X, 2 -- Y, 3 -- Z)
@@ -72,13 +72,15 @@ plt.imshow( -Scheme( eig1, eig2, eig3, Lambda_opt ), extent = extent, vmin=-3, v
 plt.title( "Vissual impresion for $\lambda_{th} = %1.3f$"%(Lambda_opt) )
 plt.yticks( (),() )
 plt.xticks( (0,Box_L) )
+plt.xlabel( "[$h^{-1}$ Mpc]" )
 
 #Vweb Plot with Lambda_th = 0
 plt.subplot( 2, 2, 2 )
-plt.imshow( 10**(Fractional_Anisotropy( eig1, eig2, eig3 )), extent = extent,  cmap = "binary" )
+plt.imshow( Fractional_Anisotropy( eig1, eig2, eig3 ), extent = extent,  cmap = "binary" )
 plt.title( "Fractional\nAnisotropy" )
 plt.yticks( (),() )
 plt.xticks( (0,Box_L) )
+plt.xlabel( "[$h^{-1}$ Mpc]" )
 
 #Vweb Plot with Lambda_th = 0.1
 plt.subplot( 2, 2, 3 )

### 2014-04-30 bench/codes_figures/delta_L1_correlation.py

@@ -1,0 +1,63 @@
+#delta_L1_correlation.py
+#
+#This code plots the correlation between the density and the eigenvalue L1 of each web scheme
+#Usage: FA_L1_correlation.py <show(0) or save(1)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+webs = ['Tweb', 'Vweb']
+#Colors and labels
+colors = [ 'red', 'blue' ]
+
+#==================================================================================================
+#Typical halo mass for each environment
+#==================================================================================================
+#Colors
+plt.figure( figsize=(5.8,5) )
+
+i_web = 0
+for web in webs:
+    #Loading files with quartiles
+    quartiles = np.loadtxt( '%sdelta_L1_%s.dat'%(data_figures_fold,web) )
+    
+    #Quartiles regions-------
+    plt.fill_between( quartiles[:,0], quartiles[:,1], quartiles[:,3], color = colors[i_web], alpha = 0.2 )
+    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = '--' )
+    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = '--' )
+
+    #Medians-----------------
+    plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i_web], linewidth = 3, label = web )
+
+    plt.grid(1)
+    plt.ylabel( '$\\rho$', fontsize = 12 )
+    plt.xlabel( '$\lambda_{3}$', fontsize = 12)
+    plt.xlim( (-0.2,2) )
+    plt.ylim( (-1,0.5) )
+    plt.legend( loc='lower right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
+    #Lambda_th line
+    if web == 'Tweb':
+	lamb_opt = 0.36
+    elif web == 'Vweb':
+	lamb_opt = 0.202
+    plt.vlines( lamb_opt, -1, 0.5, linestyle = '-', color = colors[i_web], linewidth = 2 )
[…]

### 2014-04-30 cosmic_voids.tex
Anlysis of the plot of FA vs Lambda_1. Tomography of the cosmic web.

@@
 tracer of the underlying matter field in order to be more consistent with
-available observational data. First, we analyse distributions of mass and 
-peculiar velocity in order to assign typical values to each type of 
-environment. In the figure \ref{fig:typical_mass_velocity} we calculate 
-both distributions for web schemes and using the FOF catalogue of the 
-simulation. Thick lines correspond to the median of the distribution and 
-filled regions limited by dashed lines correspond to quartiles $Q_1$ and 
-$Q_3$, it means, $50\%$ of all halos are within such regions for every 
-\lth value and for each type of environment. We rather use median and 
-quartiles as measure of dispersion because there are some very unusual and 
-extreme values that makes the usual analysis based upon means and standard 
-deviations less reliable.
+available observational data. In the figure \ref{fig:halos_fractions} we 
+calculate fractions of halos within each one of the defined environments 
+based upon the FOF catalogue of the simulation and for an extensive \lth 
+range. Then we look for some key feature that could indicated us a 
+possible optimal value of the \lth value. One first step forward our quest 
+is the behaviour of the V-web scheme compared with the T-web. As was 
+previously established by \SRKED{Hoffman et al. (2012)} and as can be seen 
+in the figure \ref{fig:halos_fractions}, V-web scheme is significantly more
+sensible to variations of the $\lambda_{th}$ value, since all fractions of
+halos for the V-web change significantly in the range $[0,0.4]$, whereas, 
+for the T-web scheme, fractions change smoothly throughout all \lth range 
+covered. From this, it is then expected that the optimal \lth value for 
+the V-web scheme is less than the T-web value.
+
+The more notorious characteristic of the figure \ref{fig:halos_fractions} 
+is the behaviour of the fraction of halos within sheet regions for both 
+web schemes, increasing until a local maximum, and then decreasing. The 
+increasing or decreasing rate of the fraction of halos for some region 
+could be interpreted as a measure of the degree of non-linearity of such 
+region for some specific \lth value. For example, filaments and knots, 
+that are the most non-linear regions of the universe, have a negative rate
+for all covered \lth range. In the case of voids, the situation is 
+completely opposite, where fractions of halos increase in everywhere. If 
+we think in terms of the underlying matter field of the cosmic web, \lth 
+is just a cutting parameter between highly non-linear regions (filament 
+and knots) and low non-linear (voids and sheets). Furthermore, if we take 
+into account that dark matter halos are much more likely to form in highly 
+non-linear regions, it is expected the obtained behaviour of the fractions 
+of halos for voids, filaments and knots as we increase the \lth value. 
+However, the behaviour of the fraction of halos in sheets is less clear,
+increasing for low \lth values (such as voids) and decreasing for higher 
+\lth values (such as filaments and knots). This indicates the transitional 
+character of sheet regions in the cosmic web. Our proposal here is to 
+select as optimal \lth the value where the fraction of sheets reaches a
+local maximum. According to this, we find for the T-web scheme an optimal 
+value $\lambda_{opt}^T = 0.36$ and for the V-web scheme $\lambda_{opt}^V = 
+0.20$. In the figure \ref{fig:visual_impression} we show the visual 
+impression of the cosmic web along with the density field for different 
+\lth values including the optimal values. It can be noticed that the found 
+optimal values reproduce well the visual impression.
+
+As we have taken halos as tracers of the cosmic web, we analyse 
+distributions of mass and peculiar velocity in order to assign typical 
+values to each type of environment. In the figure 
+\ref{fig:typical_mass_velocity} we calculate both distributions for both 
+web schemes and using the FOF catalogue of the simulation. Thick lines 
+correspond to the median of the distribution and filled regions limited by
+dashed lines correspond to quartiles $Q_1$ and $Q_3$, it means, $50\%$ of
+all halos are within such regions for every \lth value and for each type 
+of environment. We rather use median and quartiles as measure of 
+dispersion because there are some very unusual and extreme values that 
+makes the usual analysis based upon means and standard deviations less 
+reliable.
 
@@
 like density field and distribution of halos mass, are well-differentiated 
-among each region, while for the V-web scheme, based upon the shear 
-velocity tensor, all dynamical quantities, as the peculiar velocity field 
-and the distribution of halos velocity are alike expected to be 
+among each region, while the V-web scheme, based upon the shear velocity 
+tensor, all dynamical quantities, as the peculiar velocity field and the 
+distribution of the velocity of halos are also expected to be 
 well-differentiated among regions as quantified by this scheme.
@@
 Finally, we also calculate typical distributions of the density and 
-peculiar velocity fields on the volume cells associated to each type of 
-environment, obtaining completely analogous results. Furthermore, we use a 
-BDM catalogue of the simulation as well, obtaining very similar conclusions.
+peculiar velocity fields in each type of environment, obtaining completely
+analogous results. Furthermore, we also use a BDM catalogue of the 
+simulation, obtaining very similar conclusions.
 
@@
 
-In order to overcome the percolation of voids in our classification scheme,
+In order to deal with percolation of voids in our classification scheme,
 we introduce the fractional anisotropy as defined in \SRKED{[reference, 
@@
 voids, where both of them exhibit low to middle values of the FA, 
-indicating a high isotropy regarding the physical property quantified by 
+indicating a high isotropy regarding the physical properties quantified by 
 each web scheme, i.e. the density field for the T-web and the peculiar 
@@
 more spread. This can be explained appealing to the low dispersion of the 
-density field with respect to the peculiar velocity in highly non-linear 
+density field compared with the peculiar velocity in highly non-linear 
 regions like knots. For more linear regions like voids, the behaviour of 
@@
 environment, voids are regions where 
-$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$, this implies that
+$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$. This implies that
 the boundaries of void regions are controlled completely by the $\lambda_1$
 eigenvalue of the web scheme and the threshold value. Therefore, as we 
-increase the threshold value $\lambda_th$, all voids grow up progressively 
-through contours of $\lambda_3$ field until certain critical value where 
-voids are very large so the visual impression is no longer reliable.
+increase the threshold value $\lambda_{th}$, all voids grow up 
+progressively through contours of the $\lambda_3$ field until certain 
+critical value where they are so large that the visual impression is no 
+longer reproduced. Our objective here is to find a reliable quantity that 
+allows to trace the geometry of void regions as classified by each web 
+scheme. In the figure \ref{fig:L1_correlations} we calculate the 
+distributions of the fractional anisotropy index and the density field 
+regarding the $\lambda_1$ eigenvalue for both web schemes over all the 
+cells of the simulation. Thick lines correspond to the median of the 
+distributions, whereas coloured regions correspond to the $50\%$ of the
+sample, delimited by quartiles $Q_1$ and $Q_3$.
+
+The first important conclusion is regarding the distribution of the FA 
+index, where there is an almost perfect correlation with the $\lambda_1$ 
+eigenvalue for low values of it. This result can be interpreted as an 
+one-dimensional tomography of void regions, where low $\lambda_1$ values 
+are associated to the central regions of voids and they are the more 
+isotropic structures found, with FA values close to 0. As we increase the 
+$\lambda_1$ value, corresponding to progressively outer layers of void 
+regions, the FA index increases as well, maintaining a perfect correlation 
+approximately until the optimal threshold value for each scheme. Because 
+of the definition of the fractional anisotropy index, it presents the 
+highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$. 
+Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
+threshold, such that the outer regions of voids becomes highly anisotropic, 
+it would imply that voids are invading filaments and sheets, so the optimal
+threshold is a limit value up to which we can have void regions. For other
+type of environment such as sheets, filaments and knots, the $\lambda_1$
+eigenvalue does not control their spatial boundaries, so the correlation
+with the FA index is no longer valid. The larger dispersion in the 
+distribution indicates that contours of the FA field are no longer 
+corresponding to contours of the $\lambda_1$ field. Nevertheless, for high
+$\lambda_1$ values, i.e. $\lambda_1>1.0$, the median value of the FA index
+decreases to lower values, indicating the presence of isotropic knots. All
+of this allows us to conclude that the distribution of the FA with respect
+to the $\lambda_1$ eigenvalue is not only an one-dimensional tomography of 
+voids, but also an one-dimensional projection of the global structure of
+the cosmic web, starting in highly isotropic central voids, passing 
+through very anisotropic sheets and filaments, until isotropic knot 
+regions.
 
@@
 %.........................................................................
-%FIGURE 1: Typical mass and pecular velocity
+%FIGURE 1: Fraction of halos in each environment
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}  
+  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}
+
+  \captionof{figure}{\small Fractions of halos embedded in each one of 
+  the defined environments according to the \lth value. T-web scheme 
+  (left panel) and V-web scheme (right panel). The optimal parameters 
+  found are $\lambda_{opt}^{T}=0.36$ and $\lambda_{opt}^{V}=0.20$.}
+
+  \label{fig:halos_fractions}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 2: Visual impression of the cosmic web
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
+  width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
+  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
+  width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}
+
+  \captionof{figure}{\small Visual impression of the density field (left 
+  panels), and of each classification scheme with the $\lambda_{th}$ values 
+  obtained by our criteria (others panels). The color convention for each 
+  environment is (white) - void, (light gray) - sheet, (gray) - filament, 
+  (black) - knot. For each web scheme, it has been used the previously 
+  established optimal threshold as a reference value, so plots are done 
+  with the next values $\lambda_{th} = 0.0$, $\lambda_{th} = 
+  \lambda_{opt}/2$, $\lambda_{th} = \lambda_{opt}$ and $\lambda_{th} = 
+  2\lambda_{opt}$.}
+
+  \label{fig:visual_impression}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 3: Typical mass and pecular velocity
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 2: Typical mass and pecular velocity
+%FIGURE 4: Typical mass and pecular velocity
 \begin{flushleft}
@@
   panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
-  defined type of environments, where voids corresponds to white zones, 
+  defined types of environment, where voids corresponds to white zones, 
   sheets to gray, filaments to dark gray and finally knots to black regions. 
@@
 
+%.........................................................................
+%FIGURE 5: Typical mass and pecular velocity
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/FA_L1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/delta_L1.pdf}
+
+  \captionof{figure}{\small In this figure is shown the distribution of the
+  fractional anisotropy (left panel) and density field (right panel) with 
+  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
+  lines. V-web, blue lines) as calculated over all the cells of the grid.
+  Thick central lines correspond to the median of the distribution and 
+  coloured regions to the $50\%$ of the cells, delimited by quartiles 
+  $Q_1$ and $Q_3$.}
+
+  \label{fig:L1_correlations}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
 \end{document}

### 2014-04-30 cosmic_voids.tex
Anlysis of the plot of FA vs Lambda_1. Tomography of the cosmic web.

@@
 to the $\lambda_1$ eigenvalue is not only an one-dimensional tomography of 
-voids, but also an one-dimensional projection of the global structure of
-the cosmic web, starting in highly isotropic central voids, passing 
-through very anisotropic sheets and filaments, until isotropic knot 
-regions.
+voids, but also a sort of one-dimensional projection of the global 
+structure of the cosmic web, starting in highly isotropic central voids, 
+passing through very anisotropic sheets and filaments, until isotropic 
+knot regions.
 

### 2014-05-01 cosmic_voids.tex
Analysis of the distribution of density vs L1

@@
 
+%-------------------------------------------------------------------------
+\subsection{Fractional anisotropy as tracer of the cosmic web}
+\label{subsec:FA_web}
+%-------------------------------------------------------------------------
+
 According to the recent growing interest in studying galaxy formation in 
@@
 knot regions.
+
+For the distribution of the density with respect to the $\lambda_1$ 
+eigenvalue, it can be appreciated an analogous behaviour, where central 
+regions of voids present the most under-dense values of the overall cosmic 
+web. For outer layers of voids, the density field grows progressively 
+until sheets and filaments are reached. However, the dispersion in the 
+distributions indicates that the geometry of voids as quantified by both 
+web schemes is not compatible with the density field, i.e. contours of the
+$\lambda_1$ eigenvalue do not coincide with contours of the density field. 
+Then, the density is not a reliable quantity to be used as tracer of voids. 
+Furthermore, another advantage of using the FA index instead of the 
+density is the non-monotonous behaviour of the FA median value, with a 
+local maximum that allows to identify the boundaries of void regions.
 

### 2014-05-01 bench/codes_figures/FA_L1_correlation.py

@@ -43,7 +43,7 @@ for web in webs:
     
     plt.grid(1)
     plt.ylabel( 'FA', fontsize = 12 )
-    plt.xlabel( '$\lambda_{3}$', fontsize = 12)
+    plt.xlabel( '$\lambda_{1}$', fontsize = 12)
     plt.xlim( (-0.3,2) )
     plt.ylim( (0,1) )
     plt.legend( loc='lower right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )

### 2014-05-01 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -38,6 +38,13 @@ Cut = 10
 my_cmapC = plt.cm.get_cmap('gray')
 my_cmap4 = plt.cm.get_cmap('gray', 4)
 
+from matplotlib.colors import colorConverter
+cmap2 = mpl.colors.LinearSegmentedColormap.from_list('my_cmap2',["black","white"],2)
+cmap2._init()
+alphas = np.ones( cmap2.N+3)
+alphas[0] = 0
+cmap2._lut[:,-1] = alphas
+
 #==================================================================================================
 #			PLOTING WEB SCHEME AND DENSITY FIELD FOR SIMULATION
 #==================================================================================================
@@ -68,7 +75,8 @@ eig3 = CutFieldZ( eig_filename+"_3", Cut, 16, Coor = axe )
 
 #Vweb Plot with Lambda_th = 0.3
 plt.subplot( 2, 2, 1 )
-plt.imshow( -Scheme( eig1, eig2, eig3, Lambda_opt ), extent = extent, vmin=-3, vmax=0, cmap = my_cmap4 )
+#plt.imshow( -Scheme( eig1, eig2, eig3, Lambda_opt ), extent = extent, vmin=-3, vmax=0, cmap = my_cmap4 )
+plt.imshow( Fractional_Anisotropy( eig1, eig2, eig3 ), extent = extent,  cmap = "binary" )
 plt.title( "Vissual impresion for $\lambda_{th} = %1.3f$"%(Lambda_opt) )
 plt.yticks( (),() )
 plt.xticks( (0,Box_L) )
@@ -77,6 +85,7 @@ plt.xlabel( "[$h^{-1}$ Mpc]" )
 #Vweb Plot with Lambda_th = 0
 plt.subplot( 2, 2, 2 )
 plt.imshow( Fractional_Anisotropy( eig1, eig2, eig3 ), extent = extent,  cmap = "binary" )
+plt.imshow( Scheme( eig1, eig2, eig3, 0.0 )[::-1,], extent = extent, vmin=0, vmax=0.5, cmap = cmap2, origin='lower' )
 plt.title( "Fractional\nAnisotropy" )
 plt.yticks( (),() )
 plt.xticks( (0,Box_L) )

### 2014-05-01 bench/codes_figures/delta_L1_correlation.py

@@ -42,7 +42,7 @@ for web in webs:
 
     plt.grid(1)
     plt.ylabel( '$\\rho$', fontsize = 12 )
-    plt.xlabel( '$\lambda_{3}$', fontsize = 12)
+    plt.xlabel( '$\lambda_{1}$', fontsize = 12)
     plt.xlim( (-0.2,2) )
     plt.ylim( (-1,0.5) )
     plt.legend( loc='lower right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )

### 2014-05-01 bench/codes_figures/sd.py

@@ -1,0 +1,28 @@
+from matplotlib.colors import colorConverter
+import matplotlib.pyplot as plt
+import numpy as np
+import matplotlib as mpl
+
+# create dummy data
+zvals = np.ones((100,100))# np.random.rand(100,100)*10-5
+zvals2 = np.random.rand(100,100)*10-5
+
+# generate the colors for your colormap
+color1 = colorConverter.to_rgba('white')
+color2 = colorConverter.to_rgba('black')
+
+# make the colormaps
+cmap1 = mpl.colors.LinearSegmentedColormap.from_list('my_cmap',['green','blue'],256)
+cmap2 = mpl.colors.LinearSegmentedColormap.from_list('my_cmap2',[color1,color2],256)
+
+cmap2._init() # create the _lut array, with rgba values
+
+# create your alpha array and fill the colormap with them.
+# here it is progressive, but you can create whathever you want
+alphas = np.linspace(0, 0.8, cmap2.N+3)
+cmap2._lut[:,-1] = alphas
+
+img2 = plt.imshow(zvals, interpolation='nearest', cmap=cmap1, origin='lower')
+#img3 = plt.imshow(zvals2, interpolation='nearest', cmap=cmap2, origin='lower')
+
+plt.show()

### 2014-05-02 bench/codes_analysis/Central_Voids_Properties.c
Including analysis of local minima of the FA

@@ -6,7 +6,7 @@
 #define NMAX1 1000
 #define NMAX2 100000
 
-//Usage  Central_Voids_Properties.out <eig_filename> <delta_filename> <output_filename>
+//Usage  Central_Voids_Properties.out <eig_filename> <delta_filename> <output_filename> <Number of neighbour cells>
 
 float FractionalAnisotropy( float eig1, float eig2, float eig3 )
 { 
@@ -27,7 +27,7 @@ int main(int argc, char **argv)
     int i,j,k,l;
     int ic,jc,kc;
     int it,jt,kt;
-    int b = 1;
+    int b = atoi( argv[4] );
     long long int n, nt;
 
     int isminim;
@@ -141,40 +141,40 @@ int main(int argc, char **argv)
     sprintf( filename, "%s", argv[3] );
     central_voids = fopen(filename, "w");
     //Head
-    fprintf( central_voids, "i\tj\tk\tFA\tDelta" );
+    fprintf( central_voids, "#i\tj\tk\tL1\tFA\tDelta\n" );
     
     for( i=0;i<n_x;i++ )
     for( j=0;j<n_x;j++ )
     for( k=0;k<n_x;k++ ){
 	//Overall index
 	n = k + n_x*(j + n_x*i);
-	//Setting this cell as a possible local minima
-	isminim = 1;
-
 	//Setting the neighborhood
-	for( ic=-b; ic<=b; ic++ )
-	for( jc=-b; jc<=b; jc++ )
-	for( kc=-b; kc<=b; kc++ )
-	if( ic!=0 || jc!=0 || kc!=0 ){    
-	    it = i + ic; jt = j + jc; kt = k + kc;
-	    //Neighbor out of limits (Periodic boundary conditions) (X direction)
-	    if( i+ic>=n_x )		it = 0;
-	    if( i+ic<0 )		it = n_x-1;
-	    //Neighbor out of limits (Periodic boundary conditions) (Y direction)
-	    if( j+jc>=n_x )		jt = 0;
-	    if( j+jc<0 )		jt = n_x-1;
-	    //Neighbor out of limits (Periodic boundary conditions) (Z direction)
-	    if( k+kc>=n_x )		kt = 0;
-	    if( k+kc<0 )		kt = n_x-1;
-	    
-	    //Overall index of the neighbour
-	    nt = kt + n_x*(jt + n_x*it);
-	    
[…]

### 2014-05-02 bench/codes_analysis/_Head.py

@@ -473,7 +473,7 @@ def FA_lambda1_correlation( filename_eig, lamb_min, lamb_max, N_lam, FA_min, FA_
     return datos
 
 #..................................................................................................
-#Density correlator
+#Properties of central voids
 #..................................................................................................
 def density_lambda1_correlation( filename_eig, delta_file, lamb_min, lamb_max, N_lam, lambda_min, lambda_max, N_lambda ):
     os.system( "./Density_L1_Correlation.out %s %s %f %f %d %f %f %d"%

### 2014-05-02 bench/codes_analysis/central_voids_properties.py

@@ -1,0 +1,41 @@
+#central_voids_properties.py
+#
+#This code builds a data structure with local minimums regarding the FA index over all cells of the
+#simulation for each web scheme
+#Usage: central_voids_properties.py <Tweb or Vweb> <Number of cells per neighbourhood>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+web = sys.argv[1]
+#Number of neighbour cells
+b = int(sys.argv[2])
+
+#==================================================================================================
+#			CONSTRUCTING MEDIANS OF DENSITY REGARDING LAMBDA_1
+#==================================================================================================
+
+print simulation
+
+#Loading eigenvalues
+eigV_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
+
+#Loading density
+delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,simulation,N_sec,smooth)
+
+#Building data
+os.system( "./Central_Voids_Properties.out %s %s %s %d"%( eigV_filename, delta_filename, "temp.tmp", b ) )
+
+#Saving file
+os.system( 'mv temp.tmp %scentral_void_cells_%s_b%d.dat'%(data_figures_fold,web,b) )

### 2014-05-02 bench/codes_figures/FA_L1_correlation.py

@@ -35,8 +35,8 @@ for web in webs:
 
     #Quartiles regions-------
     plt.fill_between( quartiles[:,0], quartiles[:,1], quartiles[:,3], color = colors[i_web], alpha = 0.2 )
-    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = '--' )
-    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = '--' )
+    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = '-' )
+    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = '-' )
 
     #Medians-----------------
     plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i_web], linewidth = 3, label = web )

### 2014-05-02 bench/codes_figures/central_voids.py

@@ -1,0 +1,88 @@
+#central_voids.py
+#
+#This code plots different properties of the central cells of voids, such as lambda_1 value, FA and
+#finally density
+#Usage: central_voids.py <show(0) or save(1)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+webs = ['Tweb', 'Vweb']
+#Colors and labels
+colors = [ 'red', 'blue' ]
+#Number of neighbour cells
+b = [1,2]
+#Bins
+bins = [100, 50, 50]
+
+#==================================================================================================
+#Typical halo mass for each environment
+#==================================================================================================
+#Colors
+plt.figure( figsize=(15,5) )
+plt.subplots_adjust( right = 0.99, left = 0.03 )
+
+i_web = 0
+for web in webs:
+    #Loading files with quartiles
+    properties1 = np.loadtxt( '%scentral_void_cells_%s_b%d.dat'%(data_figures_fold,web,b[0]) )
+    properties2 = np.loadtxt( '%scentral_void_cells_%s_b%d.dat'%(data_figures_fold,web,b[1]) )
+    
+    #Lambda_1 eigenvalue
+    plt.subplot(1,3,1)
+    #Making histogram
+    hist1d = np.histogram( properties1[:,3] , bins=bins[0], normed=True )
+    hist1d2 = np.histogram( properties2[:,3] , bins=bins[0], normed=True )
+    #Plotting
+    plt.plot(hist1d[1][:-1], hist1d[0], color = colors[i_web], linewidth = 3, label = "%s"%(web))
+    plt.plot(hist1d2[1][:-1], hist1d2[0], color = colors[i_web], linewidth = 1, linestyle = "-")
+    plt.grid(1)
+    plt.ylabel( 'Normed distribution', fontsize = 12 )
+    plt.xlabel( '$\lambda_{1}$', fontsize = 12)
+    plt.legend( loc='upper right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )    
[…]

### 2014-05-02 bench/codes_figures/delta_L1_correlation.py

@@ -34,8 +34,8 @@ for web in webs:
     
     #Quartiles regions-------
     plt.fill_between( quartiles[:,0], quartiles[:,1], quartiles[:,3], color = colors[i_web], alpha = 0.2 )
-    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = '--' )
-    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = '--' )
+    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = '-' )
+    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = '-' )
 
     #Medians-----------------
     plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i_web], linewidth = 3, label = web )

### 2014-05-02 bench/codes_figures/void_volume_regions.py

@@ -46,7 +46,7 @@ for web in webs:
     void_regs = np.transpose(np.loadtxt("%s/%s/%s/%d/voids%s/voids_%1.2f/void_regions.dat"%\
     (foldglobal, simulation, web, N_sec, void_scheme, Lambda_th[i_web] )))
 
-    hist1d = np.histogram( np.log10(void_regs[1]) , bins=20, normed=False	 )
+    hist1d = np.histogram( np.log10(void_regs[1]) , bins=20, normed=False )
     
     ax1.semilogy( hist1d[1][:-1], hist1d[0], linewidth = 3, label = "%s"%(web))
     i_web += 1

### 2014-05-07 bench/codes_figures/FA_L1_correlation.py
Removing any reference to the Threshold optimal value in the figures

@@ -49,16 +49,19 @@ for web in webs:
     plt.legend( loc='lower right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
     #Lambda_th line
     if web == 'Tweb':
-	lamb_opt = 0.36
+	lamb_opt = 0.265
+	plt.text( lamb_opt + 0.03, 0.6, '$\lambda^%s_{opt}$=%1.3f'%(web[0],lamb_opt), fontsize = 12,\
+	color=colors[i_web], rotation=90 )
     elif web == 'Vweb':
-	lamb_opt = 0.202
+	lamb_opt = 0.175
+	plt.text( lamb_opt - 0.12, 0.6, '$\lambda^%s_{opt}$=%1.3f'%(web[0],lamb_opt), fontsize = 12,\
+	color=colors[i_web], rotation=90 )
     plt.plot( [lamb_opt,lamb_opt], [0,1], linestyle = '-', color = colors[i_web], linewidth = 2 )
-    plt.text( lamb_opt + 0.02, 0.6, '$\lambda^%s_{opt}$=%1.2f'%(web[0],lamb_opt), fontsize = 12,\
-    color=colors[i_web], rotation=90 )
     
     i_web += 1
 
-plt.plot( [-0.3,2], [0.97,0.97], '-', color='black', linewidth=2 )
+plt.plot( [-0.3,2], [0.95,0.95], '-', color='black', linewidth=2 )
+plt.text( -0.3, 0.962, 'FA$_{th}$=0.95', fontsize = 12, color="black" )
 
 if sys.argv[1] == '1':
     plt.savefig( '%sFA_L1.pdf'%(figures_fold) )

### 2014-05-07 bench/codes_figures/delta_L1_correlation.py

@@ -46,14 +46,16 @@ for web in webs:
     plt.xlim( (-0.2,2) )
     plt.ylim( (-1,0.5) )
     plt.legend( loc='lower right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
-    #Lambda_th line
+        #Lambda_th line
     if web == 'Tweb':
-	lamb_opt = 0.36
+	lamb_opt = 0.265
+	plt.text( lamb_opt + 0.03, 0.3, '$\lambda^%s_{opt}$=%1.3f'%(web[0],lamb_opt), fontsize = 12,\
+	color=colors[i_web], rotation=90 )
     elif web == 'Vweb':
-	lamb_opt = 0.202
+	lamb_opt = 0.175
+	plt.text( lamb_opt - 0.12, 0.3, '$\lambda^%s_{opt}$=%1.3f'%(web[0],lamb_opt), fontsize = 12,\
+	color=colors[i_web], rotation=90 )
     plt.vlines( lamb_opt, -1, 0.5, linestyle = '-', color = colors[i_web], linewidth = 2 )
-    plt.text( lamb_opt + 0.02, 0.3, '$\lambda^%s_{opt}$=%1.2f'%(web[0],lamb_opt), fontsize = 12,\
-    color=colors[i_web], rotation=90 )
     
     i_web += 1
 

### 2014-05-08 cosmic_voids.tex
Including analysis of local minima of the FA
New analysis of FA vs L1 figure, deleting any reference of lambda_th as defined trhough the number of halos

@@
 tracer of the underlying matter field in order to be more consistent with
-available observational data. In the figure \ref{fig:halos_fractions} we 
-calculate fractions of halos within each one of the defined environments 
-based upon the FOF catalogue of the simulation and for an extensive \lth 
-range. Then we look for some key feature that could indicated us a 
-possible optimal value of the \lth value. One first step forward our quest 
-is the behaviour of the V-web scheme compared with the T-web. As was 
-previously established by \SRKED{Hoffman et al. (2012)} and as can be seen 
-in the figure \ref{fig:halos_fractions}, V-web scheme is significantly more
-sensible to variations of the $\lambda_{th}$ value, since all fractions of
-halos for the V-web change significantly in the range $[0,0.4]$, whereas, 
-for the T-web scheme, fractions change smoothly throughout all \lth range 
-covered. From this, it is then expected that the optimal \lth value for 
-the V-web scheme is less than the T-web value.
-
-The more notorious characteristic of the figure \ref{fig:halos_fractions} 
-is the behaviour of the fraction of halos within sheet regions for both 
-web schemes, increasing until a local maximum, and then decreasing. The 
-increasing or decreasing rate of the fraction of halos for some region 
-could be interpreted as a measure of the degree of non-linearity of such 
-region for some specific \lth value. For example, filaments and knots, 
-that are the most non-linear regions of the universe, have a negative rate
-for all covered \lth range. In the case of voids, the situation is 
-completely opposite, where fractions of halos increase in everywhere. If 
-we think in terms of the underlying matter field of the cosmic web, \lth 
-is just a cutting parameter between highly non-linear regions (filament 
-and knots) and low non-linear (voids and sheets). Furthermore, if we take 
-into account that dark matter halos are much more likely to form in highly 
-non-linear regions, it is expected the obtained behaviour of the fractions 
-of halos for voids, filaments and knots as we increase the \lth value. 
-However, the behaviour of the fraction of halos in sheets is less clear,
-increasing for low \lth values (such as voids) and decreasing for higher 
-\lth values (such as filaments and knots). This indicates the transitional 
-character of sheet regions in the cosmic web. Our proposal here is to 
-select as optimal \lth the value where the fraction of sheets reaches a
-local maximum. According to this, we find for the T-web scheme an optimal 
-value $\lambda_{opt}^T = 0.36$ and for the V-web scheme $\lambda_{opt}^V = 
-0.20$. In the figure \ref{fig:visual_impression} we show the visual 
-impression of the cosmic web along with the density field for different 
-\lth values including the optimal values. It can be noticed that the found 
-optimal values reproduce well the visual impression.
-
-As we have taken halos as tracers of the cosmic web, we analyse 
-distributions of mass and peculiar velocity in order to assign typical 
-values to each type of environment. In the figure 
-\ref{fig:typical_mass_velocity} we calculate both distributions for both 
-web schemes and using the FOF catalogue of the simulation. Thick lines 
-correspond to the median of the distribution and filled regions limited by
-dashed lines correspond to quartiles $Q_1$ and $Q_3$, it means, $50\%$ of
-all halos are within such regions for every \lth value and for each type 
-of environment. We rather use median and quartiles as measure of 
-dispersion because there are some very unusual and extreme values that 
-makes the usual analysis based upon means and standard deviations less 
-reliable.
+available observational data. Therefore, we analyse distributions of mass 
+and peculiar velocity in order to assign typical values to each type of 
+environment. In the figure \ref{fig:typical_mass_velocity} we calculate 
+both distributions for both web schemes and using the FOF catalogue of the 
+simulation. Thick lines correspond to the median of the distribution and 
+filled regions limited by dashed lines correspond to quartiles $Q_1$ and 
+$Q_3$, it means, $50\%$ of all halos are within such regions for every 
+\lth value and for each type of environment. We rather use median and 
+quartiles as measure of dispersion because there are some very unusual 
+and extreme values that makes the usual analysis based upon means and 
+standard deviations less reliable.
 
@@
 consistent with expectations, where low mass halos are typical in voids 
-until high mass halos in knots. For the case of the V-web scheme, all
-medians and dispersions are completely overlapped, specially for values 
-grater than the optimal \lth value, indicating that it is not possible to
-assign typical mass ranges to each environment as quantified by this 
-scheme. For peculiar velocities, this situation is opposite, where V-web
-scheme is much more adequate to assign typical distributions of velocity
-to each environment. Although T-web also makes a differentiation in the 
-distributions of velocity, this is very slight compared with the V-web 
-case. These results can be explained by appealing the physical origin of 
-each web scheme. As T-web is based upon the Hessian matrix of the 
-potential field, it is expected all quantities related to the potential, 
-like density field and distribution of halos mass, are well-differentiated 
-among each region, while the V-web scheme, based upon the shear velocity 
-tensor, all dynamical quantities, as the peculiar velocity field and the 
-distribution of the velocity of halos are also expected to be 
-well-differentiated among regions as quantified by this scheme.
+and higher mass halos in knots. For the case of the V-web scheme, all
+medians and dispersions are completely overlapped, indicating that it is 
+not possible to assign typical mass ranges to each environment as 
+quantified by this scheme. For peculiar velocities, this situation is 
+opposite, where V-web scheme is much more adequate to assign typical 
+distributions of velocity to each environment. Although T-web also makes 
+a differentiation in the distributions of velocity, this is very slight 
+compared with the V-web case. These results can be explained by appealing 
+the physical origin of each web scheme. As T-web is based upon the Hessian 
+matrix of the potential field, it is expected all quantities related to 
+the potential, like density field and distribution of halos mass, are 
+well-differentiated among each region, while the V-web scheme, based upon 
+the shear velocity tensor, all dynamical quantities, as the peculiar 
+velocity field and the distribution of the velocity of halos are also 
+expected to be well-differentiated among regions as quantified by this 
+scheme.
 
@@
 %-------------------------------------------------------------------------
-\subsection{Fractional anisotropy as tracer of the cosmic web}
-\label{subsec:FA_web}
+\subsection{Fractional anisotropy as tracer of voids}
+\label{subsec:FA_voids}
 %-------------------------------------------------------------------------
@@
 
-As has been established \SRKED{[references]}, both schemes presented in
-the previous section (V-web and T-web) for classifying the cosmic web 
+As has been established \SRKED{[references]}, both web schemes presented 
+in the previous section (V-web and T-web) for classifying the cosmic web 
 present many advantages compared with classification schemes based
@@
 impression provided by each scheme, phenomenons like percolation depends 
-on it as well. Percolation is one of the key features of the structure of 
-void regions, indicating how voids are merged among them, and how they 
-permeate all the cosmic web.
+on it as well. Although percolation is one of the key features of the 
+structure of void regions, indicating how voids are merged among them, and 
+how they permeate all the cosmic web, our primal interest here is studying 
+properties of single voids. Nevertheless, in the next section we shall 
+analyse briefly the percolation phenomenon for both web schemes.
 
@@
 each web scheme, i.e. the density field for the T-web and the peculiar 
-velocity for the V-web. For the T-web, the FA field around knots presents 
-a very narrow distribution, whereas for the V-web the same distribution is
-more spread. This can be explained appealing to the low dispersion of the 
-density field compared with the peculiar velocity in highly non-linear 
-regions like knots. For more linear regions like voids, the behaviour of 
-the FA field is quite similar between both schemes, what is consistent 
-with the equivalence of the T-web and the V-web in the linear regime 
-\SRKED{[reference, Hoffman]}.
+velocity for the V-web. For the T-web, the FA field near to knots presents 
+a very narrow distribution around a local minima, whereas for the V-web 
+such distribution is more spread out. This can be explained appealing to 
+the low fluctuations of the density field compared with the peculiar 
+velocity in highly non-linear regions like knots. For more linear regions 
+like voids, the behaviour of the FA field is quite similar between both 
+schemes, what is consistent with the equivalence of the T-web and the 
+V-web in the linear regime \SRKED{[reference, Hoffman]}.
 
@@
 cells of the simulation. Thick lines correspond to the median of the 
-distributions, whereas coloured regions correspond to the $50\%$ of the
+distributions, whereas coloured regions correspond to $50\%$ of the
 sample, delimited by quartiles $Q_1$ and $Q_3$.
@@
 $\lambda_1$ value, corresponding to progressively outer layers of void 
-regions, the FA index increases as well, maintaining a perfect correlation 
-approximately until the optimal threshold value for each scheme. Because 
-of the definition of the fractional anisotropy index, it presents the 
+regions or less isotropic voids, the FA index increases as well, 
+maintaining a very reliable correlation approximately until $FA=0.95$. 
+This limit value of the FA can be traduced in terms of an optimal \lth, 
+where we obtain $\lambda_{opt}^V = 0.175$ for the V-web scheme and 
+$\lambda_{opt}^T = 0.265$ for the T-web scheme, both values consistent 
+with optimal thresholds normally taken in previous works \SRKED{[references]}. 
+Due to the definition of the fractional anisotropy index, it presents the 
 highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$.
 Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
-threshold, such that the outer regions of voids becomes highly anisotropic, 
-it would imply that voids are invading filaments and sheets, so the optimal
-threshold is a limit value up to which we can have void regions. For other
-type of environment such as sheets, filaments and knots, the $\lambda_1$
-eigenvalue does not control their spatial boundaries, so the correlation
-with the FA index is no longer valid. The larger dispersion in the 
-distribution indicates that contours of the FA field are no longer 
-corresponding to contours of the $\lambda_1$ field. Nevertheless, for high
-$\lambda_1$ values, i.e. $\lambda_1>1.0$, the median value of the FA index
-decreases to lower values, indicating the presence of isotropic knots. All
-of this allows us to conclude that the distribution of the FA with respect
-to the $\lambda_1$ eigenvalue is not only an one-dimensional tomography of 
-voids, but also a sort of one-dimensional projection of the global 
-structure of the cosmic web, starting in highly isotropic central voids, 
-passing through very anisotropic sheets and filaments, until isotropic 
-knot regions.
+FA limit, such that the outer regions of voids becomes highly anisotropic, 
+it would imply that voids are invading filaments and sheets, so the 
+optimal \lth value is a limit value up to which we can have void regions. 
+For other type of environment such as sheets, filaments and knots, the 
+$\lambda_1$ eigenvalue does not control their spatial boundaries, so the 
+correlation with the FA index is no longer valid beyond the threshold 
+values, furthermore the larger dispersion of the FA distribution also 
+indicates that contours of the FA field are no longer corresponding to 
+contours of the $\lambda_1$ field. Nevertheless, for high $\lambda_1$ 
+values, i.e. $\lambda_1>1.0$, the median value of the FA index decreases 
+to lower values, indicating the presence of isotropic knots. All of this 
+allows us to conclude that the distribution of the FA with respect to the 
+$\lambda_1$ eigenvalue is not only an one-dimensional tomography of voids, 
+but also a sort of one-dimensional projection of the global structure of 
+the cosmic web, starting in highly isotropic central voids, passing 
+through very anisotropic sheets and filaments, until isotropic knot 
+regions.
 
@@
 $\lambda_1$ eigenvalue do not coincide with contours of the density field. 
-Then, the density is not a reliable quantity to be used as tracer of voids. 
-Furthermore, another advantage of using the FA index instead of the 
+Then, the density is not a reliable quantity to be used as tracer of our 
+voids. Furthermore, another advantage of using the FA index instead of the
 density is the non-monotonous behaviour of the FA median value, with a 
-local maximum that allows to identify the boundaries of void regions.
+local maxima that allows to identify properly the boundaries of voids.
+
+%-------------------------------------------------------------------------
+\subsection{Identifying void regions}
+\label{subsec:identification}
+%-------------------------------------------------------------------------
 
@@
 %.........................................................................
-%FIGURE 1: Fraction of halos in each environment
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/halos_fraction_FOF_Tweb.pdf}  
-  \includegraphics[trim = 0mm 0mm 5mm 5mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/halos_fraction_FOF_Vweb.pdf}
-
-  \captionof{figure}{\small Fractions of halos embedded in each one of 
-  the defined environments according to the \lth value. T-web scheme 
-  (left panel) and V-web scheme (right panel). The optimal parameters 
-  found are $\lambda_{opt}^{T}=0.36$ and $\lambda_{opt}^{V}=0.20$.}
-
-  \label{fig:halos_fractions}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 2: Visual impression of the cosmic web
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
-  width=0.75\textheight]{./figures/cosmicweb_visual_Tweb.pdf}
-  \includegraphics[trim = 42mm 10mm 37mm 10mm, clip, keepaspectratio=true,
-  width=0.75\textheight]{./figures/cosmicweb_visual_Vweb.pdf}
-
-  \captionof{figure}{\small Visual impression of the density field (left 
-  panels), and of each classification scheme with the $\lambda_{th}$ values 
-  obtained by our criteria (others panels). The color convention for each 
-  environment is (white) - void, (light gray) - sheet, (gray) - filament, 
-  (black) - knot. For each web scheme, it has been used the previously 
-  established optimal threshold as a reference value, so plots are done 
-  with the next values $\lambda_{th} = 0.0$, $\lambda_{th} = 
-  \lambda_{opt}/2$, $\lambda_{th} = \lambda_{opt}$ and $\lambda_{th} = 
-  2\lambda_{opt}$.}
-
-  \label{fig:visual_impression}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 3: Typical mass and pecular velocity
+%FIGURE 1: Typical mass and pecular velocity
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 4: Typical mass and pecular velocity
+%FIGURE 2: FA and vissual impression
 \begin{flushleft}
@@
   \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
-  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb(null).pdf}
+  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
 
   \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
-  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb(null).pdf}
+  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
 
@@
   while high values of FA (FA $\lesssim 1$) are consistent with filaments 
-  and highly planar sheets.}
+  and highly planar sheets. Thin dark red curves correspond to contours of
+  $FA=0.95$, which is approximately the transitional FA between voids and
+  other cosmological regions.}
 
@@
 %.........................................................................
-%FIGURE 5: Typical mass and pecular velocity
+%FIGURE 3: Distributions of FA and density regarding the Lambda_1 eigenvalue
 \begin{flushleft}

### 2014-05-08 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -22,10 +22,10 @@ N_sec = 256
 #Web scheme
 web = sys.argv[1]
 #Values to evaluate lambda_th
-if web == 'Tweb':
-    Lambda_opt = 0.36
-if web == 'Vweb':
-    Lambda_opt = 0.20
+#if web == 'Tweb':
+    #Lambda_opt = 0.36
+#if web == 'Vweb':
+    #Lambda_opt = 0.20
 Lambda_opt = 0
 #Smooth parameter
 smooth = '_s1'
@@ -75,8 +75,8 @@ eig3 = CutFieldZ( eig_filename+"_3", Cut, 16, Coor = axe )
 
 #Vweb Plot with Lambda_th = 0.3
 plt.subplot( 2, 2, 1 )
-#plt.imshow( -Scheme( eig1, eig2, eig3, Lambda_opt ), extent = extent, vmin=-3, vmax=0, cmap = my_cmap4 )
-plt.imshow( Fractional_Anisotropy( eig1, eig2, eig3 ), extent = extent,  cmap = "binary" )
+plt.imshow( -Scheme( eig1, eig2, eig3, Lambda_opt ), extent = extent, vmin=-3, vmax=0, cmap = my_cmap4 )
+
 plt.title( "Vissual impresion for $\lambda_{th} = %1.3f$"%(Lambda_opt) )
 plt.yticks( (),() )
 plt.xticks( (0,Box_L) )
@@ -85,7 +85,9 @@ plt.xlabel( "[$h^{-1}$ Mpc]" )
 #Vweb Plot with Lambda_th = 0
 plt.subplot( 2, 2, 2 )
 plt.imshow( Fractional_Anisotropy( eig1, eig2, eig3 ), extent = extent,  cmap = "binary" )
-plt.imshow( Scheme( eig1, eig2, eig3, 0.0 )[::-1,], extent = extent, vmin=0, vmax=0.5, cmap = cmap2, origin='lower' )
+plt.contour( Fractional_Anisotropy( eig1, eig2, eig3 )[::-1,], levels=[0.95], extent = extent, \
+colors="red", alpha=0.5, linewidths=0.5 )
+#plt.imshow( Scheme( eig1, eig2, eig3, 0.0 )[::-1,], extent = extent, vmin=0, vmax=0.5, cmap = cmap2, origin='lower' )
 plt.title( "Fractional\nAnisotropy" )
 plt.yticks( (),() )
[…]

### 2014-05-08 cosmic_voids.tex
Subsection of watershed transform over FA field for void classification

@@
 %-------------------------------------------------------------------------
-\subsection{The cosmic web in Bolshoi}
-\label{subsec:web_in_simulations}
+\subsection{Dark matter halos as tracers of the cosmic web}
+\label{subsec:halos_cosmicweb}
 %-------------------------------------------------------------------------
@@
 Finally, we also calculate typical distributions of the density and 
-peculiar velocity fields in each type of environment, obtaining completely
-analogous results. Furthermore, we also use a BDM catalogue of the 
-simulation, obtaining very similar conclusions.
+peculiar velocity fields in each type of environment by using all cells of
+the simulation grid instead of dark matter halos, obtaining completely
+analogous results. Furthermore, we also use a BDM catalogue for the dark
+matter halos, obtaining very similar results.
 
@@
 velocity for the V-web. For the T-web, the FA field near to knots presents 
-a very narrow distribution around a local minima, whereas for the V-web 
+a very narrow distribution around a local minimum, whereas for the V-web 
 such distribution is more spread out. This can be explained appealing to 
@@
 %-------------------------------------------------------------------------
-\subsection{Identifying void regions}
+\subsection{Identifying void regions through web schemes}
 \label{subsec:identification}
 %-------------------------------------------------------------------------
+
+Resuming our endeavour at identifying voids in cosmological simulations, 
+previous techniques based on web classification schemes usually perform a 
+FOF-like algorithm over cells previously marked as voids according to some 
+established criteria in order to construct bulk void regions 
+\SRKED{[references]}. Although this method has some success at classifying 
+voids, percolation is completely inevitable, where the only way to reduce 
+it is artificially decreasing the global volume fraction of void regions 
+such that they do not merge significantly each other.
+
+Once has been determined the reliability of the FA index for tracing 
+different properties of voids, our novel proposal here is rather using the 
+FA field for classifying void regions. As was concluded in the previous 
+subsection, the geometry of voids is completely traced by contours of the
+FA field, where central parts of voids and high density knot regions 
+exhibit particularly low values of the FA index. Therefore, through a 
+watershed transform all voids are classified, where each single void 
+region corresponds to the basin of a local minimum of the FA field, where
+those local minimums are restricted to be embedded into a type-void cell
+in order to avoid degeneracy with knots.
 

### 2014-05-12 cosmic_voids.tex
Some corrections, adding introduction to section of properties of voids

@@
 one-dimensional tomography of void regions, where low $\lambda_1$ values 
-are associated to the central regions of voids and they are the more 
+are associated to the central regions of voids, these being the most 
 isotropic structures found, with FA values close to 0. As we increase the 
@@
 
-Once defined the proper scheme to classify bulk voids in the simulation,
-we proceed to analyse their physical properties, like the inertia values,
+Once defined our method to classify bulk voids based upon web 
+classification schemes of the cosmic web, we proceed to analyse some 
+physical properties in order to compare their consistency with the 
+geometry of voids as quantified by our method and by density-based schemes.
+Next, through the reduced inertia tensor we quantify the shape distribution 
+of voids. Finally, we compute numerical radial profiles of density and 
+peculiar velocity of bulk voids.
+
+%-------------------------------------------------------------------------
+\subsection{Statistics of halos in voids}
+\label{subsec:shape_voids}
+%-------------------------------------------------------------------------
+
+One of the main challenges in observational void finding is the discrete 
+nature of galaxy surveys
+
+ we calculate contours of discrete fields like the median mass and 
+the local number of local dark matter halos and
+
+, like the inertia values,
 the density and peculiar velocities profiles as calculated over the grid 

### 2014-05-29 cosmic_voids.tex
Removing section of properties selection of both web schemes

@@
 
-%-------------------------------------------------------------------------
-\subsection{Dark matter halos as tracers of the cosmic web}
-\label{subsec:halos_cosmicweb}
-%-------------------------------------------------------------------------
-
-Both established schemes to quantify the cosmic web depend on continuous 
-and smooth physical quantities, i.e the peculiar velocity field and the 
-density field. To calculate these quantities, a discretization over the 
-volume of the simulation is performed, so all the properties are reduced 
-to single values associated to discrete cells. According to this, we 
-divide the overall volume into $(256)^3$ cells, so each cell has an 
-associated comoving cubic volume of $0.98 \mbox{ Mpc h}^{-1}$. Finally, in 
-order to reduce possible effects due to the discretization process, a 
-gaussian softening is performed between neighbour cells.
-
-Once defined the numerical details about both classification schemes, we
-shall analyse the dependence on the threshold value $\lambda_{th}$ for 
-each one. For this, we shall use the distribution of dark matter halos as 
-tracer of the underlying matter field in order to be more consistent with
-available observational data. Therefore, we analyse distributions of mass 
-and peculiar velocity in order to assign typical values to each type of 
-environment. In the figure \ref{fig:typical_mass_velocity} we calculate 
-both distributions for both web schemes and using the FOF catalogue of the 
-simulation. Thick lines correspond to the median of the distribution and 
-filled regions limited by dashed lines correspond to quartiles $Q_1$ and 
-$Q_3$, it means, $50\%$ of all halos are within such regions for every 
-\lth value and for each type of environment. We rather use median and 
-quartiles as measure of dispersion because there are some very unusual 
-and extreme values that makes the usual analysis based upon means and 
-standard deviations less reliable.
-
-A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
-is the median mass for each region. In the case of the T-web, although 
-dispersions of the distribution of mass for each environment are 
-considerably overlapped each other, the median value is very 
-well-differentiated among types of environment, indicating that it is 
-possible to assign typical values of mass to each region, and being 
-consistent with expectations, where low mass halos are typical in voids 
-and higher mass halos in knots. For the case of the V-web scheme, all
-medians and dispersions are completely overlapped, indicating that it is 
-not possible to assign typical mass ranges to each environment as 
-quantified by this scheme. For peculiar velocities, this situation is 
-opposite, where V-web scheme is much more adequate to assign typical 
-distributions of velocity to each environment. Although T-web also makes 
-a differentiation in the distributions of velocity, this is very slight 
-compared with the V-web case. These results can be explained by appealing 
-the physical origin of each web scheme. As T-web is based upon the Hessian 
-matrix of the potential field, it is expected all quantities related to 
-the potential, like density field and distribution of halos mass, are 
-well-differentiated among each region, while the V-web scheme, based upon 
-the shear velocity tensor, all dynamical quantities, as the peculiar 
-velocity field and the distribution of the velocity of halos are also 
-expected to be well-differentiated among regions as quantified by this 
-scheme.
-
-Finally, we also calculate typical distributions of the density and 
-peculiar velocity fields in each type of environment by using all cells of
-the simulation grid instead of dark matter halos, obtaining completely
-analogous results. Furthermore, we also use a BDM catalogue for the dark
-matter halos, obtaining very similar results.
-
 %*************************************************************************
@@
 increase the threshold value $\lambda_{th}$, all voids grow up 
-progressively through contours of the $\lambda_3$ field until certain 
+progressively through contours of the $\lambda_1$ field until certain 
 critical value where they are so large that the visual impression is no 
@@
 Once has been determined the reliability of the FA index for tracing 
-different properties of voids, our novel proposal here is rather using the 
-FA field for classifying void regions. As was concluded in the previous 
+the geometry of voids, our novel proposal here is rather using the FA 
+field for classifying void regions. As was concluded in the previous 
 subsection, the geometry of voids is completely traced by contours of the
@@
 %.........................................................................
-%FIGURE 1: Typical mass and pecular velocity
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Tweb.pdf}
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Vweb.pdf}
-
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Tweb.pdf}
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Vweb.pdf}
-
-  \captionof{figure}{\small Distribution of masses of dark matter halos
-  according the region where they are embedded for both web schemes 
-  (upper panels) and of peculiar velocity (lower panels). It can be 
-  noticed that the T-web scheme selects different mass ranges according
-  to the environment, while the V-web scheme is better selecting ranges
-  of peculiar velocity of the dark matter halos. This can be understood
-  taking into account the physical origin of each web scheme.}
-
-  \label{fig:typical_mass_velocity}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 2: FA and vissual impression
+%FIGURE 1: FA and vissual impression
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 3: Distributions of FA and density regarding the Lambda_1 eigenvalue
+%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
 \begin{flushleft}

### 2014-05-29 bench/codes_figures/cosmicweb_fractional_anisotropy.py
Including found regions of bulk voids and updating to BDM catalogues

@@ -41,9 +41,9 @@ smooth = '_s1'
 #Coordinate to cut (1 -- X, 2 -- Y, 3 -- Z)
 axe = 1
 #Cut
-Cut = 100
+Cut = 200
 #Halos slice cut [Mpc]
-dx = 5
+dx = 2
 
 #Colors
 my_cmapC = plt.cm.get_cmap('gray')
@@ -65,8 +65,8 @@ FIGURE SCHEME
 |  1  |  2  |  3  |
 -------------------
 '''
-plt.figure( figsize=(8,8) )
-plt.subplots_adjust( top=0.93, bottom = 0.07, right = .98, left = 0.04, hspace = 0.14, wspace=0.0 )
+plt.figure( figsize=(18,7) )
+plt.subplots_adjust( top=0.93, bottom = 0.07, right = .98, left = 0.04, hspace = 0.14, wspace=0.08 )
 #Extent
 extent = [0, Box_L, 0, Box_L]
 
@@ -90,9 +90,9 @@ eig2 = CutFieldZ( eig_filename+"_2", Cut, 16, Coor = axe )
 eig3 = CutFieldZ( eig_filename+"_3", Cut, 16, Coor = axe )
 
 #Visual impression
-plt.subplot( 1, 4, 1 )
+plt.subplot( 1, 3, 1 )
 Coor, X = CutHaloZ( Cut*Box_L/(1.0*N_sec)-dx/2.0, dx, GH, plot = False )
-plt.plot( Coor[0], Coor[1], 'o', color = 'blue', markersize = 2 )
+plt.plot( Coor[0], Coor[1], '.', color = 'blue', markersize = 2 )
 plt.imshow( -np.transpose(Scheme( eig1, eig2, eig3, Lambda_opt )[::,::-1]), extent = extent, vmin=-3, vmax=0, cmap = my_cmap4 )
 plt.title( "Vissual impresion for $\lambda_{th} = %1.3f$"%(Lambda_opt) )
 plt.yticks( (),() )
@@ -100,10 +100,10 @@ plt.xticks( (0,Box_L) )
 plt.xlabel( "[$h^{-1}$ Mpc]" )
 
 #FA field
-plt.subplot( 1, 4, 2 )
-plt.imshow( np.transpose(Fractional_Anisotropy( eig1, eig2, eig3 )[::,::-1]), extent = extent,  cmap = "binary" )
+plt.subplot( 1, 3, 2 )
[…]

### 2014-05-29 cosmic_voids.tex
Updating paper

@@
 
-  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
-  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
-
-  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
-  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+  \includegraphics[trim = 16mm 10mm 5mm 8mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+  \includegraphics[trim = 16mm 10mm 5mm 8mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
 

### 2014-06-05 bench/codes_analysis/density_classification.py
Little error in labels of figures

@@ -18,7 +18,7 @@ N_sec = 256
 #Smooth parameter
 smooth = '_s1'
 #N delta
-N_delta = 300
+N_delta = 100000
 
 #==================================================================================================
 #			CONSTRUCTING MEDIANS OF DENSITY REGARDING LAMBDA_1
@@ -32,6 +32,11 @@ delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,simulation,N_sec,smooth)
 os.system( "./Density_Classification.out %s %d"%( delta_filename, N_delta ) )
 datos = np.loadtxt( "temp.tmp" )
 
-plt.loglog( datos[:,0]+1, datos[:,1]/(N_sec**3), "-" )
+plt.semilogx( datos[:,0]+1, np.cumsum(datos[:,1])/(N_sec**3), "-" )
+
+plt.hlines( 0.5097, 1e-3, 1e3 ) #Voids
+plt.hlines( 0.8735, 1e-3, 1e3 ) #Sheets
+plt.hlines( 0.9902, 1e-3, 1e3 ) #Filaments
+
 plt.grid()
 plt.show()

### 2014-06-05 bench/codes_figures/cosmicweb_density_field.py

@@ -1,9 +1,9 @@
-
-#cosmicweb_fractional_anisotropy.py
+#cosmicweb_density_field.py
 #
 #This code perform a graphic scheme of the visual impresion for a defined cutting off of Bolshoi
-#simulation, using the FA, it is shown how is the behaviour of voids found through web schemes.
-#Usage cosmicweb_fractional_anisotropy.py <Vweb or Tweb> <catalogue, BDM or FOF> <show(0) or save(1)>
+#simulation, using the density field it is performed a classification scheme of voids based upon
+#cuts of the density.
+#Usage cosmicweb_density_field.py <catalogue, BDM or FOF> <show(0) or save(1)>
 #
 #by: Sebastian Bustamante
 
@@ -19,22 +19,13 @@ Box_L = 250
 #Number of sections
 N_sec = 256
 
-#Web scheme
-web = sys.argv[1]
-
 #Halo Scheme
-catalog = sys.argv[2]
+catalog = sys.argv[1]
 
 #Void catalogue
 void_scheme = "FAG"
 #Void lambda_th
 lambda_void = 0.0
-
-#Values to evaluate lambda_th
-if web == 'Tweb':
-    Lambda_opt = 0.265
-if web == 'Vweb':
-    Lambda_opt = 0.175
 #Smooth parameter
 smooth = '_s1'
 #Coordinate to cut (1 -- X, 2 -- Y, 3 -- Z)
@@ -71,27 +62,21 @@ extent = [0, Box_L, 0, Box_L]
 
 #Loading Density filename
 delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,simulation,N_sec,smooth)
-#Loading Vweb filename
-eig_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
 #Loading general catalog of halos
 GH = np.loadtxt('%s%sC_GH_%s.dat'%(foldglobal,simulation,catalog))
 #Catalogueof voids
 voids = CutFieldZ( "%s/%s/%s/%d/voids%s/voids_%1.2f/void_index.dat"%\
-(foldglobal, simulation, web, N_sec, void_scheme, lambda_void ), Cut, 'plain', Coor = axe )    
[…]

### 2014-06-05 cosmic_voids.tex
Updating pdf

@@
 %.........................................................................
-%FIGURE 1: FA and vissual impression
+%Table of sizes of each sample defined in Bolshoi
+\begin{table}[h]
 \begin{flushleft}
-\begin{figure*}
-\centering
+\begin{center}
+  \begin{tabular}{l  r  r  r r} \hline\hline
+	\textbf{Volume}					&				&\textbf{Scheme}& \\
+	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\rho_{th}}$  \\ \hline
+	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
+	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
+	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
+	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
+  \end{tabular}  
+  \captionof{table}{\small Size of each sample defined in the Bolshoi 
+  simulation and for each of the two schemes used to detect halos (FOF 
+  and BDM).}
 
-  \includegraphics[trim = 16mm 10mm 5mm 8mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
-  \includegraphics[trim = 16mm 10mm 5mm 8mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+  \label{tab:Samples_Size}
 
-  \captionof{figure}{\small In left panels is shown the visual impression 
-  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
-  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
-  defined types of environment, where voids corresponds to white zones, 
-  sheets to gray, filaments to dark gray and finally knots to black regions. 
-  In the right panels is shown the fractional anisotropy field for the same 
-  slide of the simulation and for each web schemes, where black regions 
-  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
-  degeneration of low values of FA for knots and central regions of voids, 
-  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
-  and highly planar sheets. Thin dark red curves correspond to contours of
-  $FA=0.95$, which is approximately the transitional FA between voids and
-  other cosmological regions.}
-
-  \label{fig:FA_field}
-  \vspace{0.1 cm}
-
-\end{figure*}
+\end{center}
 \end{flushleft}
+\end{table}
 %.........................................................................
@@
 %.........................................................................
-%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
+%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
 \begin{flushleft}
@@
 
+%.........................................................................
+%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}
+
+  \captionof{figure}{\small In this figure is shown the distribution of the
+  fractional anisotropy (left panel) and density field (right panel) with 
+  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
+  lines. V-web, blue lines) as calculated over all the cells of the grid.
+  Thick central lines correspond to the median of the distribution and 
+  coloured regions to the $50\%$ of the cells, delimited by quartiles 
+  $Q_1$ and $Q_3$.}
+
+  \label{fig:L1_correlations}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 3: FA and vissual impression
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
+
+  \captionof{figure}{\small In left panels is shown the visual impression 
+  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
+  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
+  defined types of environment, where voids corresponds to white zones, 
+  sheets to gray, filaments to dark gray and finally knots to black regions. 
+  In the right panels is shown the fractional anisotropy field for the same 
+  slide of the simulation and for each web schemes, where black regions 
+  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
+  degeneration of low values of FA for knots and central regions of voids, 
+  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
+  and highly planar sheets. Thin dark red curves correspond to contours of
+  $FA=0.95$, which is approximately the transitional FA between voids and
+  other cosmological regions.}
+
+  \label{fig:FA_field}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
 \end{document}

### 2014-06-25 bench/codes_figures/void_volume_regions.py
Adding volume function of voids in paper tex file

@@ -32,12 +32,12 @@ colors = ["gray", "black"]
 #			CONSTRUCTING REGIONS VOLUME
 #==================================================================================================
 
-fig = plt.figure( figsize=(5*len(webs),5) )
-fig.subplots_adjust( top = 0.9, right = 0.98, left = 0.05, wspace = 0.11 )
+fig = plt.figure( figsize=(4.5*len(webs),4.5) )
+fig.subplots_adjust( top = 0.9, right = 0.98, left = 0.05, wspace = 0.05, bottom = 0.1 )
 ax1 = [fig.add_subplot(1,len(webs),i+1) for i in xrange(len(webs))]
 ax2 = [ax1[i].twiny() for i in xrange(len(webs))]
 
-tick_locations = np.array( [0,1,2,3,4,5,6] )
+tick_locations = np.linspace(0,4,5)
 #Function to build the second axe
 def tick_function(X):
     return ((10**X*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
@@ -67,8 +67,8 @@ for web in webs:
 	    distro = np.cumsum(hist1d[0][::-1])[::-1]
 	    
 	#Plot
-	ax1[i_web].semilogy( hist1d[1][:-1], distro, linewidth = 1.5, linestyle = linestyles[i_iter],\
-	color = colors[i_iter%2], label = "%s (%s)"%(web, iter))
+	ax1[i_web].semilogy( hist1d[1][:-1], distro, linewidth = 2.0, linestyle = linestyles[i_iter],\
+	color = colors[i_iter%2], label = "%s (%s)"%(web, iter) )
       
 	i_iter += 1
 	
@@ -79,7 +79,9 @@ for i in range(len(webs)):
     #Axe 1
     ax1[i].grid()
     ax1[i].text( 0.1, 10**3.8, labels[i], fontsize = 12, fontweight = "bold" )
+    ax1[i].set_xticks( np.linspace(0,5,6) )
     ax1[i].set_xlim( (0,4.5) )
+    
     if i == 0:
 	ax1[i].set_ylabel( "Number of voids" )
     else:
@@ -90,10 +92,11 @@ for i in range(len(webs)):
 	#ax1[i].legend( fancybox = True, shadow = True, loc = 'lower left', ncol = len(webs), fontsize = 9 )
 
     #Axe 2
+    ax2[i].set_xlim( (0,4.5) )
     ax2[i].set_xticks( tick_locations )
[…]

### 2014-07-01 cosmic_voids.tex
Adding volume function of voids in paper tex file
Updating pdf paper

@@
 %.........................................................................
-%FIGURE 3: FA and vissual impression
+%FIGURE 3: volume functions
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/voids_regions_volume_all.pdf}
+
+  \captionof{figure}{\small Volume functions of voids catalogued by each 
+  used scheme. Left panel (watershed transform over the FA field of the T-web 
+  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
+  (over the density field). Gray curves correspond to voids without boundary 
+  removal whereas black curves are associated to voids merged through boundary 
+  removal process. Dotted lines correspond to original continuous fields, 
+  while segmented lines correspond to fields with a 1st-order median filtering 
+  and continuous lines to a 2nd-order median filtering.}
+
+  \label{fig:FA_field}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 4: FA and vissual impression
 \begin{flushleft}

### 2014-07-01 bench/codes_figures/cosmicweb_density_field.py

@@ -25,7 +25,7 @@ catalog = sys.argv[1]
 #Void catalogue
 void_scheme = "DLG"
 #Void parameters ( Nth-order median filtering,  Boolean for boundary removals )
-config = "151"
+config = "51"
 #Smooth parameter
 smooth = '_s1'
 #Coordinate to cut (1 -- X, 2 -- Y, 3 -- Z)

### 2014-07-01 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -29,7 +29,7 @@ catalog = sys.argv[2]
 #Void catalogue
 void_scheme = "FAG"
 #Void parameters ( Nth-order median filtering,  Boolean for boundary removals )
-config = "141"
+config = "21"
 
 #Values to evaluate lambda_th
 if web == 'Tweb':

### 2014-07-01 bench/codes_figures/void_percolation_analysis.py

@@ -16,14 +16,14 @@ simulation = "BOLSHOI/"
 #Number of sections
 N_sec = 256
 #Web Scheme
-webs = ['Vweb', 'Tweb', 'Tweb'] 
-labels = ['FA-Vweb', 'FA-Tweb', 'Density']
+webs = ['Tweb', 'Vweb', 'Tweb'] 
+labels = ['FA-Tweb', 'FA-Vweb', 'Density']
 #Void finder schemes
 void_schemes = ['FAG','FAG','DLG']
 #Order of median filtering
 Nfilter = 15
 #Minim volum to consider a void
-VOL = 20
+VOL = 0
 
 #Colors
 colors = ["green", "blue", "red"]
@@ -69,8 +69,8 @@ for web in webs:
     VoidsMedian1 = np.array( VoidsMedian1 )
 	
     plt.subplot(121)
-    plt.semilogy( VoidsNumber0, color = colors[i_web], linestyle = "--", linewidth = 2 )
-    plt.semilogy( VoidsNumber1, color = colors[i_web], linestyle = "-", linewidth = 2 )
+    plt.plot( VoidsNumber0/10000., color = colors[i_web], linestyle = "--", linewidth = 2 )
+    plt.plot( VoidsNumber1/10000., color = colors[i_web], linestyle = "-", linewidth = 2 )
     
     plt.subplot(122)
     plt.plot( VoidsVolume0/10000., color = colors[i_web], linestyle = "--", linewidth = 2 )
@@ -92,6 +92,6 @@ plt.grid()
 
 
 if sys.argv[1] == '1':
-    plt.savefig( '%svoids_regions_volume.pdf'%(figures_fold) )
+    plt.savefig( '%svoids_percolation_analysis.pdf'%(figures_fold) )
 else:
     plt.show()

### 2014-07-01 bench/codes_figures/void_volume_regions_all.py

@@ -1,0 +1,93 @@
+#void_volume_regions_all.py
+#
+#This code calculate an volume functions for each void finder scheme
+#Usage void_volume_regions_all.py <normal(0) or cumulative(1)> <show(0) or save(1)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Web Scheme
+webs = ['Tweb', 'Vweb', 'DLG'] 
+labels = ['FA-Tweb', 'FA-Vweb', 'Density']
+#Void finder scheme (FAG or FOF)
+void_scheme = 'FAG'
+#Schemes used for each web
+schemes = [ "21","31","51" ]
+
+#Colors
+colors = ["green", "blue", "red"]
+
+#==================================================================================================
+#			CONSTRUCTING REGIONS VOLUME
+#==================================================================================================
+
+fig = plt.figure( figsize=(5,5) )
+fig.subplots_adjust( top = 0.9, right = 0.98, left = 0.12, wspace = 0.05, bottom = 0.1 )
+ax1 = [fig.add_subplot(1,1,i+1) for i in xrange(1)]
+ax2 = [ax1[i].twiny() for i in xrange(1)]
+
+tick_locations = np.linspace(0,4,5)
+#Function to build the second axe
+def tick_function(X):
+    return ((10**X*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
+
+i_web = 0
+for web in webs:
+    print simulation, web
+
+    #DENSITY WATERSHED TRANSFORM
+    if web == 'DLG':
+	void_regs = np.transpose(np.loadtxt("%s/%s/%s/%d/voids%s/voids_%s/void_regions.dat"%\
+	(foldglobal, simulation, "Tweb", N_sec, web, schemes[i_web] )))
+    #FA WATERSHED TRANSFORM    
+    else:
+	void_regs = np.transpose(np.loadtxt("%s/%s/%s/%d/voids%s/voids_%s/void_regions.dat"%\
+	(foldglobal, simulation, web, N_sec, void_scheme, schemes[i_web] )))
+
[…]

### 2014-07-02 bench/codes_figures/void_percolation_analysis.py
New percolation analysis, codes, figures and pdf

@@ -32,6 +32,12 @@ colors = ["green", "blue", "red"]
 #			CONSTRUCTING FIGURE
 #==================================================================================================
 
+plt.figure( figsize = (10,5) )
+plt.subplots_adjust( left = 0.06, right = 0.98, top = 0.94, bottom = 0.1 )
+#Function to build equivalent radius
+def tick_function(X):
+    return ((10**X*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
+
 i_web = 0
 for web in webs:
     print simulation, web
@@ -73,8 +79,8 @@ for web in webs:
     plt.plot( VoidsNumber1/10000., color = colors[i_web], linestyle = "-", linewidth = 2 )
     
     plt.subplot(122)
-    plt.plot( VoidsVolume0/10000., color = colors[i_web], linestyle = "--", linewidth = 2 )
-    plt.plot( VoidsVolume1/10000., color = colors[i_web], linestyle = "-", linewidth = 2, label = labels[i_web] )
+    plt.plot( VoidsVolume0, color = colors[i_web], linestyle = "--", linewidth = 2 )
+    plt.plot( VoidsVolume1, color = colors[i_web], linestyle = "-", linewidth = 2, label = labels[i_web] )
     
     #plt.plot( VoidsMedian0/10000., color = colors[i_web], linestyle = "--", linewidth = 2 )
     #plt.plot( VoidsMedian1/10000., color = colors[i_web], linestyle = "-", linewidth = 2, label = labels[i_web] )
@@ -85,11 +91,17 @@ for web in webs:
 #Formating figures
 plt.subplot(121)
 plt.grid()
+plt.xlabel( "Order of Median Filtering ($n\ th$-MF)" )
+plt.ylabel( "Number of voids $[\\times 10^4]$" )
+plt.title( "Number of voids" )
 
 plt.subplot(122)
 plt.legend( loc='upper left', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
 plt.grid()
-
+plt.xlabel( "Order of Median Filtering ($n\ th$-MF)" )
+plt.ylabel( "Effective radius [Mpc $h^{-1}$]" )
+plt.yticks( arange(0,160000,20000), ["%1.0f"%(tick_function(np.log10(v))) for v in arange(0,160000,20000) ] )
+plt.title( "Volume of the biggest void" )
 
 if sys.argv[1] == '1':
     plt.savefig( '%svoids_percolation_analysis.pdf'%(figures_fold) )

### 2014-07-02 bench/codes_figures/void_volume_regions_all.py

@@ -85,7 +85,7 @@ for i in range(1):
     for tick in tick_locations:
 	tick_label.append( "%1.1f"%tick_function(tick) )
     ax2[i].set_xticklabels( tick_label )
-    ax2[i].set_xlabel( "Effective radius Mpc $h^{-1}$" )
+    ax2[i].set_xlabel( "Effective radius [Mpc $h^{-1}$]" )
 
 if sys.argv[2] == '1':
     plt.savefig( '%svoids_regions_volume_all.pdf'%(figures_fold) )

### 2014-07-02 cosmic_voids.tex
New percolation analysis, codes, figures and pdf
References and new format of plots

@@
 
-The spatial distribution of galaxies describes a web-like pattern, the 
-so-called cosmic web. Today it is understood that such configuration is 
-driven by gravitational instabilities. ...
-
-Relevant information about previous works and current state of the art.
+Cosmic voids are one of the more striking features of the Mpc universe, 
+where they are complementary to the filamentary 
+\cite{Neyrinck08}
 
@@
 
-As it was previously mentioned, we use an unconstrained cosmological 
-simulation, the Bolshoi simulation, to identify the possible large scale 
-environment of the Local Group. This is a similar approach to the one already 
-used by \SRKED{[reference here]}.
+We use here an unconstrained cosmological simulation, the Bolshoi 
+simulation, to identify the possible large scale environment and 
+cosmological voids.
 
@@
 particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
-We identify halos with two algorithms, the Friends-of-Friends \SRKED{
-[reference here]} algorithm and the Bound Density Maximum algorithm.
+We identify catalogues of halos through the Bound Density Maximum 
+algorithm.
 
@@
 
-\bibliographystyle{mn2e}
+\bibliographystyle{latex/mn2e}
 \bibliography{references}
@@
 %.........................................................................
-%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
+%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 3: volume functions
+%FIGURE 3: Percolation Analysis
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.6\textheight]{./figures/voids_percolation_analysis.pdf}
+
+  \captionof{figure}{\small Volume functions of voids catalogued by each 
+  used scheme. Left panel (watershed transform over the FA field of the T-web 
+  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
+  (over the density field). Gray curves correspond to voids without boundary 
+  removal whereas black curves are associated to voids merged through boundary 
+  removal process. Dotted lines correspond to original continuous fields, 
+  while segmented lines correspond to fields with a 1st-order median filtering 
+  and continuous lines to a 2nd-order median filtering.}
+
+  \label{fig:FA_field}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 4: volume functions
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 4: FA and vissual impression
+%FIGURE 5: FA and vissual impression
 \begin{flushleft}

### 2014-07-02 bench/codes_figures/cosmicweb_density_field.py

@@ -90,7 +90,7 @@ for i in xrange(N_sec):
 
 #FA field
 plt.subplot( 1, 3, 1 )
-plt.imshow( np.transpose(np.log( delta + 1 )[::,::-1]), extent = extent, cmap = "binary" )
+plt.imshow( np.transpose(np.log( delta + 1 )[::,::-1]), extent = extent, cmap = "hot" )
 #plt.contour( np.transpose(delta), levels=[-0.57], extent = extent, linestyles="-",\
 #colors=[(0.8,0.0,0.0)], alpha=1.0, linewidths=0.6 )
 plt.title( "Density Field" )

### 2014-07-02 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -104,7 +104,7 @@ for i in xrange(N_sec):
 
 #FA field
 plt.subplot( 1, 3, 1 )
-plt.imshow( np.transpose(Fractional_Anisotropy( eig1, eig2, eig3 )[::,::-1]), extent = extent, cmap = "binary" )
+plt.imshow( -np.transpose(Fractional_Anisotropy( eig1, eig2, eig3 )[::,::-1]), extent = extent, cmap = "hot" )
 #plt.contour( np.transpose(Fractional_Anisotropy( eig1, eig2, eig3 )), levels=[0.95], extent = extent, \
 #colors="red", alpha=0.5, linewidths=0.6 )
 #plt.imshow( Scheme( eig1, eig2, eig3, 0.0 )[::-1,], extent = extent, vmin=0, vmax=0.5, cmap = cmap2, origin='lower' )

### 2014-07-02 cosmic_voids.tex
Part of introduction and more references bibtex

@@
 
-Cosmic voids are one of the more striking features of the Mpc universe, 
-where they are complementary to the filamentary 
-\cite{Neyrinck08}
+Since voids where discovered in the first compiled galaxy surveys 
+\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
+Kirshner87}, they have been identified as one of the most striking features 
+of the Megaparsec universe, being a complementary aspect along with the 
+filamentary and hierarchically clustered nature of the cosmic web 
+\citep{Bond96}.
 

### 2014-07-06 cosmic_voids.tex
New title and references
Changing scale of volume function of voids, effective radius instead of log10 volume

@@
 %=========================================================================
-\title{Analysis of bulk void regions}
+\title{Fractional anisotropy as tracer of cosmic voids}
 \author[S. Bustamante and J.E. Forero-Romero]{
@@
 
+%.........................................................................
+%FIGURE 6: shape-distributions
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 6mm 8mm 5.5mm 4mm, clip, keepaspectratio=true,
+  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb_FAG.pdf}
+  \includegraphics[trim = 6mm 8mm 5.5mm 4mm, clip, keepaspectratio=true,
+  width=0.36\textheight]{./figures/voids_inertia_tensor_Vweb_FAG.pdf}
+
+  \
+
+  \includegraphics[trim = 6mm 8mm 5.5mm 4mm, clip, keepaspectratio=true,
+  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb_DLG.pdf}
+
+  \captionof{figure}{\small Volume functions of voids catalogued by each 
+  used scheme. Left panel (watershed transform over the FA field of the T-web 
+  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
+  (over the density field). Gray curves correspond to voids without boundary 
+  removal whereas black curves are associated to voids merged through boundary 
+  removal process. Dotted lines correspond to original continuous fields, 
+  while segmented lines correspond to fields with a 1st-order median filtering 
+  and continuous lines to a 2nd-order median filtering.}
+
+  \label{fig:FA_field}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
 \end{document}

### 2014-07-06 bench/codes_figures/void_inertia_distribution.py

@@ -28,6 +28,8 @@ void_scheme = sys.argv[2]
 #Nbins of each histogram
 Nbins = 20
 Nbins2D = 10
+#Minim radius for a void
+rmin = 0
 
 prop1_hist = 5
 prop2_hist = 5
@@ -81,8 +83,9 @@ bins = Nbins2D, normed = False, range = ((0,1),(0,1))  )[0][::,::-1])
 #map2d = axHist2D.imshow( Hist_lambd[::,::], interpolation='nearest', aspect = 'auto',
 #cmap = 'binary', extent = (0,1,0,1) )	
 #Scatter
-scatter = axHist2D.scatter( eigen[0]/eigen[1], eigen[1]/eigen[2], 
-c = np.log10(r_eff(np.log10(catalog[1]))), s=50, marker='.',linewidth=0.01, cmap='jet' )
+reff = r_eff(np.log10(catalog[1]))
+scatter = axHist2D.scatter( eigen[0,reff>rmin]/eigen[1,reff>rmin], eigen[1,reff>rmin]/eigen[2,reff>rmin], 
+c = np.log10(reff[reff>rmin]), s=50, marker='.',linewidth=0.01, cmap='jet', vmin = 0.1, vmax = 1.2 )
 
 #Create the colorbar
 axc, kw = matplotlib.colorbar.make_axes( axHistx, orientation = "vertical", shrink=1., pad=.1, aspect=10 )

### 2014-07-06 bench/codes_figures/void_volume_regions_all.py

@@ -30,11 +30,11 @@ colors = ["green", "blue", "red"]
 #==================================================================================================
 
 fig = plt.figure( figsize=(5,5) )
-fig.subplots_adjust( top = 0.9, right = 0.98, left = 0.12, wspace = 0.05, bottom = 0.1 )
+fig.subplots_adjust( top = 0.9, right = 0.96, left = 0.12, wspace = 0.05, bottom = 0.1 )
 ax1 = [fig.add_subplot(1,1,i+1) for i in xrange(1)]
 ax2 = [ax1[i].twiny() for i in xrange(1)]
 
-tick_locations = np.linspace(0,4,5)
+tick_locations = np.linspace(0,20,6)
 #Function to build the second axe
 def tick_function(X):
     return ((10**X*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
@@ -52,7 +52,7 @@ for web in webs:
 	void_regs = np.transpose(np.loadtxt("%s/%s/%s/%d/voids%s/voids_%s/void_regions.dat"%\
 	(foldglobal, simulation, web, N_sec, void_scheme, schemes[i_web] )))
 
-    hist1d = np.histogram( np.log10(void_regs[1]) , bins=20, normed=False )
+    hist1d = np.histogram( tick_function(np.log10(void_regs[1])) , bins=15, normed=False )
     
     #Normal distribution
     if sys.argv[1] == '0':
@@ -71,11 +71,11 @@ for web in webs:
 for i in range(1):
     #Axe 1
     ax1[i].grid()
-    ax1[i].set_xticks( np.linspace(0,5,6) )
-    ax1[i].set_xlim( (0,4.5) )
+    ax1[i].set_xticks( np.linspace(0,20,6) )
+    ax1[i].set_xlim( (0,20) )
     
     ax1[i].set_ylabel( "Number of voids" )
-    ax1[i].set_xlabel( "Comoving volume $\log_{10}[ (0.98$ Mpc $h^{-1} )^{-3} ]$" )
+    ax1[i].set_xlabel( "Effective radius [Mpc $h^{-1}$]" )
     ax1[i].legend( loc='upper right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
 
     #Axe 2
@@ -83,9 +83,9 @@ for i in range(1):
     ax2[i].set_xticks( tick_locations )
     tick_label = []
[…]

### 2014-07-08 bench/codes_figures/monte_carlo_FA.py
New format for figures of size distribution

@@ -1,33 +1,0 @@
-#monte_carlo_FA.py
-#
-#This code makes a MonteCarlo studying of the FA function as defined in Libeskind12 in order to 
-#determine values of the FA according to the geometry.
-#Usage monte_carlo_FA.py
-#
-#by: Sebastian Bustamante
-
-execfile('_Head.py')
-
-#==================================================================================================
-#			PARAMETERS
-#==================================================================================================
-#Simulation
-simulation = "BOLSHOI/"
-#Number of sections
-N_sec = 256
-#Web Scheme
-webs = ['Tweb', 'Vweb'] 
-#Colors
-colors = ['green', 'blue']
-#Void finder scheme (FOF or LAY)
-void_scheme = 'LAY'
-#Lambda values
-Lambda_th = np.arange( 0, 1.0, 0.01 )
-
-#==================================================================================================
-#			CONSTRUCTING REGIONS VOLUME
-#==================================================================================================
-if sys.argv[1] == '1':
-    plt.savefig( '%svoids_regions_percolation_%s.pdf'%(figures_fold,void_scheme) )
-else:
-    plt.show()

### 2014-07-11 time-machine/cosmic_voids(29-05-14).tex
.

--- 2014-07-02 cosmic_voids.tex
@@
 
-Cosmic voids are one of the more striking features of the Mpc universe, 
-where they are complementary to the filamentary 
-\cite{Neyrinck08}
+The spatial distribution of galaxies describes a web-like pattern, the 
+so-called cosmic web. Today it is understood that such configuration is 
+driven by gravitational instabilities. ...
+
+Relevant information about previous works and current state of the art.
 
@@
 
-We use here an unconstrained cosmological simulation, the Bolshoi 
-simulation, to identify the possible large scale environment and 
-cosmological voids.
+As it was previously mentioned, we use an unconstrained cosmological 
+simulation, the Bolshoi simulation, to identify the possible large scale 
+environment of the Local Group. This is a similar approach to the one already 
+used by \SRKED{[reference here]}.
 
@@
 particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
-We identify catalogues of halos through the Bound Density Maximum 
-algorithm.
+We identify halos with two algorithms, the Friends-of-Friends \SRKED{
+[reference here]} algorithm and the Bound Density Maximum algorithm.
 
@@
 features of the cosmic web.
+
+%-------------------------------------------------------------------------
+\subsection{Dark matter halos as tracers of the cosmic web 
+\SRKED{(Possibly not included) [?]}}
+\label{subsec:halos_cosmicweb}
+%-------------------------------------------------------------------------
+
+Both established schemes to quantify the cosmic web depend on continuous 
+and smooth physical quantities, i.e the peculiar velocity field and the 
+density field. To calculate these quantities, a discretization over the 
+volume of the simulation is performed, so all the properties are reduced 
+to single values associated to discrete cells. According to this, we 
+divide the overall volume into $(256)^3$ cells, so each cell has an 
+associated comoving cubic volume of $0.98 \mbox{ Mpc h}^{-1}$. Finally, in 
+order to reduce possible effects due to the discretization process, a 
+gaussian softening is performed between neighbour cells.
+
+Once defined the numerical details about both classification schemes, we
+shall analyse the dependence on the threshold value $\lambda_{th}$ for 
+each one. For this, we shall use the distribution of dark matter halos as 
+tracer of the underlying matter field in order to be more consistent with
+available observational data. Therefore, we analyse distributions of mass 
+and peculiar velocity in order to assign typical values to each type of 
+environment. In the figure \ref{fig:typical_mass_velocity} we calculate 
+both distributions for both web schemes and using the FOF catalogue of the 
+simulation. Thick lines correspond to the median of the distribution and 
+filled regions limited by dashed lines correspond to quartiles $Q_1$ and 
+$Q_3$, it means, $50\%$ of all halos are within such regions for every 
+\lth value and for each type of environment. We rather use median and 
+quartiles as measure of dispersion because there are some very unusual 
+and extreme values that makes the usual analysis based upon means and 
+standard deviations less reliable.
+
+A first interesting feature of the figure  \ref{fig:typical_mass_velocity} 
+is the median mass for each region. In the case of the T-web, although 
+dispersions of the distribution of mass for each environment are 
+considerably overlapped each other, the median value is very 
+well-differentiated among types of environment, indicating that it is 
+possible to assign typical values of mass to each region, and being 
+consistent with expectations, where low mass halos are typical in voids 
+and higher mass halos in knots. For the case of the V-web scheme, all
+medians and dispersions are completely overlapped, indicating that it is 
+not possible to assign typical mass ranges to each environment as 
+quantified by this scheme. For peculiar velocities, this situation is 
+opposite, where V-web scheme is much more adequate to assign typical 
+distributions of velocity to each environment. Although T-web also makes 
+a differentiation in the distributions of velocity, this is very slight 
+compared with the V-web case. These results can be explained by appealing 
+the physical origin of each web scheme. As T-web is based upon the Hessian 
+matrix of the potential field, it is expected all quantities related to 
+the potential, like density field and distribution of halos mass, are 
+well-differentiated among each region, while the V-web scheme, based upon 
+the shear velocity tensor, all dynamical quantities, as the peculiar 
+velocity field and the distribution of the velocity of halos are also 
+expected to be well-differentiated among regions as quantified by this 
+scheme.
+
+Finally, we also calculate typical distributions of the density and 
+peculiar velocity fields in each type of environment by using all cells of
+the simulation grid instead of dark matter halos, obtaining completely
+analogous results. Furthermore, we also use a BDM catalogue for the dark
+matter halos, obtaining very similar results.
 
@@
 increase the threshold value $\lambda_{th}$, all voids grow up 
-progressively through contours of the $\lambda_1$ field until certain 
+progressively through contours of the $\lambda_3$ field until certain 
 critical value where they are so large that the visual impression is no 
@@
 
-\bibliographystyle{latex/mn2e}
+\bibliographystyle{mn2e}
 \bibliography{references}
@@
 %.........................................................................
-%Table of sizes of each sample defined in Bolshoi
-\begin{table}[h]
+%FIGURE 1: Typical mass and pecular velocity
 \begin{flushleft}
-\begin{center}
-  \begin{tabular}{l  r  r  r r} \hline\hline
-	\textbf{Volume}					&				&\textbf{Scheme}& \\
-	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\rho_{th}}$  \\ \hline
-	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
-	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
-	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
-	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
-  \end{tabular}  
-  \captionof{table}{\small Size of each sample defined in the Bolshoi 
-  simulation and for each of the two schemes used to detect halos (FOF 
-  and BDM).}
+\begin{figure*}
+\centering
 
-  \label{tab:Samples_Size}
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Tweb.pdf}
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/halos_typical_mass_FOF_Vweb.pdf}
 
-\end{center}
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Tweb.pdf}
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/halos_typical_velocity_FOF_Vweb.pdf}
+
+  \captionof{figure}{\small Distribution of masses of dark matter halos
+  according the region where they are embedded for both web schemes 
+  (upper panels) and of peculiar velocity (lower panels). It can be 
+  noticed that the T-web scheme selects different mass ranges according
+  to the environment, while the V-web scheme is better selecting ranges
+  of peculiar velocity of the dark matter halos. This can be understood
+  taking into account the physical origin of each web scheme.}
+
+  \label{fig:typical_mass_velocity}
+  \vspace{0.1 cm}
+
+\end{figure*}
 \end{flushleft}
-\end{table}
 %.........................................................................
@@
 %.........................................................................
-%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
+%FIGURE 2: FA and vissual impression
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
+  width=0.5\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+
+  \includegraphics[trim = 25mm 200mm 18mm 15mm, clip, keepaspectratio=true,
+  width=0.5\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+
+  \captionof{figure}{\small In left panels is shown the visual impression 
+  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
+  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
+  defined types of environment, where voids corresponds to white zones, 
+  sheets to gray, filaments to dark gray and finally knots to black regions. 
+  In the right panels is shown the fractional anisotropy field for the same 
+  slide of the simulation and for each web schemes, where black regions 
+  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
+  degeneration of low values of FA for knots and central regions of voids, 
+  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
+  and highly planar sheets. Thin dark red curves correspond to contours of
+  $FA=0.95$, which is approximately the transitional FA between voids and
+  other cosmological regions.}
+
+  \label{fig:FA_field}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 3: Distributions of FA and density regarding the Lambda_1 eigenvalue
 \begin{flushleft}
@@
 
-%.........................................................................
-%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}
-
-  \captionof{figure}{\small In this figure is shown the distribution of the
-  fractional anisotropy (left panel) and density field (right panel) with 
-  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
-  lines. V-web, blue lines) as calculated over all the cells of the grid.
-  Thick central lines correspond to the median of the distribution and 
-  coloured regions to the $50\%$ of the cells, delimited by quartiles 
-  $Q_1$ and $Q_3$.}
-
-  \label{fig:L1_correlations}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 3: Percolation Analysis
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.6\textheight]{./figures/voids_percolation_analysis.pdf}
-
-  \captionof{figure}{\small Volume functions of voids catalogued by each 
-  used scheme. Left panel (watershed transform over the FA field of the T-web 
-  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
-  (over the density field). Gray curves correspond to voids without boundary 
-  removal whereas black curves are associated to voids merged through boundary 
-  removal process. Dotted lines correspond to original continuous fields, 
-  while segmented lines correspond to fields with a 1st-order median filtering 
-  and continuous lines to a 2nd-order median filtering.}
-
-  \label{fig:FA_field}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 4: volume functions
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/voids_regions_volume_all.pdf}
-
-  \captionof{figure}{\small Volume functions of voids catalogued by each 
-  used scheme. Left panel (watershed transform over the FA field of the T-web 
-  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
-  (over the density field). Gray curves correspond to voids without boundary 
-  removal whereas black curves are associated to voids merged through boundary 
-  removal process. Dotted lines correspond to original continuous fields, 
-  while segmented lines correspond to fields with a 1st-order median filtering 
-  and continuous lines to a 2nd-order median filtering.}
-
-  \label{fig:FA_field}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 5: FA and vissual impression
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
-
-  \captionof{figure}{\small In left panels is shown the visual impression 
-  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
-  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
-  defined types of environment, where voids corresponds to white zones, 
-  sheets to gray, filaments to dark gray and finally knots to black regions. 
-  In the right panels is shown the fractional anisotropy field for the same 
-  slide of the simulation and for each web schemes, where black regions 
-  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
-  degeneration of low values of FA for knots and central regions of voids, 
-  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
-  and highly planar sheets. Thin dark red curves correspond to contours of
-  $FA=0.95$, which is approximately the transitional FA between voids and
-  other cosmological regions.}
-
-  \label{fig:FA_field}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
 \end{document}

### 2014-07-12 cosmic_voids.tex
New format for figures of size distribution
Removing median filtering

--- 2014-07-02 cosmic_voids.tex
@@
 %.........................................................................
-%FIGURE 3: Percolation Analysis
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.6\textheight]{./figures/voids_percolation_analysis.pdf}
-
-  \captionof{figure}{\small Volume functions of voids catalogued by each 
-  used scheme. Left panel (watershed transform over the FA field of the T-web 
-  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
-  (over the density field). Gray curves correspond to voids without boundary 
-  removal whereas black curves are associated to voids merged through boundary 
-  removal process. Dotted lines correspond to original continuous fields, 
-  while segmented lines correspond to fields with a 1st-order median filtering 
-  and continuous lines to a 2nd-order median filtering.}
-
-  \label{fig:FA_field}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 4: volume functions
+%FIGURE 3: volume functions
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 5: FA and vissual impression
+%FIGURE 4: FA and vissual impression
 \begin{flushleft}
@@
 
+%.........................................................................
+%FIGURE 5: shape-distributions
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 6mm 1mm 5mm 4mm, clip, keepaspectratio=true,
+  width=0.75\textheight]{./figures/voids_inertia_tensor.pdf}
+
+  \captionof{figure}{\small Volume functions of voids catalogued by each 
+  used scheme. Left panel (watershed transform over the FA field of the T-web 
+  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
+  (over the density field). Gray curves correspond to voids without boundary 
+  removal whereas black curves are associated to voids merged through boundary 
+  removal process. Dotted lines correspond to original continuous fields, 
+  while segmented lines correspond to fields with a 1st-order median filtering 
+  and continuous lines to a 2nd-order median filtering.}
+
+  \label{fig:FA_field}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
 \end{document}

### 2014-07-16 cosmic_voids.tex
Label of volume filling fractions

@@
 
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
   width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
   width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

### 2014-07-16 bench/codes_figures/cosmicweb_volume_fractions.py

@@ -1,7 +1,7 @@
 #cosmicweb_volume_fraction.py
 #
 #This code computes the volume fraction for both web schemes for some L_th values
-#Usage cosmicweb_volume_fraction.py <Vweb or Tweb> <catalogue, BDM or FOF> <show(0) or save(1)>
+#Usage cosmicweb_volume_fraction.py <Vweb or Tweb> <show(0) or save(1)>
 #
 #by: Sebastian Bustamante
 
@@ -65,6 +65,7 @@ plt.plot( regs[0], regs[0]*0.0, color = 'gray', label = "knots", linewidth=2.0 )
 
 plt.xlim( L_min, 1.0 )
 plt.legend( loc='lower right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
+plt.title( "%s"%(web) )
 plt.xlabel( "$\lambda_{th}$" )
 plt.ylabel( "Volume fraction" )
 #Lambda_th line

### 2014-07-16 bench/codes_figures/void_volume_regions_all.py

@@ -21,6 +21,7 @@ labels = ['FA-Tweb', 'FA-Vweb', 'Density']
 void_scheme = 'FAG'
 #Schemes used for each web
 schemes = [ "21","31","51" ]
+schemes = [ "01","01","01" ]
 
 #Colors
 colors = ["green", "blue", "red"]
@@ -34,7 +35,7 @@ fig.subplots_adjust( top = 0.9, right = 0.96, left = 0.12, wspace = 0.05, bottom
 ax1 = [fig.add_subplot(1,1,i+1) for i in xrange(1)]
 ax2 = [ax1[i].twiny() for i in xrange(1)]
 
-tick_locations = np.linspace(0,20,6)
+tick_locations = np.linspace(0,16,6)
 #Function to build the second axe
 def tick_function(X):
     return ((10**X*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
@@ -63,7 +64,8 @@ for web in webs:
 	
     #Plot
     ax1[0].semilogy( hist1d[1][:-1], distro, linewidth = 2.0, linestyle = "-",\
-    color = colors[i_web], label = "%s (%s-order MF)"%(labels[i_web], schemes[i_web][0]) )
+    #color = colors[i_web], label = "%s (%s-order MF)"%(labels[i_web], schemes[i_web][0]) )
+    color = colors[i_web], label = "%s"%(labels[i_web]) )
       
     i_web += 1
     
@@ -71,15 +73,15 @@ for web in webs:
 for i in range(1):
     #Axe 1
     ax1[i].grid()
-    ax1[i].set_xticks( np.linspace(0,20,6) )
-    ax1[i].set_xlim( (0,20) )
+    ax1[i].set_xticks( np.linspace(0,16,6) )
+    ax1[i].set_xlim( (0,16) )
     
     ax1[i].set_ylabel( "Number of voids" )
     ax1[i].set_xlabel( "Effective radius [Mpc $h^{-1}$]" )
     ax1[i].legend( loc='upper right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
 
     #Axe 2
-    ax2[i].set_xlim( (0,4.5) )
+    ax2[i].set_xlim( (0,4.2) )
     ax2[i].set_xticks( tick_locations )
     tick_label = []
     for tick in tick_locations:

### 2014-07-24 cosmic_voids.tex
References and part of the introduction

@@
 %=========================================================================
-\title{Fractional anisotropy as tracer of cosmic voids}
+\title{Fractional anisotropy as an optimal tracer of cosmic voids}
 \author[S. Bustamante and J.E. Forero-Romero]{
@@
 \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
-Kirshner87}, they have been identified as one of the most striking features 
-of the Megaparsec universe, being a complementary aspect along with the 
-filamentary and hierarchically clustered nature of the cosmic web 
-\citep{Bond96}.
+Kirshner87}, they have been identified, along with the filamentary and 
+hierarchically clustered nature of the cosmic web, as one of the most 
+striking features of the Megaparsec universe \citep{Bond96}. Nevertheless, 
+due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
+h^{-1}$), statistically significant catalogues of voids \citep{Pan10, 
+Sutter12b, Nadathur14} only have become available after modern large galaxy 
+surveys like the two-degree field Galaxy Survey \citep{Colless01, 
+Colless03} and the Sloan Digital Sky Survey \citep{York00,Abazajian03}, 
+thereby triggering a plethora of more refined observational and 
+statistical studies of voids throughout the last decade \citep{Hoyle04,
+Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
+Tikhonov07, BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}
+
+Theoretical 
+efforts for describing the evolution of the large-scale universe, leaded 
+by the seminal work of \citet{Zeldovich70}, are highly consistent with the 
+cosmic web picture, where planar pancake-like regions of matter enclose 
+enormous sub-dense voids and are bordered, in turn, by thin filaments and
+high-density clumpy knots.
 
@@
 Quantifying the shape of voids is gaining importance due to cosmological 
-tests such as the Alcock-Paczynski test \SRKED{[Sutter, et.al (2012)]}, so 
+tests such as the Alcock-Paczynski test \SRKED{[Sutter et al 2012]}, so 
 we compute here the reduced inertia tensor through the next expression in 
@@
   \begin{tabular}{l  r  r  r r} \hline\hline
-	\textbf{Volume}					&				&\textbf{Scheme}& \\
-	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\rho_{th}}$  \\ \hline
+	\textbf{volume}					&				&\textbf{scheme}& \\
+	\textbf{fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
 	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 

### 2014-07-24 cosmic_voids.tex
Theoretical part of the introduction and references to numerical works on voids

@@
 h^{-1}$), statistically significant catalogues of voids \citep{Pan10, 
-Sutter12b, Nadathur14} only have become available after modern large galaxy 
-surveys like the two-degree field Galaxy Survey \citep{Colless01, 
+Sutter12b, Nadathur14} only have become available after modern large 
+galaxy surveys like the two-degree field Galaxy Survey \citep{Colless01,
 Colless03} and the Sloan Digital Sky Survey \citep{York00,Abazajian03}, 
@@
 
-Theoretical 
-efforts for describing the evolution of the large-scale universe, leaded 
-by the seminal work of \citet{Zeldovich70}, are highly consistent with the 
-cosmic web picture, where planar pancake-like regions of matter enclose 
-enormous sub-dense voids and are bordered, in turn, by thin filaments and
-high-density clumpy knots.
+On the theoretical side, early descriptions of the evolution of the 
+large-scale universe, leaded by the seminal work of \citet{Zeldovich70}, 
+are highly consistent with the cosmic web picture, where planar 
+pancake-like regions of matter enclose enormous sub-dense voids and are 
+bordered, in turn, by thin filaments and high-density clumpy knots. First
+theoretical models for describing formation, dynamics and properties of
+voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were quickly
+complemented and extended by first numerical studies based on simulations
+\citep{Martel90, Regos91, Weygaert93, Dubinski93}. This tendency of using
+numerical results from N-body simulations, fuelled by last generation 
+computing systems, has become increasingly common in the two last decades
+as a powerful analysis tool in studies of cosmic voids \citep{Gottlober03}.
 

### 2014-07-29 cosmic_voids.tex
Abstract and another part of the introduction

@@
 \parbox[t]{\textwidth}{\raggedright 
-  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
+  Sebastian Bustamante \thanks{sbustamante@udea.edu.co}$^{1}$,
   Jaime E. Forero-Romero$^{2}$ 
@@
 \begin{abstract}
+In the last decades voids have been identified as one of the most 
+important features of the Megaparsec Universe, therefore a full 
+understanding of their properties is required in order to a proper 
+description of the large-scale structure of the Cosmic Web. Identifying
+voids in cosmological observations and N-body simulations is hence an 
+important enterprise that must be carried out and accordingly, a plethora 
+of different void finding techniques can be found in the literature.
+
+We present here a novel approximation for finding voids in cosmological 
+simulations based upon two different schemes commonly used for quantifying
+the cosmic web, i.e. the T-web and the V-web (the so-called web schemes), 
+which have proven to be very adequate for that purpose. Unlike previously 
+defined void finding techniques based on the density field, we use here 
+the fractional anisotropy (FA) computed from the eigenvalues of each web 
+scheme and then, through a Watershed Transform, we identify individual 
+voids as the catching basins of local minima of the FA field. Like other 
+Watershed Transform-based schemes, ours retains the same advantages, i.e., 
+it is relatively free-parameter and makes no significant assumptions on 
+the shape and structure of voids.
+
+We test our method on the Bolshoi simulation and compare it with a
+density-based scheme. We find our method gives a better resemblance to the
+visual impression of the cosmic web in addition to a more robust 
+description of voids as it allows to identify, in a very clear manner, 
+their spatial limits as regions where the FA is maximized, normally 
+corresponding to walls and filaments. This is mainly because of the 
+non-monotonic behaviour of the FA, what allows to use it as a sort of 
+one-dimensional tomography of the cosmic web.
 
@@
 \begin{keywords}
-Cosmology: large-scale Structure of Universe, 
-galaxies: star formation - line: formation
+Cosmology: theory - large-scale structure of Universe -
+Methods: data analysis - numerical - N-body simulations
 \end{keywords}
@@
 hierarchically clustered nature of the cosmic web, as one of the most 
-striking features of the Megaparsec universe \citep{Bond96}. Nevertheless,
+striking features of the Megaparsec Universe \citep{Bond96}. Nevertheless,
 due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
@@
 On the theoretical side, early descriptions of the evolution of the 
-large-scale universe, leaded by the seminal work of \citet{Zeldovich70}, 
+large-scale Universe, leaded by the seminal work of \citet{Zeldovich70}, 
 are highly consistent with the cosmic web picture, where planar 
@@
 \citep{Martel90, Regos91, Weygaert93, Dubinski93}. This tendency of using
-numerical results from N-body simulations, fuelled by last generation 
-computing systems, has become increasingly common in the two last decades
-as a powerful analysis tool in studies of cosmic voids \citep{Gottlober03}.
+numerical data from N-body simulations, fuelled by last generation 
+computing systems, has become increasingly common in the last years as a 
+powerful analysis toolkit of cosmic voids (for an extensive compilation of 
+previous numerical works, see \citet{Colberg08}).
 

### 2014-07-31 cosmic_voids.tex
Adding motivation to the introduction

@@
 simulations based upon two different schemes commonly used for quantifying
-the cosmic web, i.e. the T-web and the V-web (the so-called web schemes), 
+the Cosmic Web, i.e. the T-web and the V-web (the so-called web schemes), 
 which have proven to be very adequate for that purpose. Unlike previously 
@@
 density-based scheme. We find our method gives a better resemblance to the
-visual impression of the cosmic web in addition to a more robust 
+visual impression of the Cosmic Web in addition to a more robust 
 description of voids as it allows to identify, in a very clear manner, 
@@
 non-monotonic behaviour of the FA, what allows to use it as a sort of 
-one-dimensional tomography of the cosmic web.
+one-dimensional tomography of the Cosmic Web.
 
@@
 Kirshner87}, they have been identified, along with the filamentary and 
-hierarchically clustered nature of the cosmic web, as one of the most 
+hierarchically clustered nature of the Cosmic Web, as one of the most 
 striking features of the Megaparsec Universe \citep{Bond96}. Nevertheless,
@@
 On the theoretical side, early descriptions of the evolution of the 
-large-scale Universe, leaded by the seminal work of \citet{Zeldovich70}, 
-are highly consistent with the cosmic web picture, where planar 
-pancake-like regions of matter enclose enormous sub-dense voids and are 
-bordered, in turn, by thin filaments and high-density clumpy knots. First
-theoretical models for describing formation, dynamics and properties of
-voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were quickly
-complemented and extended by first numerical studies based on simulations
-\citep{Martel90, Regos91, Weygaert93, Dubinski93}. This tendency of using
-numerical data from N-body simulations, fuelled by last generation 
-computing systems, has become increasingly common in the last years as a 
-powerful analysis toolkit of cosmic voids (for an extensive compilation of 
-previous numerical works, see \citet{Colberg08}).
+large-scale Universe based on gravitational instabilities in primordial 
+stages and leaded by the seminal work of \citet{Zeldovich70}, are highly 
+consistent with the Cosmic Web picture, where planar pancake-like regions 
+of matter enclose enormous sub-dense voids and are bordered, in turn, by 
+thin filaments and high-density clumpy knots. First theoretical models for 
+describing formation, dynamics and properties of voids \citep{Hoffman82, 
+Icke84, Bertschinger85, Blumenthal92} were dramatically complemented and 
+extended by first numerical studies based on simulations \citep{Martel90, 
+Regos91, Weygaert93, Dubinski93}. This tendency of using numerical data 
+from N-body simulations, fuelled by last generation computing systems and
+ever more efficient numerical algorithms, has become increasingly common 
+in the last years as a powerful analysis toolkit of cosmic voids (for an 
+extensive compilation of previous numerical works, see \citet{Colberg08}).
+
+At present, studying voids may be considered as a threefold enterprise: 
+first, they are a key ingredient of the Cosmic Web as they dominate almost 
+the entire volume distribution at large-scales and additionally, they 
+compensate over-density structures in the total budget of matter. This 
+implies that a full understanding of their dynamics and properties is 
+essential for fathoming the high complexity of the Cosmic Web. Second, 
+they provide a valuable resource for inferring and probing cosmological 
+parameters as their structure and dynamics are highly determined by these 
+values. Third, they constitute and unique and still largely pristine 
+environment in which can be tested and probed theories of galaxy formation 
+and evolution.
 

### 2014-08-07 cosmic_voids.tex
References of different void-finding schemes

@@
 On the theoretical side, early descriptions of the evolution of the 
-large-scale Universe based on gravitational instabilities in primordial 
+large-scale Universe, based on gravitational instabilities in primordial 
 stages and leaded by the seminal work of \citet{Zeldovich70}, are highly 
@@
 of matter enclose enormous sub-dense voids and are bordered, in turn, by 
-thin filaments and high-density clumpy knots. First theoretical models for 
-describing formation, dynamics and properties of voids \citep{Hoffman82, 
-Icke84, Bertschinger85, Blumenthal92} were dramatically complemented and 
-extended by first numerical studies based on simulations \citep{Martel90, 
-Regos91, Weygaert93, Dubinski93}. This tendency of using numerical data 
-from N-body simulations, fuelled by last generation computing systems and
-ever more efficient numerical algorithms, has become increasingly common 
-in the last years as a powerful analysis toolkit of cosmic voids (for an 
-extensive compilation of previous numerical works, see \citet{Colberg08}).
+thin filaments and high-density clumpy knots \citep{Bond96}. First 
+theoretical models for describing formation, dynamics and properties of 
+voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were 
+dramatically complemented and extended by first numerical studies based 
+on simulations \citep{Martel90, Regos91, Weygaert93, Dubinski93}. This 
+tendency of using numerical data from N-body simulations, fuelled by last 
+generation computing systems and ever more efficient numerical algorithms, 
+has become increasingly common in the last years as a powerful analysis 
+toolkit of cosmic voids (for an extensive compilation of previous 
+numerical works, see \citet{Colberg08}).
 
-At present, studying voids may be considered as a threefold enterprise: 
-first, they are a key ingredient of the Cosmic Web as they dominate almost 
-the entire volume distribution at large-scales and additionally, they 
-compensate over-density structures in the total budget of matter. This 
-implies that a full understanding of their dynamics and properties is 
-essential for fathoming the high complexity of the Cosmic Web. Second, 
-they provide a valuable resource for inferring and probing cosmological 
-parameters as their structure and dynamics are highly determined by these 
-values. Third, they constitute and unique and still largely pristine 
-environment in which can be tested and probed theories of galaxy formation 
-and evolution.
+At present, studying voids may be considered as a threefold enterprise
+\citep{Platen07}: first, they are a key ingredient of the Cosmic Web as 
+they dominate almost the entire volume distribution at large-scales and 
+additionally, they compensate over-dense structures in the total budget of 
+matter. This implies that a full understanding of their evolution and 
+properties is essential for fathoming the high complexity of the Cosmic 
+Web. Second, they provide a valuable resource for inferring and probing 
+cosmological parameters as their structure and dynamics are highly 
+determined by these values. Third, they constitute and unique and still 
+largely pristine environment in which can be tested and probed theories 
+of galaxy formation and evolution.
+
+Although a visual recognition of voids on galaxy surveys and simulations
+is possible in most cases, a formal systematic identification of them 
+is necessary for statistically meaningful studies. However, a basic yet 
+essential issue remains regarding the definition itself of what a void is. 
+There is not a general consensus about an unambiguous definition of cosmic 
+voids and therefore, there can be found many different void finding 
+techniques throughout the literature (for a detailed comparison of 
+different schemes, see the Void Finder Comparison Project 
+\citet{Colberg08}). In spite of the diversity of existing schemes, they 
+can be roughly classified into two main types: first, schemes based on 
+spatial or redshift distribution of galaxies in surveys or catalogues of 
+dark matter halos in simulations \citep{Kauffmann91, Muller00, Gottlober03,
+Hoyle04, Brunino07, Foster09, Micheletti14, Sutter14}, and second, schemes 
+based on the smooth and continuous matter density field either from 
+simulations or reconstruction procedures on surveys \citep{Plionis02, 
+Colberg05, Shandarin06, Platen07, Neyrinck08, Neyrinck13, Ricciardelli2013}
 

### 2014-08-10 cosmic_voids.tex
Finishing introduction

@@
 \parbox[t]{\textwidth}{\raggedright 
-  Sebastian Bustamante \thanks{sbustamante@udea.edu.co}$^{1}$,
+  Sebastian Bustamante \thanks{sebastian.bustamante@udea.edu.co}$^{1}$,
   Jaime E. Forero-Romero$^{2}$ 
@@
 description of the large-scale structure of the Cosmic Web. Identifying
-voids in cosmological observations and N-body simulations is hence an 
-important enterprise that must be carried out and accordingly, a plethora 
-of different void finding techniques can be found in the literature.
+voids in cosmological observations (e.g. redshift galaxy surveys) and 
+N-body simulations is hence an important enterprise that must be carried 
+out and accordingly, a plethora of different void finding techniques can 
+be found in the literature.
 
@@
 
-We test our method on the Bolshoi simulation and compare it with a
-density-based scheme. We find our method gives a better resemblance to the
-visual impression of the Cosmic Web in addition to a more robust 
-description of voids as it allows to identify, in a very clear manner, 
-their spatial limits as regions where the FA is maximized, normally 
-corresponding to walls and filaments. This is mainly because of the 
-non-monotonic behaviour of the FA, what allows to use it as a sort of 
-one-dimensional tomography of the Cosmic Web.
+We test our method on the Bolshoi simulation and compare with a
+density-based scheme. We find our method gives a better resemblance of 
+the visual impression of the distribution of voids within the Cosmic Web, 
+in addition to a more robust description of voids as it allows to identify,
+in a very clear manner, their outlines as regions where the FA is 
+maximized, normally corresponding to walls and filaments. This is mainly 
+because of the non-monotonic behaviour of the FA, what allows to use it 
+as a sort of one-dimensional tomography of the Cosmic Web.
 
@@
 Sutter12b, Nadathur14} only have become available after modern large 
-galaxy surveys like the two-degree field Galaxy Survey \citep{Colless01,
-Colless03} and the Sloan Digital Sky Survey \citep{York00,Abazajian03}, 
-thereby triggering a plethora of more refined observational and 
-statistical studies of voids throughout the last decade \citep{Hoyle04,
+galaxy surveys like the two-degree field Galaxy Redshift Survey \citep{
+Colless01, Colless03} and the Sloan Digital Sky Survey \citep{York00,
+Abazajian03}, thereby triggering a plethora of more refined observational 
+and statistical studies of voids throughout the last decade \citep{Hoyle04,
 Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
@@
 consistent with the Cosmic Web picture, where planar pancake-like regions 
-of matter enclose enormous sub-dense voids and are bordered, in turn, by 
+of matter enclose enormous underdense voids and are bordered, in turn, by 
 thin filaments and high-density clumpy knots \citep{Bond96}. First 
@@
 they dominate almost the entire volume distribution at large-scales and 
-additionally, they compensate over-dense structures in the total budget of 
+additionally, they compensate overdense structures in the total budget of 
 matter. This implies that a full understanding of their evolution and 
@@
 \citet{Colberg08}). In spite of the diversity of existing schemes, they 
-can be roughly classified into two main types: first, schemes based on 
-spatial or redshift distribution of galaxies in surveys or catalogues of 
-dark matter halos in simulations \citep{Kauffmann91, Muller00, Gottlober03,
-Hoyle04, Brunino07, Foster09, Micheletti14, Sutter14}, and second, schemes 
-based on the smooth and continuous matter density field either from 
-simulations or reconstruction procedures on surveys \citep{Plionis02, 
-Colberg05, Shandarin06, Platen07, Neyrinck08, Neyrinck13, Ricciardelli2013}
+can be roughly classified into two main types: first, geometric schemes 
+based on point spatial or redshift distribution of galaxies in surveys or 
+catalogues of dark matter halos in simulations \citep{Kauffmann91, 
+Muller00, Gottlober03, Hoyle04, Brunino07, Foster09, Micheletti14, 
+Sutter14}, and second, schemes based on the smooth and continuous matter 
+density field either from simulations or from reconstruction procedures 
+on surveys \citep{Plionis02, Colberg05, Shandarin06, Platen07, Neyrinck08,
+Neyrinck13, Ricciardelli2013}.
+
+Here we introduce a new tracer of the structure of cosmic voids built from 
+two tensorial web schemes, i.e. the T-web, based on the Hessian of the 
+gravitational potential or tidal tensor \citep{Hahn07, Forero09}, and the 
+V-web, based on the velocity shear tensor \citep{Hoffman12}. These web 
+schemes classify the Cosmic Web into four different types of environment
+depending on the counting of the number of eigenvalues below an 
+user-defined threshold ($\lambda_{th}$), namely voids (3 eigenvalues below
+$\lambda_{th}$), sheets (2), filaments (1) and knots or clusters (0).
+The tidal and the shear tensors have proven to be more fundamental than 
+the density field as they also trace the collapsing or expanding nature of 
+the matter field, which ultimately is what defines the underlying dynamics 
+of the Cosmic Web. Furthermore, the density field is degenerated regarding 
+the defined types of environment \citep{Hahn07}, which implies that is not 
+possible to assign a priori a range of density values to each of them. 
+This yields that the usually adopted definition of voids as underdense 
+regions in the large-scale matter distribution, is not precise enough as 
+it excludes a proper description of the internal structure of voids.
+
+Following the recent trend of using digital image-processing techniques 
+developed in other disciplines (e.g. medical sciences and computer imaging) 
+for analysing the structure of the Cosmic Web, we propose here, much in 
+the same way as \citet{Libeskind13}, the fractional anisotropy (FA) as a 
+tracer of the internal structure and the outline of cosmic voids. The FA 
+was initially introduced by \citet{Basser95} for quantifying the 
+anisotropy degree of the diffusivity of water molecules through cerebral
+tissue in nuclear magnetic resonance imaging. In this context we use the 
+same quantity for determining the anisotropy degree of the local 
+environment from either the orbital dynamics as set by the eigenvalues of
+the tidal tensor (T-web), or the dynamics of the velocity field as set by 
+the eigenvalues of the shear tensor (V-web). In both cases, the FA is not
+determined directly from the density field, hence it is suitable for 
+describing the structure of high non-linear regions (e.g. filaments, 
+knots and very dense walls) as well as for revealing the fainter 
+substructure exhibited by quasi-linear regions like voids.
+
+Once established the FA as the tracer field of cosmic voids, we proceed to
+identify individual voids as basins of local minima. For this purpose we
+implement a technique defined by \citet{Beucher79} and \citet{Beucher93} 
+and widely used in the field of image analysis and mathematical morphology, 
+i.e. the \textit{watershed transform algorithm}. This technique has been 
+already implemented on void finding schemes by \citet{Platen07} and 
+\citet{Neyrinck08} with very interesting results, where individual voids 
+are identified as catching basins of local minima of the density field. 
+The attractiveness of this algorithm lies in it is parameter-free and does 
+not require to make any assumption on the shape and morphology of voids. 
+Although we just use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on 
+a Cartesian mesh for estimating the density and tensor fields, instead of 
+the more sophisticated \textit{Delaunay tessellation for field estimator} 
+(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
+watershed transform should not be significantly affected as we are 
+interested in quasi-linear regions where the \texttt{CIC} gives similar 
+estimations.
+
+This paper is organized as follows.
 
@@
 eigenvalue, it can be appreciated an analogous behaviour, where central 
-regions of voids present the most under-dense values of the overall cosmic 
+regions of voids present the most underdense values of the overall cosmic 
 web. For outer layers of voids, the density field grows progressively 

### 2014-08-12 cosmic_voids.tex
Adding organization of the paper

@@
 possible to assign a priori a range of density values to each of them. 
-This yields that the usually adopted definition of voids as underdense 
-regions in the large-scale matter distribution, is not precise enough as 
-it excludes a proper description of the internal structure of voids.
+This yields that the usually adopted definition of voids as simply 
+underdense regions in the large-scale matter distribution, is not precise 
+enough as it excludes a proper description of the internal structure of 
+voids.
 
@@
 determined directly from the density field, hence it is suitable for 
-describing the structure of high non-linear regions (e.g. filaments, 
+describing both, the structure of high non-linear regions (e.g. filaments,
 knots and very dense walls) as well as for revealing the fainter 
@@
 are identified as catching basins of local minima of the density field. 
-The attractiveness of this algorithm lies in it is parameter-free and does 
-not require to make any assumption on the shape and morphology of voids. 
-Although we just use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on 
-a Cartesian mesh for estimating the density and tensor fields, instead of 
+The appeal of this algorithm lies in that is parameter-free and does not 
+require to make any assumption on the shape and morphology of voids. 
+Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
+Cartesian mesh for estimating the density and tensor fields, instead of 
 the more sophisticated \textit{Delaunay tessellation for field estimator} 
@@
 
-This paper is organized as follows.
+This paper is organized as follows. In section 2 we describe the used
+simulation for testing our void finding algorithm, i.e. the Bolshoi
+simulation. Alternatively to the web schemes T-web and V-web, we propose 
+a very basic web classifier based on three threshold values defined on the
+density field, this is used in our comparisons as a representative of all 
+density-based schemes. A detailed description of these schemes is 
+presented in section 3. In section 4 we describe how the FA can be used 
+for tracing the structure of voids. Once obtained meaningful catalogues of 
+voids for each scheme, we proceed to compare some typical and general 
+interest properties of voids such as volume functions, distributions of 
+size and density and velocity profiles. This is done in section 5. Finally
+in section 6 we analyse and evaluate our findings.
 

### 2014-08-12 cosmic_voids.tex
Simulation section and other references

@@
 
-We use here an unconstrained cosmological simulation, the Bolshoi 
-simulation, to identify the possible large scale environment and 
-cosmological voids.
+We use here an unconstrained cosmological simulation (the Bolshoi 
+simulation) to identify the possible large scale environment and the 
+distribution of cosmic voids at $z=0$. The Bolshoi simulation follows the 
+non-linear evolution of a dark matter density field on a cubic volume of 
+size $250$\hMpc sampled with $2048^3$ particles. The cosmological 
+parameters in the simulation are $\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}
+=0.73$, $h=0.70$, $n=0.95$ and $\sigma_{8}=0.82$ for the matter density, 
+cosmological constant, dimensionless Hubble parameter, spectral index of 
+primordial density perturbations and normalization for the power spectrum
+respectively, consistent with the seventh year of data of the Wilkinson 
+Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. For more detailed 
+technical information about the simulation, see \citet{Klypin11}.
 
-The Bolshoi simulation follows the non-linear evolution of a dark matter 
-density field on a cubic volume of size $250$\hMpc sampled with $2048^3$ 
-particles. The cosmological parameters in the simulation are 
-$\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}=0.73$, $h=0.70$, $n=0.95$ and 
-$\sigma_{8}=0.82$ for the matter density, cosmological constant, 
-dimensionless Hubble parameter, spectral index of primordial density 
-perturbations and normalization for the power spectrum. The mass of each 
-particle in the simulation is $m_{\rm p}=1.4\times 10^{8}$\hMsun.
-We identify catalogues of halos through the Bound Density Maximum 
-algorithm.
+With the above parameters the mass of each particle in the simulation is 
+$m_{\rm p}=1.4\times 10^{8}$\hMsun. Throughout this paper we shall use a
+catalogue of halos identified through the Bound Density Maximum algorithm
+\citep{Klypin99}. These halos have been selected to have an overdensity of
+200 times the critical density in addition to be mutually excluded of the
+virial radius of other halos. Mass, comoving position and peculiar 
+velocity of each halo at $z=0$ were obtained through the public available 
+Multidark database \footnote{\url{http://www.multidark.org/MultiDark/}} 
+\citep{Riebe11}. For estimating the density and velocity fields we use a 
+\textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
+cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
+through a finite-difference scheme, the tidal and shear tensors are 
+computed. Finally the eigenvalues and eigenvectors of each tensor are 
+obtained for each cell of the grid. Neglecting substructures presented 
+below Megaparsec scales and taking into account our focus in voids, which 
+are a prominent characteristic of the Megaparsec Universe, we apply a 
+Gaussian softening of one cell to all our fields.
 

### 2014-08-12 cosmic_voids.tex
Description of the T-web scheme

@@
 \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
-cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
-through a finite-difference scheme, the tidal and shear tensors are 
-computed. Finally the eigenvalues and eigenvectors of each tensor are 
+cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then 
+through finite-differences and FFT methods the tidal and shear tensors 
+are computed. Finally the eigenvalues and eigenvectors of each tensor are
 obtained for each cell of the grid. Neglecting substructures presented 
@@
 are a prominent characteristic of the Megaparsec Universe, we apply a 
-Gaussian softening of one cell to all our fields.
+Gaussian softening of one cell to all fields.
 
 %*************************************************************************
-\section{Algorithms to quantify the cosmic web}
+\section{Algorithms to quantify the Cosmic Web}
 \label{sec:algorithms_cosmic_web}
@@
 
-The first algorithm  we use to identify the cosmic web is based upon the
-diagonalization of the tidal tensor, defined as the Hessian of a 
-normalized gravitational potential
+This scheme was initially proposed by \citet{Hahn07} as a novel 
+alternative for classifying the Cosmic Web based upon the tidal tensor, 
+that is somehow more fundamental than the density field as it also allows 
+to quantify the orbital dynamics of the matter field. This approach is 
+reached by a second-order expansion of the equations of motion around 
+local minima of the gravitational potential and then extended to any 
+position. The second-order term corresponds to the tidal tensor, which is 
+defined as the Hessian of the normalized gravitational potential
 
@@
 %.........................................................................
-where $\bar{\rho}$ is the average density in the Universe, $G$ is the 
-gravitational constant and $\delta$ is the dimensionless matter 
-overdensity.
+with $\bar{\rho}$ the average density in the Universe, $G$ the 
+gravitational constant and $\delta$ the dimensionless matter overdensity.
+
+Since the tidal tensor can be represented in any cell by a real and 
+symmetric $3\times 3$ matrix, it is ensured the possibility to diagonalize 
+it and obtain three real eigenvalues $\lambda_{1} > \lambda_{2}>\lambda_3$.
+This set of eigenvalues can be used as indicators of the local orbital 
+stability in each proper direction, which in turn can be translated into 
+a classification scheme of the Cosmic Web. A counting of the number of 
+positive (stable) or negative (unstable) eigenvalues allows to catalogue
+a single cell into one of the next four types of environment: voids (3 
+negatives eigenvalues), sheets (2), filaments (1) and knots (0). A 
+significant improvement to this scheme was introduced by \citet{Forero09}
+by means of a relaxation of the stability criterion. The relative strength 
+of each eigenvalue is no longer defined by the sign, but instead by a
+threshold value $\lambda_{th}$ which can be tuned in such a way that the
+visual impression of the web-like matter distribution is reproduced.
 

### 2014-08-13 cosmic_voids.tex
Finishing T-web and V-web descriptions and reordering figures and tables

@@
 %-------------------------------------------------------------------------
-\subsection{The tidal web (T-web)}
+\subsection{The tidal web finder (T-web)}
 \label{subsec:Tweb}
@@
 This scheme was initially proposed by \citet{Hahn07} as a novel 
-alternative for classifying the Cosmic Web based upon the tidal tensor, 
+alternative for classifying the Cosmic Web based on the tidal tensor, 
 that is somehow more fundamental than the density field as it also allows 
@@
 %Tidal Tensor
-\begin{equation}
-T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}}
-\end{equation}
+\eq{V_web}
+{	T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}}	}
 %.........................................................................
@@
 %Poisson
-\begin{equation}
-\nabla^2\phi = \delta,
-\end{equation}
+\eq{Poisson}
+{	\nabla^2\phi = \delta,	}
 %.........................................................................
@@
 symmetric $3\times 3$ matrix, it is ensured the possibility to diagonalize 
-it and obtain three real eigenvalues $\lambda_{1} > \lambda_{2}>\lambda_3$.
-This set of eigenvalues can be used as indicators of the local orbital 
-stability in each proper direction, which in turn can be translated into 
-a classification scheme of the Cosmic Web. A counting of the number of 
-positive (stable) or negative (unstable) eigenvalues allows to catalogue
-a single cell into one of the next four types of environment: voids (3 
-negatives eigenvalues), sheets (2), filaments (1) and knots (0). A 
-significant improvement to this scheme was introduced by \citet{Forero09}
+it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
+\lambda_3$. This set of eigenvalues can be used as indicators of the local 
+orbital stability in each proper direction, which in turn can be 
+translated into a classification scheme of the Cosmic Web. A counting of 
+the number of positive (stable) or negative (unstable) eigenvalues allows 
+to catalogue a single cell into one of the next four types of environment: 
+voids (3 negatives eigenvalues), sheets (2), filaments (1) and knots (0). 
+A significant improvement to this scheme was introduced by \citet{Forero09}
 by means of a relaxation of the stability criterion. The relative strength 
 of each eigenvalue is no longer defined by the sign, but instead by a
-threshold value $\lambda_{th}$ which can be tuned in such a way that the
+threshold value $\lambda_{th}$ that can be tuned in such a way that the
 visual impression of the web-like matter distribution is reproduced.
@@
 %-------------------------------------------------------------------------
-\subsection{The velocity  web (V-web)}
+\subsection{The velocity web finder (V-web)}
 \label{subsec:Vweb}
@@
 
-We also use a kinematical method to define the cosmic-web environment in 
-the simulation. The method has been thoroughly described in XXX and 
-applied to study the shape and spin alignment in the Bolshoi simulation 
-here XX. We refer the reader to these papers to find a detailed 
-description of the algorithm, its limitations and capabilities. Here we 
-summarize the most relevant points for the discussion.
-
-The V-web method for environment finding is based on the local shear 
-tensor calculated from the smoothed DM velocity field in the simulation.
-The central quantity is the following dimensionless quantity
+We also use a kinematical scheme to define the Cosmic Web environment in 
+the simulation. The scheme has been thoroughly described in 
+\citet{Hoffman12} and applied to study the shape and spin alignment in the
+Bolshoi simulation in \citet{Libeskind13}. We refer the reader to these 
+papers to find a detailed description of the algorithm, its limitations 
+and capabilities. The V-web scheme for environment finding is based on the
+local velocity shear tensor calculated from the smoothed dark matter 
+velocity field in the simulation. The central quantity is given by the 
+following dimensionless expression
 
@@
 \eq{V_web}
-{
-\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
-{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}}
-}
+{	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
+{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}}	}
 %.........................................................................
 where $v_{\alpha}$ and $x_{\alpha}$ represent the $\alpha$ component of 
-the comoving velocity and position, respectively. $\Sigma_{\alpha\beta}$ 
-can be represented by a $3\times 3$ symmetric matrix with real values,
-that ensures that is possible to diagonalize and obtain three real 
-eigenvalues $\lambda_{1} > \lambda_{2}>\lambda_3$ whose sum (the trace of
-$\Sigma_{\alpha\beta}$) is proportional to the divergence of the local 
-velocity field smoothed on the physical scale ${\mathcal R}$.
+the comoving velocity and position, respectively. Like the tidal tensor, 
+$\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
+matrix with real values, hence diagonalizing it is obtained three real 
+eigenvalues $\lambda_{1}\geq\lambda_{2}\geq\lambda_3$ whose sum (the 
+trace of $\Sigma_{\alpha\beta}$) is proportional to the divergence of the 
+local velocity field smoothed on the physical scale ${\mathcal R}$.
 
-The relative strength of the three eigenvalues with respect to a threshold
-value $\lambda_{th}$ allows for the local classification of the matter 
-distribution into four web types: voids, sheets, filaments and peaks, 
-which correspond to regions with 3, 2, 1 or 0 eigenvalues with values 
-larger than $\lambda_{th}$. Below we shall discuss a novel approach to 
-define an adequate threshold value based on the visual impression of void
-regions, furthermore we study other possible values based on other visual
-features of the cosmic web.
+In the same way, the relative strength of the three eigenvalues with 
+respect to a threshold value $\lambda_{th}$ allows for the local 
+classification of the matter distribution into the previous four web types. 
+For the threshold choosing in both schemes, the V-web and the T-web, it is
+usual to fine-tuning the value in such a way that the visual appearance of
+the Cosmic Web as seen in simulations and galaxy surveys is reproduced. 
+However, we do not take this approach here, instead we propose a novel 
+approach for the threshold choosing based on the maximization of the 
+fractional anisotropy field occurring in filaments and very dense walls.
+
+%.........................................................................
+%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
+\begin{flushleft}
+\begin{figure*}
+\centering
+  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}
+
+  \captionof{figure}{\small In this figure is shown the distribution of the
+  fractional anisotropy (left panel) and density field (right panel) with 
+  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
+  lines. V-web, blue lines) as calculated over all the cells of the grid.
+  Thick central lines correspond to the median of the distribution and 
+  coloured regions to the $50\%$ of the cells, delimited by quartiles 
+  $Q_1$ and $Q_3$.}
+
+  \label{fig:VFF}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/FA_L1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/delta_L1.pdf}
+
+  \captionof{figure}{\small Distribution of the fractional anisotropy 
+  (upper panel) and density field (lower panel) with respect to the 
+  eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
+  blue lines) as calculated over all the cells of the grid. Thick central 
+  lines correspond to the median of the distribution and coloured regions 
+  to the $50\%$ of the cells, delimited by quartiles $Q_1$ and $Q_3$.}
+
+  \label{fig:L1_correlations}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%-------------------------------------------------------------------------
+\subsection{Density-based web finder}
+\label{subsec:Vweb}
+%-------------------------------------------------------------------------
+
+In order to compare our tracing field based on the fractional anisotropy,
+we define here a very basic approach for environmental finding based on 
+three thresholds set in the density field. Although the density field is
+a key quantity for understanding the large-scale Universe, the filamentary 
+structure of the Cosmic Web is poorly traced by it (see figure 
+\ref{fig:FA_field}).
+
+%.........................................................................
+%Table with volume filling fraction
+\begin{table}[h]
+\begin{flushleft}
+\begin{center}
+  \begin{tabular}{c  c  c  c c} \hline\hline
+	\textbf{Volume}					&				&\textbf{Scheme}& \\
+	\textbf{Filling}				&				&				&					  &  \textbf{Threshold} \\ 
+	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
+	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
+	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
+	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
+	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
+  \end{tabular}  
+  \captionof{table}{\small Size of each sample defined in the Bolshoi 
+  simulation and for each of the two schemes used to detect halos (FOF 
+  and BDM).}
+
+  \label{tab:VFF}
+\end{center}
+\end{flushleft}
+\end{table}
+%.........................................................................
 
@@
 %*************************************************************************
+
+%.........................................................................
+%FIGURE 4: FA and vissual impression
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
+
+  \captionof{figure}{\small In left panels is shown the visual impression 
+  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
+  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
+  defined types of environment, where voids corresponds to white zones, 
+  sheets to gray, filaments to dark gray and finally knots to black regions. 
+  In the right panels is shown the fractional anisotropy field for the same 
+  slide of the simulation and for each web schemes, where black regions 
+  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
+  degeneration of low values of FA for knots and central regions of voids, 
+  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
+  and highly planar sheets. Thin dark red curves correspond to contours of
+  $FA=0.95$, which is approximately the transitional FA between voids and
+  other cosmological regions.}
+
+  \label{fig:FA_field}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
 
@@
 %.........................................................................
-%Table of sizes of each sample defined in Bolshoi
-\begin{table}[h]
-\begin{flushleft}
-\begin{center}
-  \begin{tabular}{l  r  r  r r} \hline\hline
-	\textbf{volume}					&				&\textbf{scheme}& \\
-	\textbf{fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
-	Voids							&	$54.88\%$	&	$47.06\%$	&	$50.97\%$	&	$ -0.57$			\\ 
-	Sheets							&	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	&	$0.60$				\\
-	Filaments						&	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 	&	$8.82$				\\
-	Knots							&	$0.75\%$	&	$1.22\%$	&	$0.98\%$  	&	--		\\ \hline\hline
-  \end{tabular}  
-  \captionof{table}{\small Size of each sample defined in the Bolshoi 
-  simulation and for each of the two schemes used to detect halos (FOF 
-  and BDM).}
-
-  \label{tab:Samples_Size}
-
-\end{center}
-\end{flushleft}
-\end{table}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/FA_L1.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/delta_L1.pdf}
-
-  \captionof{figure}{\small In this figure is shown the distribution of the
-  fractional anisotropy (left panel) and density field (right panel) with 
-  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
-  lines. V-web, blue lines) as calculated over all the cells of the grid.
-  Thick central lines correspond to the median of the distribution and 
-  coloured regions to the $50\%$ of the cells, delimited by quartiles 
-  $Q_1$ and $Q_3$.}
-
-  \label{fig:L1_correlations}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}
-
-  \captionof{figure}{\small In this figure is shown the distribution of the
-  fractional anisotropy (left panel) and density field (right panel) with 
-  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
-  lines. V-web, blue lines) as calculated over all the cells of the grid.
-  Thick central lines correspond to the median of the distribution and 
-  coloured regions to the $50\%$ of the cells, delimited by quartiles 
-  $Q_1$ and $Q_3$.}
-
-  \label{fig:L1_correlations}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
 %FIGURE 3: volume functions
@@
 
-  \label{fig:FA_field}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 4: FA and vissual impression
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
-
-  \captionof{figure}{\small In left panels is shown the visual impression 
-  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
-  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
-  defined types of environment, where voids corresponds to white zones, 
-  sheets to gray, filaments to dark gray and finally knots to black regions. 
-  In the right panels is shown the fractional anisotropy field for the same 
-  slide of the simulation and for each web schemes, where black regions 
-  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
-  degeneration of low values of FA for knots and central regions of voids, 
-  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
-  and highly planar sheets. Thin dark red curves correspond to contours of
-  $FA=0.95$, which is approximately the transitional FA between voids and
-  other cosmological regions.}
-
-  \label{fig:FA_field}
+  \label{fig:volume_function}
   \vspace{0.1 cm}
@@
 
-  \label{fig:FA_field}
+  \label{fig:shape_distro}
   \vspace{0.1 cm}

### 2014-08-13 cosmic_voids.tex
Captioning table 1 and figure 3 (visual impression). Finishing density-based web finder

@@
 %-------------------------------------------------------------------------
-\subsection{The tidal web finder (T-web)}
+\subsection{The tidal web (T-web)}
 \label{subsec:Tweb}
@@
 %-------------------------------------------------------------------------
-\subsection{The velocity web finder (V-web)}
+\subsection{The velocity web (V-web)}
 \label{subsec:Vweb}
@@
 
-  \captionof{figure}{\small In this figure is shown the distribution of the
-  fractional anisotropy (left panel) and density field (right panel) with 
-  respect to the eigenvalue $\lambda_1$ for each web scheme (T-web, red 
-  lines. V-web, blue lines) as calculated over all the cells of the grid.
-  Thick central lines correspond to the median of the distribution and 
-  coloured regions to the $50\%$ of the cells, delimited by quartiles 
-  $Q_1$ and $Q_3$.}
+  \captionof{figure}{\small Volume Filling Fraction for each type of 
+  environment with respect to the chosen threshold $\lambda_{th}$ for both
+  web schemes (T-web, left panel. V-web, right panel). For each case, the 
+  threshold value is chosen such that the fractional anisotropy along the 
+  void-sheet boundaries has a value of $FA=0.95$.}
 
@@
 
-  \captionof{figure}{\small Distribution of the fractional anisotropy 
-  (upper panel) and density field (lower panel) with respect to the 
+  \captionof{figure}{\small Distributions of fractional anisotropy 
+  (left panel) and density field (right panel) with respect to the 
   eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
-  blue lines) as calculated over all the cells of the grid. Thick central 
-  lines correspond to the median of the distribution and coloured regions 
-  to the $50\%$ of the cells, delimited by quartiles $Q_1$ and $Q_3$.}
+  blue lines) as calculated over all cells of the grid. Thick central 
+  lines correspond to the median and filled regions to the $50\%$ of 
+  the distribution.}
 
@@
 %-------------------------------------------------------------------------
-\subsection{Density-based web finder}
+\subsection{The density-based web finder}
 \label{subsec:Vweb}
@@
 
-In order to compare our tracing field based on the fractional anisotropy,
-we define here a very basic approach for environmental finding based on 
-three thresholds set in the density field. Although the density field is
-a key quantity for understanding the large-scale Universe, the filamentary 
-structure of the Cosmic Web is poorly traced by it (see figure 
-\ref{fig:FA_field}).
+Although the density field is a key quantity for understanding the 
+large-scale Universe, the filamentary structure of the Cosmic Web is 
+poorly traced by it (see e.g. figure \ref{fig:FA_field}). In order to 
+compare our new proposal about the the fractional anisotropy as a tracer 
+field of voids, we define a very basic approach for environmental finding 
+based on three thresholds of the density field.
 
@@
 	\textbf{Filling} &				&				&					  &  \textbf{Threshold} \\ 
-	\textbf{Fraction}				&\textbf{T-web}	&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
+	\textbf{Fraction}&\textbf{T-web}&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
 	Voids			 &	$54.88\%$	&	$47.06\%$	&	$50.97\%$	 	  &	$ -0.57$			\\ 
@@
   \end{tabular}  
-  \captionof{table}{\small Size of each sample defined in the Bolshoi 
-  simulation and for each of the two schemes used to detect halos (FOF 
-  and BDM).}
+  \captionof{table}{\small VFF for each type of environment and for each
+  web scheme. VFF for the density-based scheme are defined as the 
+  arithmetic mean of the T-web and the V-web. The last column corresponds 
+  to the threshold values in the density field in order to obtain the 
+  required VFF. Note there is not any value associated to knots as there 
+  is not a higher order environment.}
 
@@
 
-%*************************************************************************
-\section{Finding bulk voids}
-\label{sec:bulk_voids}
-%*************************************************************************
-
 %.........................................................................
 %FIGURE 4: FA and vissual impression
-\begin{flushleft}
 \begin{figure*}
@@
   width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+  \vspace{0.1 cm}
   \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
   width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+  \vspace{0.1 cm}  
   \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
@@
 
-  \captionof{figure}{\small In left panels is shown the visual impression 
-  of the cosmic web for each web scheme (T-web, upper panels. V-web, lower 
-  panels) obtained for $\lambda_{th}=0.0$. It can be seen each one of the 
-  defined types of environment, where voids corresponds to white zones, 
-  sheets to gray, filaments to dark gray and finally knots to black regions. 
-  In the right panels is shown the fractional anisotropy field for the same 
-  slide of the simulation and for each web schemes, where black regions 
-  correspond to FA$=1$ and white regions to FA$=0$. It can be noticed the 
+  \captionof{figure}{\small Left panels show the visual impression of the 
+  Cosmic Web for each web scheme (T-web, upper panels. V-web, middle 
+  panels. Density, lower panels). It can be noticed each environment 
+  sketched such that voids corresponds to white, sheets to gray, filaments 
+  to dark gray and knots to black regions. Right panels show the fractional 
+  anisotropy field for the same slide of the simulation and for each web 
+  scheme. Black regions correspond to the maxim value, i.e. FA$=1$, while 
+  white and light yellow regions to FA$=0$. It is worth noting the 
   degeneration of low values of FA for knots and central regions of voids, 
-  while high values of FA (FA $\lesssim 1$) are consistent with filaments 
-  and highly planar sheets. Thin dark red curves correspond to contours of
-  $FA=0.95$, which is approximately the transitional FA between voids and
-  other cosmological regions.}
+  thus indicating a high isotropy for both processes. In the same way, high 
+  values of FA (FA $\lesssim 1$) are consistent the anisotropic geometry 
+  exhibited by filaments and very flat sheets.}
 
   \label{fig:FA_field}
-  \vspace{0.1 cm}
 
 \end{figure*}
-\end{flushleft}
 %.........................................................................
+
+In next section we shall describe an alternative approximation to select 
+the threshold value $\lambda_{th}$, and as will be shown, one of its main 
+advantages is the similar volume filling fraction (VFF) of each 
+environment as compared between both web schemes. Using this result, we 
+propose here a heuristic classification of the Cosmic Web based on 
+three density thresholds assigned to each boundary (i.e. void-sheet, 
+sheet-filament and filament-knot)\footnote{The progressive sequence 
+void-sheet-filament-knot along any path in the Cosmic Web should be always
+satisfied as each used field is smoothed. For instance, it should not be 
+possible to find a knot-type cell abutting another sheet or void-type 
+cell.} such that the corresponding VFF values are similar to the values 
+obtained for the T-web and the V-web, specifically they are defined 
+to be the arithmetic mean of both schemes.
+
+%*************************************************************************
+\section{Finding bulk voids}
+\label{sec:bulk_voids}
+%*************************************************************************
 

### 2014-09-04 bench/codes_figures/void_radial_density_bins.py
Adding line for saving plots directly in folder

@@ -3,7 +3,7 @@
 #This code computes radial histograms of the density profile of voids as computed by the three 
 #defined schemes
 #
-#Usage: run void_radial_density_bins.py <Vweb or Tweb> <FAG or DLT>
+#Usage: run void_radial_density_bins.py <Vweb or Tweb> <FAG or DLT> <show(0) or save(1)>
 #
 #by: Sebastian Bustamante
 
@@ -44,6 +44,7 @@ def r_eff(X):
 #==================================================================================================
 #			COMPUTING RADIAL PROFILES OF DENSITY FOR EVERY RADIAL BIN
 #==================================================================================================
+plt.figure( figsize=(5.5,5) )
 for ri in xrange( len(RadBins)-1 ):
     reff_range = [ RadBins[ri],RadBins[ri+1] ]
     #Loading index of voids
@@ -74,8 +75,8 @@ for ri in xrange( len(RadBins)-1 ):
         values = np.sort(values)
         try:
             median[i_r] = values[ int(len(values)*0.5) ]
-            Q1[i_r] = values[ int(len(values)*0.25) ]
-            Q2[i_r] = values[ int(len(values)*0.75) ]
+            #Q1[i_r] = values[ int(len(values)*0.25) ]
+            #Q2[i_r] = values[ int(len(values)*0.75) ]
         except:
             pass
         i_r += 1
@@ -85,7 +86,16 @@ for ri in xrange( len(RadBins)-1 ):
     plt.fill_between( Rnorm, Q1, Q2, alpha = 0.3, color = color[ri] )
     plt.plot( Rnorm, median, color = color[ri], linewidth = 2, 
     label = "%1.2f$\leq$r$_{eff}$<%1.2f"%(reff_range[0],reff_range[1]) )
+    
+plt.ylabel( "Density contrast $\delta$" )
+plt.xlabel( "Normalized radius $r/r_{eff}$" )
+plt.ylim( (-1,0.0) )
 plt.grid(1)
 plt.title( "%s %s"%(web, void_scheme) )
 plt.legend( loc="lower right", fancybox=True, shadow=True, fontsize=9 )
-plt.show()
+plt.subplots_adjust( right = 0.95, left = 0.15, top = 0.95 )
+if sys.argv[3] == '1':
+    plt.savefig( '%svoids_density_%s%s.pdf'%(figures_fold,web,void_scheme) )
+else:
+    plt.show()
+    

### 2014-09-04 cosmic_voids.tex
New plots of density profiles of voids for each scheme

@@
 %=========================================================================
-\title{Fractional anisotropy as an optimal tracer of cosmic voids}
+\title{Fractional anisotropy as a tracer of cosmic voids}
 \author[S. Bustamante and J.E. Forero-Romero]{
@@
 due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
-h^{-1}$), statistically significant catalogues of voids \citep{Pan10, 
+h^{-1}$), statistically meaningful catalogues of voids \citep{Pan10, 
 Sutter12b, Nadathur14} only have become available after modern large 
@@
 large-scale Universe, based on gravitational instabilities in primordial 
-stages and leaded by the seminal work of \citet{Zeldovich70}, are highly 
+stages and leaded by the seminal work of \citet{Zeldovich70}, are 
 consistent with the Cosmic Web picture, where planar pancake-like regions 
@@
 determined by these values. Third, they constitute and unique and still 
-largely pristine environment in which can be tested and probed theories 
-of galaxy formation and evolution.
+largely pristine environment in which can be tested galaxy evolution.
 
-Although a visual recognition of voids on galaxy surveys and simulations
-is possible in most cases, a formal systematic identification of them 
-is necessary for statistically meaningful studies. However, a basic yet 
-essential issue remains regarding the definition itself of what a void is. 
-There is not a general consensus about an unambiguous definition of cosmic 
-voids and therefore, there can be found many different void finding 
-techniques throughout the literature (for a detailed comparison of 
-different schemes, see the Void Finder Comparison Project 
-\citet{Colberg08}). In spite of the diversity of existing schemes, they 
-can be roughly classified into two main types: first, geometric schemes 
-based on point spatial or redshift distribution of galaxies in surveys or 
-catalogues of dark matter halos in simulations \citep{Kauffmann91, 
-Muller00, Gottlober03, Hoyle04, Brunino07, Foster09, Micheletti14, 
-Sutter14}, and second, schemes based on the smooth and continuous matter 
-density field either from simulations or from reconstruction procedures 
-on surveys \citep{Plionis02, Colberg05, Shandarin06, Platen07, Neyrinck08,
-Neyrinck13, Ricciardelli2013}.
+Although a visual recognition of voids in galaxy surveys and simulations
+is possible in most cases, a formal systematic identification is necessary 
+for statistically meaningful studies. However, a basic yet essential issue 
+remains regarding the definition itself of what a void is. There is not a 
+general consensus about an unambiguous definition of cosmic voids and 
+therefore, there can be found many different void finding techniques 
+throughout the literature (for a detailed comparison of different schemes, 
+see the Void Finder Comparison Project \citet{Colberg08}). In spite of the 
+diversity of existing schemes, they can be roughly classified into two 
+main types: first, geometric schemes based on point spatial or redshift 
+distribution of galaxies in surveys or catalogues of dark matter halos in 
+simulations \citep{Kauffmann91, Muller00, Gottlober03, Hoyle04, Brunino07, 
+Foster09, Micheletti14, Sutter14}, and second, schemes based on the smooth 
+and continuous matter density field either from simulations or from 
+reconstruction procedures on surveys \citep{Plionis02, Colberg05, 
+Shandarin06, Platen07, Neyrinck08, Neyrinck13, Ricciardelli2013}.
 
@@
 \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
-cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then 
+cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
 through finite-differences and FFT methods the tidal and shear tensors 
@@
 poorly traced by it (see e.g. figure \ref{fig:FA_field}). In order to 
-compare our new proposal about the the fractional anisotropy as a tracer 
-field of voids, we define a very basic approach for environmental finding 
-based on three thresholds of the density field.
+compare our new proposal based on the the fractional anisotropy as a 
+tracer field of voids, we define a very basic approach for environmental 
+finding based on three thresholds of the density field.
 
@@
 %.........................................................................
-%FIGURE 3: volume functions
+%FIGURE 4: volume functions
 \begin{flushleft}
@@
   \label{fig:volume_function}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 5: Density profile of voids for each defined scheme
+\begin{flushleft}
+\begin{figure*}
+\centering
+  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_density_TwebFAG.pdf}
+  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_density_VwebFAG.pdf}
+  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}
+
+  \captionof{figure}{\small Density profiles of voids for each finding 
+  scheme.}
+
+  \label{fig:VFF}
   \vspace{0.1 cm}

### 2014-09-09 cosmic_voids.tex
new abstract

@@
 \begin{abstract}
-In the last decades voids have been identified as one of the most 
-important features of the Megaparsec Universe, therefore a full 
-understanding of their properties is required in order to a proper 
-description of the large-scale structure of the Cosmic Web. Identifying
-voids in cosmological observations (e.g. redshift galaxy surveys) and 
-N-body simulations is hence an important enterprise that must be carried 
-out and accordingly, a plethora of different void finding techniques can 
-be found in the literature.
-
-We present here a novel approximation for finding voids in cosmological 
-simulations based upon two different schemes commonly used for quantifying
-the Cosmic Web, i.e. the T-web and the V-web (the so-called web schemes), 
-which have proven to be very adequate for that purpose. Unlike previously 
-defined void finding techniques based on the density field, we use here 
-the fractional anisotropy (FA) computed from the eigenvalues of each web 
-scheme and then, through a Watershed Transform, we identify individual 
-voids as the catching basins of local minima of the FA field. Like other 
-Watershed Transform-based schemes, ours retains the same advantages, i.e., 
-it is relatively free-parameter and makes no significant assumptions on 
-the shape and structure of voids.
-
-We test our method on the Bolshoi simulation and compare with a
-density-based scheme. We find our method gives a better resemblance of 
-the visual impression of the distribution of voids within the Cosmic Web, 
-in addition to a more robust description of voids as it allows to identify,
-in a very clear manner, their outlines as regions where the FA is 
-maximized, normally corresponding to walls and filaments. This is mainly 
-because of the non-monotonic behaviour of the FA, what allows to use it 
-as a sort of one-dimensional tomography of the Cosmic Web.
-
+Finding and characterizing voids in the large scale structure of the
+universe is an important task in cosmological studies. 
+In this paper we present a novel approach to find voids in
+cosmological simulations.  
+It is based on algorithms that use the tidal and the
+velocity shear tensors to define the cosmic web.
+Voids are identified using the fractional anisotropy (FA) computed
+from the eigenvalues of each web scheme. We define the void boundaries
+using a watershed transform based on the local minima of the FA; the
+boundaries are regions where the FA is maximized, corresponding to
+walls and filaments.  This void definition does not have any free
+parameter and does not make any assumption on the shape or structure
+of the voids.  We test the method on the Bolshoi simulation and report
+on the density and velocity profiles for the voids found using this
+new scheme.
 \end{abstract}

### 2014-09-13 cosmic_voids.tex
Changing label of plots for FA-WT

@@
 void-sheet-filament-knot along any path in the Cosmic Web should be always
-satisfied as each used field is smoothed. For instance, it should not be 
-possible to find a knot-type cell abutting another sheet or void-type 
-cell.} such that the corresponding VFF values are similar to the values 
-obtained for the T-web and the V-web, specifically they are defined 
-to be the arithmetic mean of both schemes.
+satisfied as each used field is smoothed.} such that the corresponding VFF 
+values are similar to the values obtained for the T-web and the V-web, 
+specifically they are defined to be the arithmetic mean of both schemes.
 

### 2014-09-14 bench/codes_figures/cosmicweb_volume_fractions.py
More contrasting colours for the environs

@@ -36,6 +36,8 @@ N_l = 100
 L_min = -0.3
 L_max = 1
 L_max += (L_max-L_min)/(1.0*N_l+1)
+#Colors
+colors = ["navy", "yellowgreen", "orangered", "c"]
 
 #==================================================================================================
 #			PLOTING VOLUME FRACTION OF EACH REGION
@@ -51,17 +53,17 @@ eig_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
 regs = Counts( eig_filename, delta_filename, L_min, L_max, N_l )
 
 #Fraction of Voids
-plt.fill_between( regs[0], regs[5]/regs[9], color = 'red' )
-plt.plot( regs[0], regs[5]/regs[9], color = 'red', label = "voids", linewidth=2.0 )
+plt.fill_between( regs[0], regs[5]/regs[9], color = colors[0] )
+plt.plot( regs[0], regs[5]/regs[9], color = colors[0], label = "voids", linewidth=2.0 )
 #Fraction of Sheets
-plt.fill_between( regs[0], (regs[5]+regs[6])/regs[9], regs[5]/regs[9], color = 'blue' )
-plt.plot( regs[0], (regs[5]+regs[6])/regs[9], color = 'blue', label = "sheets", linewidth=2.0 )
+plt.fill_between( regs[0], (regs[5]+regs[6])/regs[9], regs[5]/regs[9], color = colors[1] )
+plt.plot( regs[0], (regs[5]+regs[6])/regs[9], color = colors[1], label = "sheets", linewidth=2.0 )
 #Fraction of Filaments
-plt.fill_between( regs[0], (regs[5]+regs[6]+regs[7])/regs[9], (regs[5]+regs[6])/regs[9], color = 'green' )
-plt.plot( regs[0], (regs[5]+regs[6]+regs[7])/regs[9], color = 'green', label = "filaments", linewidth=2.0 )
+plt.fill_between( regs[0], (regs[5]+regs[6]+regs[7])/regs[9], (regs[5]+regs[6])/regs[9], color = colors[2] )
+plt.plot( regs[0], (regs[5]+regs[6]+regs[7])/regs[9], color = colors[2], label = "filaments", linewidth=2.0 )
 #Fraction of Knots
[…]

### 2014-09-14 bench/codes_figures/FA_Prolatenes_simulation.py
New figures, Fractional Anisotropy and Prolatenes for a random sample of the simulation

@@ -1,0 +1,83 @@
+#FA_Prolatenes_simulation.py
+#
+#This code performs an scatter plot of the FA and the Prolatenes index for random samples of the
+#simulation
+#Usage FA_Prolatenes_MonteCarlo.py <Tweb or Vweb> <0-Show  1-Save>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Labels of graphs
+labels = "BOLSHOI"
+#Box lenght
+Box_L = 250
+#Number of sections
+N_sec = 256
+#Web scheme
+web = sys.argv[1]
+#Values to evaluate lambda_th
+Lambda_opt = 0
+#Smooth parameter
+smooth = '_s1'
+#Coordinate to cut (1 -- X, 2 -- Y, 3 -- Z)
+axe = 1
+#Cut
+Cuts = [10, 50, 100, 150]
+#Lambda_th
+Lth = { "Tweb":0.265, "Vweb":0.175 }
+#Colors
+colors = ["navy", "yellowgreen", "orangered", "c"]
+#colors = ["red", "blue", "green", "gray"]
+#Labels
+labels = ["voids", "sheets", "filaments", "knots"]
+
+#==================================================================================================
+#			PLOTING WEB SCHEME AND DENSITY FIELD FOR SIMULATION
+#==================================================================================================
+fig = plt.figure( figsize=(7,7) )
+
+#Loading Density filename
+delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,simulation,N_sec,smooth)
+#Loading Vweb filename
+eig_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
+
+for Cut in Cuts:
+    #Loading Fields
+    delta = CutFieldZ( delta_filename, Cut, 32, Coor = axe )
+    eig1 = CutFieldZ( eig_filename+"_1", Cut, 16, Coor = axe )
+    eig2 = CutFieldZ( eig_filename+"_2", Cut, 16, Coor = axe )
[…]

### 2014-09-14 bench/codes_figures/FA_scheme.py

@@ -1,8 +1,8 @@
-#cosmicweb_fractional_anisotropy.py
+#FA_scheme.py
 #
-#This code perform a graphic scheme of the visual impresion for a defined cutting off of Bolshoi
+#This code perform a contour plot of the visual impresion for a defined cutting off of Bolshoi
 #simulation, using the density field and FA is shown how is the behaviour of voids
-#Usage cosmicweb_fractional_anisotropy.py <Vweb or Tweb> <show(0) or save(1)>
+#Usage FA_scheme.py <Vweb or Tweb> <show(0) or save(1)>
 #
 #by: Sebastian Bustamante
 

### 2014-09-14 bench/codes_figures/_Head.py

@@ -376,6 +376,15 @@ def Fractional_Anisotropy( eig1, eig2, eig3 ):
     (eig1**2 + eig2**2 + eig3**2))
 
     return FA
+
+
+#..................................................................................................  
+#Prolatenes
+#..................................................................................................
+def Prolatenes( eig1, eig2, eig3):
+    #return ( eig3+eig1-2*eig2 )/( eig3-eig1 )   		#Non normalized
+    #return ( eig3+eig1-2*eig2 )/abs( 2*(eig1+eig2+eig3) )	#Classical normalization
+    return -( eig3+eig1-2*eig2 )/(eig1**2+eig2**2+eig3**2)	#My normalization
     
     
 #..................................................................................................

### 2014-09-17 bench/codes_figures/FA_Prolatenes_MonteCarlo.py
Improved FA-prolatenes figure

@@ -12,7 +12,7 @@ execfile('_Head.py')
 #			PARAMETERS
 #==================================================================================================
 #Number of points
-N = 50000
+N = 500000
 #Normalization condition
 Rmax = 3.0
 Rmin = -1.0
@@ -22,7 +22,9 @@ Nscale = 1.0
 n_fa = int(10/Nscale)+1
 n_p = int(10/Nscale)
 #Tiny value of the FA and the prolatenes (<0.5)
-frac = 0.47
+frac = 0.1
+#Resolution
+Nres = 4
 
 #==================================================================================================
 #			FUNCTIONS
@@ -57,6 +59,7 @@ for i in xrange(N):
 p = np.array(p)
 fa = np.array(fa)
 l = np.array(l)
+cont = np.array(range(N))
     
     
 #==================================================================================================
@@ -84,7 +87,9 @@ if sys.argv[1] == "1":
 	    ax = fig.add_subplot(111, projection='3d')
 
 	    try:
-		coef = l[ (fa<fa_array[fai+1]-fa_tin)*(fa>=fa_array[fai]+fa_tin)*(p<p_array[pi+1]-p_tin)*(p>=p_array[pi]+p_tin) ][0]
+		cont_tmp = cont[ (fa<fa_array[fai+1]-fa_tin)*(fa>=fa_array[fai]+fa_tin)*(p<p_array[pi+1]-p_tin)*(p>=p_array[pi]+p_tin) ]
+		i_c = cont_tmp[np.argsort( fa[cont_tmp] )[0]]
+		coef = l[ i_c ]
 		coef = coef - Rmin
 		
 		rx, ry, rz = 1.0/coef
@@ -100,7 +105,7 @@ if sys.argv[1] == "1":
 		z = rz * np.outer(np.ones_like(u), np.cos(v))
 
 		# Plot:
-		ax.plot_surface(x, y, z,  rstride=4, cstride=4, color='b')
+		ax.plot_surface(x, y, z,  rstride=10, cstride=10, color='#cdc9c9')
 
 		# Adjustment of the axes, so that they all have the same span:
 		max_radius = max(rx, ry, rz)*2/3.
@@ -110,7 +115,7 @@ if sys.argv[1] == "1":
 		None
 	
 	    plt.axis('off')
[…]

### 2014-09-17 cosmic_voids.tex
New figures, Fractional Anisotropy and Prolatenes for a random sample of the simulation
Improved FA-prolatenes figure
Codes to plot velocity, figures of radial profiles and updated notebook

@@
 
-%.........................................................................
-%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{flushleft}
-\begin{figure*}
-\centering
-  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}
-
-  \captionof{figure}{\small Volume Filling Fraction for each type of 
-  environment with respect to the chosen threshold $\lambda_{th}$ for both
-  web schemes (T-web, left panel. V-web, right panel). For each case, the 
-  threshold value is chosen such that the fractional anisotropy along the 
-  void-sheet boundaries has a value of $FA=0.95$.}
-
-  \label{fig:VFF}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/FA_L1.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/delta_L1.pdf}
-
-  \captionof{figure}{\small Distributions of fractional anisotropy 
-  (left panel) and density field (right panel) with respect to the 
-  eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
-  blue lines) as calculated over all cells of the grid. Thick central 
-  lines correspond to the median and filled regions to the $50\%$ of 
-  the distribution.}
-
-  \label{fig:L1_correlations}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
 %-------------------------------------------------------------------------
@@
 \end{table}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 4: FA and vissual impression
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
-  \vspace{0.1 cm}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
-  \vspace{0.1 cm}  
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
-
-  \captionof{figure}{\small Left panels show the visual impression of the 
-  Cosmic Web for each web scheme (T-web, upper panels. V-web, middle 
-  panels. Density, lower panels). It can be noticed each environment 
-  sketched such that voids corresponds to white, sheets to gray, filaments 
-  to dark gray and knots to black regions. Right panels show the fractional 
-  anisotropy field for the same slide of the simulation and for each web 
-  scheme. Black regions correspond to the maxim value, i.e. FA$=1$, while 
-  white and light yellow regions to FA$=0$. It is worth noting the 
-  degeneration of low values of FA for knots and central regions of voids, 
-  thus indicating a high isotropy for both processes. In the same way, high 
-  values of FA (FA $\lesssim 1$) are consistent the anisotropic geometry 
-  exhibited by filaments and very flat sheets.}
-
-  \label{fig:FA_field}
-
-\end{figure*}
 %.........................................................................
@@
 %.........................................................................
-%FIGURE 4: volume functions
+%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
+\begin{flushleft}
+\begin{figure*}
+\centering
+  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}
+
+  \captionof{figure}{\small Volume Filling Fraction for each type of 
+  environment with respect to the chosen threshold $\lambda_{th}$ for both
+  web schemes (T-web, left panel. V-web, right panel). For each case, the 
+  threshold value is chosen such that the fractional anisotropy along the 
+  void-sheet boundaries has a value of $FA=0.95$.}
+
+  \label{fig:VFF}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/FA_L1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/delta_L1.pdf}
+
+  \captionof{figure}{\small Distributions of fractional anisotropy 
+  (left panel) and density field (right panel) with respect to the 
+  eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
+  blue lines) as calculated over all cells of the grid. Thick central 
+  lines correspond to the median and filled regions to the $50\%$ of 
+  the distribution.}
+
+  \label{fig:L1_correlations}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 3: FA of some regions and shape illustration
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
+  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/FA_Prolatenes.png}
+
+  \captionof{figure}{\small }
+
+  \label{fig:L1_correlations}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 4: FA and vissual impression
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+  \vspace{0.1 cm}
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+  \vspace{0.1 cm}  
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
+
+  \captionof{figure}{\small Left panels show the visual impression of the 
+  Cosmic Web for each web scheme (T-web, upper panels. V-web, middle 
+  panels. Density, lower panels). It can be noticed each environment 
+  sketched such that voids corresponds to white, sheets to gray, filaments 
+  to dark gray and knots to black regions. Right panels show the fractional 
+  anisotropy field for the same slide of the simulation and for each web 
+  scheme. Black regions correspond to the maxim value, i.e. FA$=1$, while 
+  white and light yellow regions to FA$=0$. It is worth noting the 
+  degeneration of low values of FA for knots and central regions of voids, 
+  thus indicating a high isotropy for both processes. In the same way, high 
+  values of FA (FA $\lesssim 1$) are consistent the anisotropic geometry 
+  exhibited by filaments and very flat sheets.}
+
+  \label{fig:FA_field}
+
+\end{figure*}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 5: volume functions
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 5: Density profile of voids for each defined scheme
+%FIGURE 6: Density profile of voids for each defined scheme
 \begin{flushleft}
@@
 \centering
-  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
   width=0.24\textheight]{./figures/voids_density_TwebFAG.pdf}
-  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
   width=0.24\textheight]{./figures/voids_density_VwebFAG.pdf}
-  \includegraphics[trim = 3mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
   width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}
 
-  \captionof{figure}{\small Density profiles of voids for each finding 
-  scheme.}
+  \
+
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_velocity_TwebFAG.pdf}
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_velocity_VwebFAG.pdf}
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_velocity_TwebDLG.pdf}
+
+  \captionof{figure}{\small Density and velocity profiles of voids for 
+  each finding scheme.}
 
@@
 %.........................................................................
-%FIGURE 5: shape-distributions
+%FIGURE 7: shape-distributions
 \begin{flushleft}

### 2014-09-17 bench/codes_figures/void_radial_velocity_bins.py

@@ -1,0 +1,107 @@
+#void_radial_velocity_bins.py
+#
+#This code computes radial histograms of the velocity profile of voids as computed by the three 
+#defined schemes
+#
+#Usage: run void_radial_velocity_bins.py <Vweb or Tweb> <FAG or DLT> <show(0) or save(1)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Box lenght [Mpc]
+L_box = 250.
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+web = sys.argv[1]
+#Void finder scheme (FAG or DLG)
+void_scheme = sys.argv[2]
+#Cutt of respect to the number of cells
+N_cut = 2
+
+#Number of middle points for mapping the velocity field
+N = 100
+#Number of times the effective radius of the void
+Rreff = 2.0
+#Effective radial bins 
+#RadBins = [ 1, 2.3, 3.6, 4.8, 6.5, 20 ]
+RadBins = [ 1, 2.6, 4.2, 6.0, 20 ]
+#Colors 
+color = ["green", "blue", "red", "black", "cyan"]
+#Labels 
+labels = { "FAG":"FA-WT", "DLG":"Density-WT" }
+
+
+#Effective radius function
+def r_eff(X):
+    return ((10**np.log10(X)*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
+
+#==================================================================================================
+#			COMPUTING RADIAL PROFILES OF VELOCITY FOR EVERY RADIAL BIN
+#==================================================================================================
+plt.figure( figsize=(5.5,5) )
+for ri in xrange( len(RadBins)-1 ):
+    reff_range = [ RadBins[ri],RadBins[ri+1] ]
+    #Loading index of voids
+    voids = np.loadtxt('%svoids_density_%s/void_regions_%s.dat'%(data_figures_fold,void_scheme,web))
+    indexes = voids[ (reff_range[0]<=r_eff(voids[:,1]))*(r_eff(voids[:,1])<reff_range[1]) ,0 ]
[…]

### 2014-09-24 cosmic_voids.tex
Deleting information of catalog of halos

@@
 cosmological parameters as their structure and dynamics are highly 
-determined by these values. Third, they constitute and unique and still 
+determined by these values. Third, they constitute an unique and still 
 largely pristine environment in which can be tested galaxy evolution.
@@
 the eigenvalues of the shear tensor (V-web). In both cases, the FA is not
-determined directly from the density field, hence it is suitable for 
+determined directly from the density field, it hence is suitable for 
 describing both, the structure of high non-linear regions (e.g. filaments,
-knots and very dense walls) as well as for revealing the fainter 
-substructure exhibited by quasi-linear regions like voids.
+knots and very dense walls) as well as the fainter substructure exhibited 
+by quasi-linear regions like voids.
 
@@
 identify individual voids as basins of local minima. For this purpose we
-implement a technique defined by \citet{Beucher79} and \citet{Beucher93} 
+implement a technique developed by \citet{Beucher79} and \citet{Beucher93} 
 and widely used in the field of image analysis and mathematical morphology, 
@@
 are identified as catching basins of local minima of the density field. 
-The appeal of this algorithm lies in that is parameter-free and does not 
-require to make any assumption on the shape and morphology of voids. 
+The appeal of this algorithm consists in that is parameter-free and does 
+not require any assumption on the shape and morphology of voids. 
 Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
@@
 simulation. Alternatively to the web schemes T-web and V-web, we propose 
-a very basic web classifier based on three threshold values defined on the
-density field, this is used in our comparisons as a representative of all 
-density-based schemes. A detailed description of these schemes is 
+a heuristic web classifier based on three thresholds of the density field. 
+This is used in order to illustrate the differences of our scheme with a
+density-based classifier. A detailed description of these methods is 
 presented in section 3. In section 4 we describe how the FA can be used 
-for tracing the structure of voids. Once obtained meaningful catalogues of 
-voids for each scheme, we proceed to compare some typical and general 
+for tracing the structure of voids. Once obtained meaningful catalogues 
+of voids for each scheme, we proceed to compare some typical and general 
 interest properties of voids such as volume functions, distributions of 
@@
 
-With the above parameters the mass of each particle in the simulation is 
-$m_{\rm p}=1.4\times 10^{8}$\hMsun. Throughout this paper we shall use a
-catalogue of halos identified through the Bound Density Maximum algorithm
-\citep{Klypin99}. These halos have been selected to have an overdensity of
-200 times the critical density in addition to be mutually excluded of the
-virial radius of other halos. Mass, comoving position and peculiar 
-velocity of each halo at $z=0$ were obtained through the public available 
-Multidark database \footnote{\url{http://www.multidark.org/MultiDark/}} 
-\citep{Riebe11}. For estimating the density and velocity fields we use a 
+For estimating the density and velocity fields we use a 
 \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
@@
 through finite-differences and FFT methods the tidal and shear tensors 
-are computed. Finally the eigenvalues and eigenvectors of each tensor are
+are computed. Finally, the eigenvalues and eigenvectors of the tensor are
 obtained for each cell of the grid. Neglecting substructures presented 
@@
 that is somehow more fundamental than the density field as it also allows 
-to quantify the orbital dynamics of the matter field. This approach is 
-reached by a second-order expansion of the equations of motion around 
+to quantify the orbital dynamics of the matter field. This approach 
+consists of a second-order expansion of the equations of motion around 
 local minima of the gravitational potential and then extended to any 
 position. The second-order term corresponds to the tidal tensor, which is
-defined as the Hessian of the normalized gravitational potential
+defined as the Hessian matrix of the normalized gravitational potential
 
@@
 In next section we shall describe an alternative approximation to select 
-the threshold value $\lambda_{th}$, and as will be shown, one of its main 
-advantages is the similar volume filling fraction (VFF) of each 
-environment as compared between both web schemes. Using this result, we 
-propose here a heuristic classification of the Cosmic Web based on 
-three density thresholds assigned to each boundary (i.e. void-sheet, 
-sheet-filament and filament-knot)\footnote{The progressive sequence 
-void-sheet-filament-knot along any path in the Cosmic Web should be always
-satisfied as each used field is smoothed.} such that the corresponding VFF 
-values are similar to the values obtained for the T-web and the V-web, 
-specifically they are defined to be the arithmetic mean of both schemes.
+the threshold value $\lambda_{th}$. One of the main results is the similar 
+volume filling fraction (VFF) for each environment in both web schemes. 
+Using this result, we propose here a heuristic classification of the 
+Cosmic Web based on three density thresholds assigned to each boundary 
+(i.e. void-sheet, sheet-filament and filament-knot)\footnote{The 
+progressive sequence void-sheet-filament-knot along any path through the 
+Cosmic Web should be always satisfied as each used field is smoothed.} 
+such that the corresponding VFF values are similar to the values obtained 
+for the T-web and the V-web, specifically they are defined to be the 
+arithmetic mean of both schemes.
 
@@
 
-According to the recent growing interest in studying galaxy formation in 
-low-density regions as cosmological tests, classifying void regions is 
-becoming an important task in cosmology. Most of those classification 
-schemes for voids in cosmological simulations are based upon the density 
-field, setting a cut off value below which some region becomes a void 
-\SRKED{[references]}. Some more advanced classification schemes are based 
-on Voronoi tessellations applied over the tracer particles of the 
-simulation in order to compute the density field. Then, through a watershed 
-transform, a hierarchy of void regions are found \SRKED{[references, 
-ZOBOV algorithm]}.
-
-As has been established \SRKED{[references]}, both web schemes presented 
-in the previous section (V-web and T-web) for classifying the cosmic web 
-present many advantages compared with classification schemes based
-completely upon the density field, e.g. a more robust description of the
-dynamic a kinematic of the cosmic web, a more reliable quantification of 
-the visual impression, among others. With the aim of exploiting all of 
-these advantages, we propose here a novel approach to classify voids in
-cosmological simulations based entirely on the web schemes.
-
-The original version of the T-web scheme \SRKED{[reference, Hahn]} was not
-successful at reproducing the visual impression of the cosmic web, 
-however, with the introduction of a threshold parameter \SRKED{[reference, 
-Forero-Romero]}, this scheme, and even the V-web \SRKED{[reference, 
-Hoffman]}, improved enormously. As this free parameter controls the visual 
-impression provided by each scheme, phenomenons like percolation depends 
-on it as well. Although percolation is one of the key features of the 
-structure of void regions, indicating how voids are merged among them, and 
-how they permeate all the cosmic web, our primal interest here is studying 
-properties of single voids. Nevertheless, in the next section we shall 
-analyse briefly the percolation phenomenon for both web schemes.
-
-In order to deal with percolation of voids in our classification scheme,
-we introduce the fractional anisotropy as defined in \SRKED{[reference, 
-Libeskind]}.
+The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
+conceived to quantify the anisotropy degree of a diffusion process, e.g. 
+the diffusivity of water molecules through cerebral issue in nuclear
+magnetic resonance imaging. Here we propose the FA, much in the same 
+way as \citet{Libeskind13}, as a tracer of cosmic voids.
 
@@
 %.........................................................................
-where the eigenvalues are taken from any of the two web schemes. This 
-index, such as it is defined, allows quantifying the local anisotropy 
-degree of the cosmological environment, where $FA=0$ corresponds to highly
-isotropic regions and $FA=1$ anisotropic ones.
+where the eigenvalues are taken from either the T-web or the V-web 
+(FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
+corresponds with a isotropic dynamic and $FA=1$ with a highly anisotropic 
+distribution.
 

### 2014-09-24 cosmic_voids.tex
Rewriting and streamlining FA as a tracer of voids subsection

@@
 Here we introduce a new tracer of the structure of cosmic voids built from 
-two tensorial web schemes, i.e. the T-web, based on the Hessian of the 
+two tensorial web schemes, i.e. the Tweb, based on the Hessian of the 
 gravitational potential or tidal tensor \citep{Hahn07, Forero09}, and the 
-V-web, based on the velocity shear tensor \citep{Hoffman12}. These web 
+Vweb, based on the velocity shear tensor \citep{Hoffman12}. These web 
 schemes classify the Cosmic Web into four different types of environment
@@
 environment from either the orbital dynamics as set by the eigenvalues of
-the tidal tensor (T-web), or the dynamics of the velocity field as set by 
-the eigenvalues of the shear tensor (V-web). In both cases, the FA is not
+the tidal tensor (Tweb), or the dynamics of the velocity field as set by 
+the eigenvalues of the shear tensor (Vweb). In both cases, the FA is not
 determined directly from the density field, it hence is suitable for 
@@
 simulation for testing our void finding algorithm, i.e. the Bolshoi
-simulation. Alternatively to the web schemes T-web and V-web, we propose 
+simulation. Alternatively to the web schemes Tweb and Vweb, we propose 
 a heuristic web classifier based on three thresholds of the density field. 
@@
 %-------------------------------------------------------------------------
-\subsection{The tidal web (T-web)}
+\subsection{The tidal web (Tweb)}
 \label{subsec:Tweb}
@@
 %-------------------------------------------------------------------------
-\subsection{The velocity web (V-web)}
+\subsection{The velocity web (Vweb)}
 \label{subsec:Vweb}
@@
 papers to find a detailed description of the algorithm, its limitations 
-and capabilities. The V-web scheme for environment finding is based on the
+and capabilities. The Vweb scheme for environment finding is based on the
 local velocity shear tensor calculated from the smoothed dark matter 
@@
 classification of the matter distribution into the previous four web types. 
-For the threshold choosing in both schemes, the V-web and the T-web, it is
+For the threshold choosing in both schemes, the Tweb and the Vweb, it is
 usual to fine-tuning the value in such a way that the visual appearance of
@@
 large-scale Universe, the filamentary structure of the Cosmic Web is 
-poorly traced by it (see e.g. figure \ref{fig:FA_field}). In order to 
+poorly traced by it (see e.g. Fig. \ref{fig:FA_field}). In order to 
 compare our new proposal based on the the fractional anisotropy as a 
@@
 	\textbf{Filling} &				&				&					  &  \textbf{Threshold} \\ 
-	\textbf{Fraction}&\textbf{T-web}&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
+	\textbf{Fraction}&\textbf{Tweb}&\textbf{Vweb}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
 	Voids			 &	$54.88\%$	&	$47.06\%$	&	$50.97\%$	 	  &	$ -0.57$			\\ 
@@
   web scheme. VFF for the density-based scheme are defined as the 
-  arithmetic mean of the T-web and the V-web. The last column corresponds 
+  arithmetic mean of the Tweb and the Vweb. The last column corresponds 
   to the threshold values in the density field in order to obtain the 
@@
 the threshold value $\lambda_{th}$. One of the main results is the similar 
-volume filling fraction (VFF) for each environment in both web schemes. 
-Using this result, we propose here a heuristic classification of the 
-Cosmic Web based on three density thresholds assigned to each boundary 
-(i.e. void-sheet, sheet-filament and filament-knot)\footnote{The 
-progressive sequence void-sheet-filament-knot along any path through the 
-Cosmic Web should be always satisfied as each used field is smoothed.} 
-such that the corresponding VFF values are similar to the values obtained 
-for the T-web and the V-web, specifically they are defined to be the 
-arithmetic mean of both schemes.
+volume filling fraction (VFF) for each environment in both web schemes 
+(see Fig. \ref{fig:VFF}). Using this result, we propose here a heuristic 
+classification of the Cosmic Web based on three density thresholds 
+assigned to each boundary (i.e. void-sheet, sheet-filament and 
+filament-knot)\footnote{The progressive sequence void-sheet-filament-knot 
+along any path through the Cosmic Web should be always satisfied as each 
+used field is smoothed.} such that the corresponding VFF values are 
+similar to the values obtained for the Tweb and the Vweb, specifically 
+they are defined to be the arithmetic mean of both schemes.
 
 %*************************************************************************
-\section{Finding bulk voids}
+\section{Finding voids}
 \label{sec:bulk_voids}
@@
 %.........................................................................
-where the eigenvalues are taken from either the T-web or the V-web 
+where the eigenvalues are taken from either the Tweb or the Vweb 
 (FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
@@
 
-In the figure \ref{fig:FA_field} we calculate the FA field over the 
-simulation for both web schemes. The first interesting feature of this
-figure is the degeneration presented for knots and central regions of 
-voids, where both of them exhibit low to middle values of the FA, 
-indicating a high isotropy regarding the physical properties quantified by 
-each web scheme, i.e. the density field for the T-web and the peculiar 
-velocity for the V-web. For the T-web, the FA field near to knots presents 
-a very narrow distribution around a local minimum, whereas for the V-web 
-such distribution is more spread out. This can be explained appealing to 
-the low fluctuations of the density field compared with the peculiar 
-velocity in highly non-linear regions like knots. For more linear regions 
-like voids, the behaviour of the FA field is quite similar between both 
-schemes, what is consistent with the equivalence of the T-web and the 
-V-web in the linear regime \SRKED{[reference, Hoffman]}.
+In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
+web schemes and the logarithmic density field over a slide of the 
+simulation. Some important points can be concluded of this figure.
 
-According to the classification scheme adopted for the cosmological 
-environment, voids are regions where 
-$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$. This implies that
-the boundaries of void regions are controlled completely by the $\lambda_1$
-eigenvalue of the web scheme and the threshold value. Therefore, as we 
-increase the threshold value $\lambda_{th}$, all voids grow up 
-progressively through contours of the $\lambda_1$ field until certain 
-critical value where they are so large that the visual impression is no 
-longer reproduced. Our objective here is to find a reliable quantity that 
-allows to trace the geometry of void regions as classified by each web 
-scheme. In the figure \ref{fig:L1_correlations} we calculate the 
-distributions of the fractional anisotropy index and the density field 
-regarding the $\lambda_1$ eigenvalue for both web schemes over all the 
-cells of the simulation. Thick lines correspond to the median of the 
-distributions, whereas coloured regions correspond to $50\%$ of the
-sample, delimited by quartiles $Q_1$ and $Q_3$.
+%.........................................................................
+\begin{itemize}
+\item Voids display a highly isotropic expanding dynamic at their centres, 
+becoming gradually more anisotropic at outer regions.
+\item Knots feature with very isotropic collapses. For the Tweb, the FA 
+exhibits very narrow distribution around knots whereas for the Vweb, these
+distributions are more spread out, thereby indicating strong differences 
+between the density and the velocity fields in highly non-linear regions.
+\item The filamentary structure of the Cosmic Web is very good traced by
+high FA values (black regions), thus indicating very anisotropic dynamics 
+for sheets and filaments.
+\item The density field poorly traces the Cosmic Web. This is a somehow 
+expected result due to the semi-infinite range of the density field, what 
+makes more difficult to trace structures.
+\end{itemize}
+%.........................................................................
 
-The first important conclusion is regarding the distribution of the FA 
-index, where there is an almost perfect correlation with the $\lambda_1$ 
-eigenvalue for low values of it. This result can be interpreted as an 
-one-dimensional tomography of void regions, where low $\lambda_1$ values 
-are associated to the central regions of voids, these being the most 
-isotropic structures found, with FA values close to 0. As we increase the 
-$\lambda_1$ value, corresponding to progressively outer layers of void 
-regions or less isotropic voids, the FA index increases as well, 
-maintaining a very reliable correlation approximately until $FA=0.95$. 
-This limit value of the FA can be traduced in terms of an optimal \lth, 
-where we obtain $\lambda_{opt}^V = 0.175$ for the V-web scheme and 
-$\lambda_{opt}^T = 0.265$ for the T-web scheme, both values consistent 
-with optimal thresholds normally taken in previous works \SRKED{[references]}. 
-Due to the definition of the fractional anisotropy index, it presents the 
-highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$.
-Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
-FA limit, such that the outer regions of voids becomes highly anisotropic, 
-it would imply that voids are invading filaments and sheets, so the 
-optimal \lth value is a limit value up to which we can have void regions. 
-For other type of environment such as sheets, filaments and knots, the 
-$\lambda_1$ eigenvalue does not control their spatial boundaries, so the 
-correlation with the FA index is no longer valid beyond the threshold 
-values, furthermore the larger dispersion of the FA distribution also 
-indicates that contours of the FA field are no longer corresponding to 
-contours of the $\lambda_1$ field. Nevertheless, for high $\lambda_1$ 
-values, i.e. $\lambda_1>1.0$, the median value of the FA index decreases 
-to lower values, indicating the presence of isotropic knots. All of this 
-allows us to conclude that the distribution of the FA with respect to the 
-$\lambda_1$ eigenvalue is not only an one-dimensional tomography of voids, 
-but also a sort of one-dimensional projection of the global structure of 
-the cosmic web, starting in highly isotropic central voids, passing 
-through very anisotropic sheets and filaments, until isotropic knot 
-regions.
+Some of these results are consistent with those of \citet{Libeskind13}.
+Finally, from Fig. \ref{fig:FA_field} we conclude that the FA, unlike the
+density field, displays a non-monotonic behaviour, where low values are 
+characteristic of central regions of voids, reaching high values in sheets
+and filaments and becoming low again in knots.
 
-For the distribution of the density with respect to the $\lambda_1$ 
-eigenvalue, it can be appreciated an analogous behaviour, where central 
-regions of voids present the most underdense values of the overall cosmic 
-web. For outer layers of voids, the density field grows progressively 
-until sheets and filaments are reached. However, the dispersion in the 
-distributions indicates that the geometry of voids as quantified by both 
-web schemes is not compatible with the density field, i.e. contours of the
-$\lambda_1$ eigenvalue do not coincide with contours of the density field. 
-Then, the density is not a reliable quantity to be used as tracer of our 
-voids. Furthermore, another advantage of using the FA index instead of the
-density is the non-monotonous behaviour of the FA median value, with a 
-local maxima that allows to identify properly the boundaries of voids.
+For both web schemes, voids are regions where $\lambda_3\leq\lambda_2\leq
+\lambda_1\leq\lambda_{th}$. This implies that the outlines of voids
+are completely fixed by the relative strength of the $\lambda_1$ 
+eigenvalue with respect to the threshold value. Therefore, as we 
+increase/decrease the threshold value $\lambda_{th}$, voids expand/diminish
+progressively through contours of $\lambda_1$. In Fig. 
+\ref{fig:L1_correlations} we calculate the distribution of the FA as well
+as of the density field with respect to $\lambda_1$ for both web schemes 
+over all cells of the simulation.
+
+From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
+tracer of voids as is perfectly correlated with low values of $\lambda_1$. 
+Then, it reaches a maximum value, namely sheets and filaments, for finally
+reaching knots, which feature low FA values. This behaviour can be thought 
+as a sort of one-dimensional tomography of the Cosmic Web. This 
+characteristic allows us to propose an optimal threshold value for both 
+web schemes where the FA is maximized. Specifically we propose a value of 
+$FA=0.95$, corresponding with a threshold $\lambda_{opt}^T = 0.265$ for
+the Tweb and $\lambda_{opt}^V = 0.175$ for the Vweb.  For a threshold 
+above these values, voids would span over very anisotropic regions, which 
+should correspond to sheets and filaments. A threshold below would imply 
+very low volume filling fractions of voids and dominant sheets. Finally 
+from the same figure, the density field do not correlate well with 
+$\lambda_1$ (as calculated for both web schemes). Moreover, due to its 
+monotonic increase, an estimate of a optimal threshold is not as clear as 
+for the FA.
+
+Once set the optimal thresholds for the web schemes, we proceed in Fig. 
+\ref{fig:FAShapeness} to sample the FA along with the prolatenes for a 
+random sample of cells classified into the four environments. Then, we 
+associate a spheroidal geometry with different ranges of these properties
+in order to illustrate the underlying local dynamics of the sampled cells.
+
+From this figure we conclude that sheets displays, as expected, very 
+anisotropic distributions, namely above $FA=0.95$. They are also biased 
+towards oblate geometries, however there are some elongated sheets as 
+well. Filaments are not as anisotropic as sheets, ranging from middle up 
+to high FA values. They exhibit prolate geometries, but a considerable 
+amount of them are biased towards slightly more oblate values. Voids and 
+knots are the only environments featuring with low FA values, thus 
+indicating very isotropic expanding/collapsing dynamics at their centres. 
+However, voids span over a very wide range of FA and geometries, whereas 
+knots only span over low to middle FA values and display a biased oblate 
+geometry.
 
@@
 %-------------------------------------------------------------------------
-
-Resuming our endeavour at identifying voids in cosmological simulations, 
-previous techniques based on web classification schemes usually perform a 
-FOF-like algorithm over cells previously marked as voids according to some 
-established criteria in order to construct bulk void regions 
-\SRKED{[references]}. Although this method has some success at classifying 
-voids, percolation is completely inevitable, where the only way to reduce 
-it is artificially decreasing the global volume fraction of void regions 
-such that they do not merge significantly each other.
-
-Once has been determined the reliability of the FA index for tracing 
-the geometry of voids, our novel proposal here is rather using the FA 
-field for classifying void regions. As was concluded in the previous 
-subsection, the geometry of voids is completely traced by contours of the
-FA field, where central parts of voids and high density knot regions 
-exhibit particularly low values of the FA index. Therefore, through a 
-watershed transform all voids are classified, where each single void 
-region corresponds to the basin of a local minimum of the FA field, where
-those local minimums are restricted to be embedded into a type-void cell
-in order to avoid degeneracy with knots.
 
@@
 %.........................................................................
-%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
+%FIGURE 1: Volume Filling Fractions for environs
 \begin{flushleft}
@@
   environment with respect to the chosen threshold $\lambda_{th}$ for both
-  web schemes (T-web, left panel. V-web, right panel). For each case, the 
+  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
   threshold value is chosen such that the fractional anisotropy along the 
-  void-sheet boundaries has a value of $FA=0.95$.}
+  void-sheet boundaries has a median value of $FA=0.95$.}
 
@@
 
-  \captionof{figure}{\small Distributions of fractional anisotropy 
-  (left panel) and density field (right panel) with respect to the 
-  eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
+  \captionof{figure}{\small Distributions of the fractional anisotropy 
+  (left panel) and the density field (right panel) with respect to the 
+  eigenvalue $\lambda_1$ for each web scheme (Tweb, red lines. Vweb, 
   blue lines) as calculated over all cells of the grid. Thick central 
-  lines correspond to the median and filled regions to the $50\%$ of 
+  lines correspond with the median and filled regions with the $50\%$ of
   the distribution.}
@@
 
-  \label{fig:L1_correlations}
+  \label{fig:FAShapeness}
   \vspace{0.1 cm}
@@
 
-  \label{fig:VFF}
+  \label{fig:RhoVel}
   \vspace{0.1 cm}

### 2014-10-14 cosmic_voids.tex
Updating velocity profiles of voids

@@
 %-------------------------------------------------------------------------
-\subsection{Shape of voids}
-\label{subsec:shape_voids}
-%-------------------------------------------------------------------------
-
-Quantifying the shape of voids is gaining importance due to cosmological 
-tests such as the Alcock-Paczynski test \SRKED{[Sutter et al 2012]}, so 
-we compute here the reduced inertia tensor through the next expression in 
-order to determine shape distributions of bulk voids.
-
-%.........................................................................
-%Reduced inertia tensor
-\eq{ReducedIntertia}
-{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
-%.........................................................................
-where $l$ is an index associated to each cell of the current region, 
-$i$ and $j$ indexes run over each spatial direction and finally 
-$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$. All 
-positions are measured from the respective geometric center of each void.
-
-The eigenvalues of the reduced inertia tensor, i.e. the principal moments
-of inertia, are used to quantify the shape of each bulk void. They are 
-denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
-\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
-distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$ for voids larger 
-than 8 cells in order to avoid statistic fluctuations due to small regions.
-We rather calculate histograms for these ratio quantities instead of each 
-single value in order to avoid using an arbitrary normalization. For both 
-schemes, it can be noticed that the shape distribution is completely 
-spread out, thereby indicating a non-preferred geometry of void regions, 
-which is in agreement with the well established high anisotropy of matter 
-flows associated to this type of region.
-
-For a better quantification, we also perform a classification of the shape 
-of voids by setting a threshold in the analysed ratio quantities. An 
-anisotropic or tri-axial shape correspond to voids where $\tau_1/\tau_2 < 
-0.7$ and $\tau_2/\tau_3 < 0.7$, where there is not any symmetry among the
-principal directions. We find about $57.2\% \sim 61.0\%$ of total voids 
-consistent with this shape, for the T-web and V-web respectively. A 
-pancake or quasi-oblate shape is associated to voids where $\tau_1/\tau_2 
-< 0.7$ and $\tau_2/\tau_3 > 0.7$. We found $13.1\% \sim 17.9\%$ of 
-consistent voids. Filamentary or quasi-prolate voids satisfy $\tau_1/\tau_2 
-> 0.7$ and $\tau_2/\tau_3 < 0.7$, with $25.4\% \sim 18.1\%$ of all voids.
-Finally, isotropic or quasi-spheric voids are found when $\tau_1/\tau_2 
-> 0.7$ and $\tau_2/\tau_3 > 0.7$, with $4.2\% \sim 3.1\%$ of total voids 
-compatible with this shape. The threshold value of $0.7$ adopted here for
-the ratios of the moments of inertia is just for illustrative purposes, 
-where such distinction is rather fuzzy and continuous. However, the 
-previous analysis allows us to conclude that voids are quite asymmetric 
-structures.
-
-%-------------------------------------------------------------------------
 \subsection{Density profile of voids}
@@
 
-%.........................................................................
-%FIGURE 7: shape-distributions
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 6mm 1mm 5mm 4mm, clip, keepaspectratio=true,
-  width=0.75\textheight]{./figures/voids_inertia_tensor.pdf}
-
-  \captionof{figure}{\small Volume functions of voids catalogued by each 
-  used scheme. Left panel (watershed transform over the FA field of the T-web 
-  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
-  (over the density field). Gray curves correspond to voids without boundary 
-  removal whereas black curves are associated to voids merged through boundary 
-  removal process. Dotted lines correspond to original continuous fields, 
-  while segmented lines correspond to fields with a 1st-order median filtering 
-  and continuous lines to a 2nd-order median filtering.}
-
-  \label{fig:shape_distro}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
 \end{document}

### 2014-10-24 cosmic_voids.tex
New profiles of density and velocity. Removing density-watershed method

@@
 simulation for testing our void finding algorithm, i.e. the Bolshoi
-simulation. Alternatively to the web schemes Tweb and Vweb, we propose 
-a heuristic web classifier based on three thresholds of the density field. 
-This is used in order to illustrate the differences of our scheme with a
-density-based classifier. A detailed description of these methods is 
-presented in section 3. In section 4 we describe how the FA can be used 
-for tracing the structure of voids. Once obtained meaningful catalogues 
-of voids for each scheme, we proceed to compare some typical and general 
-interest properties of voids such as volume functions, distributions of 
-size and density and velocity profiles. This is done in section 5. Finally 
-in section 6 we analyse and evaluate our findings.
+simulation. A detailed description of these methods is presented in 
+section 3. In section 4 we describe how the FA can be used for tracing the 
+structure of voids. Once obtained meaningful catalogues of voids for each 
+scheme, we proceed to compare some typical and general interest properties 
+of voids such as volume functions, distributions of size and density and 
+velocity profiles. This is done in section 5. Finally in section 6 we 
+analyse and evaluate our findings.
 
@@
 
-%-------------------------------------------------------------------------
-\subsection{The density-based web finder}
-\label{subsec:Vweb}
-%-------------------------------------------------------------------------
-
-Although the density field is a key quantity for understanding the 
-large-scale Universe, the filamentary structure of the Cosmic Web is 
-poorly traced by it (see e.g. Fig. \ref{fig:FA_field}). In order to 
-compare our new proposal based on the the fractional anisotropy as a 
-tracer field of voids, we define a very basic approach for environmental 
-finding based on three thresholds of the density field.
-
-%.........................................................................
-%Table with volume filling fraction
-\begin{table}[h]
-\begin{flushleft}
-\begin{center}
-  \begin{tabular}{c  c  c  c c} \hline\hline
-	\textbf{Volume}  &				&\textbf{Scheme}& \\
-	\textbf{Filling} &				&				&					  &  \textbf{Threshold} \\ 
-	\textbf{Fraction}&\textbf{Tweb}&\textbf{Vweb}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
-	Voids			 &	$54.88\%$	&	$47.06\%$	&	$50.97\%$	 	  &	$ -0.57$			\\ 
-	Sheets		     &	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	      &	$0.60$				\\
-	Filaments		 &	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 		  &	$8.82$				\\
-	Knots			 &	$0.75\%$	&	$1.22\%$	&	$0.98\%$  		  &	--		\\ \hline\hline
-  \end{tabular}  
-  \captionof{table}{\small VFF for each type of environment and for each
-  web scheme. VFF for the density-based scheme are defined as the 
-  arithmetic mean of the Tweb and the Vweb. The last column corresponds 
-  to the threshold values in the density field in order to obtain the 
-  required VFF. Note there is not any value associated to knots as there 
-  is not a higher order environment.}
-
-  \label{tab:VFF}
-\end{center}
-\end{flushleft}
-\end{table}
-%.........................................................................
-
-In next section we shall describe an alternative approximation to select 
-the threshold value $\lambda_{th}$. One of the main results is the similar 
-volume filling fraction (VFF) for each environment in both web schemes 
-(see Fig. \ref{fig:VFF}). Using this result, we propose here a heuristic 
-classification of the Cosmic Web based on three density thresholds 
-assigned to each boundary (i.e. void-sheet, sheet-filament and 
-filament-knot)\footnote{The progressive sequence void-sheet-filament-knot 
-along any path through the Cosmic Web should be always satisfied as each 
-used field is smoothed.} such that the corresponding VFF values are 
-similar to the values obtained for the Tweb and the Vweb, specifically 
-they are defined to be the arithmetic mean of both schemes.
-
 %*************************************************************************
@@
 (FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
-corresponds with a isotropic dynamic and $FA=1$ with a highly anisotropic 
+corresponds with an isotropic dynamic and $FA=1$ with a highly anisotropic 
 distribution.
@@
 In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
-web schemes and the logarithmic density field over a slide of the 
+web schemes and the logarithmic density field for a slide of the 
 simulation. Some important points can be concluded of this figure.
@@
 between the density and the velocity fields in highly non-linear regions.
-\item The filamentary structure of the Cosmic Web is very good traced by
+\item The filamentary structure of the Cosmic Web is very well traced by
 high FA values (black regions), thus indicating very anisotropic dynamics 
@@
 %FIGURE 1: Volume Filling Fractions for environs
-\begin{flushleft}
-\begin{figure*}
-\centering
-  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}
-
-  \captionof{figure}{\small Volume Filling Fraction for each type of 
-  environment with respect to the chosen threshold $\lambda_{th}$ for both
-  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
-  threshold value is chosen such that the fractional anisotropy along the 
-  void-sheet boundaries has a median value of $FA=0.95$.}
-
-  \label{fig:VFF}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
+%\begin{flushleft}
+%\begin{figure*}
+%\centering
+%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
+%  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
+%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
+%  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}  
+%  
+%  \captionof{figure}{\small Volume Filling Fraction for each type of 
+%  environment with respect to the chosen threshold $\lambda_{th}$ for both
+%  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
+%  threshold value is chosen such that the fractional anisotropy along the 
+%  void-sheet boundaries has a median value of $FA=0.95$.}
+%
+%  \label{fig:VFF}
+%  \vspace{0.1 cm}
+%
+%\end{figure*}
+%\end{flushleft}
 %.........................................................................
@@
   \vspace{0.1 cm}  
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
+%  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+%  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
 
@@
   \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_density_TwebFAG.pdf}
+  width=0.3\textheight]{./figures/voids_density_TwebFAG.pdf}
   \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_density_VwebFAG.pdf}
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}
+  width=0.3\textheight]{./figures/voids_density_VwebFAG.pdf}
+%  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+%  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}
 
@@
   \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_velocity_TwebFAG.pdf}
+  width=0.3\textheight]{./figures/voids_velocity_TwebFAG.pdf}
   \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_velocity_VwebFAG.pdf}
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_velocity_TwebDLG.pdf}
+  width=0.3\textheight]{./figures/voids_velocity_VwebFAG.pdf}
+%  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+%  width=0.24\textheight]{./figures/voids_velocity_TwebDLG.pdf}
 

### 2014-10-24 bench/codes_analysis/Void_Density.c

@@ -12,6 +12,7 @@ int main(int argc, char **argv)
 {   
     FILE *in, *out;
     FLOAT2 *delta;
+    FLOAT2 RC_mag;
     char filename[NMAX1];
     int eig;
     
@@ -88,8 +89,9 @@ int main(int argc, char **argv)
 	
 	//Overall index
 	n = kt + n_x*(jt + n_x*it);
-	
-	fprintf( out, "%d\t%d\t%d\t%1.5e\n", i,j,k,delta[n] );
+	//Radial distance
+	RC_mag = sqrt( pow(X-i,2) + pow(Y-j,2) + pow(Z-k,2) );
+	fprintf( out, "%1.5e\t%1.5e\n", RC_mag, delta[n] );
     }
     
     fclose( out );

### 2014-10-24 bench/codes_analysis/Void_Velocity.c

@@ -8,27 +8,11 @@
 //Usage  Void_Velocity.out <delta_filename> <momentum_filename> <output_filename> <X> <Y> <Z> <R>
 
 
-//Function to compute radial velocity of cell belonging to the current void
-FLOAT2 radial_velocity( int XC, int YC, int ZC, 
-			int X, int Y, int Z, 
-			FLOAT1 Vx, FLOAT1 Vy, FLOAT1 Vz )
-{
-    FLOAT2 RC_mag, Vel_proj;
-    
-    //Norm of relative distance vector
-    RC_mag = sqrt( pow(XC-X,2) + pow(YC-Y,2) + pow(ZC-Z,2) );
-  
-    //Projecting velocity vector
-    Vel_proj = ( Vx*(X-XC) + Vy*(Y-YC) + Vz*(Z-ZC) )/RC_mag;
-    
-    return Vel_proj;
-}
-
-
 int main(int argc, char **argv)
 {   
     FILE *in, *out;
     FLOAT2 *delta;
+    FLOAT2 RC_mag;
     FLOAT1 *p1, *p2, *p3;
     FLOAT1 vn1, vn2, vn3, v_rad;
     char filename[NMAX1];
@@ -51,10 +35,10 @@ int main(int argc, char **argv)
     
     //Loading centre and radius of void============================================================
     int X, Y, Z, R;
-    X = atoi( argv[3] );	//X coordinate
-    Y = atoi( argv[4] );	//Y coordinate
-    Z = atoi( argv[5] );	//Z coordinate
-    R = atoi( argv[6] );	//Radius of void
+    X = atoi( argv[4] );	//X coordinate
+    Y = atoi( argv[5] );	//Y coordinate
+    Z = atoi( argv[6] );	//Z coordinate
+    R = atoi( argv[7] );	//Radius of void
     //=============================================================================================
            	
     //LOADING DENSITY FIELD========================================================================
@@ -135,7 +119,6 @@ int main(int argc, char **argv)
 	    fread(&dumb,sizeof(int),1,in);}}
     //=============================================================================================
     
-    
     //Creating file to store density
     out=fopen(argv[3], "w");
     
@@ -162,10 +145,9 @@ int main(int argc, char **argv)
[…]

### 2014-10-24 bench/codes_analysis/_Head.py

@@ -223,22 +223,22 @@ def Regions_Histograms( filename_eig, filename_delta, min_L, max_L, N_L, min_D, 
 #Density profile of a void in a box
 #..................................................................................................
 def Void_Density( filename_delta, X, Y, Z, R ):
-    os.system( "./Void_Density.out %s temp.tmp %d %d %d %d"%( 
+    os.system( "./Void_Density.out %s temp.tmpr %d %d %d %d"%( 
     filename_delta, X, Y, Z, R ) )
-    datos = np.transpose( np.loadtxt( "temp.tmp" ) )
-    os.system( "rm temp.tmp" )
-    return np.array([datos[0],datos[1],datos[2]]), datos[3]
+    datos = np.transpose( np.loadtxt( "temp.tmpr" ) )
+    os.system( "rm temp.tmpr" )
+    return datos[0], datos[1]
 
 
 #..................................................................................................
 #Radial projected velocity profile of a void in a box
 #..................................................................................................
 def Void_Velocity( filename_delta, filename_momentum, X, Y, Z, R ):
-    os.system( "./Void_Velocity.out %s %s temp.tmp %d %d %d %d"%( 
+    os.system( "./Void_Velocity.out %s %s temp.tmpv %d %d %d %d"%( 
     filename_delta, filename_momentum, X, Y, Z, R ) )
-    datos = np.transpose( np.loadtxt( "temp.tmp" ) )
-    os.system( "rm temp.tmp" )
-    return np.array([datos[0],datos[1],datos[2]]), datos[3]
+    datos = np.transpose( np.loadtxt( "temp.tmpv" ) )
+    os.system( "rm temp.tmpv" )
+    return datos[0], datos[1]
 
 
 #..................................................................................................

### 2014-10-24 bench/codes_analysis/halos_file_rho.py

@@ -3,7 +3,7 @@
 #This code builds a data file with tabulated densities corresponding to each halo, both BDM and
 #FOF schemes.
 #
-#Usage: run halos_file_lambdas.py <Vweb or Tweb> <BDM or FOF>
+#Usage: run halos_file_rho.py <BDM or FOF>
 #
 #by: Sebastian Bustamante
 
@@ -20,10 +20,8 @@ Box_L = 250
 N_sec = 256
 #Smooth parameter
 smooth = '_s1'
-#Web Scheme
-web = sys.argv[1]
 #Catalog Scheme
-catalog = sys.argv[2]
+catalog = sys.argv[1]
 
 #==================================================================================================
 #			CONSTRUCTING FILES WITH HALOS ENVIRONMENT
@@ -32,27 +30,23 @@ catalog = sys.argv[2]
 #Box Lenght
 L = Box_L
 
-#Loading Eigenvalues Vweb filename
-eigV_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,fold,web,N_sec,smooth)
+#Loading density filename
+rho_filename = '%s%s%s/%d/Delta%s'%(foldglobal,simulation,"Tweb",N_sec,smooth)
 #Loading All properties of Halos
-halos = np.transpose(np.loadtxt('%s%s/C_GH_%s.dat'%(foldglobal,fold, catalog)))
-datos = np.transpose(np.loadtxt('%s%s/C_GH_%s.dat'%(foldglobal,fold, catalog)))
+halos = np.transpose(np.loadtxt('%s%s/C_GH_%s.dat'%(foldglobal,simulation, catalog)))
+datos = np.loadtxt('%s%s/C_GH_%s.dat'%(foldglobal,simulation, catalog))
 Nhalos = len(halos[0])
 
-#Saving environment of each halo
-eig = np.zeros( (3,Nhalos) )
+#Saving density of each halo
+rho = np.zeros( (Nhalos) )
 for i in xrange( N_sec ):
     #Showing the advance
     progress(50, int(100*i/(1.0*N_sec)) )
     
     #loading index of halos in a same X cut
-    temp, index = CutHaloX( 
-    i*L*1.0/N_sec, L*1.0/N_sec, 
-    datos, plot=False )
[…]

### 2014-10-24 bench/codes_analysis/void_radial_density.py

@@ -30,9 +30,9 @@ void_scheme = sys.argv[2]
 N_cut = 2
 
 #Bins of histogram
-bins = 20
+bins = 40
 #Number of times the effective radius of the void
-Nreff = 2.0
+Nreff = 3.0
 
 #==================================================================================================
 #			COMPUTING GEOMETRIC CENTER OF VOIDS
@@ -52,7 +52,7 @@ GC = np.loadtxt( "%s/%s/%s/%d/voids%s/voids_%s/GC.dat"%\
 (foldglobal, simulation, web, N_sec, void_scheme, config ))
 
 #Sweeping throughout all regions
-for i_void in voids[0]:
+for i_void in xrange(1, len(voids[0])):
     sys.stdout.write( " In region:\t%d\r" %(int(i_void)) )
     sys.stdout.flush()
     
@@ -65,34 +65,20 @@ for i_void in voids[0]:
     dist = [0,0,0]
 
     #Loading cells of the current void
-    cells, rhos = Void_Density( "%s/%s/%s/%d/Delta%s"%\
+    Rdis, rhos = Void_Density( "%s/%s/%s/%d/Delta%s"%\
     (foldglobal, simulation, web, N_sec, smooth), cgc[0], cgc[1], cgc[2], int(Nreff*reff) )
-    cells = np.transpose(cells)
-          
-    #Subdensitycenter
-    csd = cells[np.argsort(rhos)[0]]
-    cgc = csd
     
     #Radial Histogram
-    hist = np.zeros( bins+1 )
-    ncell = np.zeros( bins+1 )
-    rbins = 10**np.linspace( np.log10(0.1), np.log10(Nreff*reff), bins+1 )
+    delta = np.zeros( bins )
+    #rbins = np.linspace( 0.99, Nreff*reff, bins+1 )
+    rbins = 10**np.linspace( np.log10(0.99), np.log10(Nreff*reff), bins+1 )
 
     #print i_void, reff
-    for i_cell in xrange(len(cells)):
-	for i_coor in xrange(3):
-	    dist[i_coor] = abs(cells[i_cell,i_coor] - cgc[i_coor])
-	    if dist[i_coor] >= N_sec: dist[i_coor] = N_sec - dist[i_coor]
-	rdist = norm( dist )*L_box/(1.0*N_sec)+0.1
[…]

### 2014-10-24 bench/codes_analysis/void_radial_velocity.py

@@ -30,9 +30,9 @@ void_scheme = sys.argv[2]
 N_cut = 2
 
 #Bins of histogram
-bins = 20
+bins = 40
 #Number of times the effective radius of the void
-Nreff = 2.0
+Nreff = 3.0
 
 #==================================================================================================
 #			COMPUTING GEOMETRIC CENTER OF VOIDS
@@ -62,38 +62,23 @@ for i_void in voids[0]:
     reff = Reff( np.log10(N_data) )
     #Geometric center
     cgc = GC[ i_void-1, 4: ]
-    dist = [0,0,0]
 
     #Loading cells of the current void
-    cells, rvel = Void_Velocity( "%s/%s/%s/%d/M"%\
+    Rdis, rvel = Void_Velocity( "%s/%s/%s/%d/M"%\
     (foldglobal, simulation, "Vweb", N_sec), "%s/%s/%s/%d/P"%\
     (foldglobal, simulation, "Vweb", N_sec), cgc[0], cgc[1], cgc[2], int(Nreff*reff) )
-    cells = np.transpose(cells)
-          
-    #Subdensitycenter
-    csd = cells[np.argsort(rvel)[0]]
-    cgc = csd
     
     #Radial Histogram
-    hist = np.zeros( bins+1 )
-    ncell = np.zeros( bins+1 )
-    rbins = 10**np.linspace( np.log10(0.1), np.log10(Nreff*reff), bins+1 )
+    vel_rad = np.zeros( bins )
+    #rbins = np.linspace( 0.99, Nreff*reff, bins+1 )
+    rbins = 10**np.linspace( np.log10(0.99), np.log10(Nreff*reff), bins+1 )
 
     #print i_void, reff
-    for i_cell in xrange(len(cells)):
-	for i_coor in xrange(3):
-	    dist[i_coor] = abs(cells[i_cell,i_coor] - cgc[i_coor])
-	    if dist[i_coor] >= N_sec: dist[i_coor] = N_sec - dist[i_coor]
-	rdist = norm( dist )*L_box/(1.0*N_sec)+0.1
-	rbin = int( (np.log10(rdist)- np.log10(0.1))*bins/(np.log10(Nreff*reff) - np.log10(0.1)) )
-	if rbin <= bins:
-	    ncell[rbin] += 1
-	    hist[rbin] += rvel[ i_cell ]
-
-    #Deleting empty regions
[…]

### 2014-10-24 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -72,18 +72,30 @@ extent = [0, Box_L, 0, Box_L]
 
 #Loading Density filename
 delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,simulation,N_sec,smooth)
+#Loading Mass filename
+mass_filename = '%s%sVweb/%d/M'%(foldglobal,simulation,N_sec)
+#Loading Momentums filename
+px_filename = '%s%sVweb/%d/P_0'%(foldglobal,simulation,N_sec)
+py_filename = '%s%sVweb/%d/P_1'%(foldglobal,simulation,N_sec)
+pz_filename = '%s%sVweb/%d/P_2'%(foldglobal,simulation,N_sec)
 #Loading Vweb filename
 eig_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
 #Loading general catalog of halos
 GH = np.loadtxt('%s%sC_GH_%s.dat'%(foldglobal,simulation,catalog))
 #Catalogue of voids
 voids = CutFieldZ( "%s/%s/%s/%d/voids%s/voids_%s/void_index.dat"%\
-(foldglobal, simulation, web, N_sec, void_scheme, config ), Cut, 'plain', Coor = axe )    
+(foldglobal, simulation, web, N_sec, void_scheme, config ), Cut, 'plain', Coor = axe )
+
 #Loading Fields
 delta = CutFieldZ( delta_filename, Cut, 32, Coor = axe )
 eig1 = CutFieldZ( eig_filename+"_1", Cut, 16, Coor = axe )
 eig2 = CutFieldZ( eig_filename+"_2", Cut, 16, Coor = axe )
 eig3 = CutFieldZ( eig_filename+"_3", Cut, 16, Coor = axe )
+mass = CutFieldZ( mass_filename, Cut, 32, Coor = axe )
+px = CutFieldZ( px_filename, Cut, 32, Coor = axe )
+py = CutFieldZ( py_filename, Cut, 32, Coor = axe )
+pz = CutFieldZ( pz_filename, Cut, 32, Coor = axe )
+
 #Calculating contour of voids
 contours = np.zeros( (N_sec,N_sec) )
 #Sweeping matrix
@@ -126,6 +138,7 @@ plt.xlabel( "[$h^{-1}$ Mpc]" )
 
 #Void Regions
 plt.subplot( 1, 3, 3 )
[…]

### 2014-10-24 bench/codes_figures/cosmicweb_velocity_field.py

@@ -1,0 +1,97 @@
+#cosmicweb_velocity_field.py
+#
+#This code sketches and slide of the simulation, showing the density field along with the velocity
+#field projected
+#cosmicweb_velocity_field.py <show(0) or save(1)> <format (png, pdf)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Box lenght
+Box_L = 250
+#Number of sections
+N_sec = 256
+
+#Smooth parameter
+smooth = '_s1'
+#Coordinate to cut (1 -- X, 2 -- Y, 3 -- Z)
+axe = 1
+#Cut
+Cut = 50
+#Halos slice cut [Mpc]
+dx = 2
+
+#Colors
+my_cmapC = plt.cm.get_cmap('gray')
+my_cmap4 = plt.cm.get_cmap('gray', 4)
+
+from matplotlib.colors import colorConverter
+cmap2 = mpl.colors.LinearSegmentedColormap.from_list('my_cmap2',["white","black"],2)
+cmap2._init()
+alphas = np.ones( cmap2.N+3)
+alphas[0] = 0
+cmap2._lut[:,-1] = alphas
+
+#==================================================================================================
+#			PLOTING WEB SCHEME AND DENSITY FIELD FOR SIMULATION
+#==================================================================================================
+'''
+FIGURE SCHEME
+-------------------
+|  1  |  2  |  3  |
+-------------------
+'''
+plt.figure( figsize=(8,8) )
+#Extent
+extent = [0, N_sec, 0, N_sec]
+
+#Loading Density filename
+delta_filename = '%s%sTweb/%d/Delta%s'%(foldglobal,simulation,N_sec,smooth)
+#Loading Mass filename
+mass_filename = '%s%sVweb/%d/M'%(foldglobal,simulation,N_sec)
+#Loading Momentums filename
+px_filename = '%s%sVweb/%d/P_0'%(foldglobal,simulation,N_sec)
[…]

### 2014-10-24 bench/codes_figures/halos_mass_environment.py

@@ -1,0 +1,91 @@
+#halos_fraction.py
+#
+#This code calculates plots of fraction of halos in each one of the defined environments for a 
+#range od threshold values
+#Usage: halos_fraction.py <Vweb or Tweb> <FAG or DLG> <BDM or FOF> <show(0) or save(1)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Voids scheme
+voids = sys.argv[2]
+#Web Scheme
+web = sys.argv[1]
+#Catalogue
+catalog = sys.argv[3]
+#Colors
+colors = {"voids":"navy", "sheets":"yellowgreen", "filaments":"orangered", "knots":"c"}
+#Bins for masses
+Nbins = 20
+#Mass ranges
+Mmin = 10**(10.5)
+Mmax = 1e15
+
+#Values to evaluate lambda_th
+if web == 'Tweb':
+    Lambda_opt = 0.265
+if web == 'Vweb':
+    Lambda_opt = 0.175
+if voids == "DLG":
+    th_vd = -0.57
+    th_sh = 0.60
+    th_fl = 8.82
+
+#==================================================================================================
+#			Fraction of halos in each environment for different masses
+#==================================================================================================
+
+plt.figure( figsize=(5,5) )
+
+#Loading density filename
+rho_filename = '%s%s%s/%d/Delta%s'%(foldglobal,simulation,"Tweb",N_sec,smooth)
+
+#Loading Properties of halos
+masses = np.transpose(np.loadtxt('%s%s/C_GH_%s.dat'%(foldglobal,simulation, catalog)))[8]
[…]

### 2014-10-24 bench/codes_figures/void_radial_density_bins.py

@@ -28,14 +28,14 @@ void_scheme = sys.argv[2]
 N_cut = 2
 
 #Number of middle points for mapping the density field
-N = 100
+N = 25
 #Number of times the effective radius of the void
-Rreff = 2.0
+Rreff = 2.5
 #Effective radial bins 
-#RadBins = [ 1, 2.3, 3.6, 4.8, 6.5, 20 ]
-RadBins = [ 1, 2.6, 4.2, 6.0, 20 ]
+#RadBins = [ 0, 2, 4, 6, 8, 10, 12, 14, 16 ]
+RadBins = [ 0, 1.5, 3, 4.5, 6, 7.5, 9, 10.5, 12 ]
 #Colors 
-color = ["green", "blue", "red", "black", "cyan"]
+color = ["#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000"]
 #Labels 
 labels = { "FAG":"FA-WT", "DLG":"Density-WT" }
 
@@ -68,12 +68,14 @@ for ri in xrange( len(RadBins)-1 ):
 		(data_figures_fold,void_scheme,web,i))
 	    except:
                 pass
+	    if len(rprofile)==2:
+		continue
 	    #interpolating
 	    ur = rprofile[:,0]/r_eff(voids[i-1,1])
 	    rho = rprofile[:,1]
 	    rho[np.abs(rho)==0.00] = np.min(rho)
 	    try:
-		rho_interp = interp.interp1d( ur/ur[-1]*Rreff, rho )
+		rho_interp = interp.interp1d( ur, rho )
 		#Finding median and quartiles
 		values.append( rho_interp(r) )
             except:
@@ -95,13 +97,12 @@ for ri in xrange( len(RadBins)-1 ):
     
 plt.ylabel( "Density contrast $\delta$" )
 plt.xlabel( "Normalized radius $r/r_{eff}$" )
-plt.ylim( (-1,0.0) )
+plt.ylim( (-1,0.2) )
 plt.grid(1)
 plt.title( "%s %s"%(web, labels[void_scheme]) )
-plt.legend( loc="lower right", fancybox=True, shadow=True, fontsize=9 )
+plt.legend( loc="lower right", fancybox=True, shadow=True, fontsize=9, ncol=2 )
 plt.subplots_adjust( right = 0.95, left = 0.15, top = 0.95 )
 if sys.argv[3] == '1':
[…]

### 2014-10-24 bench/codes_figures/void_radial_velocity_bins.py

@@ -27,15 +27,15 @@ void_scheme = sys.argv[2]
 #Cutt of respect to the number of cells
 N_cut = 2
 
-#Number of middle points for mapping the velocity field
-N = 100
+#Number of middle points for mapping the density field
+N = 50
 #Number of times the effective radius of the void
-Rreff = 2.0
+Rreff = 2.5
 #Effective radial bins 
-#RadBins = [ 1, 2.3, 3.6, 4.8, 6.5, 20 ]
-RadBins = [ 1, 2.6, 4.2, 6.0, 20 ]
+#RadBins = [ 0, 2, 4, 6, 8, 10, 12, 14, 16 ]
+RadBins = [ 0, 1.5, 3, 4.5, 6, 7.5, 9, 10.5, 12 ]
 #Colors 
-color = ["green", "blue", "red", "black", "cyan"]
+color = ["#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000"]
 #Labels 
 labels = { "FAG":"FA-WT", "DLG":"Density-WT" }
 
@@ -73,7 +73,7 @@ for ri in xrange( len(RadBins)-1 ):
 	    vel = vprofile[:,1]
 	    vel[np.abs(vel)==0.00] = np.min(vel)
 	    try:
-		vel_interp = interp.interp1d( ur/ur[-1]*Rreff, vel )
+		vel_interp = interp.interp1d( ur, vel )
 		#Finding median and quartiles
 		values.append( vel_interp(r) )
             except:
@@ -81,8 +81,8 @@ for ri in xrange( len(RadBins)-1 ):
         values = np.sort(values)
         try:
             median[i_r] = values[ int(len(values)*0.5) ]
-            #Q1[i_r] = values[ int(len(values)*0.25) ]
-            #Q2[i_r] = values[ int(len(values)*0.75) ]
+            #Q1[i_r] = -values[ int(len(values)*0.25) ]
+            #Q2[i_r] = -values[ int(len(values)*0.75) ]
         except:
             pass
         i_r += 1
@@ -95,13 +95,12 @@ for ri in xrange( len(RadBins)-1 ):
     
 plt.ylabel( "radial velocity $v \cdot u_r$ [km/s]" )
 plt.xlabel( "Normalized radius $r/r_{eff}$" )
-plt.ylim( (-800,200) )
+plt.ylim( (-40,100) )
 plt.grid(1)
[…]

### 2014-11-23 cosmic_voids.tex
New figures changing radial bins in order to have a more significant statistics per bin

@@
   \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/voids_density_TwebFAG.pdf}
+  width=0.25\textheight]{./figures/voids_density_TwebFAG0.pdf}
   \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/voids_density_VwebFAG.pdf}
-%  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-%  width=0.24\textheight]{./figures/voids_density_TwebDLG.pdf}
+  width=0.25\textheight]{./figures/voids_density_VwebFAG0.pdf}
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/voids_density_TwebFAG1.pdf}
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/voids_density_VwebFAG1.pdf}
 
-  \
+  \captionof{figure}{\small Density of voids for each finding scheme.}
 
+  \label{fig:RhoVel}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%FIGURE 7: Velocity profile of voids for each defined scheme
+\begin{flushleft}
+\begin{figure*}
+\centering
   \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/voids_velocity_TwebFAG.pdf}
+  width=0.25\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
   \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/voids_velocity_VwebFAG.pdf}
-%  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-%  width=0.24\textheight]{./figures/voids_velocity_TwebDLG.pdf}
+  width=0.25\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
+  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
+  width=0.25\textheight]{./figures/voids_velocity_VwebFAG1.pdf}
 
-  \captionof{figure}{\small Density and velocity profiles of voids for 
-  each finding scheme.}
+  \captionof{figure}{\small Velocity of voids for each finding scheme.}
 

### 2014-11-23 cosmic_voids.tex
Subsection explaining FA.

@@
 watershed transform should not be significantly affected as we are 
-interested in quasi-linear regions where the \texttt{CIC} gives similar 
+interested in low density regions where the \texttt{CIC} gives similar 
 estimations.
@@
 %-------------------------------------------------------------------------
-\subsection{Fractional anisotropy as tracer of voids}
+\subsection{The fractional anisotropy}
 \label{subsec:FA_voids}
@@
 In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
-web schemes and the logarithmic density field for a slide of the 
-simulation. Some important points can be concluded of this figure.
+web schemes over a slide of the simulation. Some important points can be 
+concluded from this figure (these results are consistent with those of 
+\citet{Libeskind13}).
 
@@
 \item Knots feature with very isotropic collapses. For the Tweb, the FA 
-exhibits very narrow distribution around knots whereas for the Vweb, these
+exhibits very narrow distribution around knots. For the Vweb, these
 distributions are more spread out, thereby indicating strong differences 
 between the density and the velocity fields in highly non-linear regions.
-\item The filamentary structure of the Cosmic Web is very well traced by
-high FA values (black regions), thus indicating very anisotropic dynamics 
-for sheets and filaments.
-\item The density field poorly traces the Cosmic Web. This is a somehow 
-expected result due to the semi-infinite range of the density field, what 
-makes more difficult to trace structures.
+\item The filamentary structure of the Cosmic Web is well traced by high 
+FA values (black regions), thus indicating very anisotropic dynamics for 
+sheets and filaments.
+\item The FA, unlike the density field, displays a non-monotonic behaviour, 
+where low values are characteristic of central regions of voids, reaching 
+high values in sheets and filaments and becoming low again in knots. 
+%\item The density field poorly traces the Cosmic Web. This is a somehow 
+%expected result due to the semi-infinite range of the density field, what 
+%makes more difficult to trace structures.
 \end{itemize}
@@
 
-Some of these results are consistent with those of \citet{Libeskind13}.
-Finally, from Fig. \ref{fig:FA_field} we conclude that the FA, unlike the
-density field, displays a non-monotonic behaviour, where low values are 
-characteristic of central regions of voids, reaching high values in sheets
-and filaments and becoming low again in knots.
+%-------------------------------------------------------------------------
+\subsection{Voids using web schemes}
+\label{subsec:web_voids}
+%-------------------------------------------------------------------------
 
@@
 \ref{fig:L1_correlations} we calculate the distribution of the FA as well
-as of the density field with respect to $\lambda_1$ for both web schemes 
-over all cells of the simulation.
+as of the density field with respect to $\lambda_1$ over all cells of the 
+grid.
 
 From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
-tracer of voids as is perfectly correlated with low values of $\lambda_1$. 
-Then, it reaches a maximum value, namely sheets and filaments, for finally
-reaching knots, which feature low FA values. This behaviour can be thought 
-as a sort of one-dimensional tomography of the Cosmic Web. This 
+tracer of voids as is almost perfectly correlated with low values of 
+$\lambda_1$. Then, it reaches a maximum value, namely sheets and filaments, 
+for finally reaching knots, which feature low FA values. This behaviour can 
+be thought as a sort of one-dimensional tomography of the Cosmic Web. This
 characteristic allows us to propose an optimal threshold value for both 
@@
 above these values, voids would span over very anisotropic regions, which 
-should correspond to sheets and filaments. A threshold below would imply 
-very low volume filling fractions of voids and dominant sheets. Finally 
-from the same figure, the density field do not correlate well with 
-$\lambda_1$ (as calculated for both web schemes). Moreover, due to its 
-monotonic increase, an estimate of a optimal threshold is not as clear as 
-for the FA.
+must correspond to sheets and filaments. A threshold below would imply 
+very low volume filling fractions of voids and dominant sheets. Finally, 
+the density field do not correlate well with $\lambda_1$ (as calculated 
+for both web schemes). Moreover, due to its monotonic increase, an estimate 
+of an optimal threshold is not as clear as for the FA.
 
@@
 %.........................................................................
-%FIGURE 1: Volume Filling Fractions for environs
-%\begin{flushleft}
-%\begin{figure*}
-%\centering
-%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-%  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
-%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-%  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}  
-%  
-%  \captionof{figure}{\small Volume Filling Fraction for each type of 
-%  environment with respect to the chosen threshold $\lambda_{th}$ for both
-%  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
-%  threshold value is chosen such that the fractional anisotropy along the 
-%  void-sheet boundaries has a median value of $FA=0.95$.}
-%
-%  \label{fig:VFF}
-%  \vspace{0.1 cm}
-%
-%\end{figure*}
-%\end{flushleft}
+%FIGURE 1: FA and vissual impression
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+  \vspace{0.1 cm}
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+
+  \captionof{figure}{\small Left panels show the visual impression of the 
+  FA field over a slide of the simulation for each web scheme (T-web, upper 
+  panels. V-web, middle panels). Black regions correspond with high values, 
+  i.e. FA$\approx 1$, while white and light yellow regions to FA$\approx 0$. 
+  It is worth noting the degeneration of low values of FA for knots and 
+  central regions of voids, thus indicating a high isotropy for both 
+  processes. In the same way, high values of FA are consistent with the 
+  anisotropic geometry exhibited by filaments and very flat sheets. Middle 
+  panels sketch the components of the Cosmic Web using the optimal threshold 
+  values. Voids corresponds with white, sheets to gray, filaments to dark 
+  gray and knots with black regions. Finally right panels sketch the 
+  distribution of the catalogued voids by our method.}
+
+  \label{fig:FA_field}
+
+\end{figure*}
 %.........................................................................
@@
 
-  \captionof{figure}{\small Distributions of the fractional anisotropy 
-  (left panel) and the density field (right panel) with respect to the 
-  eigenvalue $\lambda_1$ for each web scheme (Tweb, red lines. Vweb, 
-  blue lines) as calculated over all cells of the grid. Thick central 
-  lines correspond with the median and filled regions with the $50\%$ of
-  the distribution.}
+  \captionof{figure}{\small Distributions of the FA (left panel) and the 
+  density field (right panel) with respect to the eigenvalue $\lambda_1$ 
+  for each web scheme (Tweb, red lines. Vweb, blue lines) as calculated 
+  over all cells of the grid. Thick central lines correspond with the median 
+  and filled regions with the $50\%$ of the distribution.}
 
@@
 %.........................................................................
-%FIGURE 4: FA and vissual impression
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
-  \vspace{0.1 cm}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
-  \vspace{0.1 cm}  
-%  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-%  width=0.73\textheight]{./figures/cosmicweb_density.pdf}
-
-  \captionof{figure}{\small Left panels show the visual impression of the 
-  Cosmic Web for each web scheme (T-web, upper panels. V-web, middle 
-  panels. Density, lower panels). It can be noticed each environment 
-  sketched such that voids corresponds to white, sheets to gray, filaments 
-  to dark gray and knots to black regions. Right panels show the fractional 
-  anisotropy field for the same slide of the simulation and for each web 
-  scheme. Black regions correspond to the maxim value, i.e. FA$=1$, while 
-  white and light yellow regions to FA$=0$. It is worth noting the 
-  degeneration of low values of FA for knots and central regions of voids, 
-  thus indicating a high isotropy for both processes. In the same way, high 
-  values of FA (FA $\lesssim 1$) are consistent the anisotropic geometry 
-  exhibited by filaments and very flat sheets.}
-
-  \label{fig:FA_field}
-
-\end{figure*}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 5: volume functions
+%FIGURE 4: volume functions
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 6: Density profile of voids for each defined scheme
+%FIGURE 5: Density profile of voids for each defined scheme
 \begin{flushleft}
@@
 %.........................................................................
-%FIGURE 7: Velocity profile of voids for each defined scheme
+%FIGURE 6: Velocity profile of voids for each defined scheme
 \begin{flushleft}
@@
 
+%.........................................................................
+%FIGURE 1: Volume Filling Fractions for environs
+%\begin{flushleft}
+%\begin{figure*}
+%\centering
+%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
+%  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
+%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
+%  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}  
+%  
+%  \captionof{figure}{\small Volume Filling Fraction for each type of 
+%  environment with respect to the chosen threshold $\lambda_{th}$ for both
+%  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
+%  threshold value is chosen such that the fractional anisotropy along the 
+%  void-sheet boundaries has a median value of $FA=0.95$.}
+%
+%  \label{fig:VFF}
+%  \vspace{0.1 cm}
+%
+%\end{figure*}
+%\end{flushleft}
+%.........................................................................
+
+%.........................................................................
+%%FIGURE 4: density field,impression
+%\begin{figure*}
+%\centering
+
+%  \includegraphics[trim = 16mm 10mm 295mm 12mm, clip, keepaspectratio=true,
+%  width=0.27\textheight]{./figures/cosmicweb_density.pdf}  
+%  \captionof{figure}{\small }
+
+%  \label{fig:density_field}
+%\end{figure*}
+%.........................................................................
+
 \end{document}

### 2014-12-11 cosmic_voids.tex
Correction of labels for fractional anisotropy profiles

@@
 web schemes over a slide of the simulation. Some important points can be 
-concluded from this figure (these results are consistent with those of 
-\citet{Libeskind13}).
+concluded from this figure:
 
@@
 the density field do not correlate well with $\lambda_1$ (as calculated 
-for both web schemes). Moreover, due to its monotonic increase, an estimate 
-of an optimal threshold is not as clear as for the FA.
+for both web schemes), and due to its monotonic increase, an estimate of 
+an optimal threshold is not as clear as for the FA.
 
 Once set the optimal thresholds for the web schemes, we proceed in Fig. 
-\ref{fig:FAShapeness} to sample the FA along with the prolatenes for a 
-random sample of cells classified into the four environments. Then, we 
-associate a spheroidal geometry with different ranges of these properties
-in order to illustrate the underlying local dynamics of the sampled cells.
-
-From this figure we conclude that sheets displays, as expected, very 
-anisotropic distributions, namely above $FA=0.95$. They are also biased 
-towards oblate geometries, however there are some elongated sheets as 
-well. Filaments are not as anisotropic as sheets, ranging from middle up 
-to high FA values. They exhibit prolate geometries, but a considerable 
-amount of them are biased towards slightly more oblate values. Voids and 
-knots are the only environments featuring with low FA values, thus 
-indicating very isotropic expanding/collapsing dynamics at their centres. 
-However, voids span over a very wide range of FA and geometries, whereas 
-knots only span over low to middle FA values and display a biased oblate 
-geometry.
+\ref{fig:FAShapeness} to sample the FA and the prolateness for a random 
+sample of cells previously classified into one of the four environments. 
+The prolateness is introduced here for differentiating sheets and filaments
+featuring high FA values. In order to illustrate the underlying local 
+dynamics sampled by the cells, we also sketch different spheroidal 
+geometries according to the relative strength of each eigenvalue, and 
+then, we associate them to different ranges of the FA and the prolateness. 
+From this, we conclude sheets display very anisotropic distributions, 
+namely above $FA=0.95$. They are also biased towards oblate geometries, 
+however there are some elongated sheets as well. Filaments are not as 
+anisotropic as sheets, ranging from middle up to high FA values. They 
+exhibit prolate geometries, but a considerable fraction of them are biased 
+towards slightly more oblate values. Voids and knots are the only 
+environments featuring with low FA values, thus indicating very isotropic 
+expanding/collapsing dynamics at their centres. However, voids span over 
+a very wide range of FA and geometries, whereas knots only span over low 
+to middle FA values and display a biased oblate geometry.
 
@@
 %.........................................................................
+
+\[ \mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr \]
+
+\[ \mathcal{C} < 1 \]
+
+\[ \mathcal{C} > 1 \]
 
@@
 
-  \captionof{figure}{\small }
+  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
+  random sample of cells (left panel) and for different spherical 
+  geometries (right panel). For the cells, each environment is coded with
+  a different colour, i.e. voids corresponds with dark blue points, 
+  sheets with green, filaments with orange and knots with cyan. The axis 
+  of the spheroids are computed from the relative strengths of the 
+  eigenvalues, so their shape sketch the relative expanding/collapsing 
+  dynamics into each direction.}
 
@@
 
-  \captionof{figure}{\small Volume functions of voids catalogued by each 
-  used scheme. Left panel (watershed transform over the FA field of the T-web 
-  scheme). Central panel (over the FA field of the V-web scheme). Right panel 
-  (over the density field). Gray curves correspond to voids without boundary 
-  removal whereas black curves are associated to voids merged through boundary 
-  removal process. Dotted lines correspond to original continuous fields, 
-  while segmented lines correspond to fields with a 1st-order median filtering 
-  and continuous lines to a 2nd-order median filtering.}
+  \captionof{figure}{\small Volume functions of voids for both built 
+  catalogues. Watershed-Tweb (red curves), Watershed-Vweb (blue curves).
+  Continuous lines corresponds with the total number of voids, dot-dashed
+  with sub-compensated voids and dashed lines with over-compensated voids. }
 
@@
 \centering
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_density_TwebFAG0.pdf}
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_density_VwebFAG0.pdf}
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_density_TwebFAG1.pdf}
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_density_VwebFAG1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_density_TwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_FA_TwebFAG0.pdf}
+
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_density_VwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_FA_VwebFAG0.pdf}
+
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_density_TwebFAG1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_FA_TwebFAG1.pdf}
+
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_density_VwebFAG1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_velocity_VwebFAG1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.24\textheight]{./figures/voids_FA_VwebFAG1.pdf}
 
@@
 
-%.........................................................................
-%FIGURE 6: Velocity profile of voids for each defined scheme
-\begin{flushleft}
-\begin{figure*}
-\centering
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
-  \includegraphics[trim = 1mm 2mm 4mm 0mm, clip, keepaspectratio=true,
-  width=0.25\textheight]{./figures/voids_velocity_VwebFAG1.pdf}
-
-  \captionof{figure}{\small Velocity of voids for each finding scheme.}
-
-  \label{fig:RhoVel}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 1: Volume Filling Fractions for environs
-%\begin{flushleft}
-%\begin{figure*}
-%\centering
-%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-%  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
-%  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
-%  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}  
-%  
-%  \captionof{figure}{\small Volume Filling Fraction for each type of 
-%  environment with respect to the chosen threshold $\lambda_{th}$ for both
-%  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
-%  threshold value is chosen such that the fractional anisotropy along the 
-%  void-sheet boundaries has a median value of $FA=0.95$.}
-%
-%  \label{fig:VFF}
-%  \vspace{0.1 cm}
-%
-%\end{figure*}
-%\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%%FIGURE 4: density field,impression
-%\begin{figure*}
-%\centering
-
-%  \includegraphics[trim = 16mm 10mm 295mm 12mm, clip, keepaspectratio=true,
-%  width=0.27\textheight]{./figures/cosmicweb_density.pdf}  
-%  \captionof{figure}{\small }
-
-%  \label{fig:density_field}
-%\end{figure*}
-%.........................................................................
-
 \end{document}

### 2014-12-11 bench/codes_figures/_Head.py

@@ -630,3 +630,29 @@ def box_plot( Quintile, min, max, Q1, Q3, Median, subplot, color, width="fixed",
     subplot.hlines( min, 0.05+Quintile*0.9/4-tick, 0.05+Quintile*0.9/4+tick, color, "-", linewidth = 2 )
     subplot.hlines( max, 0.05+Quintile*0.9/4-tick, 0.05+Quintile*0.9/4+tick, color, "-", linewidth = 2 )
     subplot.add_patch(rect1)
+    
+    
+#..................................................................................................
+#Embedded subplot
+#Taken from: http://stackoverflow.com/questions/17458580/embedding-small-plots-inside-subplots-in-matplotlib
+#..................................................................................................
+def add_subplot_axes(ax,rect,axisbg='w'):
+    fig = plt.gcf()
+    box = ax.get_position()
+    width = box.width
+    height = box.height
+    inax_position  = ax.transAxes.transform(rect[0:2])
+    transFigure = fig.transFigure.inverted()
+    infig_position = transFigure.transform(inax_position)    
+    x = infig_position[0]
+    y = infig_position[1]
+    width *= rect[2]
+    height *= rect[3]  # <= Typo was here
+    subax = fig.add_axes([x,y,width,height],axisbg=axisbg)
+    x_labelsize = subax.get_xticklabels()[0].get_size()
+    y_labelsize = subax.get_yticklabels()[0].get_size()
+    x_labelsize *= rect[2]**0.5
+    y_labelsize *= rect[3]**0.5
+    subax.xaxis.set_tick_params(labelsize=x_labelsize)
+    subax.yaxis.set_tick_params(labelsize=y_labelsize)
+    return subax

### 2014-12-11 bench/codes_figures/void_radial_FA_bins.py

@@ -1,10 +1,10 @@
-#void_radial_velocity_bins.py
+#void_radial_FA_bins.py
 #
-#This code computes radial histograms of the velocity profile of voids as computed by the three 
+#This code computes FA histograms of the density profile of voids as computed by the three 
 #defined schemes
 #
-#Usage: run void_radial_velocity_bins.py <Vweb or Tweb> <FAG or DLT> <overcomp(0) undercomp(1)> 
-#<show(0) or save(1)>  <no label(0) or label(1)>
+#Usage: run void_FA_density_bins.py <Vweb or Tweb> <FAG or DLT> <overcomp(0) undercomp(1)> 
+#<show(0) or save(1)> <no label(0) or label(1)>
 #
 #by: Sebastian Bustamante
 
@@ -33,7 +33,7 @@ config = "01"
 comp = int(sys.argv[3])
 
 #Number of middle points for mapping the density field
-N = 40
+N = 80
 #Number of times the effective radius of the void
 Rreff = 8
 #Effective radial bins 
@@ -53,14 +53,10 @@ def r_eff(X):
     return ((10**np.log10(X)*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
 
 #==================================================================================================
-#			COMPUTING RADIAL PROFILES OF VELOCITY FOR EVERY RADIAL BIN
+#			COMPUTING RADIAL PROFILES OF DENSITY FOR EVERY RADIAL BIN
 #==================================================================================================
 fig = plt.figure( figsize=(4.5,4) )
 ax = fig.add_subplot(111)
-#Embedded subplot
-#rect = [0.1,0.05,0.4,0.4]
-#ax1 = add_subplot_axes(ax,rect)
-
 for ri in xrange( len(RadBins)-1 ):
     reff_range = [ RadBins[ri],RadBins[ri+1] ]
     #Loading index of voids
@@ -76,32 +72,34 @@ for ri in xrange( len(RadBins)-1 ):
     median = np.zeros( N )
     Q1 = np.zeros( N )
     Q2 = np.zeros( N )
-    Rnorm = np.linspace( 0.01, Rreff, N )
+    Rnorm = np.linspace( 0, Rreff, N )
     #Loading single voids
     i_r = 0
     for r in Rnorm:
[…]

### 2014-12-11 bench/codes_figures/void_radial_density_bins.py

@@ -3,7 +3,8 @@
 #This code computes radial histograms of the density profile of voids as computed by the three 
 #defined schemes
 #
-#Usage: run void_radial_density_bins.py <Vweb or Tweb> <FAG or DLT> <show(0) or save(1)>
+#Usage: run void_radial_density_bins.py <Vweb or Tweb> <FAG or DLT> <undercomp(0) overcomp(1)> 
+#<show(0) or save(1)> <no label(0) or label(1)>
 #
 #by: Sebastian Bustamante
 
@@ -26,19 +27,26 @@ web = sys.argv[1]
 void_scheme = sys.argv[2]
 #Cutt of respect to the number of cells
 N_cut = 2
+#Configuration 
+config = "01"
+#Compensated
+comp = int(sys.argv[3])
 
 #Number of middle points for mapping the density field
-N = 40
+N = 80
 #Number of times the effective radius of the void
 Rreff = 8
 #Effective radial bins 
-RadBins = [ 2, 3, 4, 5, 6, 7, 8, 9, 10, 12 ]
+#RadBins = [ 2, 3, 4, 5, 6, 7, 8, 9, 10, 12 ]
+RadBins = [ 2.0, 3.2, 4.4, 5.6, 6.8, 8.3, 12 ]
 #Colors 
 #color = ["#000000","#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
-color = ["#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
+#color = ["#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
+color = ["#0000BE", "#067EF4", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
 #Labels 
 labels = { "FAG":"FA-WT", "DLG":"Density-WT" }
-
+#Compensated
+comp_label = ["Subcompensated", "Overcompensated"]
 
 #Effective radius function
 def r_eff(X):
@@ -47,12 +55,22 @@ def r_eff(X):
 #==================================================================================================
 #			COMPUTING RADIAL PROFILES OF DENSITY FOR EVERY RADIAL BIN
[…]

### 2014-12-11 bench/codes_figures/void_volume_regions_all.py

@@ -16,15 +16,17 @@ simulation = "BOLSHOI/"
 N_sec = 256
 #Web Scheme
 webs = ['Tweb', 'Vweb', 'DLG'] 
+webs = ['Tweb', 'Vweb'] 
 labels = ['FA-Tweb', 'FA-Vweb', 'Density']
 #Void finder scheme (FAG or FOF)
 void_scheme = 'FAG'
 #Schemes used for each web
-schemes = [ "21","31","51" ]
+#schemes = [ "21","31","51" ]
+#schemes = [ "01","01","01" ]
 schemes = [ "01","01","01" ]
 
 #Colors
-colors = ["green", "blue", "red"]
+colors = ["red", "blue", "green"]
 
 #==================================================================================================
 #			CONSTRUCTING REGIONS VOLUME
@@ -52,12 +54,20 @@ for web in webs:
     else:
 	void_regs = np.transpose(np.loadtxt("%s/%s/%s/%d/voids%s/voids_%s/void_regions.dat"%\
 	(foldglobal, simulation, web, N_sec, void_scheme, schemes[i_web] )))
+      
+    #Loading compensated
+    comp = np.loadtxt("%s/%s/%s/%d/voids%s/voids_%s/comp_half.dat"%\
+    (foldglobal, simulation, web, N_sec, void_scheme, schemes[i_web] ))
 
     hist1d = np.histogram( tick_function(np.log10(void_regs[1])) , bins=15, normed=False )
+    hist1d_o = np.histogram( tick_function(np.log10(void_regs[1][comp[:,1]==1])) , bins=15, normed=False )
+    hist1d_u = np.histogram( tick_function(np.log10(void_regs[1][comp[:,1]==0])) , bins=15, normed=False )
     
     #Normal distribution
     if sys.argv[1] == '0':
 	distro = hist1d[0]
+	distro_o = hist1d_o[0]
+	distro_u = hist1d_u[0]
     #Cumulative distribution
     else:
 	distro = np.cumsum(hist1d[0][::-1])[::-1]
@@ -65,9 +75,13 @@ for web in webs:
 	
     #Normal Plot
     if sys.argv[1] == '0':
-	ax1[0].semilogy( hist1d[1][:-1], distro, linewidth = 2.0, linestyle = "-",\
[…]

### 2014-12-18 cosmic_voids.tex
revisado abstract y primer parrafo de la introduccion

@@
 \begin{abstract}
-Finding and characterizing voids in the large scale structure of the
-universe is an important task in cosmological studies. 
+Finding and characterizing underdense regions (voids) in the large
+scale structure of the Universe is an important task in cosmological
+studies.  
 In this paper we present a novel approach to find voids in
 cosmological simulations.  
-It is based on algorithms that use the tidal and the
-velocity shear tensors to define the cosmic web.
+Our approach is based on algorithms that use the tidal and the
+velocity shear tensors to locally define the cosmic web.
 Voids are identified using the fractional anisotropy (FA) computed
-from the eigenvalues of each web scheme. We define the void boundaries
-using a watershed transform based on the local minima of the FA; the
-boundaries are regions where the FA is maximized, corresponding to
-walls and filaments.  This void definition does not have any free
-parameter and does not make any assumption on the shape or structure
-of the voids.  We test the method on the Bolshoi simulation and report
-on the density and velocity profiles for the voids found using this
-new scheme.
+from the eigenvalues of each web scheme. 
+We define the void boundaries using a watershed transform based on the
+local minima of the FA and its boundaries as the regions where the FA
+is maximized
+This void identification technique does not have any free parameters
+and does not make any assumption on the shape or structure of the
+voids.  
+We test the method on the Bolshoi simulation and report on the density
+and velo ity profiles for the voids found using this new scheme. 
 \end{abstract}
@@
 
-Since voids where discovered in the first compiled galaxy surveys 
-\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
-Kirshner87}, they have been identified, along with the filamentary and 
-hierarchically clustered nature of the Cosmic Web, as one of the most 
-striking features of the Megaparsec Universe \citep{Bond96}. Nevertheless,
-due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
-h^{-1}$), statistically meaningful catalogues of voids \citep{Pan10, 
-Sutter12b, Nadathur14} only have become available after modern large 
-galaxy surveys like the two-degree field Galaxy Redshift Survey \citep{
-Colless01, Colless03} and the Sloan Digital Sky Survey \citep{York00,
-Abazajian03}, thereby triggering a plethora of more refined observational 
-and statistical studies of voids throughout the last decade \citep{Hoyle04,
-Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
-Tikhonov07, BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}
+Since voids were found in the first compiled galaxy surveys 
+they have been identified as one of the most striking features of the
+Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
+  Kirshner81,  Kirshner87, Bond96}. 
+However,  due to the large volume extension of void regions ($\sim
+5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
+voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
+through  modern galaxy surveys like the two-degree field Galaxy
+Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
+Sky Survey \citep{York00, Abazajian03}.
+This advancement generated a great interest to study voids
+observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
+  Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
+  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.
 

### 2014-12-19 cosmic_voids.tex
revisados los 5 primeros parrafos de la introduccion

@@
 Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
-  Kirshner81,  Kirshner87, Bond96}. 
+  Kirshner81, Zeldovich82,Kirshner87, Bond96}. 
 However,  due to the large volume extension of void regions ($\sim
@@
 
-On the theoretical side, early descriptions of the evolution of the 
-large-scale Universe, based on gravitational instabilities in primordial 
-stages and leaded by the seminal work of \citet{Zeldovich70}, are 
-consistent with the Cosmic Web picture, where planar pancake-like regions 
-of matter enclose enormous underdense voids and are bordered, in turn, by 
-thin filaments and high-density clumpy knots \citep{Bond96}. First 
-theoretical models for describing formation, dynamics and properties of 
-voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were 
-dramatically complemented and extended by first numerical studies based 
-on simulations \citep{Martel90, Regos91, Weygaert93, Dubinski93}. This 
-tendency of using numerical data from N-body simulations, fuelled by last 
-generation computing systems and ever more efficient numerical algorithms, 
-has become increasingly common in the last years as a powerful analysis 
-toolkit of cosmic voids (for an extensive compilation of previous 
-numerical works, see \citet{Colberg08}).
+On the theoretical side the rough theoretical framework that explains
+the origin of voids was stablished in the seminal work of
+\citet{Zeldovich70} and refined in the following decades.  
+The first detailed theoretical models describing formation, dynamics
+and properties of  voids \citep{Hoffman82, Icke84, Bertschinger85,
+  Blumenthal92} were  complemented and extended by numerical studies
+\citep{Martel90, Regos91, Weygaert93, Dubinski93, Bond96}. 
+Currently, the dominant tendency to study voids relies on using data
+from N-body simulations. For an extensive compilation of previous 
+numerical works we refer the reader to \citet{Colberg08}.
 
-At present, studying voids may be considered as a threefold enterprise
-\citep{Platen07}: first, they are a key ingredient of the Cosmic Web as 
-they dominate almost the entire volume distribution at large-scales and 
-additionally, they compensate overdense structures in the total budget of 
-matter. This implies that a full understanding of their evolution and 
-properties is essential for fathoming the high complexity of the Cosmic 
-Web. Second, they provide a valuable resource for inferring and probing 
+The relevance of voids to cosmological studies can be summarized in
+three aspects \citep{Platen07}. 
+First, voids are a key ingredient of the Cosmic Web. 
+They dominate the volume distribution at large-scales and
+additionally, they compensate overdense structures in the total budget
+of  matter.  
+Second, voids provide a valuable resource for inferring and probing 
 cosmological parameters as their structure and dynamics are highly 
-determined by these values. Third, they constitute an unique and still 
-largely pristine environment in which can be tested galaxy evolution.
+determined by these values. 
+Third, they are a  largely a largely pristine environment to test
+galaxy evolution.
 
 Although a visual recognition of voids in galaxy surveys and simulations
-is possible in most cases, a formal systematic identification is necessary 
-for statistically meaningful studies. However, a basic yet essential issue 
-remains regarding the definition itself of what a void is. There is not a 
-general consensus about an unambiguous definition of cosmic voids and 
-therefore, there can be found many different void finding techniques 
-throughout the literature (for a detailed comparison of different schemes, 
-see the Void Finder Comparison Project \citet{Colberg08}). In spite of the 
-diversity of existing schemes, they can be roughly classified into two 
-main types: first, geometric schemes based on point spatial or redshift 
-distribution of galaxies in surveys or catalogues of dark matter halos in 
-simulations \citep{Kauffmann91, Muller00, Gottlober03, Hoyle04, Brunino07, 
-Foster09, Micheletti14, Sutter14}, and second, schemes based on the smooth 
-and continuous matter density field either from simulations or from 
-reconstruction procedures on surveys \citep{Plionis02, Colberg05, 
-Shandarin06, Platen07, Neyrinck08, Neyrinck13, Ricciardelli2013}.
+is possible in most cases, a formal systematic identification is desirable
+for statistical studies. 
+However, the community does not have an unambiguous definition of cosmic
+voids. 
+There are nany different void finding techniques in the literature
+(for a detailed comparison of different schemes,  see the Void Finder
+Comparison Project \citet{Colberg08}). 
+In spite of the diversity of existing schemes, they can be roughly
+classified into two main types. First, geometric schemes based on
+point spatial or redshift  distribution of galaxies in surveys or dark
+matter halos in  simulations \citep{Kauffmann91, Muller00,
+  Gottlober03, Hoyle04, Brunino07,  Foster09, Micheletti14, Sutter14};
+second, schemes based on the smooth  and continuous matter density
+field either from simulations or from  reconstruction procedures on
+surveys \citep{Plionis02, Colberg05,  Shandarin06, Platen07,
+  Neyrinck08, MunozCuartas11, Neyrinck13, Ricciardelli2013}.
 
-Here we introduce a new tracer of the structure of cosmic voids built from 
-two tensorial web schemes, i.e. the Tweb, based on the Hessian of the 
-gravitational potential or tidal tensor \citep{Hahn07, Forero09}, and the 
-Vweb, based on the velocity shear tensor \citep{Hoffman12}. These web 
-schemes classify the Cosmic Web into four different types of environment
-depending on the counting of the number of eigenvalues below an 
-user-defined threshold ($\lambda_{th}$), namely voids (3 eigenvalues below
-$\lambda_{th}$), sheets (2), filaments (1) and knots or clusters (0).
+Here we introduce a new tracer of the structure of cosmic voids that
+can be used once the continous matter density or velocity distribution
+is known. 
+The algorithm is based on two tensorial schemes used to classify the
+cosmic web. 
+The first (the T-web) is based on the Hessian of the gravitational potential or
+tidal tensor \citep{Hahn07, Forero09}. 
+The second (the V-web) is based on the velocity shear tensor
+\citep{Hoffman12}. 
+These web schemes classify the Cosmic Web into four different types of
+environment depending on the counting of the number of eigenvalues below an 
+user-defined threshold ($\lambda_{rm th}$): voids, sheets, filaments and
+knots for $3,2,1$ or $0$ eigenvalues below $\lambda_{\rm th}$, respectively.
+
+%%
+
 The tidal and the shear tensors have proven to be more fundamental than 

### 2014-12-20 cosmic_voids.tex
introduccion revisada

@@
 %=========================================================================
-\title{Fractional anisotropy as a tracer of cosmic voids}
+\title{Tidal field anisotropy as a tracer of cosmic voids}
 \author[S. Bustamante and J.E. Forero-Romero]{
@@
 
-%%
+This procedure allows a new description of the internal structure
+of voids that goes beyond a simple definition of a void as just an
+underdense regions in the large-scale matter distribution.
+The tidal and the shear tensors encode more information than the
+density field as they trace the collapsing or expanding
+nature of the matter field, which defines the dynamics of the Cosmic
+Web.
 
-The tidal and the shear tensors have proven to be more fundamental than 
-the density field as they also trace the collapsing or expanding nature of 
-the matter field, which ultimately is what defines the underlying dynamics 
-of the Cosmic Web. Furthermore, the density field is degenerated regarding 
-the defined types of environment \citep{Hahn07}, which implies that is not 
-possible to assign a priori a range of density values to each of them. 
-This yields that the usually adopted definition of voids as simply 
-underdense regions in the large-scale matter distribution, is not precise 
-enough as it excludes a proper description of the internal structure of 
-voids.
+The tracer that we use to define the voids is the fractional
+anisotropy (FA) computed from the set of eigenvalues of the tensor
+under consideration. 
+The FA  was initially introduced by \citet{Basser95} to quantify the
+anisotropy degree of the diffusivity of water molecules through
+cerebral tissue in nuclear magnetic resonance
+imaging.
+\citet{Libeskind13} introduced this concept in the context of Cosmic
+Web classification schemes.
 
-Following the recent trend of using digital image-processing techniques 
-developed in other disciplines (e.g. medical sciences and computer imaging) 
-for analysing the structure of the Cosmic Web, we propose here, much in 
-the same way as \citet{Libeskind13}, the fractional anisotropy (FA) as a 
-tracer of the internal structure and the outline of cosmic voids. The FA 
-was initially introduced by \citet{Basser95} for quantifying the 
-anisotropy degree of the diffusivity of water molecules through cerebral
-tissue in nuclear magnetic resonance imaging. In this context we use the 
-same quantity for determining the anisotropy degree of the local 
-environment from either the orbital dynamics as set by the eigenvalues of
-the tidal tensor (Tweb), or the dynamics of the velocity field as set by 
-the eigenvalues of the shear tensor (Vweb). In both cases, the FA is not
-determined directly from the density field, it hence is suitable for 
-describing both, the structure of high non-linear regions (e.g. filaments,
-knots and very dense walls) as well as the fainter substructure exhibited 
-by quasi-linear regions like voids.
+Once we establish the FA as a conveniente tracer for voids, we proceed to
+identify individual voids as basins of local minima. For this purpose we
+implement a \textit{watershed transform algorithm}
+\citep{Beucher79,Beucher93} which has been already implemented on void
+finding schemes\citep{Platen07,Neyrinck08} defining voids as catching
+basins of local minima of the density field.  
+We use insted minima of the FA field to find define the voids.
 
-Once established the FA as the tracer field of cosmic voids, we proceed to
-identify individual voids as basins of local minima. For this purpose we
-implement a technique developed by \citet{Beucher79} and \citet{Beucher93} 
-and widely used in the field of image analysis and mathematical morphology, 
-i.e. the \textit{watershed transform algorithm}. This technique has been 
-already implemented on void finding schemes by \citet{Platen07} and 
-\citet{Neyrinck08} with very interesting results, where individual voids 
-are identified as catching basins of local minima of the density field. 
-The appeal of this algorithm consists in that is parameter-free and does 
-not require any assumption on the shape and morphology of voids. 
-Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
-Cartesian mesh for estimating the density and tensor fields, instead of 
-the more sophisticated \textit{Delaunay tessellation for field estimator} 
-(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
-watershed transform should not be significantly affected as we are 
-interested in low density regions where the \texttt{CIC} gives similar 
-estimations.
-
-This paper is organized as follows. In section 2 we describe the used
-simulation for testing our void finding algorithm, i.e. the Bolshoi
-simulation. A detailed description of these methods is presented in 
-section 3. In section 4 we describe how the FA can be used for tracing the 
-structure of voids. Once obtained meaningful catalogues of voids for each 
-scheme, we proceed to compare some typical and general interest properties 
-of voids such as volume functions, distributions of size and density and 
-velocity profiles. This is done in section 5. Finally in section 6 we 
-analyse and evaluate our findings.
-
-%*************************************************************************
-\section{The Simulation}
-\label{sec:the_simulation}
-%*************************************************************************
-
-We use here an unconstrained cosmological simulation (the Bolshoi 
-simulation) to identify the possible large scale environment and the 
-distribution of cosmic voids at $z=0$. The Bolshoi simulation follows the 
-non-linear evolution of a dark matter density field on a cubic volume of 
-size $250$\hMpc sampled with $2048^3$ particles. The cosmological 
-parameters in the simulation are $\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}
-=0.73$, $h=0.70$, $n=0.95$ and $\sigma_{8}=0.82$ for the matter density, 
-cosmological constant, dimensionless Hubble parameter, spectral index of 
-primordial density perturbations and normalization for the power spectrum
-respectively, consistent with the seventh year of data of the Wilkinson 
-Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. For more detailed 
-technical information about the simulation, see \citet{Klypin11}.
-
-For estimating the density and velocity fields we use a 
-\textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
-cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
-through finite-differences and FFT methods the tidal and shear tensors 
-are computed. Finally, the eigenvalues and eigenvectors of the tensor are
-obtained for each cell of the grid. Neglecting substructures presented 
-below Megaparsec scales and taking into account our focus in voids, which
-are a prominent characteristic of the Megaparsec Universe, we apply a 
-Gaussian softening of one cell to all fields.
+This paper is organized as follows. 
+In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
+we use to find the cosmic web in N-body simulations. 
+Then in Section \ref{sec:bulk_voids} we explain in detail our void
+finder based on the fractional anisotropy of the tidal and shear
+tensor fields. 
+In Section \ref{sec:experiments} we describe the setup
+for the numerical experiments we perform to show the performance of
+the new void finding technique. 
+Our results are presented in \ref{sec:results} to finally comment and
+conclude about this findings in Section \ref{sec:conclusions}.
 
@@
 %*************************************************************************
-\section{Finding voids}
+\section{A new void finding technique}
 \label{sec:bulk_voids}
@@
 %.........................................................................
+
+\subsection{Watershed algorithm}
+\label{sec:watershed}
+
+This algorithm is parameter-free and does  not require any assumption
+on the shape and morphology of voids.  
+Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
+Cartesian mesh for estimating the density and tensor fields, instead of 
+the more sophisticated \textit{Delaunay tessellation for field estimator} 
+(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
+watershed transform should not be significantly affected as we are 
+interested in low density regions where the \texttt{CIC} gives similar 
+estimations.
 
@@
 %*************************************************************************
-\section{Properties of voids}
-\label{sec:properties}
+\section{Numerical Experiments}
+\label{sec:experiments}
+%*************************************************************************
+
+We use here an unconstrained cosmological simulation (the Bolshoi 
+simulation) to identify the possible large scale environment and the 
+distribution of cosmic voids at $z=0$. The Bolshoi simulation follows the 
+non-linear evolution of a dark matter density field on a cubic volume of 
+size $250$\hMpc sampled with $2048^3$ particles. The cosmological 
+parameters in the simulation are $\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}
+=0.73$, $h=0.70$, $n=0.95$ and $\sigma_{8}=0.82$ for the matter density, 
+cosmological constant, dimensionless Hubble parameter, spectral index of 
+primordial density perturbations and normalization for the power spectrum
+respectively, consistent with the seventh year of data of the Wilkinson 
+Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. For more detailed 
+technical information about the simulation, see \citet{Klypin11}.
+
+For estimating the density and velocity fields we use a 
+\textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
+cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
+through finite-differences and FFT methods the tidal and shear tensors 
+are computed. Finally, the eigenvalues and eigenvectors of the tensor are
+obtained for each cell of the grid. Neglecting substructures presented 
+below Megaparsec scales and taking into account our focus in voids, which
+are a prominent characteristic of the Megaparsec Universe, we apply a 
+Gaussian softening of one cell to all fields.
+
+%*************************************************************************
+\section{Results}
+\label{sec:results}
 %*************************************************************************

### 2015-01-06 cosmic_voids.tex
2 ultimos parrafos de la introduccion revisados

@@
 
-Once we establish the FA as a conveniente tracer for voids, we proceed to
-identify individual voids as basins of local minima. For this purpose we
-implement a \textit{watershed transform algorithm}
-\citep{Beucher79,Beucher93} which has been already implemented on void
-finding schemes\citep{Platen07,Neyrinck08} defining voids as catching
-basins of local minima of the density field.  
-We use insted minima of the FA field to find define the voids.
+Once we establish the FA as a void tracer, we proceed to
+identify individual voids as basins of local minima. 
+For this we implement a \textit{watershed transform algorithm}
+\citep{Beucher79,Beucher93} which has been used to define as catching
+basins of local minima of the density field
+\citep{Platen07,Neyrinck08}; we use insted minima of the FA field to
+find define the voids.
 
@@
 tensor fields. 
-In Section \ref{sec:experiments} we describe the setup
-for the numerical experiments we perform to show the performance of
-the new void finding technique. 
+In Section \ref{sec:experiments} we describe the numerical experiments
+we perform to show the performance of the new void finding technique.  
 Our results are presented in \ref{sec:results} to finally comment and
-conclude about this findings in Section \ref{sec:conclusions}.
+conclude about these findings in Section \ref{sec:conclusions}.
 

### 2015-01-06 cosmic_voids.tex
updated presentation of the method, removed ellipticity-prolateneess

@@
 %*************************************************************************
-\section{Algorithms to quantify the Cosmic Web}
+\section{Algorithms to label the Cosmic Web}
 \label{sec:algorithms_cosmic_web}
@@
 
-This scheme was initially proposed by \citet{Hahn07} as a novel 
-alternative for classifying the Cosmic Web based on the tidal tensor, 
-that is somehow more fundamental than the density field as it also allows 
-to quantify the orbital dynamics of the matter field. This approach 
-consists of a second-order expansion of the equations of motion around 
-local minima of the gravitational potential and then extended to any 
-position. The second-order term corresponds to the tidal tensor, which is
-defined as the Hessian matrix of the normalized gravitational potential
+This scheme was initially proposed by \citet{Hahn07} as an
+alternative for classifying the Cosmic Web based on the tidal tensor.
+The tidal tensor allows a classification in terms of the orbital
+dinamics of the matter field
+This approach extends to second-order the equations of motion around 
+local minima of the gravitational potential. 
+The second-order term corresponds to the tidal tensor, which is
+defined as the Hessian matrix of the normalized gravitational
+potential.
 
@@
 \eq{V_web}
-{	T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}}	}
+{	T_{\alpha\beta} = \frac{\partial^2\phi}{\partial x_{\alpha}\partial x_{\beta}},	}
 %.........................................................................
-where the physical gravitational potential has been rescaled by a factor 
-$4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
-equation
+where the physical gravitational potential has been rescaled by a
+factor of   $4\pi G\bar{\rho}$ in such a way that $\phi$ satisfies the following 
+Poisson equation
 
@@
 with $\bar{\rho}$ the average density in the Universe, $G$ the 
-gravitational constant and $\delta$ the dimensionless matter overdensity.
+gravitational constant and $\delta$ the dimensionless matter
+overdensity.
 
-Since the tidal tensor can be represented in any cell by a real and 
-symmetric $3\times 3$ matrix, it is ensured the possibility to diagonalize 
+Since the tidal tensor can be represented by a real and  symmetric
+$3\times 3$ matrix, it is always possible to diagonalize  
 it and obtain three real eigenvalues $\lambda_{1}\geq\lambda_{2}\geq
-\lambda_3$. This set of eigenvalues can be used as indicators of the local 
-orbital stability in each proper direction, which in turn can be 
-translated into a classification scheme of the Cosmic Web. A counting of 
-the number of positive (stable) or negative (unstable) eigenvalues allows 
-to catalogue a single cell into one of the next four types of environment: 
+\lambda_3$ with its corresponding eigenvectors ${\bf u}_{1}$, ${\bf u}_{2}$,
+${\bf u}_{3}$. 
+This set of eigenvalues are indicators of the local  orbital stability
+in each direction ${\bf u}_i$, which is to label the Cosmic Web.
+The number of positive (stable) or negative (unstable) eigenvalues allows 
+to label a location into one of the next four types of environment: 
 voids (3 negatives eigenvalues), sheets (2), filaments (1) and knots (0). 
-A significant improvement to this scheme was introduced by \citet{Forero09}
+A modification to this scheme was introduced by \citet{Forero09}
 by means of a relaxation of the stability criterion. The relative strength 
 of each eigenvalue is no longer defined by the sign, but instead by a
-threshold value $\lambda_{th}$ that can be tuned in such a way that the
-visual impression of the web-like matter distribution is reproduced.
+threshold value $\lambda_{\rm th}$ that can be tuned in such a way
+that the visual impression of the web-like matter distribution is
+reproduced.
 
@@
 
-We also use a kinematical scheme to define the Cosmic Web environment in 
-the simulation. The scheme has been thoroughly described in 
-\citet{Hoffman12} and applied to study the shape and spin alignment in the
-Bolshoi simulation in \citet{Libeskind13}. We refer the reader to these 
-papers to find a detailed description of the algorithm, its limitations 
-and capabilities. The Vweb scheme for environment finding is based on the
+We also use a kinematic scheme to define the Cosmic Web environment in 
+the simulation, which has been thoroughly described in 
+\cite{Hoffman12}.
+This scheme has been used to study the shape, spin and peculiar
+velocity alignments of dark matter halos with the cosmic web
+\citep{Libeskind13,Forero2014}. 
+We refer the reader to these papers to find a detailed description of
+the algorithm, its limitations  and capabilities.    
+The Vweb scheme for environment finding is based on the
 local velocity shear tensor calculated from the smoothed dark matter 
-velocity field in the simulation. The central quantity is given by the 
-following dimensionless expression
+velocity field in the simulation. This tensor is given by the 
+following expression
 
@@
 {	\Sigma_{\alpha\beta} = -\frac{1}{2H_0}\pr{\frac{\partial v_{\alpha}}
-{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}}	}
+{\partial x_{\beta}}+\frac{\partial v_{\beta}}{\partial x_{\alpha}}},}
 %.........................................................................
@@
 $\Sigma_{\alpha\beta}$ can be represented by a $3\times 3$ symmetric 
-matrix with real values, hence diagonalizing it is obtained three real 
-eigenvalues $\lambda_{1}\geq\lambda_{2}\geq\lambda_3$ whose sum (the 
-trace of $\Sigma_{\alpha\beta}$) is proportional to the divergence of the 
-local velocity field smoothed on the physical scale ${\mathcal R}$.
+matrix with real values, making it possible to find three real
+eigenvalues and its corresponding eigenvectors.
+%$\lambda_{1}\geq\lambda_{2}\geq\lambda_3$.
+%whose sum (the 
+%trace of $\Sigma_{\alpha\beta}$) is proportional to the divergence of the 
+%local velocity field smoothed on the physical scale ${\mathcal R}$.
 
-In the same way, the relative strength of the three eigenvalues with 
-respect to a threshold value $\lambda_{th}$ allows for the local 
-classification of the matter distribution into the previous four web types. 
-For the threshold choosing in both schemes, the Tweb and the Vweb, it is
-usual to fine-tuning the value in such a way that the visual appearance of
-the Cosmic Web as seen in simulations and galaxy surveys is reproduced. 
-However, we do not take this approach here, instead we propose a novel 
-approach for the threshold choosing based on the maximization of the 
-fractional anisotropy field occurring in filaments and very dense walls.
+In this case we also use the relative strength of the three eigenvalues with 
+respect to a threshold value $\lambda_{th}$ to classify the cosmic web
+in the four web types we have already described.
+
+Usually, the threshold is a free parameter that is tuned to reproduce
+the visual appearence of the comic web. 
+In this paper we take a different approach.
+We find the optimal value of the threshold based on the maximization
+of the fractional anisotropy field in the locations label as filaments
+and walls.
+
+\section{Numerical Simulations}
+\label{sec:simulatins}
+
+We use the Bolshoi simulation to test the method describe in the
+paper. 
+This simulation follows the non-linear evolution of a dark
+matter density field on a cubic volume of  size $250$\hMpc sampled
+with $2048^3$ particles. 
+The cosmological parameters in the simulation are $\Omega_{\rm m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$,
+$n=0.95$ and $\sigma_{8}=0.82$ for the matter density,   cosmological
+constant, dimensionless Hubble parameter, spectral index of
+primordial density perturbations and normalization for the power
+spectrum, respectively. 
+This values are consistent with the seventh year of data of the Wilkinson 
+Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. 
+For more detailed  technical information about the simulation, see
+\citet{Klypin11}.
+
+We find the cosmic web we estimate first the density and velocity
+fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
+cells, corresponding to a spatial resolution of $0.98$\hMpc per cell
+side.  
+These fields are smoothed with a gaussian filter with a width of
+$\sigma=0.98$\hMpc. 
+We compute the tidal and shear tensors through finite-differences and
+Finally, the eigenvalues and eigenvectors of the tensor are
+obtained for each grid cell.
+The data we use here is publicly available through the MultiDark
+database \url{http://www.multidark.org/MultiDark/} which is described
+in \citet{Riebe11}.
 
@@
 conceived to quantify the anisotropy degree of a diffusion process, e.g. 
-the diffusivity of water molecules through cerebral issue in nuclear
-magnetic resonance imaging. Here we propose the FA, much in the same 
-way as \citet{Libeskind13}, as a tracer of cosmic voids.
+the diffusivity of water molecules through cerebral tissue in nuclear
+magnetic resonance imaging. 
+Here we propose the FA, much in the same way as \citet{Libeskind13},
+as a tracer of cosmic voids.
 
+The FA is defined as follows.
 %.........................................................................
@@
 \eq{fractional_anisotropy}
-{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
+{{\mathrm{FA}} = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
 (\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
-\lambda_2^2 + \lambda_3^2} } }
+\lambda_2^2 + \lambda_3^2} },}
 %.........................................................................
 where the eigenvalues are taken from either the Tweb or the Vweb 
-(FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
-corresponds with an isotropic dynamic and $FA=1$ with a highly anisotropic 
+(FA-Tweb and FA-Vweb respectively). Such as it is defined, FA$=0$ 
+corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) and FA$=1$ with a highly anisotropic 
 distribution.
 
-In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
-web schemes over a slide of the simulation. Some important points can be 
-concluded from this figure:
+In left panels of Fig. \ref{fig:FA_field} we show the FA field for both 
+web schemes over a slide of the simulation. 
+From this Figure we can observe that both voids and knots display a highly isotropic
+expanding dynamic at their centres, becoming gradually more
+anisotropic at outer regions. 
+On the other hand the filamentary structure is traced by high FA
+values. These characteristics are the key to use the FA as a tracer of
+cosmic voids.
 
 %.........................................................................
-\begin{itemize}
-\item Voids display a highly isotropic expanding dynamic at their centres, 
-becoming gradually more anisotropic at outer regions.
-\item Knots feature with very isotropic collapses. For the Tweb, the FA 
-exhibits very narrow distribution around knots. For the Vweb, these
-distributions are more spread out, thereby indicating strong differences 
-between the density and the velocity fields in highly non-linear regions.
-\item The filamentary structure of the Cosmic Web is well traced by high 
-FA values (black regions), thus indicating very anisotropic dynamics for 
-sheets and filaments.
-\item The FA, unlike the density field, displays a non-monotonic behaviour, 
-where low values are characteristic of central regions of voids, reaching 
-high values in sheets and filaments and becoming low again in knots. 
-%\item The density field poorly traces the Cosmic Web. This is a somehow 
-%expected result due to the semi-infinite range of the density field, what 
-%makes more difficult to trace structures.
-\end{itemize}
+%FIGURE 1: FA and vissual impression
+\begin{figure*}
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+  \vspace{0.1 cm}
+  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+  \caption{Left colum. Visual impression of the 
+  FA field over a slide of the simulation for each web scheme (T-web, upper 
+  panels. V-web, middle panels). 
+  Middle column. Components of the Cosmic Web using $\lambda_{th}$
+  values that put an upper bound of $FA=0.95$ to voids. Voids
+  corresponds with white, sheets to gray, filaments to dark gray and
+  knots with black regions. 
+  Right column. Sketches the distribution of the catalogued voids by
+  our method.}
+  \label{fig:FA_field}
+\end{figure*}
 %.........................................................................
 
-\subsection{Watershed algorithm}
+%-------------------------------------------------------------------------
+\subsection{Fractional anisotropy as a void tracer}
+\label{subsec:web_voids}
+%-------------------------------------------------------------------------
+
+%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
+\begin{flushleft}
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/FA_L1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/delta_L1.pdf}
+
+  \captionof{figure}{\small Distributions of the FA (left panel) and the 
+  density field (right panel) with respect to the eigenvalue $\lambda_1$ 
+  for each web scheme (Tweb, red lines. Vweb, blue lines) as calculated 
+  over all cells of the grid. Thick central lines correspond with the median 
+  and filled regions with the $50\%$ of the distribution.}
+
+  \label{fig:L1_correlations}
+  \vspace{0.1 cm}
+
+\end{figure*}
+\end{flushleft}
+%.........................................................................
+
+Voids are regions where $\lambda_3\leq\lambda_2\leq
+\lambda_1\leq\lambda_{th}$. 
+This implies that a void is completely fixed by the relative strength
+of the $\lambda_1$ eigenvalue with respect to the $\lambda_{th}$.   
+As we  increase/decrease the threshold value $\lambda_{th}$, voids
+increase/decrease progressively through contours of
+increasing/decreasing $\lambda_1$.
+
+Voids are thus characterized by low values of both FA and
+$\lambda_1$. 
+In Fig. \ref{fig:L1_correlations} we show that the these two values
+are indeed closely correlated.  
+The left panel shows the correlation between $\lambda_1$ and $FA$ for
+all the grid cells in the simulation while the right panel shows the
+correlation between $\lambda_1$ and the local overdensity $\delta$.  
+This shows that the overdensity has a large scatter at fixed
+$\lambda_1$.
+
+From Figs. \ref{fig:FA_field} and \ref{fig:L1_correlations} we
+conclude that the FA is a good tracer of voids as it is almost perfectly
+correlated with low values of $\lambda_1$. 
+We propose that voids should be composed completely by regions of
+FA$<0.95$.
+If we increase the values of $\lambda_1$ from its minimum until it
+we reach FA$=0.95$ in \ref{fig1:L1_correlations} we find that this
+correspond to critical values of $\lambda_{1}^T = 0.265$ and
+$\lambda_{1}^V = 0.175$ for the Tweb and Vweb, respectively.
+This means that setting $\lambda_{th}$ to either
+$\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
+all the cells $FA<0.95$.   
+The middle column in Fig. \ref{fig:FA_field} shows the web
+classification for this choice of $\lambda_{th}$, demonstrating that
+it is a sensible choice to define voids.
+
+\subsection{Defining voids with a watershed algorithm}
 \label{sec:watershed}
 
+{\bf Reescribir para describir lo que hace el algoritmo}
 This algorithm is parameter-free and does  not require any assumption
@@
 
-%-------------------------------------------------------------------------
-\subsection{Voids using web schemes}
-\label{subsec:web_voids}
-%-------------------------------------------------------------------------
+%Once set the optimal thresholds for the web schemes, we proceed in Fig. 
+%\ref{fig:FAShapeness} to sample the FA and the prolateness for a random 
+%sample of cells previously classified into one of the four
+%environments.
 
-For both web schemes, voids are regions where $\lambda_3\leq\lambda_2\leq
-\lambda_1\leq\lambda_{th}$. This implies that the outlines of voids
-are completely fixed by the relative strength of the $\lambda_1$ 
-eigenvalue with respect to the threshold value. Therefore, as we 
-increase/decrease the threshold value $\lambda_{th}$, voids expand/diminish
-progressively through contours of $\lambda_1$. In Fig. 
-\ref{fig:L1_correlations} we calculate the distribution of the FA as well
-as of the density field with respect to $\lambda_1$ over all cells of the 
-grid.
+%The prolateness is introduced here for differentiating sheets and filaments
+%featuring high FA values. 
+%In order to illustrate the underlying local 
+%dynamics sampled by the cells, we also sketch different spheroidal 
+%geometries according to the relative strength of each eigenvalue, and 
+%then, we associate them to different ranges of the FA and the prolateness.
 
-From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
-tracer of voids as is almost perfectly correlated with low values of 
-$\lambda_1$. Then, it reaches a maximum value, namely sheets and filaments, 
-for finally reaching knots, which feature low FA values. This behaviour can 
-be thought as a sort of one-dimensional tomography of the Cosmic Web. This
-characteristic allows us to propose an optimal threshold value for both 
-web schemes where the FA is maximized. Specifically we propose a value of 
-$FA=0.95$, corresponding with a threshold $\lambda_{opt}^T = 0.265$ for
-the Tweb and $\lambda_{opt}^V = 0.175$ for the Vweb.  For a threshold 
-above these values, voids would span over very anisotropic regions, which 
-must correspond to sheets and filaments. A threshold below would imply 
-very low volume filling fractions of voids and dominant sheets. Finally, 
-the density field do not correlate well with $\lambda_1$ (as calculated 
-for both web schemes), and due to its monotonic increase, an estimate of 
-an optimal threshold is not as clear as for the FA.
-
-Once set the optimal thresholds for the web schemes, we proceed in Fig. 
-\ref{fig:FAShapeness} to sample the FA and the prolateness for a random 
-sample of cells previously classified into one of the four environments. 
-The prolateness is introduced here for differentiating sheets and filaments
-featuring high FA values. In order to illustrate the underlying local 
-dynamics sampled by the cells, we also sketch different spheroidal 
-geometries according to the relative strength of each eigenvalue, and 
-then, we associate them to different ranges of the FA and the prolateness. 
-From this, we conclude sheets display very anisotropic distributions, 
-namely above $FA=0.95$. They are also biased towards oblate geometries, 
-however there are some elongated sheets as well. Filaments are not as 
-anisotropic as sheets, ranging from middle up to high FA values. They 
-exhibit prolate geometries, but a considerable fraction of them are biased 
-towards slightly more oblate values. Voids and knots are the only 
-environments featuring with low FA values, thus indicating very isotropic 
-expanding/collapsing dynamics at their centres. However, voids span over 
-a very wide range of FA and geometries, whereas knots only span over low 
-to middle FA values and display a biased oblate geometry.
-
-%-------------------------------------------------------------------------
-\subsection{Identifying void regions through web schemes}
-\label{subsec:identification}
-%-------------------------------------------------------------------------
-
-%*************************************************************************
-\section{Numerical Experiments}
-\label{sec:experiments}
-%*************************************************************************
-
-We use here an unconstrained cosmological simulation (the Bolshoi 
-simulation) to identify the possible large scale environment and the 
-distribution of cosmic voids at $z=0$. The Bolshoi simulation follows the 
-non-linear evolution of a dark matter density field on a cubic volume of 
-size $250$\hMpc sampled with $2048^3$ particles. The cosmological 
-parameters in the simulation are $\Omega_{\rm m}=0.27$, $\Omega_{\Lambda}
-=0.73$, $h=0.70$, $n=0.95$ and $\sigma_{8}=0.82$ for the matter density, 
-cosmological constant, dimensionless Hubble parameter, spectral index of 
-primordial density perturbations and normalization for the power spectrum
-respectively, consistent with the seventh year of data of the Wilkinson 
-Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. For more detailed 
-technical information about the simulation, see \citet{Klypin11}.
-
-For estimating the density and velocity fields we use a 
-\textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
-cells, corresponding to a resolution of $0.98$\hMpc per cell side. Then, 
-through finite-differences and FFT methods the tidal and shear tensors 
-are computed. Finally, the eigenvalues and eigenvectors of the tensor are
-obtained for each cell of the grid. Neglecting substructures presented 
-below Megaparsec scales and taking into account our focus in voids, which
-are a prominent characteristic of the Megaparsec Universe, we apply a 
-Gaussian softening of one cell to all fields.
+%From this, we conclude sheets display very anisotropic distributions, 
+%namely above $FA=0.95$. They are also biased towards oblate geometries, 
+%however there are some elongated sheets as well. Filaments are not as 
+%anisotropic as sheets, ranging from middle up to high FA values. They 
+%exhibit prolate geometries, but a considerable fraction of them are biased 
+%towards slightly more oblate values. Voids and knots are the only 
+%environments featuring with low FA values, thus indicating very isotropic 
+%expanding/collapsing dynamics at their centres. However, voids span over 
+%a very wide range of FA and geometries, whereas knots only span over low 
+%to middle FA values and display a biased oblate geometry.
 
@@
 %.........................................................................
-%FIGURE 1: FA and vissual impression
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
-  \vspace{0.1 cm}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
-
-  \captionof{figure}{\small Left panels show the visual impression of the 
-  FA field over a slide of the simulation for each web scheme (T-web, upper 
-  panels. V-web, middle panels). Black regions correspond with high values, 
-  i.e. FA$\approx 1$, while white and light yellow regions to FA$\approx 0$. 
-  It is worth noting the degeneration of low values of FA for knots and 
-  central regions of voids, thus indicating a high isotropy for both 
-  processes. In the same way, high values of FA are consistent with the 
-  anisotropic geometry exhibited by filaments and very flat sheets. Middle 
-  panels sketch the components of the Cosmic Web using the optimal threshold 
-  values. Voids corresponds with white, sheets to gray, filaments to dark 
-  gray and knots with black regions. Finally right panels sketch the 
-  distribution of the catalogued voids by our method.}
-
-  \label{fig:FA_field}
-
-\end{figure*}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/FA_L1.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/delta_L1.pdf}
-
-  \captionof{figure}{\small Distributions of the FA (left panel) and the 
-  density field (right panel) with respect to the eigenvalue $\lambda_1$ 
-  for each web scheme (Tweb, red lines. Vweb, blue lines) as calculated 
-  over all cells of the grid. Thick central lines correspond with the median 
-  and filled regions with the $50\%$ of the distribution.}
-
-  \label{fig:L1_correlations}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
 
@@
 %FIGURE 3: FA of some regions and shape illustration
-\begin{flushleft}
-\begin{figure*}
-\centering
+%\begin{flushleft}
+%\begin{figure*}
+%\centering
+%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
+%  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
+%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
+%  width=0.3\textheight]{./figures/FA_Prolatenes.png}
 
-  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
-  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/FA_Prolatenes.png}
+%  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
+%  random sample of cells (left panel) and for different spherical 
+%  geometries (right panel). For the cells, each environment is coded with
+%  a different colour, i.e. voids corresponds with dark blue points, 
+%  sheets with green, filaments with orange and knots with cyan. The axis 
+%  of the spheroids are computed from the relative strengths of the 
+%  eigenvalues, so their shape sketch the relative expanding/collapsing 
+%  dynamics into each direction.}
 
-  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
-  random sample of cells (left panel) and for different spherical 
-  geometries (right panel). For the cells, each environment is coded with
-  a different colour, i.e. voids corresponds with dark blue points, 
-  sheets with green, filaments with orange and knots with cyan. The axis 
-  of the spheroids are computed from the relative strengths of the 
-  eigenvalues, so their shape sketch the relative expanding/collapsing 
-  dynamics into each direction.}
+%  \label{fig:FAShapeness}
+%  \vspace{0.1 cm}
 
-  \label{fig:FAShapeness}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
+%\end{figure*}
+%\end{flushleft}
 %.........................................................................

### 2015-01-10 cosmic_voids.tex
Updating figures and pdf with colorbar

@@
 \begin{figure*}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
   width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
   \vspace{0.1 cm}
-  \includegraphics[trim = 16mm 10mm 5mm 12mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
   width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}

### 2015-01-10 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -87,7 +87,7 @@ voids = CutFieldZ( "%s/%s/%s/%d/voids%s/voids_%s/void_index.dat"%\
 (foldglobal, simulation, web, N_sec, void_scheme, config ), Cut, 'plain', Coor = axe )
 
 #Loading Fields
-delta = CutFieldZ( delta_filename, Cut, 32, Coor = axe )
+#delta = CutFieldZ( delta_filename, Cut, 32, Coor = axe )
 eig1 = CutFieldZ( eig_filename+"_1", Cut, 16, Coor = axe )
 eig2 = CutFieldZ( eig_filename+"_2", Cut, 16, Coor = axe )
 eig3 = CutFieldZ( eig_filename+"_3", Cut, 16, Coor = axe )
@@ -123,11 +123,12 @@ plt.imshow( np.transpose(Fractional_Anisotropy( eig1, eig2, eig3 )[::,::-1]), ex
 plt.title( "Fractional Anisotropy (%s)"%web )
 plt.yticks( (),() )
 plt.xticks( (0,Box_L) )
-plt.xlabel( "[$h^{-1}$ Mpc]" )
+plt.xlabel( "[	$h^{-1}$ Mpc]" )
 
-plt.colorbar( orientation = "horizontal", fraction = 0.05, pad = 0.02 )
+#plt.colorbar( orientation = "horizontal", fraction = 0.03, pad = 0.025 )
 
-##Visual impression
+
+#Visual impression
 plt.subplot( 1, 3, 2 )
 Coor, X = CutHaloZ( Cut*Box_L/(1.0*N_sec)-dx/2.0, dx, GH, plot = False )
 plt.plot( Coor[0], Coor[1], '.', color = 'blue', markersize = 1 )

### 2015-01-10 cosmic_voids.tex
Section 4.3 Watershed transform, done.

@@
 However,  due to the large volume extension of void regions ($\sim
-5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
+5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogs of
 voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
@@
 On the theoretical side the rough theoretical framework that explains
-the origin of voids was stablished in the seminal work of
+the origin of voids was established in the seminal work of
 \citet{Zeldovich70} and refined in the following decades.  
@@
 web schemes over a slide of the simulation. 
-From this Figure we can observe that both voids and knots display a highly isotropic
-expanding dynamic at their centres, becoming gradually more
+From this Figure we can observe that both, voids and knots, display a highly 
+isotropic expanding dynamic at their centres, becoming gradually more
 anisotropic at outer regions. 
@@
   width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
-  \vspace{0.1 cm}
   \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
@@
   \label{fig:L1_correlations}
-  \vspace{0.1 cm}
 
@@
 If we increase the values of $\lambda_1$ from its minimum until it
-we reach FA$=0.95$ in \ref{fig1:L1_correlations} we find that this
+we reach FA$=0.95$ in \ref{fig:L1_correlations} we find that this
 correspond to critical values of $\lambda_{1}^T = 0.265$ and
@@
 
-{\bf Reescribir para describir lo que hace el algoritmo}
-This algorithm is parameter-free and does  not require any assumption
-on the shape and morphology of voids.  
-Although we use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a 
-Cartesian mesh for estimating the density and tensor fields, instead of 
-the more sophisticated \textit{Delaunay tessellation for field estimator} 
-(\texttt{DTFE}) technique \citep{Schaap00}, our implementation of the 
-watershed transform should not be significantly affected as we are 
-interested in low density regions where the \texttt{CIC} gives similar 
-estimations.
+Once established the FA as a good tracer of voids, the next step is to
+find individuals voids in the overall distribution. For this purpose, we
+use the \textit{watershed transform algorithm} \citep{Beucher79,Beucher93}, 
+in which a void is identified as the catching basin of a local minimum of
+the FA. The use of this algorithm is advantageous as it is parameter-free 
+and does not require any assumption on the shape and morphology of voids.
+
+Previous implementations of this technique as those of \citet{Platen07,
+Neyrinck08} have shown remarkable results regarding voids finding, however
+they use the density field instead of the FA field. On the other hand, we 
+use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a Cartesian mesh for 
+estimating the density and tensor fields, instead of the more sophisticated 
+\textit{Delaunay tessellation for field estimator} (\texttt{DTFE}) technique 
+\citep{Schaap00}, but our implementation of the watershed transform should 
+not be significantly affected as we are interested in low density regions 
+where the \texttt{CIC} gives similar estimations.
+
+As suggested by \citet{Platen07} and references therein, it is necessary to
+apply a threshold merger in order to reduce spurious features and to avoid 
+void hierarchization. A natural choice is a threshold of $\delta = -0.8$, 
+which means that any ridge between two voids with density below that value
+would be removed and the respective voids merged. As we are working with the
+FA, the equivalent threshold according to Fig. \ref{fig:L1_correlations} is
+$FA = 0.65$. In right panels of Fig. \ref{fig:FA_field} we show the resulting
+catalogs of voids for both schemes.
 
@@
 
-Describing the density profiles of voids is quite important in order to 
-compare and match simulation with observational surveys, allowing possible
-constrains for different cosmology models \SRKED{[Hamaous, et.al 2014]}. 
-Here, and taking into account the previous results, we rather use an 
-ellipsoidal approximation to describe and fit the shape of bulk voids, so 
-we use the next ellipsoidal radial coordinate to describe density profiles.
-
-%.........................................................................
-%Ellipsoidal radial coordinate
-\eq{radial_coordinate}
-{
-r^2 = \frac{x^2}{\tau_1^2} + \frac{y^2}{\tau_2^2} + \frac{z^2}{\tau_3^2},
-\ \ \ \ 0\leq r \leq 1
-}
-%.........................................................................
-where we take the principal moments of inertia $\{\tau_i \}$ as the 
-lengths of the principal axes of the ellipsoid and each one of the 
-cartesian coordinates as measured in the rotated frame of each void.
-
-We use the same analytic density profile that \SRKED{[Hamaous, et.al 2014]} 
-to fit the numerical density profiles of our voids.
-
-%.........................................................................
-%Density profile
-\eq{density_profile}
-{
-\delta_v(r) = \delta_c\frac{1-(r/r_s)^\alpha}{1+(r/r_v)^\beta}
-}
-%.........................................................................
-
 \[ \mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr \]
@@
   \captionof{figure}{\small Volume functions of voids for both built 
-  catalogues. Watershed-Tweb (red curves), Watershed-Vweb (blue curves).
+  catalogs. Watershed-Tweb (red curves), Watershed-Vweb (blue curves).
   Continuous lines corresponds with the total number of voids, dot-dashed

### 2015-01-10 cosmic_voids.tex
Changing units of void size function

@@
 
-Once defined our method to classify bulk voids based upon web 
-classification schemes of the cosmic web, we proceed to analyse some 
-physical properties in order to compare their consistency with the 
-geometry of voids as quantified by our method and by density-based schemes.
-Next, through the reduced inertia tensor we quantify the shape distribution 
-of voids. Finally, we compute numerical radial profiles of density and 
-peculiar velocity of bulk voids.
-
 %-------------------------------------------------------------------------
-\subsection{Statistics of halos in voids}
+\subsection{The void size distribution}
 \label{subsec:shape_voids}
 %-------------------------------------------------------------------------
-
-One of the main challenges in observational void finding is the discrete 
-nature of galaxy surveys
-
- we calculate contours of discrete fields like the median mass and 
-the local number of local dark matter halos and
-
-, like the inertia values,
-the density and peculiar velocities profiles as calculated over the grid 
-and profiles of number of halos.
 

### 2015-01-10 bench/codes_figures/void_volume_regions_all.py

@@ -33,7 +33,7 @@ colors = ["red", "blue", "green"]
 #==================================================================================================
 
 fig = plt.figure( figsize=(5,5) )
-fig.subplots_adjust( top = 0.9, right = 0.96, left = 0.12, wspace = 0.05, bottom = 0.1 )
+fig.subplots_adjust( top = 0.9, right = 0.95, left = 0.15, wspace = 0.05, bottom = 0.1 )
 ax1 = [fig.add_subplot(1,1,i+1) for i in xrange(1)]
 ax2 = [ax1[i].twiny() for i in xrange(1)]
 
@@ -65,9 +65,9 @@ for web in webs:
     
     #Normal distribution
     if sys.argv[1] == '0':
-	distro = hist1d[0]
-	distro_o = hist1d_o[0]
-	distro_u = hist1d_u[0]
+	distro = hist1d[0]/(250.**3)
+	distro_o = hist1d_o[0]/(250.**3)
+	distro_u = hist1d_u[0]/(250.**3)
     #Cumulative distribution
     else:
 	distro = np.cumsum(hist1d[0][::-1])[::-1]
@@ -97,15 +97,15 @@ for i in range(1):
     #ax1[i].set_xticks( np.linspace(0,16,30) )
     ax1[i].set_xticks( np.linspace(0,16,6) )
     ax1[i].set_xlim( (0,16) )
-    ax1[i].set_ylim( (0,10**4.1) )
+    ax1[i].set_ylim( (0,10**-3) )
     #Cumulative distribution
     if sys.argv[1] == '1':
 	ax1[i].set_ylim( (0,1) )
 	for hcut in np.linspace(0,1,9+1):
 	    ax1[i].hlines( hcut, 0, 16, linestyle="--", color = "black", linewidth=1.0 )
     
-    ax1[i].set_ylabel( "Number of voids" )
-    ax1[i].set_xlabel( "Effective radius [Mpc $h^{-1}$]" )
+    ax1[i].set_ylabel( "Voids number density [$n/($Mpc$/h)^3$]" )
+    ax1[i].set_xlabel( "Effective radius [Mpc/$h$]" )
     ax1[i].legend( loc='upper right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )
 
     #Axe 2

### 2015-01-10 cosmic_voids.tex
Section 5.1, Enclosed mass, done

@@
 In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
-we use to find the cosmic web in N-body simulations. 
+we use to find the cosmic web in N-body simulations. In Section 
+\ref{sec:simulations} we describe the used simulation.
 Then in Section \ref{sec:bulk_voids} we explain in detail our void
@@
 tensor fields.
-In Section \ref{sec:experiments} we describe the numerical experiments
-we perform to show the performance of the new void finding technique.  
+%In Section \ref{sec:experiments} we describe the numerical experiments
+%we perform to show the performance of the new void finding technique.
 Our results are presented in \ref{sec:results} to finally comment and
@@
 \section{Numerical Simulations}
-\label{sec:simulatins}
+\label{sec:simulations}
 
@@
 (FA-Tweb and FA-Vweb respectively). Such as it is defined, FA$=0$ 
-corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) and FA$=1$ with a highly anisotropic 
-distribution.
+corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
+and FA$=1$ with a highly anisotropic distribution.
 
@@
 
+%-------------------------------------------------------------------------
 \subsection{Defining voids with a watershed algorithm}
 \label{sec:watershed}
+%-------------------------------------------------------------------------
 
@@
 %-------------------------------------------------------------------------
+\subsection{Enclosed mass}
+\label{subsec:enclosedmass}
+%-------------------------------------------------------------------------thereby allowing a good classification criterion
+
+When we analyse individual density profiles of voids (see left panels of
+Fig. \ref{fig:RhoVel}), they seem to be distributed in two different 
+families, differentiated by the presence or absence or a compensation 
+ridge (e.g. see also Fig. 14 of \citet{Colberg05}). In order to discriminate 
+each void in one of the families, we propose the compensation index, which 
+is defined as the mass of a void enclosed at a spherical volume of radius $R$ 
+and normalized by the mass of the same volume as assuming the mean background
+density instead
+
+\eq{compensation}
+{\mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}
+
+We choose an integration radius of $R=4r_{eff}$, which is large enough to 
+enclose the compensation ridge for a typical void in case there is one. 
+This leads us to voids with $\mathcal{C}>1$ have more mass than expected, 
+constituting the family of overcompensated voids. These voids generally 
+exhibit a compensation ridge. In the same fashion, voids with 
+$\mathcal{C}<1$ constitute the family of subcompensated voids.
+
+%-------------------------------------------------------------------------
 \subsection{The void size distribution}
@@
 
+%.........................................................................
+%FIGURE 3: volume functions
+\begin{flushleft}
+\begin{figure}
+\centering
+
+  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{./figures/voids_regions_volume_all.pdf}
+
+  \captionof{figure}{\small Volume size distribution of voids for both
+  catalogs. FA-Tweb (red curves), FA-Vweb (blue curves).
+  Continuous lines corresponds with the total number of voids, dot-dashed
+  with sub-compensated voids and dashed lines with over-compensated voids. }
+
+  \label{fig:volume_function}
+  \vspace{0.1 cm}
+
+\end{figure}
+\end{flushleft}
+%.........................................................................
+
 %-------------------------------------------------------------------------
-\subsection{Density profile of voids}
+\subsection{Physical profiles of voids}
 \label{subsec:density_voids}
 %-------------------------------------------------------------------------
-
-\[ \mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr \]
-
-\[ \mathcal{C} < 1 \]
-
-\[ \mathcal{C} > 1 \]
 
@@
 %.........................................................................
-%FIGURE 3: FA of some regions and shape illustration
+%FIGURE -: FA of some regions and shape illustration
 %\begin{flushleft}
@@
 %.........................................................................
-%FIGURE 4: volume functions
-\begin{flushleft}
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/voids_regions_volume_all.pdf}
-
-  \captionof{figure}{\small Volume functions of voids for both built 
-  catalogs. Watershed-Tweb (red curves), Watershed-Vweb (blue curves).
-  Continuous lines corresponds with the total number of voids, dot-dashed
-  with sub-compensated voids and dashed lines with over-compensated voids. }
-
-  \label{fig:volume_function}
-  \vspace{0.1 cm}
-
-\end{figure*}
-\end{flushleft}
-%.........................................................................
-
-%.........................................................................
-%FIGURE 5: Density profile of voids for each defined scheme
+%FIGURE 4: Density profile of voids for each defined scheme
 \begin{flushleft}

### 2015-01-13 cosmic_voids.tex
Section 5.2, The void size distribution, done

@@
 This simulation follows the non-linear evolution of a dark
-matter density field on a cubic volume of  size $250$\hMpc sampled
+matter density field on a cubic volume of  size $250$\hMpc\ sampled
 with $2048^3$ particles. 
@@
 fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
-cells, corresponding to a spatial resolution of $0.98$\hMpc per cell
+cells, corresponding to a spatial resolution of $0.98$\hMpc\ per cell
 side.  
@@
 
+%-------------------------------------------------------------------------
 %FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{flushleft}
 \begin{figure*}
@@
 \end{figure*}
-\end{flushleft}
 %.........................................................................
@@
 \label{subsec:enclosedmass}
-%-------------------------------------------------------------------------thereby allowing a good classification criterion
+%-------------------------------------------------------------------------
 
@@
 Fig. \ref{fig:RhoVel}), they seem to be distributed in two different 
-families, differentiated by the presence or absence or a compensation 
-ridge (e.g. see also Fig. 14 of \citet{Colberg05}). In order to discriminate 
-each void in one of the families, we propose the compensation index, which 
-is defined as the mass of a void enclosed at a spherical volume of radius $R$ 
-and normalized by the mass of the same volume as assuming the mean background
-density instead
+families, differentiated by the presence or absence of a compensation 
+ridge (e.g. see also Fig. 14 of \citet{Colberg05}). In order to 
+discriminate each void in one of the families, we propose the compensation 
+index $\mathcal{C}$, which is defined as the mass of a void enclosed in a 
+spherical volume of radius $R$ and normalized by the mass of the same 
+volume as assuming the mean background density instead
 
@@
 
-We choose an integration radius of $R=4r_{eff}$, which is large enough to 
+We choose an integration radius of $R=4r_{eff}$, that is large enough to 
 enclose the compensation ridge for a typical void in case there is one. 
-This leads us to voids with $\mathcal{C}>1$ have more mass than expected, 
+This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
 constituting the family of overcompensated voids. These voids generally 
-exhibit a compensation ridge. In the same fashion, voids with 
-$\mathcal{C}<1$ constitute the family of subcompensated voids.
+exhibit a compensation ridge associated to dense nearby structures. In the 
+same fashion, voids with $\mathcal{C}<1$ constitute the family of 
+subcompensated voids.
 
@@
 %FIGURE 3: volume functions
-\begin{flushleft}
 \begin{figure}
@@
   \label{fig:volume_function}
-  \vspace{0.1 cm}
 
 \end{figure}
-\end{flushleft}
 %.........................................................................
+
+Since the shape of the voids exhibit a wide range of geometries, a common 
+way to represent their size is through the equivalent spherical radius or
+effective radius, defined as $r_{eff} = [3/(4\pi)V]^{1/3}$, with $V$ the 
+total volume of the void. As mentioned before, we applied a threshold merger
+in order to avoid void hierarchization, what means we are working with the
+top hierarchy of voids. We limit our findings to voids with effective radius
+greater than the smoothing length of the density field, i.e. $\sim 1$\hMpc. 
+Below that scale numerical resolution effects becomes important. We find a
+volume filling fraction of voids of $54.88\%$ of the total volume of the 
+simulation for the FA-Tweb and $47.06\%$ for the FA-Vweb.
+
+In Fig. \ref{fig:volume_function} we show the void size distributions
+for both schemes and for the overall distribution of voids as well as for 
+overcompensated and subcompensated void subsamples. The central region of
+the distributions ($3$\hMpc\ -- $6$\hMpc), exhibit an approximately flat 
+shape, contrary to expected from highly non-linear structures like dark 
+matter halos, where the abundances increase for smaller structures. 
+The distribution of the FA-Tweb is consistent with a two-barrier problem 
+\citep{Sheth04}: formation of large voids is inhibited by the 
+\textit{void-in-void} problem (first barrier), where large voids are 
+constituted hierarchically of smaller ones. In turn, formation of small 
+voids is damped by the \textit{void-in-cloud} problem (second barrier), 
+where nearby collapsing structures limit the abundance of embedded small 
+voids.
+
+The FA-Vweb scheme does not tackle properly the \textit{void-in-cloud} 
+problem as it predicts large abundances of smaller voids. However, an 
+interesting result is the difference between the overcompensated and 
+subcompensated subsamples. Subcompensated voids, which are expected to 
+be embedded in low-density regions like walls and larger voids, exhibit
+smaller abundances compatible with the result of the FA-Tweb. Then, the 
+most dramatic contribution to the overabundance of small voids for the 
+FA-Vweb comes from overcompensated voids. This implies that, although
+nearby non-linear structures squeeze out embedded smaller voids, the
+rapid and isotropic collapse in these zones, along with the more rugged 
+nature of the velocity field make these voids still detectable by this 
+scheme.
+
+For both schemes overcompensated voids are more abundant, however at 
+larger scales abundances of subcompensated voids become comparable. This 
+is somehow expected as larger voids are more likely to abut other voids.
+A recent estimation of the radius of the local void gives $r_{LV}\approx
+10$ Mpc \citep{Nasonova11}. Taking the dimensionless Hubble constant as 
+$h = 0.70$, the size of the local void would be around $r_{eff} = 7$
+\hMpc\ in the shown distribution. For both schemes, this places the local
+void as a rather common void in terms of size, and more likely to be
+overcompensated.
 
@@
 
-%*************************************************************************
-\section{Conclusions}
-\label{sec:conclusions}
-%*************************************************************************
-
-%*************************************************************************
-\section*{Acknowledgments}  
-%*************************************************************************
-
-\bibliographystyle{latex/mn2e}
-\bibliography{references}
-
-%.........................................................................
-
-%.........................................................................
-%FIGURE -: FA of some regions and shape illustration
-%\begin{flushleft}
-%\begin{figure*}
-%\centering
-%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
-%  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
-%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
-%  width=0.3\textheight]{./figures/FA_Prolatenes.png}
-
-%  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
-%  random sample of cells (left panel) and for different spherical 
-%  geometries (right panel). For the cells, each environment is coded with
-%  a different colour, i.e. voids corresponds with dark blue points, 
-%  sheets with green, filaments with orange and knots with cyan. The axis 
-%  of the spheroids are computed from the relative strengths of the 
-%  eigenvalues, so their shape sketch the relative expanding/collapsing 
-%  dynamics into each direction.}
-
-%  \label{fig:FAShapeness}
-%  \vspace{0.1 cm}
-
-%\end{figure*}
-%\end{flushleft}
-%.........................................................................
-
 %.........................................................................
 %FIGURE 4: Density profile of voids for each defined scheme
-\begin{flushleft}
 \begin{figure*}
@@
 \end{figure*}
-\end{flushleft}
 %.........................................................................
 
+%*************************************************************************
+\section{Conclusions}
+\label{sec:conclusions}
+%*************************************************************************
+
+%*************************************************************************
+\section*{Acknowledgments}  
+%*************************************************************************
+
+\bibliographystyle{latex/mn2e}
+\bibliography{references}
+
+%.........................................................................
+%FIGURE -: FA of some regions and shape illustration
+%\begin{flushleft}
+%\begin{figure*}
+%\centering
+%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
+%  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
+%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
+%  width=0.3\textheight]{./figures/FA_Prolatenes.png}
+
+%  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
+%  random sample of cells (left panel) and for different spherical 
+%  geometries (right panel). For the cells, each environment is coded with
+%  a different colour, i.e. voids corresponds with dark blue points, 
+%  sheets with green, filaments with orange and knots with cyan. The axis 
+%  of the spheroids are computed from the relative strengths of the 
+%  eigenvalues, so their shape sketch the relative expanding/collapsing 
+%  dynamics into each direction.}
+
+%  \label{fig:FAShapeness}
+%  \vspace{0.1 cm}
+
+%\end{figure*}
+%\end{flushleft}
+%.........................................................................
 \end{document}

### 2015-01-15 cosmic_voids.tex
Introduction to Properties of voids

@@
 However,  due to the large volume extension of void regions ($\sim
-5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogs of
+5-10\ \mbox{Mpc}  h^{-1}$), statistically meaningful catalogues of
 voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
@@
 $FA = 0.65$. In right panels of Fig. \ref{fig:FA_field} we show the resulting
-catalogs of voids for both schemes.
+catalogues of voids for both schemes.
 
@@
   \captionof{figure}{\small Volume size distribution of voids for both
-  catalogs. FA-Tweb (red curves), FA-Vweb (blue curves).
+  catalogues. FA-Tweb (red curves), FA-Vweb (blue curves).
   Continuous lines corresponds with the total number of voids, dot-dashed
@@
 \subsection{Physical profiles of voids}
-\label{subsec:density_voids}
+\label{subsec:properties_voids}
 %-------------------------------------------------------------------------
@@
 
-  \captionof{figure}{\small Density of voids for each finding scheme.}
+  \captionof{figure}{\small Physical internal properties of voids for 
+  the two finding scheme. Density field (left panels), radial-projected
+  velocity field (middle panels) and FA field (right panels). The analysis
+  is performed for both, subcompensated (first two rows) and overcompensated
+  voids (last two rows).}
 
@@
 \end{figure*}
+%.........................................................................
+
+In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
+voids. We calculate the contrast density, radial-projected velocity and 
+FA profiles. For this purpose we catalogue all the voids into several 
+radial bins in order to capture possible size effects. Then, for each void, 
+we take the distance of each member cell to the void centre along with the 
+properties of interest. Normalizing these distances with the effective 
+radius, we stack all the voids catalogued in a radial bin in order to 
+compute radial profiles of the properties of interest.
+
+%.........................................................................
+\subsubsection{Density profiles}
+\label{subsubsec:density_voids}
+%.........................................................................
+
+In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
+voids. We calculate the contrast density, radial-projected velocity and 
+FA profiles. For this purpose we catalogue all the voids into several 
+radial bins in order to capture possible size effects. Then, for each void, 
+we take the distance of each member cell to the void centre along with the 
+properties of interest. Normalizing these distances with the effective 
+radius, we stack all the voids catalogued in a radial bin in order to 
+compute radial profiles of the properties of interest.
+
+%.........................................................................
+\subsubsection{Velocity profiles}
+\label{subsubsec:velocity_voids}
+%.........................................................................
+
+%.........................................................................
+\subsubsection{FA profiles}
+\label{subsubsec:FA_voids}
 %.........................................................................

### 2015-01-17 cosmic_voids.tex
5.3.1 Density profiles of voids, done

@@
 
-We choose an integration radius of $R=4r_{eff}$, that is large enough to 
+We choose an integration radius of $R=4\reff$, that is large enough to 
 enclose the compensation ridge for a typical void in case there is one. 
@@
 way to represent their size is through the equivalent spherical radius or
-effective radius, defined as $r_{eff} = [3/(4\pi)V]^{1/3}$, with $V$ the 
+effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
 total volume of the void. As mentioned before, we applied a threshold merger
@@
 10$ Mpc \citep{Nasonova11}. Taking the dimensionless Hubble constant as 
-$h = 0.70$, the size of the local void would be around $r_{eff} = 7$
+$h = 0.70$, the size of the local void would be around $\reff = 7$
 \hMpc\ in the shown distribution. For both schemes, this places the local
@@
 voids. We calculate the contrast density, radial-projected velocity and 
-FA profiles. For this purpose we catalogue all the voids into several 
-radial bins in order to capture possible size effects. Then, for each void, 
+FA profiles. For this purpose we catalogue all the voids in several radial 
+bins in order to capture possible size effects; moreover we show profiles 
+for both, subcompensated and overcompensated voids. Then, for each void, 
 we take the distance of each member cell to the void centre along with the 
 properties of interest. Normalizing these distances with the effective 
-radius, we stack all the voids catalogued in a radial bin in order to 
-compute radial profiles of the properties of interest.
+radius, we stack all the voids of a radial bin in order to compute the 
+radial profiles.
 
@@
 
-In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
-voids. We calculate the contrast density, radial-projected velocity and 
-FA profiles. For this purpose we catalogue all the voids into several 
-radial bins in order to capture possible size effects. Then, for each void, 
-we take the distance of each member cell to the void centre along with the 
-properties of interest. Normalizing these distances with the effective 
-radius, we stack all the voids catalogued in a radial bin in order to 
-compute radial profiles of the properties of interest.
+In left panels of Fig. \ref{fig:RhoVel} we compute density profiles of 
+voids stacked according to their size and their compensation index. 
+Instead of calculating the radial internal structure inside an effective
+radius, we opted for a radius well beyond that value ($8\ \reff$) in order 
+to capture the properties of neighbour structures as well.
+
+A first interesting result is the value at the void centres: the larger the 
+void, the more underdense their value at the centre, ranging from $\delta
+\approx-0.95$ for the largest voids ($8.3-12\ \hMpc$) to $\delta\approx 
+-0.8$ for the smallest voids ($2-3.2\ \hMpc$). This holds for all the voids 
+in both schemes. These very low values are consistent with most of the void 
+finding schemes based on smooth and continuous fields from simulation or 
+reconstruction procedures on surveys \citep{Plionis02, Colberg05, Shandarin06, 
+Platen07, Neyrinck08, MunozCuartas11, Neyrinck13, Ricciardelli2013}, unlike
+geometrical approaches based on point distributions, where central values
+are generally higher \citep{Colberg08}.
+
+Another important result is the steepness of the profiles at inner
+regions. For subcompensated voids, larger voids are more steep, reaching
+the mean density value at lower radius. Smaller voids exhibit moderate
+slopes, reaching the mean density at much larger radius. This indicates 
+smaller subcompensated voids are embedded into low density structures like 
+larger voids and still forming regions like walls. For subcompensated large
+voids, outer radial layers are so vast that all sort of structures are 
+stacked, thus reaching the mean density at lower radius. This result 
+remains also for overcompensated voids, where larger voids reach first 
+both, the compensation ridge and then the mean density value.
+
+Regarding overcompensated voids, a final result is related to the height 
+of the compensation ridge: the larger the void size, the lower the ridge
+height. This implies that overcompensated smaller voids are embedded in 
+very high density regions, unlike their subcompensated counterpart, thus 
+indicating two possibly different processes for small voids formation. 
+Larger voids exhibit lower ridges as outer radial layers also includes all
+sort of structures, thus being the difference between large overcompensated
+and subcompensated voids less conclusive.
+
+All the previous results hold for both finding schemes, thereby pointing 
+out to an universal radial profile of voids (subcompensated and 
+overcompensated), and not only for the internal structure \citep{Colberg05, 
+Ricciardelli2013}, but also for outer regions \citep{Lavaux12, Hamaus14}.
 

### 2015-01-20 cosmic_voids.tex
Initial analysis of velocity profiles

@@
 
+Additionally, in middle panels of Fig. \ref{fig:RhoVel} we calculate 
+radial projected velocity profiles, where positive values implies outflow 
+of matter, while negative ones indicates infall flows, all from the void 
+centre.
+
+A general feature of subcompensated voids is outward velocity profiles, 
+indicating that matter all along these voids and their outsides is being 
+pulled out. On the other hand, overcompensated voids exhibit initially
+outward profiles, as expected from a low density region. However, 
+approximately at the radius of the compensation ridge, the velocity becomes 
+negative, thus indicating an infall flow of matter further than the 
+compensation ridge. This shows that the high density structures associated 
+to a compensation ridge indeed dominate the matter flow from inside the void 
+as well as falling flows from outsides.
+
 %.........................................................................

### 2015-01-23 cosmic_voids.tex
Velocity profiles analysis, done

@@
 
+All the profiles behave linearly near to the void centres, where larger 
+voids display more steep slopes. This indicates larger voids are being
+pulled out more strongly by nearby structures. On the other hand, at 
+large radius, all the profiles decrease to the zero background velocity,
+where larger voids reach this value first as their outer radial layers 
+average a large portion of volume.
+
+Like the density, these results also point out to an universal radial 
+velocity profiles of voids \citep{Hamaus14}.
+
 %.........................................................................

### 2015-01-28 cosmic_voids.tex
FA profiles analysis. Section 5, results, done

@@
 voids stacked according to their size and their compensation index. 
-Instead of calculating the radial internal structure inside an effective
+Instead of calculating the radial internal structure inside the effective
 radius, we opted for a radius well beyond that value ($8\ \reff$) in order 
@@
 
+Finally, we also calculate FA profiles in right panels of Fig. \ref{fig:RhoVel}.
+A very interesting result from this is a very clear distinction between
+the internal profile, below the effective radius, and the external profile. 
+For subcompensated voids, they reach quickly the background 
+value after $1\reff$. On the other hand, overcompensated voids reach a FA 
+ridge at the same radius and then the background value. Central values are
+in agreement with those of the density and velocity fields, where larger 
+voids exhibit more isotropic cores, associated to higher outflows rates 
+and low mass concentrations.
+
+The difference between the radius where the density ridge is reached 
+($r\sim 2-4\hMpc$ depending on the void size), and the radius of the FA 
+ridge ($r\sim 1-1.5\hMpc$ for all voids) reinforces our previous 
+conclusions: before reaching high-density structures like filaments and 
+cluster, high-anisotropic, middle-density walls are reached, so the FA 
+ridge should be chosen as the natural frontier of voids instead of the
+density ridge. This choosing would produce smaller voids as compared with
+other voids finding methods, however contamination from external structures
+is also avoided.
+
 %*************************************************************************

### 2015-02-11 cosmic_voids.tex
intro revisada

@@
   Sebastian Bustamante \thanks{sebastian.bustamante@udea.edu.co}$^{1}$,
-  Jaime E. Forero-Romero$^{2}$ 
+  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
 }
@@
 local minima of the FA and its boundaries as the regions where the FA
-is maximized
+is maximized.
 This void identification technique does not have any free parameters
@@
 We test the method on the Bolshoi simulation and report on the density
-and velo ity profiles for the voids found using this new scheme. 
+and velocity profiles for the voids found using this new scheme. 
+We find that...
 \end{abstract}
@@
 
-Since voids were found in the first compiled galaxy surveys 
-they have been identified as one of the most striking features of the
-Cosmic Web \citep{Chincarini75,  Gregory78, Einasto80M, Einasto80N,
-  Kirshner81, Zeldovich82,Kirshner87, Bond96}. 
+Voids have been identified as one of the most striking features of the
+Universe on its larges scales since they were found in the first
+galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
+  Kirshner81, Zeldovich82,Kirshner87}.  
 However, due to the large volume extension of void regions ($\sim
@@
 voids \citep{Pan10,  Sutter12b, Nadathur14} have only become available
-through  modern galaxy surveys like the two-degree field Galaxy
-Redshift Survey \citep{ Colless01, Colless03} and the Sloan Digital
-Sky Survey \citep{York00, Abazajian03}.
-This advancement generated a great interest to study voids
-observationally during the last decade \citep{Hoyle04, Croton04, Rojas05,
+through modern galaxy surveys such as the two-degree field Galaxy
+Redshift Survey (2dF) \citep{ Colless01, Colless03} and the Sloan
+Digital Sky Survey (SDSS)\citep{York00, Abazajian03}.
+These observational breakthughs generated a great interest in the last
+decade to study voids \citep{Hoyle04, Croton04, Rojas05,
   Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
@@
 
-On the theoretical side the rough theoretical framework that explains
+On the theoretical side the basic framework that explains
 the origin of voids was established in the seminal work of
@@
 \citep{Martel90, Regos91, Weygaert93, Dubinski93, Bond96}. 
-Currently, the dominant tendency to study voids relies on using data
-from N-body simulations. For an extensive compilation of previous 
+Currently, the most popular approach to study voids relies on N-body
+simulations. For an extensive compilation of previous  
 numerical works we refer the reader to \citet{Colberg08}.
@@
 three aspects \citep{Platen07}. 
-First, voids are a key ingredient of the Cosmic Web. 
-They dominate the volume distribution at large-scales and
-additionally, they compensate overdense structures in the total budget
-of  matter.  
-Second, voids provide a valuable resource for inferring and probing 
-cosmological parameters as their structure and dynamics are highly 
-determined by these values. 
-Third, they are a  largely a largely pristine environment to test
-galaxy evolution.
+Firstly, voids are a key ingredient of the Cosmic Web. 
+They dominate the volume distribution at large scales and
+additionally, compensating overdense structures in the total matter
+budget. 
+Secondly, voids provide a valuable resource to estimate  
+cosmological parameters as their structure and dynamics are sensitive
+to them. 
+Finally, they are a largely pristine environment to test galaxy
+evolution.
 
-Although a visual recognition of voids in galaxy surveys and simulations
-is possible in most cases, a formal systematic identification is desirable
-for statistical studies. 
-However, the community does not have an unambiguous definition of cosmic
-voids. 
-There are nany different void finding techniques in the literature
-(for a detailed comparison of different schemes,  see the Void Finder
+Although visual recognition of voids in galaxy surveys and simulations
+is possible in most cases, we need a clear algorithmic identification
+procedure to make statistical studies.
+Nevertheless, the community has not reached yet an unambiguous
+definition of cosmic voids, with many different void finding
+techniques in the literature  (for a detailed comparison of different
+schemes,  see the publication on the results of the Void Finder
 Comparison Project \citet{Colberg08}).  
 In spite of the diversity of existing schemes, they can be roughly
-classified into two main types. First, geometric schemes based on
-point spatial or redshift  distribution of galaxies in surveys or dark
-matter halos in  simulations \citep{Kauffmann91, Muller00,
-  Gottlober03, Hoyle04, Brunino07,  Foster09, Micheletti14, Sutter14};
-second, schemes based on the smooth and continuous matter density
+classified into two types. First, geometric schemes based on
+point distributions (either real or redshift space) of galaxies in
+surveys or dark matter halos in  simulations \citep{Kauffmann91, Muller00, 
+  Gottlober03, Hoyle04, Brunino07,  Foster09, Micheletti14, Sutter14}.
+Second, schemes based on the smooth and continuous matter density
 field either from simulations or from reconstruction procedures on
@@
   Neyrinck08, MunozCuartas11, Neyrinck13, Ricciardelli2013}. 
+Our work is based on the second kind of schemes.
 
-Here we introduce a new tracer of the structure of cosmic voids that
-can be used once the continous matter density or velocity distribution
-is known. 
+Here we introduce a new algorithm to define voids over the continous
+matter density or velocity distribution defined on a fixed and
+homogeneous spatial grid.
 The algorithm is based on two tensorial schemes used to classify the
@@
 \citep{Hoffman12}. 
-These web schemes classify the Cosmic Web into four different types of
-environment depending on the counting of the number of eigenvalues below an 
-user-defined threshold ($\lambda_{rm th}$): voids, sheets, filaments and
-knots for $3,2,1$ or $0$ eigenvalues below $\lambda_{\rm th}$, respectively.
-
-This procedure allows a new description of the internal structure
+Our procedure allows a description of the internal structure
 of voids that goes beyond a simple definition of a void as just an
@@
 cerebral tissue in nuclear magnetic resonance
-imaging.
-\citet{Libeskind13} introduced this concept in the context of Cosmic
-Web classification schemes.
+imaging and \citet{Libeskind13} introduced this concept in the context
+of Cosmic Web classification schemes.
 
 Once we establish the FA as a void tracer, we proceed to
-identify individual voids as basins of local minima. 
-For this we implement a \textit{watershed transform algorithm}
-\citep{Beucher79,Beucher93} which has been used to define as catching
-basins of local minima of the density field
-\citep{Platen07,Neyrinck08}; we use insted minima of the FA field to
-find define the voids.
+identify individual voids as basins of FA local minima. 
+At this point we implement a \textit{watershed transform algorithm}
+\citep{Beucher79,Beucher93} which has been used to define voids as
+catching basins of local minima of the density field
+\citep{Platen07,Neyrinck08}.
 
@@
 In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
-we use to find the cosmic web in N-body simulations. In Section 
-\ref{sec:simulations} we describe the used simulation.
-Then in Section \ref{sec:bulk_voids} we explain in detail our void
-finder based on the fractional anisotropy of the tidal and shear
-tensor fields.
-%In Section \ref{sec:experiments} we describe the numerical experiments
-%we perform to show the performance of the new void finding technique.
+we use to find the cosmic web in N-body simulations. 
+In Section  \ref{sec:simulations} we describe the N-body simulation we
+use to test our algorithm. 
+In Section \ref{sec:bulk_voids} we explain in detail our void finder
+based on the fractional anisotropy of the tidal and shear tensor
+fields. 
 Our results are presented in \ref{sec:results} to finally comment and

### 2015-02-11 cosmic_voids.tex
done section 2, new figure filenames, moved simulation section

@@
-\documentclass[a4,useAMS,usenatbib,usegraphicx]{latex/mn2e} 
+\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
 %\documentclass{latex/emulateapj} 
 %External Packages and personalized macros
-\include{latex/macros}
+%=========================================================================
+%		EXTERNAL PACKAGES
+%=========================================================================
+\usepackage{amsmath} 
+\usepackage{amssymb} 
+%\usepackage[section]{placeins}
+\usepackage {graphicx}
+%\usepackage{graphics}
+\usepackage[dvips]{epsfig}
+\usepackage{epsfig}  
+\usepackage{color}
+\usepackage[normalem]{ulem}
+\usepackage{hyperref}
+\usepackage{caption}
+%Non reposionated tables
+\usepackage{float}
+\restylefloat{table}
+
+%=========================================================================
+%		INTERNAL MACROS
+%=========================================================================
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+\def\ba{\begin{eqnarray}}
+\def\ea{\end{eqnarray}}
+
+% To highlight comments 
+\definecolor{red}{rgb}{1,0.0,0.0}
+\newcommand{\red}{\color{red}}
+\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
+\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
+\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
+
+\newcommand{\LCDM}{$\Lambda$CDM~}
+\newcommand{\beq}{\begin{eqnarray}}  
+\newcommand{\eeq}{\end{eqnarray}}  
+\newcommand{\zz}{$z\sim 3$} 
+\newcommand{\apj}{ApJ}  
+\newcommand{\apjs}{ApJS}  
+\newcommand{\apjl}{ApJL}  
+\newcommand{\aj}{AJ}  
+\newcommand{\mnras}{MNRAS}  
+\newcommand{\mnrassub}{MNRAS accepted}  
+\newcommand{\aap}{A\&A}  
+\newcommand{\aaps}{A\&AS}  
+\newcommand{\araa}{ARA\&A}  
+\newcommand{\nat}{Nature}  
+\newcommand{\physrep}{PhR}
+\newcommand{\pasp}{PASP}    
+\newcommand{\pasj}{PASJ}    
+\newcommand{\avg}[1]{\langle{#1}\rangle}  
+\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
+\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
+\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc}\fi}}  
+\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc}\fi}}  
+\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc}\fi}}  
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\lya}{{Lyman$\alpha$~}}
+\newcommand{\clara}{{\texttt{CLARA}}~}
+\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
+%SAMPLES
+\newcommand{\GHBDM}{\texttt{GH}$_{\mbox{\tiny{BDM}}}$ }
+\newcommand{\GHFOF}{\texttt{GH}$_{\mbox{\tiny{FOF}}}$ }
+\newcommand{\IHBDM}{\texttt{IH}$_{\mbox{\tiny{BDM}}}$ }
+\newcommand{\IHFOF}{\texttt{IH}$_{\mbox{\tiny{FOF}}}$ }
+\newcommand{\PBDM}{\texttt{P}$_{\mbox{\tiny{BDM}}}$ }
+\newcommand{\PFOF}{\texttt{P}$_{\mbox{\tiny{FOF}}}$ }
+\newcommand{\IPBDM}{\texttt{IP}$_{\mbox{\tiny{BDM}}}$ }
+\newcommand{\IPFOF}{\texttt{IP}$_{\mbox{\tiny{FOF}}}$ }
+\newcommand{\RIPBDM}{\texttt{RIP}$_{\mbox{\tiny{BDM}}}$ }
+\newcommand{\RIPFOF}{\texttt{RIP}$_{\mbox{\tiny{FOF}}}$ }
+
+%MY COMMANDS #############################################################
+\newcommand{\sub}[1]{\mbox{\scriptsize{#1}}}
+\newcommand{\dtot}[2]{ \frac{ d #1 }{d #2} }
+\newcommand{\dpar}[2]{ \frac{ \partial #1 }{\partial #2} }
+\newcommand{\pr}[1]{ \left( #1 \right) }
+\newcommand{\corc}[1]{ \left[ #1 \right] }
+\newcommand{\lla}[1]{ \left\{ #1 \right\} }
+\newcommand{\bds}[1]{\boldsymbol{ #1 }}
+\newcommand{\oiint}{\displaystyle\bigcirc\!\!\!\!\!\!\!\!\int\!\!\!\!\!\int}
+\newcommand{\mathsize}[2]{\mbox{\fontsize{#1}{#1}\selectfont $#2$}}
+\newcommand{\eq}[2]{\begin{equation} \label{eq:#1} #2 \end{equation}}
+\newcommand{\lth}{$\lambda_{th}$ }
+\newcommand{\reff}{{\ifmmode{r_{\mbox{\tiny eff}}}\else{$r_{\mbox{\tiny eff}}$}\fi}}
+%#########################################################################
 
@@
 we use to find the cosmic web in N-body simulations. 
-In Section  \ref{sec:simulations} we describe the N-body simulation we
-use to test our algorithm. 
 In Section \ref{sec:bulk_voids} we explain in detail our void finder
@@
 fields. 
+In Section  \ref{sec:simulations} we describe the N-body simulation we
+use to test our algorithm. 
 Our results are presented in \ref{sec:results} to finally comment and
@@
 %*************************************************************************
-\section{Algorithms to label the Cosmic Web}
+\section{Algorithms to find the Cosmic Web}
 \label{sec:algorithms_cosmic_web}
@@
 
+In next two subsections we describe the major features of the two
+algorithms (T-web and V-web) we use to find and classify the cosmic web in cosmological
+N-body simulations. 
+These schemes have also been used to develop other kind of studies
+such as the alignment of the shape, spin and peculiar velocity of dark
+matter halos with the cosmic web \citep{Libeskind13,Forero2014}.
+We refer the reader to the paper of \cite{Forero09} and
+\cite{Hoffman12} to read a detailed description of each algorithm.
+
 %-------------------------------------------------------------------------
-\subsection{The tidal web (Tweb)}
+\subsection{The tidal web (T-Web)}
 \label{subsec:Tweb}
@@
 The tidal tensor allows a classification in terms of the orbital
-dinamics of the matter field
+dinamics of the matter field.
 This approach extends to second-order the equations of motion around 
@@
 ${\bf u}_{3}$. 
-This set of eigenvalues are indicators of the local  orbital stability
-in each direction ${\bf u}_i$, which is to label the Cosmic Web.
+The eigenvalues are indicators of the local  orbital stability
+in each direction ${\bf u}_i$. 
+The sign of the eigenvalues can be used to classify the Cosmic Web.
 The number of positive (stable) or negative (unstable) eigenvalues allows 
 to label a location into one of the next four types of environment: 
-voids (3 negatives eigenvalues), sheets (2), filaments (1) and knots (0). 
+voids (3 negative eigenvalues), sheets (2), filaments (1) and knots (0).
+
 A modification to this scheme was introduced by \citet{Forero09}
-by means of a relaxation of the stability criterion. The relative strength 
-of each eigenvalue is no longer defined by the sign, but instead by a
-threshold value $\lambda_{\rm th}$ that can be tuned in such a way
-that the visual impression of the web-like matter distribution is
-reproduced.
+by means of a relaxation of the stability criterion. 
+The relative strength  of each eigenvalue is no longer defined by the
+sign, but instead by a threshold value $\lambda_{\rm th}$ that can be
+tuned in such a way that the visual impression of the web-like matter
+distribution is reproduced.
 
 %-------------------------------------------------------------------------
-\subsection{The velocity web (Vweb)}
+\subsection{The velocity web (V-Web)}
 \label{subsec:Vweb}
@@
 We also use a kinematic scheme to define the Cosmic Web environment in 
-the simulation, which has been thoroughly described in 
-\cite{Hoffman12}.
-This scheme has been used to study the shape, spin and peculiar
-velocity alignments of dark matter halos with the cosmic web
-\citep{Libeskind13,Forero2014}. 
-We refer the reader to these papers to find a detailed description of
-the algorithm, its limitations  and capabilities.    
-The Vweb scheme for environment finding is based on the
+the simulation introduced by \cite{Hoffman12}.
+The V-web scheme for environment finding is based on the
 local velocity shear tensor calculated from the smoothed dark matter 
@@
 eigenvalues and its corresponding eigenvectors.
-%$\lambda_{1}\geq\lambda_{2}\geq\lambda_3$.
-%whose sum (the 
-%trace of $\Sigma_{\alpha\beta}$) is proportional to the divergence of the 
-%local velocity field smoothed on the physical scale ${\mathcal R}$.
 
@@
 respect to a threshold value $\lambda_{th}$ to classify the cosmic web
-in the four web types we have already described.
+in the four web types already mentioned.
 
@@
 and walls. 
-
-\section{Numerical Simulations}
-\label{sec:simulations}
-
-We use the Bolshoi simulation to test the method describe in the
-paper. 
-This simulation follows the non-linear evolution of a dark
-matter density field on a cubic volume of  size $250$\hMpc\ sampled
-with $2048^3$ particles. 
-The cosmological parameters in the simulation are $\Omega_{\rm m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$,
-$n=0.95$ and $\sigma_{8}=0.82$ for the matter density,   cosmological
-constant, dimensionless Hubble parameter, spectral index of
-primordial density perturbations and normalization for the power
-spectrum, respectively. 
-This values are consistent with the seventh year of data of the Wilkinson 
-Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. 
-For more detailed  technical information about the simulation, see
-\citet{Klypin11}.
-
-We find the cosmic web we estimate first the density and velocity
-fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
-cells, corresponding to a spatial resolution of $0.98$\hMpc\ per cell
-side.  
-These fields are smoothed with a gaussian filter with a width of
-$\sigma=0.98$\hMpc.
-We compute the tidal and shear tensors through finite-differences and
-Finally, the eigenvalues and eigenvectors of the tensor are
-obtained for each grid cell.
-The data we use here is publicly available through the MultiDark
-database \url{http://www.multidark.org/MultiDark/} which is described
-in \citet{Riebe11}.
+This is described in detailed in the next Section.
 
@@
 magnetic resonance imaging. 
-Here we propose the FA, much in the same way as \citet{Libeskind13},
-as a tracer of cosmic voids.
+Here we present the FA, much in the same way as \citet{Libeskind13},
+to use it as a tracer of cosmic voids.
 
@@
 %.........................................................................
-where the eigenvalues are taken from either the Tweb or the Vweb 
-(FA-Tweb and FA-Vweb respectively). Such as it is defined, FA$=0$ 
+where the eigenvalues can be taken from either the T-web or the Vweb 
+(FA-T-web and FA-Vweb respectively). Such as it is defined, FA$=0$ 
 corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
@@
   \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Tweb.pdf}
+  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
   \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{./figures/cosmicweb_FA_Vweb.pdf}
+  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
   \caption{Left colum. Visual impression of the 
@@
   \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/FA_L1.pdf}
+  width=0.3\textheight]{FA_L1.pdf}
   \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/delta_L1.pdf}
+  width=0.3\textheight]{delta_L1.pdf}
 
@@
   density field (right panel) with respect to the eigenvalue $\lambda_1$ 
-  for each web scheme (Tweb, red lines. Vweb, blue lines) as calculated 
+  for each web scheme (T-web, red lines. Vweb, blue lines) as calculated 
   over all cells of the grid. Thick central lines correspond with the median 
@@
 correspond to critical values of $\lambda_{1}^T = 0.265$ and
-$\lambda_{1}^V = 0.175$ for the Tweb and Vweb, respectively.
+$\lambda_{1}^V = 0.175$ for the T-web and Vweb, respectively.
 This means that setting $\lambda_{th}$ to either
@@
 
+\section{Numerical Simulation}
+\label{sec:simulations}
+
+We use the Bolshoi simulation to test the method describe in the
+paper. 
+This simulation follows the non-linear evolution of a dark
+matter density field on a cubic volume of  size $250$\hMpc\ sampled
+with $2048^3$ particles. 
+The cosmological parameters in the simulation are $\Omega_{\rm m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$,
+$n=0.95$ and $\sigma_{8}=0.82$ for the matter density,   cosmological
+constant, dimensionless Hubble parameter, spectral index of
+primordial density perturbations and normalization for the power
+spectrum, respectively. 
+This values are consistent with the seventh year of data of the Wilkinson 
+Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. 
+For more detailed  technical information about the simulation, see
+\citet{Klypin11}.
+
+We find the cosmic web we estimate first the density and velocity
+fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
+cells, corresponding to a spatial resolution of $0.98$\hMpc\ per cell
+side.  
+These fields are smoothed with a gaussian filter with a width of
+$\sigma=0.98$\hMpc.
+We compute the tidal and shear tensors through finite-differences and
+Finally, the eigenvalues and eigenvectors of the tensor are
+obtained for each grid cell.
+The data we use here is publicly available through the MultiDark
+database \url{http://www.multidark.org/MultiDark/} which is described
+in \citet{Riebe11}.
+
 %*************************************************************************
@@
   \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{./figures/voids_regions_volume_all.pdf}
+  width=0.3\textheight]{voids_regions_volume_all.pdf}
 
   \captionof{figure}{\small Volume size distribution of voids for both
-  catalogues. FA-Tweb (red curves), FA-Vweb (blue curves).
+  catalogues. FA-T-web (red curves), FA-Vweb (blue curves).
   Continuous lines corresponds with the total number of voids, dot-dashed
@@
 volume filling fraction of voids of $54.88\%$ of the total volume of the 
-simulation for the FA-Tweb and $47.06\%$ for the FA-Vweb.
+simulation for the FA-T-web and $47.06\%$ for the FA-Vweb.
 
@@
 matter halos, where the abundances increase for smaller structures. 
-The distribution of the FA-Tweb is consistent with a two-barrier problem 
+The distribution of the FA-T-Web is consistent with a two-barrier problem 
 \citep{Sheth04}: formation of large voids is inhibited by the 
@@
 be embedded in low-density regions like walls and larger voids, exhibit
-smaller abundances compatible with the result of the FA-Tweb. Then, the 
+smaller abundances compatible with the result of the FA-T-Web. Then, the 
 most dramatic contribution to the overabundance of small voids for the 
@@
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_density_TwebFAG0.pdf}
+  width=0.24\textheight]{voids_density_TwebFAG0.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_velocity_TwebFAG0.pdf}
+  width=0.24\textheight]{voids_velocity_TwebFAG0.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_FA_TwebFAG0.pdf}
+  width=0.24\textheight]{voids_FA_TwebFAG0.pdf}
 
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_density_VwebFAG0.pdf}
+  width=0.24\textheight]{voids_density_VwebFAG0.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_velocity_VwebFAG0.pdf}
+  width=0.24\textheight]{voids_velocity_VwebFAG0.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_FA_VwebFAG0.pdf}
+  width=0.24\textheight]{voids_FA_VwebFAG0.pdf}
 
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_density_TwebFAG1.pdf}
+  width=0.24\textheight]{voids_density_TwebFAG1.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_velocity_TwebFAG1.pdf}
+  width=0.24\textheight]{voids_velocity_TwebFAG1.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_FA_TwebFAG1.pdf}
+  width=0.24\textheight]{voids_FA_TwebFAG1.pdf}
 
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_density_VwebFAG1.pdf}
+  width=0.24\textheight]{voids_density_VwebFAG1.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_velocity_VwebFAG1.pdf}
+  width=0.24\textheight]{voids_velocity_VwebFAG1.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{./figures/voids_FA_VwebFAG1.pdf}
+  width=0.24\textheight]{voids_FA_VwebFAG1.pdf}
 
@@
 
-\bibliographystyle{latex/mn2e}
+\bibliographystyle{mn2e}
 \bibliography{references}
 
-%.........................................................................
-%FIGURE -: FA of some regions and shape illustration
-%\begin{flushleft}
-%\begin{figure*}
-%\centering
-%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
-%  width=0.3\textheight]{./figures/FA_Prolatenes_Vweb.pdf}
-%  \includegraphics[trim = 0mm 1mm 0mm 1mm, clip, keepaspectratio=true,
-%  width=0.3\textheight]{./figures/FA_Prolatenes.png}
-
-%  \captionof{figure}{\small Fractional anisotropy and prolateness for a 
-%  random sample of cells (left panel) and for different spherical 
-%  geometries (right panel). For the cells, each environment is coded with
-%  a different colour, i.e. voids corresponds with dark blue points, 
-%  sheets with green, filaments with orange and knots with cyan. The axis 
-%  of the spheroids are computed from the relative strengths of the 
-%  eigenvalues, so their shape sketch the relative expanding/collapsing 
-%  dynamics into each direction.}
-
-%  \label{fig:FAShapeness}
-%  \vspace{0.1 cm}
-
-%\end{figure*}
-%\end{flushleft}
-%.........................................................................
 \end{document}

### 2015-02-11 cosmic_voids.tex
revised section 3

@@
 studies.  
-In this paper we present a novel approach to find voids in
+In this paper we present a new algorithm to find voids in
 cosmological simulations.  
@@
 
+%.........................................................................
+%FIGURE 1: FA and vissual impression
+\begin{figure*}
+  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
+  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
+  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
+  \caption{Left colum. Visual impression of the 
+  Fractional Anisotropy field over a slide of the simulation for each
+  web scheme (T-Web is up. V-Web is down).  
+  Middle column. Cosmic Web identification. Voids
+  are white, sheets are light gray, filaments are dark gray and
+  knots are black.
+  Right column. Colors are voids identified by our Fractional
+  Anisotropy method.}
+  \label{fig:FA_field}
+\end{figure*}
+%.........................................................................
+
 In next two subsections we describe the major features of the two
@@
 
-In left panels of Fig. \ref{fig:FA_field} we show the FA field for both 
-web schemes over a slide of the simulation. 
-From this Figure we can observe that both, voids and knots, display a highly 
-isotropic expanding dynamic at their centres, becoming gradually more
-anisotropic at outer regions. 
-On the other hand the filamentary structure is traced by high FA
-values. These characteristics are the key to use the FA as a tracer of
-cosmic voids.
-
-%.........................................................................
-%FIGURE 1: FA and vissual impression
-\begin{figure*}
-  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{cosmicweb_FA_Tweb.pdf}
-  \includegraphics[trim = 16mm 8mm 5mm 12mm, clip, keepaspectratio=true,
-  width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
-  \caption{Left colum. Visual impression of the 
-  FA field over a slide of the simulation for each web scheme (T-web, upper 
-  panels. V-web, middle panels). 
-  Middle column. Components of the Cosmic Web using $\lambda_{th}$
-  values that put an upper bound of $FA=0.95$ to voids. Voids
-  corresponds with white, sheets to gray, filaments to dark gray and
-  knots with black regions. 
-  Right column. Sketches the distribution of the catalogued voids by
-  our method.}
-  \label{fig:FA_field}
-\end{figure*}
-%.........................................................................
+In the left and middle panels of Figure \ref{fig:FA_field} we show the
+FA field and web classification for both  web schemes over a slice of
+an N-body simulation (described in Section \ref{sec:simulations}). 
+Comparing these two panels we see that voids and knots (white
+and black in the middle panel of Figure 1) display low FA values at
+their  centres, becoming gradually more anisotropic at outer regions.  
+On the other hand the filamentary structure (grey in the middle panel
+of Figure 1) is traced by high FA values.  
+These characteristics are key to use the FA as a tracer of cosmic voids.
 
@@
   \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.3\textheight]{delta_L1.pdf}  
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
   width=0.3\textheight]{FA_L1.pdf}
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{delta_L1.pdf}
 
@@
 This implies that a void is completely fixed by the relative strength
-of the $\lambda_1$ eigenvalue with respect to the $\lambda_{th}$.   
+of the $\lambda_1$ eigenvalue with respect to the threshold.   
 As we increase/decrease the threshold value $\lambda_{th}$, voids
@@
 increasing/decreasing $\lambda_1$.  
-
 Voids are thus characterized by low values of both FA and
 $\lambda_1$.
+
 In Fig. \ref{fig:L1_correlations} we show that the these two values
@@
 
-Once established the FA as a good tracer of voids, the next step is to
-find individuals voids in the overall distribution. For this purpose, we
-use the \textit{watershed transform algorithm} \citep{Beucher79,Beucher93}, 
-in which a void is identified as the catching basin of a local minimum of
-the FA. The use of this algorithm is advantageous as it is parameter-free 
-and does not require any assumption on the shape and morphology of voids.
+The previous section shows that FA is a good void tracer, but it does
+not automatically suggest how to define the boundary of individual
+voids.
+For this purpose, we
+use the \textit{watershed transform algorithm}
+\citep{Beucher79,Beucher93} to identify a void as the basin of FA
+local minimum. 
+The advantage of this definition is that we can
+now forget about the free parameter $\lambda_{th}$. 
+Additionally, this algorithm does not require any assumption on the
+shape and/or morphology of the tentative voids.
 
-Previous implementations of this technique as those of \citet{Platen07,
-Neyrinck08} have shown remarkable results regarding voids finding, however
-they use the density field instead of the FA field. On the other hand, we 
-use a \textit{cloud-in-cell} (\texttt{CIC}) algorithm on a Cartesian mesh for 
-estimating the density and tensor fields, instead of the more sophisticated 
-\textit{Delaunay tessellation for field estimator} (\texttt{DTFE}) technique 
-\citep{Schaap00}, but our implementation of the watershed transform should 
-not be significantly affected as we are interested in low density regions 
-where the \texttt{CIC} gives similar estimations.
+The watershed technique has been already implemented to find voids \citet{Platen07,
+Neyrinck08} however it used the density field instead of the FA
+field as we suggest in this paper. 
+Another difference with respect to other void finding implementations
+is that we estimate all relevant quantities on a Cartesian mesh of fixed cell
+size, while it other works use an adaptive Delaunay tessellation
+\citep{Schaap00}. 
+However from the analysis of our results this different does not seem
+to introduce supurious results, at least with the mass resolution we
+have in the N-body simulation.
 
-As suggested by \citet{Platen07} and references therein, it is necessary to
-apply a threshold merger in order to reduce spurious features and to avoid 
-void hierarchization. A natural choice is a threshold of $\delta = -0.8$, 
-which means that any ridge between two voids with density below that value
-would be removed and the respective voids merged. As we are working with the
-FA, the equivalent threshold according to Fig. \ref{fig:L1_correlations} is
-$FA = 0.65$. In right panels of Fig. \ref{fig:FA_field} we show the resulting
-catalogues of voids for both schemes.
+This watershed algorithm still needs a threshold value to reduce
+spurious features and to avoid void hierarchization.  
+If the density field is used, a typical threshold is
+$\delta = -0.8$ \citep{Platen07},  which means that any ridge between
+two voids with overdensity below that value is removed to merge the
+respective voids. 
+In our case we have to find a corresponding FA value
+to define this threshold.
 
-%Once set the optimal thresholds for the web schemes, we proceed in Fig. 
-%\ref{fig:FAShapeness} to sample the FA and the prolateness for a random 
-%sample of cells previously classified into one of the four
-%environments.
+In Figure \ref{fig:L1_correlations} we find the correlations of
+the eigenvalue $\lambda_1$ with he matter overdensity (left panel) and
+the FA (right panel).
+We can use this information to find the FA threshold. 
+From the left panel we see that an underdensity of $\delta=-0.8$ is
+correspond to values of $\lambda_1=0.0$, regardless of the web-finding
+scheme.
+From the second panel we have a very tight correlation of $\lambda_1$
+with the FA, indicating that in turn $\lambda_1=0.0$ corresponds to a
+FA=$0.65$ which is the value that we have used to remove ridges.
 
-%The prolateness is introduced here for differentiating sheets and filaments
-%featuring high FA values. 
-%In order to illustrate the underlying local 
-%dynamics sampled by the cells, we also sketch different spheroidal 
-%geometries according to the relative strength of each eigenvalue, and 
-%then, we associate them to different ranges of the FA and the prolateness.
-
-%From this, we conclude sheets display very anisotropic distributions, 
-%namely above $FA=0.95$. They are also biased towards oblate geometries, 
-%however there are some elongated sheets as well. Filaments are not as 
-%anisotropic as sheets, ranging from middle up to high FA values. They 
-%exhibit prolate geometries, but a considerable fraction of them are biased 
-%towards slightly more oblate values. Voids and knots are the only 
-%environments featuring with low FA values, thus indicating very isotropic 
-%expanding/collapsing dynamics at their centres. However, voids span over 
-%a very wide range of FA and geometries, whereas knots only span over low 
-%to middle FA values and display a biased oblate geometry.
+The right column in Figure \ref{fig:FA_field} shows all the voids that
+have been identified using the watershed algorithm on the FA field.
 

### 2015-02-12 cosmic_voids.tex
seccion 3 revisada

@@
   Fractional Anisotropy field over a slide of the simulation for each
-  web scheme (T-Web is up. V-Web is down).  
+  web scheme (T-Web top. V-Web bottom).  
   Middle column. Cosmic Web identification. Voids
@@
 are indeed closely correlated.  
-The left panel shows the correlation between $\lambda_1$ and $FA$ for
+The right panel shows the correlation between $\lambda_1$ and $\delta$ for
 all the grid cells in the simulation while the right panel shows the
-correlation between $\lambda_1$ and the local overdensity $\delta$.  
-This shows that the overdensity has a large scatter at fixed
-$\lambda_1$.
+correlation between $\lambda_1$ and the FA. This shows that the
+overdensity has a large scatter at fixed $\lambda_1$.
 
@@
 $\lambda_{1}^T$/$\lambda_{1}^{V}$ automatically produces voids with
-all the cells $FA<0.95$.   
-The middle column in Fig. \ref{fig:FA_field} shows the web
+all the cells FA$<0.95$.   
+The middle panels in Figure \ref{fig:FA_field} show the web
 classification for this choice of $\lambda_{th}$, demonstrating that
-it is a sensible choice to define voids.
+this FA level is a sensitive choice to define voids.
 
@@
 voids.
-For this purpose, we
-use the \textit{watershed transform algorithm}
+For this purpose, we use the \textit{watershed transform algorithm}
 \citep{Beucher79,Beucher93} to identify a void as the basin of FA
 local minimum. 
-The advantage of this definition is that we can
-now forget about the free parameter $\lambda_{th}$. 
-Additionally, this algorithm does not require any assumption on the
-shape and/or morphology of the tentative voids.
+The advantage of this definition is that it does not require any
+assumption on the shape and/or morphology of the tentative voids.
 
-The watershed technique has been already implemented to find voids \citet{Platen07,
-Neyrinck08} however it used the density field instead of the FA
-field as we suggest in this paper. 
-Another difference with respect to other void finding implementations
-is that we estimate all relevant quantities on a Cartesian mesh of fixed cell
-size, while it other works use an adaptive Delaunay tessellation
+However, there are two main differences in our approach with respect to other
+watershed implementations.
+First, the watershed technique commonly uses the the density field
+instead of the FA field as we do in this paper
+\citep{Platen07,Neyrinck08}.   
+Second, we estimate all relevant quantities on a Cartesian mesh of
+fixed cell size, while other works use an adaptive Delaunay tessellation
 \citep{Schaap00}.
-However from the analysis of our results this different does not seem
-to introduce supurious results, at least with the mass resolution we
-have in the N-body simulation.
+However, from the analysis of our results it does not 
+introduce supurious results, at least with the mass resolution we have
+in the N-body simulation.
 
-This watershed algorithm still needs a threshold value to reduce
-spurious features and to avoid void hierarchization.  
+The watershed algorithm also needs a threshold value to reduce
+spurious features and prevent void hierarchization.  
 If the density field is used, a typical threshold is
@@
 
-The right column in Figure \ref{fig:FA_field} shows all the voids that
-have been identified using the watershed algorithm on the FA field.
+The right column in Figure \ref{fig:FA_field} shows all the individual
+voids that have been identified using the watershed algorithm on the
+FA field. 
+In what follows we describe the numerical simulation we have used to
+find voids and their detailed properties characterization.
 

### 2015-02-12 cosmic_voids.tex
reordenando las seccion de resultados

@@
 
-We use the Bolshoi simulation to test the method describe in the
-paper. 
+We use the Bolshoi simulation to test our void finding method. 
 This simulation follows the non-linear evolution of a dark
@@
 with $2048^3$ particles. 
-The cosmological parameters in the simulation are $\Omega_{\rm m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$,
-$n=0.95$ and $\sigma_{8}=0.82$ for the matter density,   cosmological
+The cosmological parameters in the simulation are $\Omega_{\rm
+  m}=0.27$,  $\Omega_{\Lambda}  =0.73$, $h=0.70$, $n=0.95$ and
+$\sigma_{8}=0.82$ for the matter density,   cosmological 
 constant, dimensionless Hubble parameter, spectral index of
@@
 spectrum, respectively. 
-This values are consistent with the seventh year of data of the Wilkinson 
-Microwave Anisotropy Probe (WMAP) \citep{Jarosik11}. 
+These values are consistent with the ninth year of data of the
+Wilkinson  Microwave Anisotropy Probe (WMAP) \citep{Hinshaw2013}. 
 For more detailed  technical information about the simulation, see
@@
 
-We find the cosmic web we estimate first the density and velocity
-fields using a  \textit{cloud-in-cell} (\texttt{CIC}) algorithm onto a grid of $256^3$ 
-cells, corresponding to a spatial resolution of $0.98$\hMpc\ per cell
-side.  
+We use data for the cosmic web identification that is publicly
+available through the MultiDark database
+\url{http://www.multidark.org/MultiDark/} which is described in
+\citet{Riebe11}. 
+Here we briefly describe the process to obtain the data. 
+For details see \cite{Forero09} (T-Web) and
+\cite{Hoffman12,Forero2014} (V-Web). 
+This data is based on a  \textit{cloud-in-cell} (\texttt{CIC})
+interpolation of the density and velocity fields of the simulation
+onto a grid of $256^3$  cells, corresponding to a spatial resolution
+of $0.98$\hMpc\ per cell side.    
 These fields are smoothed with a gaussian filter with a width of 
 $\sigma=0.98$\hMpc. 
-We compute the tidal and shear tensors through finite-differences and
-Finally, the eigenvalues and eigenvectors of the tensor are
-obtained for each grid cell.
-The data we use here is publicly available through the MultiDark
-database \url{http://www.multidark.org/MultiDark/} which is described
-in \citet{Riebe11}.
+The tidal and shear tensors and corresponding eigenvalues are computed
+through finite-differences over the potential and velocity fields.
 
@@
 
-%-------------------------------------------------------------------------
-\subsection{Enclosed mass}
-\label{subsec:enclosedmass}
-%-------------------------------------------------------------------------
+We limit our results to voids with effective radius larger than the
+smoothing length of the density field, i.e. $\sim 1$\hMpc.  
+Below that scale numerical resolution effects become important. 
+With that choice we find a volume filling fraction $54.88\%$ and
+$47.06\%$ for the FA-Vweb.
 
-When we analyse individual density profiles of voids (see left panels of
-Fig. \ref{fig:RhoVel}), they seem to be distributed in two different 
-families, differentiated by the presence or absence of a compensation 
-ridge (e.g. see also Fig. 14 of \citet{Colberg05}). In order to 
-discriminate each void in one of the families, we propose the compensation 
-index $\mathcal{C}$, which is defined as the mass of a void enclosed in a 
-spherical volume of radius $R$ and normalized by the mass of the same 
-volume as assuming the mean background density instead
-
-\eq{compensation}
-{\mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}
-
-We choose an integration radius of $R=4\reff$, that is large enough to 
-enclose the compensation ridge for a typical void in case there is one. 
-This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
-constituting the family of overcompensated voids. These voids generally 
-exhibit a compensation ridge associated to dense nearby structures. In the 
-same fashion, voids with $\mathcal{C}<1$ constitute the family of 
-subcompensated voids.
+In the following subsections we describe the results for the size
+distribution and different radial profiles for all our samples.
 
@@
 
-Since the shape of the voids exhibit a wide range of geometries, a common 
-way to represent their size is through the equivalent spherical radius or
+Void shapes exhibit a wide range of geometries.
+To define their size we use its equivalent spherical radius or
 effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
-total volume of the void. As mentioned before, we applied a threshold merger
-in order to avoid void hierarchization, what means we are working with the
-top hierarchy of voids. We limit our findings to voids with effective radius
-greater than the smoothing length of the density field, i.e. $\sim 1$\hMpc. 
-Below that scale numerical resolution effects becomes important. We find a
-volume filling fraction of voids of $54.88\%$ of the total volume of the 
-simulation for the FA-T-web and $47.06\%$ for the FA-Vweb.
+total volume of the void. 
+In Figure \ref{fig:volume_function} we show the void size
+distributions for the T-Web and the V-Web.
 
-In Fig. \ref{fig:volume_function} we show the void size distributions
-for both schemes and for the overall distribution of voids as well as for 
-overcompensated and subcompensated void subsamples. The central region of
-the distributions ($3$\hMpc\ -- $6$\hMpc), exhibit an approximately flat 
-shape, contrary to expected from highly non-linear structures like dark 
-matter halos, where the abundances increase for smaller structures. 
-The distribution of the FA-T-Web is consistent with a two-barrier problem 
-\citep{Sheth04}: formation of large voids is inhibited by the 
-\textit{void-in-void} problem (first barrier), where large voids are 
-constituted hierarchically of smaller ones. In turn, formation of small 
-voids is damped by the \textit{void-in-cloud} problem (second barrier), 
-where nearby collapsing structures limit the abundance of embedded small 
-voids.
+We see that the void distribution for the T-Web is broadly consistent with the
+expectations from a two-barrier problem  \citep{Sheth04}. 
+The formation of large voids is limited by the \textit{void-in-void}
+problem (first barrier), where large voids are constituted
+hierarchically of smaller ones. 
+In turn, the formation of small  voids is damped by the
+\textit{void-in-cloud} problem (second barrier),  where nearby
+collapsing structures limit the abundance of embedded small  voids.
 
-The FA-Vweb scheme does not tackle properly the \textit{void-in-cloud} 
-problem as it predicts large abundances of smaller voids. However, an 
-interesting result is the difference between the overcompensated and 
-subcompensated subsamples. Subcompensated voids, which are expected to 
-be embedded in low-density regions like walls and larger voids, exhibit
-smaller abundances compatible with the result of the FA-T-Web. Then, the 
-most dramatic contribution to the overabundance of small voids for the 
-FA-Vweb comes from overcompensated voids. This implies that, although
-nearby non-linear structures squeeze out embedded smaller voids, the
-rapid and isotropic collapse in these zones, along with the more rugged 
-nature of the velocity field make these voids still detectable by this 
-scheme.
+We also find that the V-Web scheme produces an over-abundance of small
+voids compared to the resuls of the T-Web.
+A large number of these small voids are embedded in dense regions. 
+They are visible in the middle panel of Figure \ref{fig:FA_field} as
+the small bubbles located inside sheets.
+The existence of these small voids could be qualitatively explained by
+dynamics of shell crossing in collapsing sheets. 
+When matter colides into a sheet, at their center it is possible to
+find crossing matter planes that effectively give a possitively
+divergen velocity field, which gives a void identification by the
+T-Web algorithm. This points has been discussed in \citet{Hoffman12}.
 
-For both schemes overcompensated voids are more abundant, however at 
-larger scales abundances of subcompensated voids become comparable. This 
-is somehow expected as larger voids are more likely to abut other voids.
-A recent estimation of the radius of the local void gives $r_{LV}\approx
-10$ Mpc \citep{Nasonova11}. Taking the dimensionless Hubble constant as 
-$h = 0.70$, the size of the local void would be around $\reff = 7$
-\hMpc\ in the shown distribution. For both schemes, this places the local
-void as a rather common void in terms of size, and more likely to be
-overcompensated.
+Comparing the abundance of large voids in the two web schemes, we find
+that the V-Web is limited to have voids on the scale of $\sim 10$\hMpc,
+while the T-Web scheme includes voids as large as $\sim 15$\hMpc. 
+Large voids in the T-Web scheme have a velocity structure that
+induces a split by the watersched algorithm in the V-Web. 
+This is eviden in the right panel of Figure \ref{fig:FA_field}.
+
+%-------------------------------------------------------------------------
+\subsection{Compenseated and overcompensated voids}
+\label{subsec:enclosedmass}
+%-------------------------------------------------------------------------
+
+We find that voids are distributed in two different  families differentiated by the
+presence/absence of an overdense matter ridge in their density
+profiles. 
+To discriminate each void in one of the families we use the
+compensation  index $\mathcal{C}$.
+It is defined as the mass of a void enclosed in a spherical volume of
+radius $R$ and normalized by the mass of the same volume assuming
+it is filled by matter with the mean background density.
+
+\eq{compensation}
+{\mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}
+
+We choose an integration radius of $R=4\reff$, that is large enough to 
+enclose the compensation ridge for a typical void in case there is one. 
+This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
+constituting the family of overcompensated voids. These voids generally 
+exhibit a compensation ridge associated to dense nearby structures. In the 
+same fashion, voids with $\mathcal{C}<1$ constitute the family of 
+subcompensated voids.
 

### 2015-02-13 cosmic_voids.tex
redistribuyendo graficas, revisando la parte de density profile

@@
   \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{delta_L1.pdf}  
+  width=0.35\textheight]{delta_L1.pdf}  
   \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{FA_L1.pdf}
+  width=0.35\textheight]{FA_L1.pdf}
 
@@
   \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
-  width=0.3\textheight]{voids_regions_volume_all.pdf}
+  width=0.35\textheight]{voids_regions_volume_all.pdf}
 
@@
 effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
-total volume of the void. 
+total volume of the void computed from the individual grid cells
+assigned to the void.   
 In Figure \ref{fig:volume_function} we show the void size
@@
 \textit{void-in-cloud} problem (second barrier),  where nearby
-collapsing structures limit the abundance of embedded small  voids.
+collapsing structures limit the abundance of small embedded voids.
 
@@
 voids compared to the resuls of the T-Web.
-A large number of these small voids are embedded in dense regions. 
+A large number of these small voids are embedded in overdense regions. 
 They are visible in the middle panel of Figure \ref{fig:FA_field} as
-the small bubbles located inside sheets.
-The existence of these small voids could be qualitatively explained by
+small bubbles located inside sheets.
+The existence of these small voids can be explained by
 dynamics of shell crossing in collapsing sheets. 
-When matter colides into a sheet, at their center it is possible to
-find crossing matter planes that effectively give a possitively
-divergen velocity field, which gives a void identification by the
-T-Web algorithm. This points has been discussed in \citet{Hoffman12}.
+As matter colides into a sheet, in their symmetry plane one will
+find crossing ahseets that effectively give a positive divergence in
+the velocity field, resulting in a void identification by the
+V-Web algorithm. This points has been discussed in \citet{Hoffman12}.
 
@@
 Large voids in the T-Web scheme have a velocity structure that
-induces a split by the watersched algorithm in the V-Web. 
-This is eviden in the right panel of Figure \ref{fig:FA_field}.
+induces a split by the watershed algorithm in the V-Web. 
+This is evident in the right panel of Figure \ref{fig:FA_field}.
+
+%.........................................................................
+%FIGURE 4: Density profile of voids for each defined scheme
+\begin{figure*}
+\centering
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_density_TwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_density_TwebFAG1.pdf}
+
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_density_VwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_density_VwebFAG1.pdf}
+
+  \captionof{figure}{\small Physical internal properties of voids for 
+  the two finding scheme. Density field (left panels), radial-projected
+  velocity field (middle panels) and FA field (right panels). The analysis
+  is performed for both, subcompensated (first two rows) and overcompensated
+  voids (last two rows).}
+  \label{fig:RhoVel}
+  \vspace{0.1 cm}
+\end{figure*}
+
+\begin{figure*}
+\centering  
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_velocity_TwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_velocity_TwebFAG1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_velocity_VwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_velocity_VwebFAG1.pdf}
+  \captionof{figure}{\small Physical internal properties of voids for 
+  the two finding scheme. Density field (left panels), radial-projected
+  velocity field (middle panels) and FA field (right panels). The analysis
+  is performed for both, subcompensated (first two rows) and overcompensated
+  voids (last two rows).}
+
+  \label{fig:RhoVel}
+  \vspace{0.1 cm}
+
+\end{figure*}
+
+\begin{figure*}
+\centering  
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_FA_TwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_FA_VwebFAG0.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_FA_TwebFAG1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_FA_VwebFAG1.pdf}
+
+  \captionof{figure}{\small Physical internal properties of voids for 
+  the two finding scheme. Density field (left panels), radial-projected
+  velocity field (middle panels) and FA field (right panels). The analysis
+  is performed for both, subcompensated (first two rows) and overcompensated
+  voids (last two rows).}
+
+  \label{fig:RhoVel}
+  \vspace{0.1 cm}
+
+\end{figure*}
+%.........................................................................
 
 %-------------------------------------------------------------------------
-\subsection{Compenseated and overcompensated voids}
+\subsection{Subcompensated and overcompensated voids}
 \label{subsec:enclosedmass}
@@
 
-We find that voids are distributed in two different  families differentiated by the
+We find that voids are distributed in two different  families
+differentiated by the 
 presence/absence of an overdense matter ridge in their density
@@
 This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
-constituting the family of overcompensated voids. These voids generally 
-exhibit a compensation ridge associated to dense nearby structures. In the 
-same fashion, voids with $\mathcal{C}<1$ constitute the family of 
-subcompensated voids.
+constituting the family of overcompensated voids. 
+These voids generally  exhibit a compensation ridge associated to
+dense nearby structures. 
+In the same fashion, voids with $\mathcal{C}<1$ constitute the family
+of  subcompensated voids.
 
-%-------------------------------------------------------------------------
-\subsection{Physical profiles of voids}
-\label{subsec:properties_voids}
-%-------------------------------------------------------------------------
+In Figure \ref{fig:RhoVel} we show the density and velocity profiles
+of voids splitted in these two families. 
+In the left column it becomes clear the difference between sub- and
+overcompensated voids.
 
 %.........................................................................
-%FIGURE 4: Density profile of voids for each defined scheme
-\begin{figure*}
-\centering
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_density_TwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_velocity_TwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_FA_TwebFAG0.pdf}
-
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_density_VwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_velocity_VwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_FA_VwebFAG0.pdf}
-
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_density_TwebFAG1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_velocity_TwebFAG1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_FA_TwebFAG1.pdf}
-
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_density_VwebFAG1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_velocity_VwebFAG1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.24\textheight]{voids_FA_VwebFAG1.pdf}
-
-  \captionof{figure}{\small Physical internal properties of voids for 
-  the two finding scheme. Density field (left panels), radial-projected
-  velocity field (middle panels) and FA field (right panels). The analysis
-  is performed for both, subcompensated (first two rows) and overcompensated
-  voids (last two rows).}
-
-  \label{fig:RhoVel}
-  \vspace{0.1 cm}
-
-\end{figure*}
+\subsection{Density profiles}
+\label{subsec:density_voids}
 %.........................................................................
 
-In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
-voids. We calculate the contrast density, radial-projected velocity and 
+We calculate the contrast density, radial-projected velocity and 
 FA profiles. For this purpose we catalogue all the voids in several radial 
@@
 
-%.........................................................................
-\subsubsection{Density profiles}
-\label{subsubsec:density_voids}
-%.........................................................................
+The left column in Figure \ref{fig:RhoVel} shows the results of
+stacked density profiles for different void sizes. 
+We normalize the radial coordinate with the effective radius to check
+for possible universal features among voids. 
+We calculate the profile out to a radius $8\ \reff$  to capture the
+the point where the overdensity reaches the mean value.
 
-In left panels of Fig. \ref{fig:RhoVel} we compute density profiles of 
-voids stacked according to their size and their compensation index. 
-Instead of calculating the radial internal structure inside the effective
-radius, we opted for a radius well beyond that value ($8\ \reff$) in order 
-to capture the properties of neighbour structures as well.
+A first interesting result is the overdensity value at the void's
+center.
+We find that larger voids have a lower overdensity value.
+The largest voids ($8.3-12\ \hMpc$) have an underdensity
+$\approx-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\approx 
+-0.8$ at their centers.
+This holds for both web schemes.
 
-A first interesting result is the value at the void centres: the larger the 
-void, the more underdense their value at the centre, ranging from $\delta
-\approx-0.95$ for the largest voids ($8.3-12\ \hMpc$) to $\delta\approx 
--0.8$ for the smallest voids ($2-3.2\ \hMpc$). This holds for all the voids 
-in both schemes. These very low values are consistent with most of the void 
-finding schemes based on smooth and continuous fields from simulation or 
-reconstruction procedures on surveys \citep{Plionis02, Colberg05, Shandarin06, 
-Platen07, Neyrinck08, MunozCuartas11, Neyrinck13, Ricciardelli2013}, unlike
-geometrical approaches based on point distributions, where central values
-are generally higher \citep{Colberg08}.
+These values are consistent with most of the void finding schemes
+based on smooth and continuous fields from simulation or
+reconstruction procedures on surveys \citep{Plionis02, Colberg05,
+  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Neyrinck13,
+  Ricciardelli2013}, unlike geometrical approaches based on point
+distributions, where central density values are generally higher
+\citep{Colberg08}.
 

### 2015-02-13 cosmic_voids.tex
re-ordenando graficas

@@
 
-  \captionof{figure}{\small Physical internal properties of voids for 
-  the two finding scheme. Density field (left panels), radial-projected
-  velocity field (middle panels) and FA field (right panels). The analysis
-  is performed for both, subcompensated (first two rows) and overcompensated
-  voids (last two rows).}
-  \label{fig:RhoVel}
+  \captionof{figure}{\small Spherically averaged radial density profile for
+    voids. The sample is split into subcompensated and overcompensated voids
+    (right and left) for the web schemes T-Web and V-Web (top and
+    bottom).}
+  \label{fig:density_profile}
   \vspace{0.1 cm}
@@
   width=0.32\textheight]{voids_velocity_VwebFAG1.pdf}
-  \captionof{figure}{\small Physical internal properties of voids for 
-  the two finding scheme. Density field (left panels), radial-projected
-  velocity field (middle panels) and FA field (right panels). The analysis
-  is performed for both, subcompensated (first two rows) and overcompensated
-  voids (last two rows).}
-
-  \label{fig:RhoVel}
+  \captionof{figure}{\small Spherically averaged radial velocity profile for
+    voids. The sample is split into subcompensated and overcompensated voids
+    (right and left) for the web schemes T-Web and V-Web (top and
+    bottom).}
+  \label{fig:velocity_profile}
   \vspace{0.1 cm}
-
 \end{figure*}
@@
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.32\textheight]{voids_FA_TwebFAG1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
   width=0.32\textheight]{voids_FA_VwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_FA_TwebFAG1.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
@@
 
-  \captionof{figure}{\small Physical internal properties of voids for 
-  the two finding scheme. Density field (left panels), radial-projected
-  velocity field (middle panels) and FA field (right panels). The analysis
-  is performed for both, subcompensated (first two rows) and overcompensated
-  voids (last two rows).}
-
-  \label{fig:RhoVel}
+  \captionof{figure}{\small Spherically averaged Fractional Anisotropy
+    profile for voids. The sample is split into subcompensated and
+    overcompensated voids  (right and left) for the web schemes T-Web and V-Web (top and  bottom).}
+  \label{fig:FA_profile}
   \vspace{0.1 cm}

### 2015-02-13 cosmic_voids.tex
revisado velocity profile

@@
 
-The left column in Figure \ref{fig:RhoVel} shows the results of
-stacked density profiles for different void sizes. 
+Figure \ref{fig:density_profile} shows the results of stacked density
+profiles for different void sizes.  
 We normalize the radial coordinate with the effective radius to check
@@
 
-Another important result is the steepness of the profiles at inner
-regions. For subcompensated voids, larger voids are more steep, reaching
-the mean density value at lower radius. Smaller voids exhibit moderate
-slopes, reaching the mean density at much larger radius. This indicates 
-smaller subcompensated voids are embedded into low density structures like 
-larger voids and still forming regions like walls. For subcompensated large
-voids, outer radial layers are so vast that all sort of structures are 
-stacked, thus reaching the mean density at lower radius. This result 
-remains also for overcompensated voids, where larger voids reach first 
-both, the compensation ridge and then the mean density value.
+A second feature about these profiles is their steepnes at inner
+regions.  
+In subcompensated voids, larger voids are steeper.
+Smaller voids exhibit moderate slopes, reaching the mean density at
+larger radii than larger voids.
+This suggests that smaller subcompensated voids are embedded into low
+density structures like voids or walls, while arge subcompensated
+voids are surrounded  by dense structures, reaching the mean density
+at lower effective radii than smaller voids.
+In overcompensated voids larger voids reach first  both the
+compensation ridge and then the mean density value.
 
@@
 
-All the previous results hold for both finding schemes, thereby pointing 
-out to an universal radial profile of voids (subcompensated and 
-overcompensated), and not only for the internal structure \citep{Colberg05, 
-Ricciardelli2013}, but also for outer regions \citep{Lavaux12, Hamaus14}.
+All the previous results hold for both finding schemes.
+This suggests an universal behaviour for the radial density profile in
+two families of subcompensated and overcompensanted voids. 
+This goes in the same direction of recent results about the internal
+\citep{Colberg05,  Ricciardelli2013} and external structure of voids
+\citep{Lavaux12, Hamaus14}. 
+Our results extend the findings of \cite{Hamaus14} into the range of
+voids with size $r_{\rm eff}<10$\hMpc.
 
@@
 
-Additionally, in middle panels of Fig. \ref{fig:RhoVel} we calculate 
-radial projected velocity profiles, where positive values implies outflow 
-of matter, while negative ones indicates infall flows, all from the void 
-centre.
+In Figure \ref{fig:velocity_profile} we present the radial velocity
+profiles. 
+Positive values correspond to outflows with respect to the center.
 
-A general feature of subcompensated voids is outward velocity profiles, 
-indicating that matter all along these voids and their outsides is being 
-pulled out. On the other hand, overcompensated voids exhibit initially
-outward profiles, as expected from a low density region. However, 
-approximately at the radius of the compensation ridge, the velocity becomes 
-negative, thus indicating an infall flow of matter further than the 
-compensation ridge. This shows that the high density structures associated 
-to a compensation ridge indeed dominate the matter flow from inside the void 
-as well as falling flows from outsides.
+We find that subcompensated voids have outflowing velocity profiles
+all the way up to the effective radius where the average radial
+density reaches the average value.
+For voids with sizes $r_{\rm eff}<8$\hMpc the outflow is always
+positive, consistent with the fact that their density profiles do not
+reach the level $\delta=0$ in the range of explored radii.
+This behaviour indicates that matter is being pulled out of the void
+into external higher density features.
 
-All the profiles behave linearly near to the void centres, where larger 
-voids display more steep slopes. This indicates larger voids are being
-pulled out more strongly by nearby structures. On the other hand, at 
-large radius, all the profiles decrease to the zero background velocity,
-where larger voids reach this value first as their outer radial layers 
-average a large portion of volume.
+On the other hand, overcompensated voids initially exhibit and outward
+profiles, (as expected from a low density region) and approximately at
+the radius of the compensation ridge, the velocity reaches a peak,
+decreases and becomes negative, showing the infalling flow of matter
+further than the compensation ridge. 
+This shows that the high density structures associated to the
+compensation ridge dominate the matter flow both from inside and
+outside the void.
 
-Like the density, these results also point out to an universal radial 
-velocity profiles of voids \citep{Hamaus14}.
+As in the density these results also consistent with a Universial
+velocity profile for voids \citep{Hamaus14}.
 

### 2015-02-13 cosmic_voids.tex
revisada seccion FA profile

@@
 
-In Figure \ref{fig:RhoVel} we show the density and velocity profiles
+In Figure \ref{fig:density_profile} we show the density and velocity profiles
 of voids splitted in these two families. 
@@
 
-Finally, we also calculate FA profiles in right panels of Fig. \ref{fig:RhoVel}.
-A very interesting result from this is a very clear distinction between
-the internal profile, below the effective radius, and the external profile. 
-For subcompensated voids, they reach quickly the background 
-value after $1\reff$. On the other hand, overcompensated voids reach a FA 
-ridge at the same radius and then the background value. Central values are
-in agreement with those of the density and velocity fields, where larger 
-voids exhibit more isotropic cores, associated to higher outflows rates 
-and low mass concentrations.
+Figure \ref{fig:FA_profile} shows the results for the FA profiles.
+We find that the FA clearly magnifies the difference between the
+internal profile $r_{\rm eff}<1$ and the external profile $r_{\rm
+  eff}>1$. 
+Subcompensanted voids in the T-Web reach an asymptotic background
+value of F=$0.8$ almost right at $r_{\rm eff}=2$. 
+For the V-Web the results are similar, albeit rather slowly with the
+effective radius.
+Overcompensated voids reach a maximum FA at the same effective radiuus
+$r_{\rm eff}=1$ and decline to reach an asymptotic value of FA=$0.85$
+at larger radii.
+
+The central FA values also show a magnified trend with the void size. 
+Larger voids have lower FA values, more clearly than the same trend
+observed with the central density value. 
+The voids in the V-Web scheme span a larger range of central FA values
+than in the T-Web scheme.
 
 The difference between the radius where the density ridge is reached 
-($r\sim 2-4\hMpc$ depending on the void size), and the radius of the FA 
-ridge ($r\sim 1-1.5\hMpc$ for all voids) reinforces our previous 
-conclusions: before reaching high-density structures like filaments and 
-cluster, high-anisotropic, middle-density walls are reached, so the FA 
-ridge should be chosen as the natural frontier of voids instead of the
-density ridge. This choosing would produce smaller voids as compared with
-other voids finding methods, however contamination from external structures
-is also avoided.
+($r_{\rm eff}=3$) and the radius of the FA  ridge ($r_{\rm eff}=1$ )
+justifies in a more quantiative way the qualitative argument
+we present in Section \ref{sec:watershed} to define void boundaries in
+our method.  Namely that as we increase the void boundary, we reach
+first middle density walls, before reashing high density structures
+associated with high anisotropy, making the FA  ridge a  natural voids
+boundary instead of the density ridge.
+
+We recognize that our choice produces smaller voids as compared with
+other voids finding methods, however this has the advantange of
+voiding the contamination from external structures.
 

### 2015-02-13 cosmic_voids.tex
fixed some typos

@@
 %.........................................................................
-\subsubsection{Velocity profiles}
-\label{subsubsec:velocity_voids}
+\subsection{Velocity profiles}
+\label{subsec:velocity_voids}
 %.........................................................................
@@
 density reaches the average value.
-For voids with sizes $r_{\rm eff}<8$\hMpc the outflow is always
+For voids with sizes $r_{\rm eff}<8\hMpc$ the outflow is always
 positive, consistent with the fact that their density profiles do not
@@
 %.........................................................................
-\subsubsection{FA profiles}
-\label{subsubsec:FA_voids}
+\subsection{Fractional Anisotropy profiles}
+\label{subsec:FA_voids}
 %.........................................................................

### 2015-02-13 cosmic_voids.tex
Optimisating format of figures for black printing. Standard size for all figures.

@@
 \centering
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_density_TwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_density_TwebFAG1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_density_TwebFAG0.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_density_TwebFAG1.pdf}
 
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_density_VwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_density_VwebFAG1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_density_VwebFAG0.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_density_VwebFAG1.pdf}
 
@@
 \centering  
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_velocity_TwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_velocity_TwebFAG1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_velocity_VwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_velocity_VwebFAG1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_velocity_TwebFAG0.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_velocity_TwebFAG1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_velocity_VwebFAG0.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_velocity_VwebFAG1.pdf}
   \captionof{figure}{\small Spherically averaged radial velocity profile for
@@
 \centering  
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_FA_TwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_FA_TwebFAG1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_FA_VwebFAG0.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
-  width=0.32\textheight]{voids_FA_VwebFAG1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_FA_TwebFAG0.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_FA_TwebFAG1.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_FA_VwebFAG0.pdf}
+  \includegraphics[trim = 2mm 2mm 5mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_FA_VwebFAG1.pdf}
 

### 2015-02-13 bench/codes_figures/FA_L1_correlation.py

@@ -21,6 +21,8 @@ smooth = '_s1'
 webs = ['Tweb', 'Vweb']
 #Colors and labels
 colors = [ 'red', 'blue' ]
+#Linestyles
+linestyles = ["-", "--"]
 
 #==================================================================================================
 #Typical halo mass for each environment
@@ -35,11 +37,12 @@ for web in webs:
 
     #Quartiles regions-------
     plt.fill_between( quartiles[:,0], quartiles[:,1], quartiles[:,3], color = colors[i_web], alpha = 0.2 )
-    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = '-' )
-    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = '-' )
+    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = linestyles[i_web] )
+    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = linestyles[i_web] )
 
     #Medians-----------------
-    plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i_web], linewidth = 3, label = web )
+    plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i_web], linewidth = 3, label = web, \
+    linestyle = linestyles[i_web] )
     
     plt.grid(1)
     plt.ylabel( 'FA', fontsize = 12 )

### 2015-02-13 bench/codes_figures/delta_L1_correlation.py

@@ -20,6 +20,8 @@ smooth = '_s1'
 webs = ['Tweb', 'Vweb']
 #Colors and labels
 colors = [ 'red', 'blue' ]
+#Linestyles
+linestyles = ["-", "--"]
 
 #==================================================================================================
 #Typical halo mass for each environment
@@ -36,12 +38,13 @@ for web in webs:
     quartiles[quartiles[:,1]==0,1] = -0.94
     quartiles[quartiles[:,3]==0,3] = -0.94
     plt.fill_between( quartiles[:,0], quartiles[:,1], quartiles[:,3], color = colors[i_web], alpha = 0.2 )
-    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = '-' )
-    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = '-' )
+    plt.plot( quartiles[:,0], quartiles[:,1], color = colors[i_web], linewidth = 1, linestyle = linestyles[i_web] )
+    plt.plot( quartiles[:,0], quartiles[:,3], color = colors[i_web], linewidth = 1, linestyle = linestyles[i_web] )
 
     #Medians-----------------
     quartiles[quartiles[:,2]==0,2] = -0.94
-    plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i_web], linewidth = 3, label = web )
+    plt.plot( quartiles[:,0], quartiles[:,2], color = colors[i_web], linewidth = 3, label = web, 
+    linestyle = linestyles[i_web] )
 
     plt.grid(1)
     plt.ylabel( '$\delta$', fontsize = 12 )

### 2015-02-13 bench/codes_figures/void_radial_FA_bins.py

@@ -37,12 +37,13 @@ N = 80
 #Number of times the effective radius of the void
 Rreff = 8
 #Effective radial bins 
-#RadBins = [ 2, 3, 4, 5, 6, 7, 8, 9, 10, 12 ]
 RadBins = [ 2.0, 3.2, 4.4, 5.6, 6.8, 8.3, 12 ]
 #Colors 
 #color = ["#000000","#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
 #color = ["#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
 color = ["#0000BE", "#067EF4", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
+#Linewidths
+linewidths = [ 2, 2.25, 2.5, 2.75, 3.0, 3.25 ]
 #Labels 
 labels = { "FAG":"FA-WT", "DLG":"Density-WT" }
 #Compensated
@@ -55,8 +56,9 @@ def r_eff(X):
 #==================================================================================================
 #			COMPUTING RADIAL PROFILES OF DENSITY FOR EVERY RADIAL BIN
 #==================================================================================================
-fig = plt.figure( figsize=(4.5,4) )
+fig = plt.figure( figsize=(5.8,5) )
 ax = fig.add_subplot(111)
+
 for ri in xrange( len(RadBins)-1 ):
     reff_range = [ RadBins[ri],RadBins[ri+1] ]
     #Loading index of voids
@@ -89,7 +91,7 @@ for ri in xrange( len(RadBins)-1 ):
 	    rho = rprofile[:,1]
 	    ur = rprofile[ np.isnan(rho)==False ,0]
 	    rho = rho[ np.isnan(rho)==False ]
-	    Reffi = r_eff(voids[i,1])
+	    #Reffi = r_eff(voids[i,1])
 	    #plt.plot( ur, rho, lw = 0.05 )
 	    try:
 		rho_interp = interp.interp1d( ur, rho )
@@ -110,7 +112,7 @@ for ri in xrange( len(RadBins)-1 ):
     Q1[Q1==0] = nan
     Q2[Q2==0] = nan
     #ax.fill_between( Rnorm, Q1, Q2, alpha = 0.3, color = color[ri] )
[…]

### 2015-02-13 bench/codes_figures/void_radial_density_bins.py

@@ -37,12 +37,13 @@ N = 80
 #Number of times the effective radius of the void
 Rreff = 8
 #Effective radial bins 
-#RadBins = [ 2, 3, 4, 5, 6, 7, 8, 9, 10, 12 ]
 RadBins = [ 2.0, 3.2, 4.4, 5.6, 6.8, 8.3, 12 ]
 #Colors 
 #color = ["#000000","#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
 #color = ["#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
 color = ["#0000BE", "#067EF4", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
+#Linewidths
+linewidths = [ 2, 2.25, 2.5, 2.75, 3.0, 3.25 ]
 #Labels 
 labels = { "FAG":"FA-WT", "DLG":"Density-WT" }
 #Compensated
@@ -55,11 +56,9 @@ def r_eff(X):
 #==================================================================================================
 #			COMPUTING RADIAL PROFILES OF DENSITY FOR EVERY RADIAL BIN
 #==================================================================================================
-fig = plt.figure( figsize=(4.5,4) )
+fig = plt.figure( figsize=(5.8,5) )
 ax = fig.add_subplot(111)
-#Embedded subplot
-#rect = [0.58,0.05,0.45,0.45]
-#ax1 = add_subplot_axes(ax,rect)
+
 for ri in xrange( len(RadBins)-1 ):
     reff_range = [ RadBins[ri],RadBins[ri+1] ]
     #Loading index of voids
@@ -92,7 +91,7 @@ for ri in xrange( len(RadBins)-1 ):
 	    rho = rprofile[:,1]
 	    ur = rprofile[ np.isnan(rho)==False ,0]
 	    rho = rho[ np.isnan(rho)==False ]
-	    Reffi = r_eff(voids[i,1])
+	    #Reffi = r_eff(voids[i,1])
 	    #plt.plot( ur, rho, lw = 0.05 )
 	    try:
 		rho_interp = interp.interp1d( ur, rho )
@@ -113,24 +112,20 @@ for ri in xrange( len(RadBins)-1 ):
     Q1[Q1==0] = nan
[…]

### 2015-02-13 bench/codes_figures/void_radial_velocity_bins.py

@@ -33,16 +33,17 @@ config = "01"
 comp = int(sys.argv[3])
 
 #Number of middle points for mapping the density field
-N = 40
+N = 80
 #Number of times the effective radius of the void
 Rreff = 8
 #Effective radial bins 
-#RadBins = [ 2, 3, 4, 5, 6, 7, 8, 9, 10, 12 ]
 RadBins = [ 2.0, 3.2, 4.4, 5.6, 6.8, 8.3, 12 ]
 #Colors 
 #color = ["#000000","#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
 #color = ["#000066", "#0000BE", "#067EF4", "#23F0D5", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
 color = ["#0000BE", "#067EF4", "#67BD65", "#FFFF00", "#FF8000", "#FF0000", "#800000"]
+#Linewidths
+linewidths = [ 2, 2.25, 2.5, 2.75, 3.0, 3.25 ]
 #Labels 
 labels = { "FAG":"FA-WT", "DLG":"Density-WT" }
 #Compensated
@@ -55,11 +56,8 @@ def r_eff(X):
 #==================================================================================================
 #			COMPUTING RADIAL PROFILES OF VELOCITY FOR EVERY RADIAL BIN
 #==================================================================================================
-fig = plt.figure( figsize=(4.5,4) )
+fig = plt.figure( figsize=(5.8,5) )
 ax = fig.add_subplot(111)
-#Embedded subplot
-#rect = [0.1,0.05,0.4,0.4]
-#ax1 = add_subplot_axes(ax,rect)
 
 for ri in xrange( len(RadBins)-1 ):
     reff_range = [ RadBins[ri],RadBins[ri+1] ]
@@ -87,11 +85,13 @@ for ri in xrange( len(RadBins)-1 ):
 		(data_figures_fold,void_scheme,web,i-1))
 	    except:
                 pass
+	    if len(vprofile)==2:
+		continue
 	    #interpolating
 	    vel = vprofile[:,1]
 	    ur = vprofile[ np.isnan(vel)==False ,0]
 	    vel = vel[ np.isnan(vel)==False ]
-	    Reffi = r_eff(voids[i,1])
+	    #Reffi = r_eff(voids[i,1])
 	    	    
[…]

### 2015-02-13 bench/codes_figures/void_volume_regions_all.py

@@ -22,7 +22,7 @@ labels = ['FA-Tweb', 'FA-Vweb', 'Density']
 void_scheme = 'FAG'
 #Schemes used for each web
 schemes = [ "01","01","01" ]
-#linestyles
+#Linestyles
 linestyles = ["-", "--"]
 
 

### 2015-02-14 cosmic_voids.tex
empezando con las conclusiones
New figure of abundance of over and subcompensated voids vs effective radius.

@@
 %FIGURE 3: volume functions
-\begin{figure}
+\begin{figure*}
 \centering
 
-  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
   width=0.35\textheight]{voids_regions_volume_all.pdf}
+  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_regions_volume_compensated.pdf}
 
   \captionof{figure}{\small Volume size distribution of voids for both
-  catalogues. FA-T-web (red curves), FA-Vweb (blue curves).
-  Continuous lines corresponds with the total number of voids, dot-dashed
-  with sub-compensated voids and dashed lines with over-compensated voids. }
+  catalogues. FA-T-web (continuous red curves), FA-Vweb (dashed blue 
+  curves). Left panel, total distributions. Right panel, distributions of 
+  subcompensanted and overcompensanted voids. }
 
@@
 
-\end{figure}
+\end{figure*}
 %.........................................................................
@@
 
+We propose in this paper a new method to find and describe void in
+cosmological dark matter simulations.
+The basis of our metho is the anisotropy of the eigenvalues from tensors
+constructed to describe the cosmic web.
+
 %*************************************************************************

### 2015-02-14 bench/codes_figures/void_volume_regions_all.py

@@ -33,7 +33,7 @@ colors = ["red", "blue", "green"]
 #			CONSTRUCTING REGIONS VOLUME
 #==================================================================================================
 
-fig = plt.figure( figsize=(5,5) )
+fig = plt.figure( figsize=(5.8,5) )
 fig.subplots_adjust( top = 0.9, right = 0.95, left = 0.15, wspace = 0.05, bottom = 0.1 )
 ax1 = [fig.add_subplot(1,1,i+1) for i in xrange(1)]
 ax2 = [ax1[i].twiny() for i in xrange(1)]
@@ -77,16 +77,15 @@ for web in webs:
     #Normal Plot
     if sys.argv[1] == '0':
 	ax1[0].semilogy( hist1d[1][:-1], distro, linewidth = 3.0, linestyle = linestyles[i_web],\
-	#color = colors[i_web], label = "%s (%s-order MF)"%(labels[i_web], schemes[i_web][0]) )
 	color = colors[i_web], label = "%s"%(labels[i_web]) )
 	
 	#Subcompensated voids
-	#ax1[0].semilogy( hist1d_o[1][:-1], distro_o, "--", linewidth = 2,\
-	#color = colors[i_web], label = "%s SC"%(labels[i_web]) )
+	#ax1[0].semilogy( hist1d_o[1][:-1], distro_o, lw = 1.5, linestyle = linestyles[i_web],\
+	#color = colors[i_web], label = "%s $C<1$"%(labels[i_web]) )
 	
 	#Overcompensated voids
-	#ax1[0].semilogy( hist1d_u[1][:-1], distro_u, "-.", linewidth = 2,\
-	#color = colors[i_web], label = "%s OC"%(labels[i_web]) )
+	#ax1[0].semilogy( hist1d_u[1][:-1], distro_u, lw = 3.0, linestyle = linestyles[i_web],\
+	#color = colors[i_web], label = "%s $C>1$"%(labels[i_web]) )
       
     #Cumulative Plot
     else:

### 2015-02-16 cosmic_voids.tex
pinkerizing the text. rewriting captions

@@
 %=========================================================================
-\title{Tidal field anisotropy as a tracer of cosmic voids}
+\title{Tensor anisotropy as a tracer of cosmic voids}
 \author[S. Bustamante and J.E. Forero-Romero]{
@@
 studies.  
-In this paper we present a new algorithm to find voids in
-cosmological simulations.  
-Our approach is based on algorithms that use the tidal and the
+In this paper we present a new method to find voids in
+cosmological simulations based on algorithms that use the tidal and the
 velocity shear tensors to locally define the cosmic web.
@@
 
-Voids have been identified as one of the most striking features of the
+Cosmic voids are one of the most striking features of the
 Universe on its larges scales since they were found in the first
@@
 
-This paper is organized as follows. 
-In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
-we use to find the cosmic web in N-body simulations. 
-In Section \ref{sec:bulk_voids} we explain in detail our void finder
-based on the fractional anisotropy of the tidal and shear tensor
-fields. 
-In Section  \ref{sec:simulations} we describe the N-body simulation we
-use to test our algorithm. 
-Our results are presented in \ref{sec:results} to finally comment and
-conclude about these findings in Section \ref{sec:conclusions}.
+%This paper is organized as follows. 
+%In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
+%we use to find the cosmic web in N-body simulations. 
+%In Section \ref{sec:bulk_voids} we explain in detail our void finder
+%based on the fractional anisotropy of the tidal and shear tensor
+%fields. 
+%In Section  \ref{sec:simulations} we describe the N-body simulation we
+%use to test our algorithm. 
+%Our results are presented in \ref{sec:results} to finally comment and
+%conclude about these findings in Section \ref{sec:conclusions}.
 
@@
   width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
-  \caption{Left colum. Visual impression of the 
-  Fractional Anisotropy field over a slide of the simulation for each
-  web scheme (T-Web top. V-Web bottom).  
-  Middle column. Cosmic Web identification. Voids
-  are white, sheets are light gray, filaments are dark gray and
-  knots are black.
-  Right column. Colors are voids identified by our Fractional
-  Anisotropy method.}
+  \caption{Visual impression of different quantities/algorithm results
+    mentioned in this paper. Fractional Anisotropy field
+    (left); osmic web classification (middle) where voids are white,
+    sheets are light gray, filaments are dark gray and knots are
+    black; and colored individual voids. Top/bottom corresponds to the 
+    T-Web/V-Web.}
   \label{fig:FA_field}
@@
 
-In next two subsections we describe the major features of the two
-algorithms (T-web and V-web) we use to find and classify the cosmic web in cosmological
-N-body simulations. 
-These schemes have also been used to develop other kind of studies
-such as the alignment of the shape, spin and peculiar velocity of dark
-matter halos with the cosmic web \citep{Libeskind13,Forero2014}.
-We refer the reader to the paper of \cite{Forero09} and
-\cite{Hoffman12} to read a detailed description of each algorithm.
+Our new method to find voids is based on two existing cosmic web
+classification schemes that work on cosmological N-body simularions.
+Both schemes depend on the construction of tensors based on the
+hessian of the potential (T-Web scheme) and the shear of the velocity
+(V-Web scheme). 
+These algorithms have been used to develop other
+kind of studies such as the alignment of the shape, spin and peculiar
+velocity of dark matter halos with the cosmic web
+\citep{Libeskind13,Forero2014}. 
+Here we summarize the most relevant aspects of each scheme, we refer
+the reader to the papers of \cite{Forero09} (T-Web) and
+\cite{Hoffman12} (V-Web) for detailed descriptions.
 
@@
 
-We also use a kinematic scheme to define the Cosmic Web environment in 
-the simulation introduced by \cite{Hoffman12}.
-The V-web scheme for environment finding is based on the
-local velocity shear tensor calculated from the smoothed dark matter 
-velocity field in the simulation. This tensor is given by the 
-following expression
+The V-web scheme for environment finding introduced by
+\cite{Hoffman12} is based on the local velocity shear tensor
+calculated from the smoothed dark matter  velocity field in the
+simulation. 
+This tensor is given by the  following expression
 
@@
 
-  \captionof{figure}{\small Distributions of the FA (left panel) and the 
-  density field (right panel) with respect to the eigenvalue $\lambda_1$ 
-  for each web scheme (T-web, red lines. Vweb, blue lines) as calculated 
-  over all cells of the grid. Thick central lines correspond with the median 
-  and filled regions with the $50\%$ of the distribution.}
-
+  \captionof{figure}{\small Overdensity (left) and Fractional
+    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
+    for each web scheme (T-web, continous lines. Vweb, dashed lines) calculated 
+    over all cells of the grid. Thick central lines correspond are the
+    median and filled regions include $50\%$ of all values. This
+    information is necesary to define void boundaries in the watershed
+    algorithm. The vertical lines in the right hand plot show the
+    equivalent threshold values for the T-Web and V-web in order to
+    have voids composed by cells with Fractional Anisotropy equal or
+    less than $0.95$.}
   \label{fig:L1_correlations}
@@
 
+%.........................................................................
+%FIGURE 3: volume functions
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_regions_volume_all.pdf}
+  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{voids_regions_volume_compensated.pdf}
+
+  \captionof{figure}{\small Volume size distribution of voids for both
+  catalogues. FA-T-web (continuous red curves), FA-Vweb (dashed blue 
+  curves). Left panel, total distributions. Right panel, distributions of 
+  subcompensanted and overcompensanted voids. }
+
+  \label{fig:volume_function}
+
+\end{figure*}
+%.........................................................................
+
 \section{Numerical Simulation}
@@
 %-------------------------------------------------------------------------
-
-%.........................................................................
-%FIGURE 3: volume functions
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_regions_volume_all.pdf}
-  \includegraphics[trim = 2mm 2mm 2mm 0mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{voids_regions_volume_compensated.pdf}
-
-  \captionof{figure}{\small Volume size distribution of voids for both
-  catalogues. FA-T-web (continuous red curves), FA-Vweb (dashed blue 
-  curves). Left panel, total distributions. Right panel, distributions of 
-  subcompensanted and overcompensanted voids. }
-
-  \label{fig:volume_function}
-
-\end{figure*}
-%.........................................................................
 

### 2015-02-16 cosmic_voids.tex
in the middle of writing conclusions

@@
 
-  \captionof{figure}{\small Volume size distribution of voids for both
-  catalogues. FA-T-web (continuous red curves), FA-Vweb (dashed blue 
-  curves). Left panel, total distributions. Right panel, distributions of 
-  subcompensanted and overcompensanted voids. }
-
+  \captionof{figure}{\small Void size distribution (left) and fraction
+    of overcompensated/subcompensated voids. The continous (dashed)
+    curves correspond to the T-Web (V-Web).}
   \label{fig:volume_function}
@@
 
-We propose in this paper a new method to find and describe void in
-cosmological dark matter simulations.
-The basis of our metho is the anisotropy of the eigenvalues from tensors
-constructed to describe the cosmic web.
+We propose in this paper that the anisotropy of the eigenvalues from
+tensors constructed to describe the cosmic web is a good tracer of
+cosmic voids. Based on this idea we go on to implement a watershed
+algorithm o the fractional anisotropy to find voids voids in a N-body
+cosmological simulations. We perform this tests on the results of two
+different tensorial schemes, the T-Web and the V-web.
+
+The first quantity we take a look at is the void size distribution
+characterized by an effective radius. 
+We find that for T-Web voids the shape of this function corresponds to
+standard expectations. 
+However, for the V-Web we find an overabundance of the smallest voids
+due to artifacts in the web finding scheme in sheets and small
+fragmented voids inside the largest voids already identified in the
+T-Web, perhaps due to the complex velocity structure in large voids
+compared to a simpler density/gravitational potential anatomy.
+
+A second step in the characterization of the voids found by our method
+was the separation into subcompensated and overcompensated samples. 
+In the T-Web $60\%$ of the voids are overcompensated, meaning that
+they are located in denser regions with a clear delimiting ridge. 
+For the V-web the overcompensated fraction increases from $60\%$ to
+$80\%$ as the void size decreases, supporting the picture of smaller
+spurious voids located in matter sheets.
+
+Finally we proceed with an ever more detailed void characterization
+through the radially averaged profiles of density, radial velocity and
+fractional anisotropy. 
+In thi case we studied separately the subcompensated and
+overcompensated voids, split this time in samples with different
+effective radii.
+
+In the density profiles the most interesting feature is that the 
+profile has a similar shape for all the different void sizes once the
+radial coordinate is expressed in units of the effective radius. 
+In these profiles it is evident the presence of an overdense ridge
+around $2<r/r_{\rm eff}<3$ for the overcompensated voids.
+Subcompensated voids do not show such a ridge keeping its density
+lower than the average value up to $r/r_{\rm eff}\sim 8$.
+
+In other studies where voids are found using considerations on the
+density fields the ridge is, almost by definition, located around
+$r/r_{\rm eff}\sim 1$ and the subcompensated voids reach average
+density around $r/r_{\rm eff}\sim 3$. 
+This indicates that voids defined by boundaries in the FA are close to
+a factor of $2$ smaller than voids found by density only considerations.
+
+Our results extend the evidence for a universal density profile down
+to smaller sizes as the one probed by \cite{Hamaus14}.
 

### 2015-02-16 cosmic_voids.tex
conclusiones al 80%

@@
 
-Our results extend the evidence for a universal density profile down
-to smaller sizes as the one probed by \cite{Hamaus14}.
+The velocity profiles show the expected correlation with the features
+already observed in the density, most notably the radial velocity is
+cero close to flat regions in the density profile and positive around
+regions of increasing density with radius.
+
+The Fractional Anisotropy profiles also show remarkable similarities,
+(inside each class of subcompensated and overcompensated)
+and a close correlation with the behaviour in the density and velocity
+profiles. 
+From these profiles it becomes clear that our choice to delimit an
+overcompensated void coincides with a ridge in the fractional
+anisotropy. For the subcompensated voids the void boundary is located
+for regions with an average FA value of $\sim 0.7-0.8$.
+
+Put together, the results for the radial profiles support the 
+evidence for a universal density profile using smaller void sizes
+than the ones probed by \cite{Hamaus14}.
 

### 2015-02-18 cosmic_voids.tex
clarifying text, cleaning typos

@@
 homogeneous spatial grid.
-The algorithm is based on two tensorial schemes used to classify the
-cosmic web. 
+The algorithm uses the results from two tensorial schemes used to
+classify the cosmic web.
 The first (the T-web) is based on the Hessian of the gravitational potential or
@@
 \citep{Hoffman12}. 
-Our procedure allows a description of the internal structure
-of voids that goes beyond a simple definition of a void as just an
-underdense regions in the large-scale matter distribution.
+Our procedure allows for a description of the internal structure
+of voids that goes beyond a simple definition of a void as an
+underdense region in the large-scale matter distribution.
 The tidal and the shear tensors encode more information than the
@@
 
-Once we establish the FA as a void tracer, we proceed to
-identify individual voids as basins of FA local minima. 
-At this point we implement a \textit{watershed transform algorithm}
+In the next sections (\S \ref{sec:algorithms_cosmic_web} and \S
+\ref{sec:bulk_voids}) we establish the FA as a void tracer and then
+proceed to identify individual voids as basins of FA local minima.  At
+this point we implement a \textit{watershed transform algorithm}
 \citep{Beucher79,Beucher93} which has been used to define voids as
-catching basins of local minima of the density field
-\citep{Platen07,Neyrinck08}.
-
-%This paper is organized as follows. 
-%In Section \ref{sec:algorithms_cosmic_web} we describe the algorithms
-%we use to find the cosmic web in N-body simulations. 
-%In Section \ref{sec:bulk_voids} we explain in detail our void finder
-%based on the fractional anisotropy of the tidal and shear tensor
-%fields. 
-%In Section  \ref{sec:simulations} we describe the N-body simulation we
-%use to test our algorithm. 
-%Our results are presented in \ref{sec:results} to finally comment and
-%conclude about these findings in Section \ref{sec:conclusions}.
+catching basins of local minima of the density field \citep{Platen07,Neyrinck08}.
+Finally we find and charachterize voids in a N-body (\S
+\ref{sec:simulations} and \S \ref{results}) using density, velocity and
+fractional anisotropy profiles.  We use these results to comment on
+the qualities of our algorithm (\S \ref{sec:conclusions}).
 
@@
     mentioned in this paper. Fractional Anisotropy field
-    (left); osmic web classification (middle) where voids are white,
+    (left); cosmic web classification (middle) where voids are white,
     sheets are light gray, filaments are dark gray and knots are
@@
 
-This scheme was initially proposed by \citet{Hahn07} as an
-alternative for classifying the Cosmic Web based on the tidal tensor.
+This scheme was initially proposed by \citet{Hahn07}  to find the
+Cosmic Web based on the tidal tensor. 
 The tidal tensor allows a classification in terms of the orbital
@@
 The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
-conceived to quantify the anisotropy degree of a diffusion process, e.g. 
-the diffusivity of water molecules through cerebral tissue in nuclear
-magnetic resonance imaging. 
+conceived to quantify the anisotropy of the diffusivity of water
+molecules through cerebral tissue in nuclear magnetic resonance imaging. 
 Here we present the FA, much in the same way as \citet{Libeskind13},
@@
 %.........................................................................
-where the eigenvalues can be taken from either the T-web or the Vweb 
-(FA-T-web and FA-Vweb respectively). Such as it is defined, FA$=0$ 
+where the eigenvalues can be taken from either the T-Web or the V-Web 
+(FA-T-Web and FA-V-Web respectively). Such as it is defined, FA$=0$ 
 corresponds to an isotropic distribution ($\lambda_1=\lambda_2=\lambda_3$) 
-and FA$=1$ with a highly anisotropic distribution.
+and FA$=1$ to a highly anisotropic distribution.
 
@@
 of Figure 1) is traced by high FA values.  
-These characteristics are key to use the FA as a tracer of cosmic voids.
+This characteristic is the  key to use the FA as a tracer of cosmic
+voids.
 
@@
     Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
-    for each web scheme (T-web, continous lines. Vweb, dashed lines) calculated 
+    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
     over all cells of the grid. Thick central lines correspond are the
@@
 correspond to critical values of $\lambda_{1}^T = 0.265$ and
-$\lambda_{1}^V = 0.175$ for the T-web and Vweb, respectively.
+$\lambda_{1}^V = 0.175$ for the T-Web and V-Web, respectively.
 This means that setting $\lambda_{th}$ to either
@@
 \subsection{Defining voids with a watershed algorithm}
-\label{sec:watershed}
+\label{subsec:watershed}
 %-------------------------------------------------------------------------
 
-The previous section shows that FA is a good void tracer, but it does
-not automatically suggest how to define the boundary of individual
-voids.
+The previous Section shows that FA is a good void tracer, but how
+should we actually define the boundary of individual voids?
 For this purpose, we use the \textit{watershed transform algorithm}
 \citep{Beucher79,Beucher93} to identify a void as the basin of FA
-local minimum. 
+local minima with boundaries of FA$=0.95$. 
 The advantage of this definition is that it does not require any
@@
 watershed implementations.
-First, the watershed technique commonly uses the the density field
-instead of the FA field as we do in this paper
+First, the watershed technique commonly uses the density field
+instead of the FA field as we do here
 \citep{Platen07,Neyrinck08}.   
@@
 \citep{Schaap00}.
-However, from the analysis of our results it does not 
-introduce supurious results, at least with the mass resolution we have
-in the N-body simulation.
+However, from the analysis of our results the choice of a fixed
+Cartesian mesh does not induce wrong results, at least with
+the mass resolution we have in the N-body simulation.
 
@@
 In Figure \ref{fig:L1_correlations} we find the correlations of
-the eigenvalue $\lambda_1$ with he matter overdensity (left panel) and
+the eigenvalue $\lambda_1$ with the matter overdensity (left panel) and
 the FA (right panel).
-We can use this information to find the FA threshold. 
-From the left panel we see that an underdensity of $\delta=-0.8$ is
-correspond to values of $\lambda_1=0.0$, regardless of the web-finding
+We can use this information to find the equivalent FA threshold. 
+From the left panel we see that an underdensity of $\delta=-0.8$ 
+corresponds to $\lambda_1=0.0$, regardless of the web-finding
 scheme.
@@
 with the FA, indicating that in turn $\lambda_1=0.0$ corresponds to a
-FA=$0.65$ which is the value that we have used to remove ridges.
-
+FA=$0.65$ which is the value that we choose to remove ridges. 
 The right column in Figure \ref{fig:FA_field} shows all the individual
@@
 FA field.
-In what follows we describe the numerical simulation we have used to
-find voids and their detailed properties characterization.
 
@@
 The formation of large voids is limited by the \textit{void-in-void}
-problem (first barrier), where large voids are constituted
+mechanism (first barrier), where large voids are constituted
 hierarchically of smaller ones. 
 In turn, the formation of small voids is damped by the
-\textit{void-in-cloud} problem (second barrier),  where nearby
+\textit{void-in-cloud} mechanism (second barrier),  where nearby
 collapsing structures limit the abundance of small embedded voids.
@@
 They are visible in the middle panel of Figure \ref{fig:FA_field} as
-small bubbles located inside sheets.
+tiny white bubbles located inside sheets.
 The existence of these small voids can be explained by
@@
 As matter colides into a sheet, in their symmetry plane one will
-find crossing ahseets that effectively give a positive divergence in
+find crossing sheets that effectively give a positive divergence in
 the velocity field, resulting in a void identification by the
-V-Web algorithm. This points has been discussed in \citet{Hoffman12}.
+V-Web algorithm. This has been already discussed in \citet{Hoffman12}.
 
@@
 induces a split by the watershed algorithm in the V-Web. 
-This is evident in the right panel of Figure \ref{fig:FA_field}.
+This increased granularity in the velocity structure of voids is
+evident in the left and right panels of Figure \ref{fig:FA_field}.
 

### 2015-02-18 cosmic_voids.tex
first pass on the conclusions

@@
 classify the cosmic web.
-The first (the T-web) is based on the Hessian of the gravitational potential or
+The first (the T-Web) is based on the Hessian of the gravitational potential or
 tidal tensor \citep{Hahn07, Forero09}. 
@@
 We also find that the V-Web scheme produces an over-abundance of small
-voids compared to the resuls of the T-Web.
+voids compared to T-Web.
 A large number of these small voids are embedded in overdense regions. 
@@
 The existence of these small voids can be explained by
-dynamics of shell crossing in collapsing sheets. 
-As matter colides into a sheet, in their symmetry plane one will
-find crossing sheets that effectively give a positive divergence in
-the velocity field, resulting in a void identification by the
-V-Web algorithm. This has been already discussed in \citet{Hoffman12}.
+dynamics of shell crossing in collapsing sheets as discussed in
+\citet{Hoffman12}.    
+The main argument is that as matter colides into a pancake-like
+fashion crossing sheets encounter each other at the symmetry plane.
+This effectively gives a positive divergence in the velocity
+field, resulting in a void identification by the V-Web algorithm.
 
@@
 The velocity profiles show the expected correlation with the features
-already observed in the density, most notably the radial velocity is
-cero close to flat regions in the density profile and positive around
+already observed in the density, most notably the radial velocity goes to
+zero close to flat regions in the density profile and is positive around
 regions of increasing density with radius.
@@
 The Fractional Anisotropy profiles also show remarkable similarities,
-(inside each class of subcompensated and overcompensated)
+(inside each class of subcompensated and overcompensated voids)
 and a close correlation with the behaviour in the density and velocity
 profiles. 
-From these profiles it becomes clear that our choice to delimit an
-overcompensated void coincides with a ridge in the fractional
-anisotropy. For the subcompensated voids the void boundary is located
-for regions with an average FA value of $\sim 0.7-0.8$.
+From these profiles it becomes clear that the limit of overcompensated
+void coincides with a ridge in of FA values close to $0.9$. 
+This value is close to the limit FA=$0.95$ we impose in the watershed
+algorithm, indicating that these voids are very close to spherical.
+For the subcompensated voids the FA quickly increases to FA values of 
+$\sim 0.7-0.8$ at $r/r_{\rm eff}\sim 1$ to find a plateau, which is
+quite far from the limiting FA$=0.95$ suggesting that these voids are
+far from spherical.
 
-Put together, the results for the radial profiles support the 
-evidence for a universal density profile using smaller void sizes
-than the ones probed by \cite{Hamaus14}.
+Put together, the results for the radially averaged profiles support the 
+evidence for a universal density profile.  
+This extends the work done
+by \cite{Hamaus14} to smaller void sizes.
+
+The method we present here finds voids with reasonable properties
+compared to different results published in the literature. 
+This gives support to a new tracer, the Fractional Anisotropy, to be
+used in the study of cosmic voids. 
+Furthermore, the complementary physical picture in the two different
+web finding algorithms opens the possibilities to make a joint
+analysis of the tidal and dynamical structure of voids.
 

### 2015-02-18 cosmic_voids.tex
minor edits

@@
 \begin{abstract}
-Finding and characterizing underdense regions (voids) in the large
-scale structure of the Universe is an important task in cosmological
-studies.  
-In this paper we present a new method to find voids in
-cosmological simulations based on algorithms that use the tidal and the
-velocity shear tensors to locally define the cosmic web.
-Voids are identified using the fractional anisotropy (FA) computed
-from the eigenvalues of each web scheme. 
-We define the void boundaries using a watershed transform based on the
-local minima of the FA and its boundaries as the regions where the FA
-is maximized.
-This void identification technique does not have any free parameters
-and does not make any assumption on the shape or structure of the
-voids.  
-We test the method on the Bolshoi simulation and report on the density
-and velocity profiles for the voids found using this new scheme. 
-We find that...
+We present a new method to find voids in cosmological simulations
+based on algorithms that use the tidal and the velocity shear tensors
+to locally define the cosmic web. 
+We use the fractional anisotropy (FA) computed from the eigenvalues
+of each web scheme as void tracer and find the voids using a watershed
+transform based on the local minima of the FA
+This void identification technique does not make any assumption on the
+shape or structure of the voids. 
+We test the method on the Bolshoi simulation and report on the
+abundance and radial averaged profiles for the density, velocity and
+fractional anistropy.
+We find that voids in the velocity shear web are smaller than voids in
+the tidal web, with a particular overabundance of very small voids in
+the inner region of filaments/sheets.
+We clasify voids as overcompansated/subcompensated depending on the
+presence/absence of an overdense matter ridge in their density
+profile, finding that close to $65\%$ and $35\%$  of the total
+population are classified into each category, respectively.
+We find evidence for the existence of universal profiles once the
+radial coordinate is normalized to the effective radius of each void
+from the radiallly averaged profiles for density, velocity and
+fractional anisotropy. 
 \end{abstract}
@@
 Finally we find and charachterize voids in a N-body (\S
-\ref{sec:simulations} and \S \ref{results}) using density, velocity and
+\ref{sec:simulations} and \S \ref{sec:results}) using density, velocity and
 fractional anisotropy profiles.  We use these results to comment on
@@
 justifies in a more quantiative way the qualitative argument
-we present in Section \ref{sec:watershed} to define void boundaries in
+we present in sub-section \ref{subsec:watershed} to define void boundaries in
 our method.  Namely that as we increase the void boundary, we reach
@@
 density around $r/r_{\rm eff}\sim 3$. 
-This indicates that voids defined by boundaries in the FA are close to
-a factor of $2$ smaller than voids found by density only considerations.
+This indicates that voids defined by FA boundaries are close smaller 
+than voids found by density only considerations close by a factor of
+$2$.
 

### 2015-02-18 bench/codes_figures/void_numbers.py
Table with number of voids for each bin of effective radius.

@@ -1,0 +1,63 @@
+#void_numbers.py
+#
+#This code computes the number of voids per bin for over and subcompensated voids
+#
+#Usage: void_numbers.py <Vweb or Tweb> <FAG or DLT> <undercomp(0) overcomp(1)> 
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Box lenght [Mpc]
+L_box = 250.
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+web = sys.argv[1]
+#Void finder scheme (FAG or DLG)
+void_scheme = sys.argv[2]
+#Cutt of respect to the number of cells
+N_cut = 2
+#Configuration 
+config = "01"
+#Compensated
+comp = int(sys.argv[3])
+
+#Number of middle points for mapping the density field
+N = 80
+#Number of times the effective radius of the void
+Rreff = 8
+#Effective radial bins 
+RadBins = [ 0.0, 2.0, 3.2, 4.4, 5.6, 6.8, 8.3, 12, 100.0 ]
+
+#Effective radius function
+def r_eff(X):
+    return ((10**np.log10(X)*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
+
+#==================================================================================================
+#			COMPUTING RADIAL PROFILES OF DENSITY FOR EVERY RADIAL BIN
+#==================================================================================================
+fig = plt.figure( figsize=(5.8,5) )
+ax = fig.add_subplot(111)
+
+Total = 0
+for ri in xrange( len(RadBins)-1 ):
+    reff_range = [ RadBins[ri],RadBins[ri+1] ]
+    #Loading index of voids
+    voids = np.loadtxt("%s/%s/%s/%d/voids%s/voids_%s/void_regions.dat"%\
+    (foldglobal, simulation, web, N_sec, void_scheme, config ))
+    #Loading compensated
+    compensated = np.loadtxt("%s/%s/%s/%d/voids%s/voids_%s/comp_half.dat"%\
+    (foldglobal, simulation, web, N_sec, void_scheme, config ))
+  
[…]

### 2015-02-20 cosmic_voids.tex
Table with number of voids for each bin of effective radius.
corrigiendo estilo

@@
 \restylefloat{table}
+%Multiple columns support for tables
+\usepackage{array}
+\usepackage{booktabs}
+\setlength{\heavyrulewidth}{1.5pt}
+\setlength{\abovetopsep}{4pt}
 
@@
 to locally define the cosmic web. 
-We use the fractional anisotropy (FA) computed from the eigenvalues
-of each web scheme as void tracer and find the voids using a watershed
-transform based on the local minima of the FA
+We use show that fractional anisotropy (FA) computed from the eigenvalues
+of each web scheme is a good void tracers. 
+Based on this result we identify voids using a watershed
+transform based on the local minima of the FA field.
 This void identification technique does not make any assumption on the
@@
 population are classified into each category, respectively.
-We find evidence for the existence of universal profiles once the
+Finally, we find evidence for the existence of universal profiles once the
 radial coordinate is normalized to the effective radius of each void
@@
   width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
-  \caption{Visual impression of different quantities/algorithm results
-    mentioned in this paper. Fractional Anisotropy field
-    (left); cosmic web classification (middle) where voids are white,
-    sheets are light gray, filaments are dark gray and knots are
-    black; and colored individual voids. Top/bottom corresponds to the 
-    T-Web/V-Web.}
+  \caption{Visual impression of different results mentioned in this
+    paper for a slice of $1\hMpc$ width in the Bolshoi simulation.  
+    Fractional Anisotropy field (left); cosmic web classification
+    (middle) where voids are white, sheets are light gray, filaments
+    are dark gray and knots are black; and colored individual
+    voids found by the a watershed algorithm on the Fractional
+    Anisotropy field. Top/bottom corresponds to the T-Web/V-Web.}
   \label{fig:FA_field}
@@
 
-Our new method to find voids is based on two existing cosmic web
+Our new void finding method is based on two existing cosmic web
 classification schemes that work on cosmological N-body simularions.
@@
     for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
-    over all cells of the grid. Thick central lines correspond are the
-    median and filled regions include $50\%$ of all values. This
-    information is necesary to define void boundaries in the watershed
-    algorithm. The vertical lines in the right hand plot show the
-    equivalent threshold values for the T-Web and V-web in order to
-    have voids composed by cells with Fractional Anisotropy equal or
-    less than $0.95$.}
+    over all grid cells in the Bolshoi simulation. 
+    Thick central lines are the median and filled regions include $50\%$ of all
+    cells. 
+    This information is necesary to define void boundaries in
+    the watershed algorithm. 
+    The vertical lines show the equivalent threshold values for the
+    T-Web and V-web in order to have voids composed by cells with
+    Fractional Anisotrop equal or less than $0.95$.}
   \label{fig:L1_correlations}
@@
 
-  \captionof{figure}{\small Void size distribution (left) and fraction
-    of overcompensated/subcompensated voids. The continous (dashed)
+  \captionof{figure}{\small Left panel, void size distribution. Right
+    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
+    function of the effective radius. The continous (dashed)
     curves correspond to the T-Web (V-Web).}
@@
 overcompensated voids.
+
+%.........................................................................
+\begin{table}[!htbp]
+\centering
+\begin{tabular}{c | c c | c c}
+\toprule
+\multicolumn{1}{c}{}&  \multicolumn{2}{c}{\textbf{Tweb}} & \multicolumn{2}{c}{\textbf{Vweb}}\\
+%\midrule
+\textbf{bin [\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
+%\midrule
+$<2.0$        &  997 & 495   & 13480  & 711\\
+$2.0-3.2$     &  791 & 471   & 2581   & 583\\
+$3.2-4.4$     &  941 & 469   & 2168   & 656\\
+$4.4-5.6$     &  869 & 467   & 1934   & 724\\
+$5.6-6.8$     &  769 & 395   & 1287   & 584\\
+$6.8-8.3$     &  665 & 362   & 700    & 315\\
+$8.3-12.0$    &  587 & 333   & 123    & 61\\
+$>12.0$       &  29  & 23    & 0      & 0\\ \hline
+\textbf{total}& 5648 & 3015  & 22273  & 3634\\
+\bottomrule
+\end{tabular}
+\caption{Number of voids for each bin of effective radius and for 
+subcompensanted and overcompansated samples.}
+\label{tab:number_voids}
+\end{table}
+%.........................................................................
+
+Table \ref{tab:number_voids} lists the number of voids in 
+each effective radius bin For the two web finding methods.
 

### 2015-02-20 bench/codes_figures/void_volume_regions_compensated.py
Little typo. Correcting figure 3, legend of over and subcompensated voids.

@@ -79,13 +79,13 @@ for web in webs:
 	
     #Normal Plot
     if sys.argv[1] == '0':	
-	#Subcompensated voids
-	ax1[0].plot( hist1d_o[1][:-1], distro_o/distro, lw = 1.5, linestyle = linestyles[i_web],\
-	color = colors[i_web], label = "%s $C<1$"%(labels[i_web]) )
-	
 	#Overcompensated voids
-	ax1[0].plot( hist1d_u[1][:-1], distro_u/distro, lw = 3.0, linestyle = linestyles[i_web],\
+	ax1[0].plot( hist1d_o[1][:-1], distro_o/distro, lw = 1.5, linestyle = linestyles[i_web],\
 	color = colors[i_web], label = "%s $C>1$"%(labels[i_web]) )
+	
+	#Subcompensated voids
+	ax1[0].plot( hist1d_u[1][:-1], distro_u/distro, lw = 3.0, linestyle = linestyles[i_web],\
+	color = colors[i_web], label = "%s $C<1$"%(labels[i_web]) )
       
     #Cumulative Plot
     else:

### 2015-02-21 cosmic_voids.tex
Little typo. Correcting figure 3, legend of over and subcompensated voids.
Correcting over-subcompensated values. Little typos

@@
 to locally define the cosmic web. 
-We use show that fractional anisotropy (FA) computed from the eigenvalues
-of each web scheme is a good void tracers. 
+We show that fractional anisotropy (FA) computed from the eigenvalues
+of each web scheme is a good void tracer. 
 Based on this result we identify voids using a watershed
@@
 the inner region of filaments/sheets.
-We clasify voids as overcompansated/subcompensated depending on the
-presence/absence of an overdense matter ridge in their density
+We clasify voids as subcompensated/overcompansated depending on the
+absence/presence of an overdense matter ridge in their density
 profile, finding that close to $65\%$ and $35\%$ of the total
@@
 Digital Sky Survey (SDSS)\citep{York00, Abazajian03}.
-These observational breakthughs generated a great interest in the last
+These observational breakthroughs generated a great interest in the last
 decade to study voids \citep{Hoyle04, Croton04, Rojas05,
@@
 
-On the theoretical side the basic framework that explains
+On the theoretical side, the basic framework that explains
 the origin of voids was established in the seminal work of
@@
 
-The FA is defined as follows.
+The FA is defined as follows
 %.........................................................................
@@
 Table \ref{tab:number_voids} lists the number of voids in 
-each effective radius bin For the two web finding methods.
+each effective radius bin for the two web finding methods.
 
@@
 We calculate the profile out to a radius $8\ \reff$  to capture the
-the point where the overdensity reaches the mean value.
+point where the overdensity reaches the mean value.
 
@@
 This suggests that smaller subcompensated voids are embedded into low
-density structures like voids or walls, while arge subcompensated
+density structures like voids or walls, while large subcompensated
 voids are surrounded  by dense structures, reaching the mean density
@@
 
-On the other hand, overcompensated voids initially exhibit and outward
+On the other hand, overcompensated voids initially exhibit outward
 profiles, (as expected from a low density region) and approximately at
@@
 We recognize that our choice produces smaller voids as compared with
-other voids finding methods, however this has the advantange of
-voiding the contamination from external structures.
+other voids finding methods, however this has the advantage of
+avoiding the contamination from external structures.
 
@@
 was the separation into subcompensated and overcompensated samples. 
-In the T-Web $60\%$ of the voids are overcompensated, meaning that
+In the T-Web $35\%$ of the voids are overcompensated, meaning that
 they are located in denser regions with a clear delimiting ridge. 
-For the V-web the overcompensated fraction increases from $60\%$ to
-$80\%$ as the void size decreases, supporting the picture of smaller
-spurious voids located in matter sheets.
+For the V-web the subcompensated fraction increases from $65\%$ to
+$85\%$ as the void size decreases, supporting the picture of smaller
+spurious voids located in low density matter sheets.
 
@@
 density around $r/r_{\rm eff}\sim 3$. 
-This indicates that voids defined by FA boundaries are close smaller 
-than voids found by density only considerations close by a factor of
-$2$.
+This indicates that voids defined by FA boundaries are smaller 
+than voids found by density only considerations close by a radial factor 
+of $2$.
 

### 2015-03-04 cosmic_voids.tex
revision de abstract, conclusiones y caption

@@
 We present a new method to find voids in cosmological simulations
-based on algorithms that use the tidal and the velocity shear tensors
-to locally define the cosmic web. 
-We show that fractional anisotropy (FA) computed from the eigenvalues
-of each web scheme is a good void tracer. 
-Based on this result we identify voids using a watershed
-transform based on the local minima of the FA field.
-This void identification technique does not make any assumption on the
-shape or structure of the voids. 
+based on the tidal and the velocity shear tensors
+definitions of the cosmic web. 
+We use the fractional anisotropy (FA) computed from the eigenvalues
+of each web scheme as a void tracer.
+We identify voids using a watershed transform based on the local
+minima of the FA field without making any assumption on the shape or
+structure of the voids.  
 We test the method on the Bolshoi simulation and report on the
@@
 fractional anisotropy. 
+Put together, all these results show that the FA is a reliable tracer
+for voids, which can be used in complementarity to other existing
+methods and tracers.
 \end{abstract}
@@
 Cosmic voids are one of the most striking features of the
-Universe on its larges scales since they were found in the first
+Universe on its larges scales ever since they were found in the first
 galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
@@
   width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
-  \caption{Visual impression of different results mentioned in this
-    paper for a slice of $1\hMpc$ width in the Bolshoi simulation.  
+  \caption{Visual impression of different fields in a slice of
+    $1\hMpc$ width in the Bolshoi simulation.   
     Fractional Anisotropy field (left); cosmic web classification
     (middle) where voids are white, sheets are light gray, filaments
-    are dark gray and knots are black; and colored individual
-    voids found by the a watershed algorithm on the Fractional
+    are dark gray and knots are black; colored individual
+    voids (right) found by the a watershed algorithm on the Fractional
     Anisotropy field. Top/bottom corresponds to the T-Web/V-Web.}
@@
     over all grid cells in the Bolshoi simulation. 
-    Thick central lines are the median and filled regions include $50\%$ of all
-    cells. 
+    Thick central lines are the median and filled regions include
+    $50\%$ of the cells in each bin.
     This information is necesary to define void boundaries in
@@
 
-We propose in this paper that the anisotropy of the eigenvalues from
-tensors constructed to describe the cosmic web is a good tracer of
-cosmic voids. Based on this idea we go on to implement a watershed
-algorithm o the fractional anisotropy to find voids voids in a N-body
-cosmological simulations. We perform this tests on the results of two
-different tensorial schemes, the T-Web and the V-web.
+In this paper we propose that the anisotropy of the eigenvalues from
+tidal and velocity shear tensors is a good tracer of  cosmic voids. 
+Based on this idea we go on to implement a watershed
+algorithm o the fractional anisotropy to find voids in a N-body
+cosmological simulation.
+We perform different test on the voids found on the anisotropy of two
+tensorial schemes, the T-Web and the V-web.
 
-The first quantity we take a look at is the void size distribution
+The first quantity examine is the void size distribution
 characterized by an effective radius. 
 We find that for T-Web voids the shape of this function corresponds to
-standard expectations. 
-However, for the V-Web we find an overabundance of the smallest voids
-due to artifacts in the web finding scheme in sheets and small
-fragmented voids inside the largest voids already identified in the
-T-Web, perhaps due to the complex velocity structure in large voids
-compared to a simpler density/gravitational potential anatomy.
+standard expectations from a two-barrier setup. 
+However, for the V-Web we find an overabundance of the smallest voids.
+This is due to artifacts in the web finding scheme in sheets and also
+to the smaller fragmented voids inside the largest voids already
+identified in the T-Web. 
+The void fragmentation hints at a complex velocity structure in large
+voids compared to its simpler density/gravitational potential anatomy.
 
 A second step in the characterization of the voids found by our method
-was the separation into subcompensated and overcompensated samples. 
-In the T-Web $35\%$ of the voids are overcompensated, meaning that
-they are located in denser regions with a clear delimiting ridge. 
-For the V-web the subcompensated fraction increases from $65\%$ to
-$85\%$ as the void size decreases, supporting the picture of smaller
-spurious voids located in low density matter sheets.
+is the separation into subcompensated and overcompensated samples. 
+In the T-Web $35\%$ of the voids are overcompensated ($65\%$
+subcompensated), meaning that they are located in denser regions with
+a clear delimiting ridge.   
+For the V-web the subcompensated fraction rises from $65\%$ to $85\%$ as the
+void size decreases, supporting the picture of smaller spurious voids
+located in low density matter sheets.
 
-Finally we proceed with an ever more detailed void characterization
+Finally we proceed with an more detailed void characterization
 through the radially averaged profiles of density, radial velocity and
 fractional anisotropy. 
-In thi case we studied separately the subcompensated and
+In this case we study separately the subcompensated and
 overcompensated voids, split this time in samples with different
@@
 
-In the density profiles the most interesting feature is that the 
-profile has a similar shape for all the different void sizes once the
-radial coordinate is expressed in units of the effective radius. 
+For the density the most interesting feature is that the  profile has
+a similar shape for all the different void sizes once the radial
+coordinate is expressed in units of the effective radius.  
 In these profiles it is evident the presence of an overdense ridge
@@
 density around $r/r_{\rm eff}\sim 3$. 
-This indicates that voids defined by FA boundaries are smaller 
-than voids found by density only considerations close by a radial factor 
-of $2$.
+This indicates that voids defined by FA boundaries are smaller  than
+voids found by density only considerations close by a radial factor of
+$2$.
 
 The velocity profiles show the expected correlation with the features
-already observed in the density, most notably the radial velocity goes to
-zero close to flat regions in the density profile and is positive around
-regions of increasing density with radius.
+already observed in the density.
+Most notably the radial velocity goes to zero close to flat regions in
+the density profile and is positive around regions of increasing
+density with radius.
 

### 2015-03-10 cosmic_voids.tex
New references

@@
 These observational breakthroughs generated a great interest in the last
-decade to study voids \citep{Hoyle04, Croton04, Rojas05,
+decade to study voids \citep{Hoyle04, Croton04, Padilla05, Rojas05,
   Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b,Tikhonov07,
-  BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}.
+  BendaBeckmann08, Foster09, Ceccarelli13, Paz13, Sutter14a}.
 
@@
 reconstruction procedures on surveys \citep{Plionis02, Colberg05,
-  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Neyrinck13,
-  Ricciardelli2013}, unlike geometrical approaches based on point
-distributions, where central density values are generally higher
+  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Ceccarelli13,
+  Paz13, Neyrinck13, Ricciardelli2013}, unlike geometrical approaches based 
+on point distributions, where central density values are generally higher
 \citep{Colberg08}.
@@
 \citep{Colberg05,  Ricciardelli2013} and external structure of voids
-\citep{Lavaux12, Hamaus14}. 
+\citep{Lavaux12, Ceccarelli13, Paz13, Hamaus14}. 
 Our results extend the findings of \cite{Hamaus14} into the range of
@@
 As in the density these results also consistent with a Universial
-velocity profile for voids \citep{Hamaus14}.
+velocity profile for voids \citep{Paz13, Hamaus14}.
 

### 2015-03-10 cosmic_voids.tex
Acknowledgement to Nelson Padilla

@@
 presence/absence of an overdense matter ridge in their density
-profiles. 
+profiles. This result was also found by \citet{Ceccarelli13} when analysing
+voids in the SDSS.
 To discriminate each void in one of the families we use the
@@
 
-As in the density these results also consistent with a Universial
+As in the density, these results are also consistent with a Universal
 velocity profile for voids \citep{Paz13, Hamaus14}.
@@
 
+We would like to thank Nelson Padilla for helpful comments and suggestions
+on the manuscript.
+
 \bibliographystyle{mn2e}

### 2015-03-12 cosmic_voids.tex
Little comment in conclusions
Acknowledgments

@@
 This extends the work done
-by \cite{Hamaus14} to smaller void sizes.
+by \cite{Hamaus14} to smaller void sizes and by \cite{Ceccarelli13} for
+the SDSS.
 
@@
 
-We would like to thank Nelson Padilla for helpful comments and suggestions
-on the manuscript.
+We would like to thank Rien van de Weygaert for his thoughtful review and 
+very helpful suggestions. Also, we thank Nelson Padilla for his comments 
+on the manuscript. SB thanks Jaime Forero-Romero for all his support and 
+guidance while developing this work. SB also thanks Juan Carlos Mu\~noz-Cuartas 
+for many clarifying discussions and helpful ideas.
 

### 2015-03-18 cosmic_voids.tex
revised abstract and conclusions

--- 2015-03-10 cosmic_voids.tex
@@
 population are classified into each category, respectively.
-Finally, we find evidence for the existence of universal profiles once the
-radial coordinate is normalized to the effective radius of each void
-from the radiallly averaged profiles for density, velocity and
-fractional anisotropy. 
+Finally, we find evidence for the existence of universal profiles from
+the radially averaged profiles for density, velocity and fractional
+anisotropy. 
+This requires that the radial coordinate is normalized to the
+effective radius of each void. 
 Put together, all these results show that the FA is a reliable tracer
@@
 Based on this idea we go on to implement a watershed
-algorithm o the fractional anisotropy to find voids in a N-body
+algorithm on the fractional anisotropy to find voids in a N-body
 cosmological simulation.
@@
 
-The first quantity examine is the void size distribution
+The first quantity we examine is the void size distribution
 characterized by an effective radius. 
-We find that for T-Web voids the shape of this function corresponds to
-standard expectations from a two-barrier setup. 
+We find that for the T-Web scheme the void size distribution has a
+shape consistent with standard expectations from a two-barrier setup. 
 However, for the V-Web we find an overabundance of the smallest voids.
-This is due to artifacts in the web finding scheme in sheets and also
-to the smaller fragmented voids inside the largest voids already
-identified in the T-Web. 
-The void fragmentation hints at a complex velocity structure in large
+This is due to two reasons. 
+First, there are artifacts in the web
+finding scheme inside sheets. 
+Second, there V-web produces smaller
+fragmented voids inside the largest voids found in the T-Web
+classification.  
+This void fragmentation hints at a complex velocity structure in large
 voids compared to its simpler density/gravitational potential anatomy.
 
-A second step in the characterization of the voids found by our method
+A second step in the void characterization 
 is the separation into subcompensated and overcompensated samples. 
@@
 void size decreases, supporting the picture of smaller spurious voids
-located in low density matter sheets.
+located in medium density matter sheets.
 
@@
 
-The Fractional Anisotropy profiles also show remarkable similarities,
-(inside each class of subcompensated and overcompensated voids)
+The Fractional Anisotropy profiles also show remarkable similarities
+inside each class of subcompensated and overcompensated voids
 and a close correlation with the behaviour in the density and velocity
@@
 evidence for a universal density profile.  
-This extends the work done
-by \cite{Hamaus14} to smaller void sizes.
+Our results extends to smaller void sizes the work done by
+\cite{Hamaus14} on simulations and by \cite{Ceccarelli13} on SDSS data.
 
@@
 
-We would like to thank Nelson Padilla for helpful comments and suggestions
-on the manuscript.
+We would like to thank Rien van de Weygaert for his thoughtful review
+and  very helpful suggestions on this manuscript.  
+We also thank Nelson Padilla and Yehuda  Hoffman for their comments on
+the manuscript.  
+SB also thanks Juan Carlos Mu\~noz-Cuartas 
+for many clarifying discussions and helpful ideas.
+JEFR acknowledges financial support from Vicerrector\'ia de
+Investigaciones at Universidad de los Andes (Colombia) through a FAPA
+grant.
 

### 2015-03-18 cosmic_voids.tex
adding text to captions

@@
 
+%-------------------------------------------------------------------------
+%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
+\begin{figure*}
+\centering
+
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{delta_L1.pdf}  
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{FA_L1.pdf}
+
+  \captionof{figure}{\small Overdensity (left) and Fractional
+    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
+    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
+    over all grid cells in the Bolshoi simulation. 
+    Thick central lines are the median and filled regions include
+    $50\%$ of the cells in each bin.
+    This information is necesary to define void boundaries in
+    the watershed algorithm. 
+    The vertical lines show the equivalent threshold values for the
+    T-Web and V-web in order to have voids composed by cells with
+    Fractional Anisotrop equal or less than $0.95$. 
+   This threshold on the eigenvalues does not influence our
+   computations. 
+   We show it as a guide to readers familiar with the
+   order of magnitude expectation for this threshold.}
+  \label{fig:L1_correlations}
+
+\end{figure*}
+%.........................................................................
+
 %*************************************************************************
@@
 %-------------------------------------------------------------------------
-
-%-------------------------------------------------------------------------
-%FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{figure*}
-\centering
-
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{delta_L1.pdf}  
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{FA_L1.pdf}
-
-  \captionof{figure}{\small Overdensity (left) and Fractional
-    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
-    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
-    over all grid cells in the Bolshoi simulation. 
-    Thick central lines are the median and filled regions include
-    $50\%$ of the cells in each bin.
-    This information is necesary to define void boundaries in
-    the watershed algorithm. 
-    The vertical lines show the equivalent threshold values for the
-    T-Web and V-web in order to have voids composed by cells with
-    Fractional Anisotrop equal or less than $0.95$.}
-  \label{fig:L1_correlations}
-
-\end{figure*}
-%.........................................................................
 
@@
     function of the effective radius. The continous (dashed)
-    curves correspond to the T-Web (V-Web).}
+    curves correspond to the T-Web (V-Web).
+    The abundance for small ($r_{eff}<2.0\hMpc$) overcompensated voids
+    shoots up in the V-Web scheme.
+    We provide in the body of the paper two reasons for this behaviour.}
   \label{fig:volume_function}

### 2015-03-18 cosmic_voids.tex
fionna\!

@@
 
-We would like to thank Rien van de Weygaert for his thoughtful review
-and  very helpful suggestions on this manuscript.  
-We also thank Nelson Padilla and Yehuda  Hoffman for their comments on
-the manuscript.  
+We would like to thank Fiona Hoyle and Rien van de Weygaert for their
+exhaustive and thoughtful reviews, accompanied with very detailed and
+helpful suggestions on earlier versions of this manuscript.  
+We also thank Nelson Padilla and Yehuda Hoffman for enlightening
+comments and discussions.
 SB also thanks Juan Carlos Mu\~noz-Cuartas 

### 2015-03-18 cosmic_voids.tex
intro revisada

@@
 
-Cosmic voids are one of the most striking features of the
+Cosmic voids are regarded as one of the most striking features of the
 Universe on its larges scales ever since they were found in the first
@@
 They dominate the volume distribution at large scales and
-additionally, compensating overdense structures in the total matter
+compensate overdense structures in the total matter
 budget. 
@@
 Nevertheless, the community has not reached yet an unambiguous
-definition of cosmic voids, with many different void finding
-techniques in the literature  (for a detailed comparison of different
-schemes,  see the publication on the results of the Void Finder
-Comparison Project \citet{Colberg08}).  
+definition of cosmic voids.
+There are many different void finding techniques in the literature
+(for a detailed comparison of different schemes,  see the publication
+on the results of the Void Finder Comparison Project \citet{Colberg08}).  
 In spite of the diversity of existing schemes, they can be roughly
-classified into two types. First, geometric schemes based on
-point distributions (either real or redshift space) of galaxies in
-surveys or dark matter halos in  simulations \citep{Kauffmann91, Muller00, 
-  Gottlober03, Hoyle04, Brunino07,  Foster09, Micheletti14, Sutter14}.
-Second, schemes based on the smooth and continuous matter density
+classified into two types: point-based and field-based. 
+There are geometric schemes based on point distributions (either real or
+redshift space)  f galaxies in surveys or dark matter halos in
+simulations \citep{Kauffmann91, Muller00,    Gottlober03, Hoyle04,
+  Brunino07,  Foster09, Micheletti14, Sutter14}. 
+While other chemes are based on the smooth and continuous matter density
 field either from simulations or from reconstruction procedures on
@@
   Neyrinck08, MunozCuartas11, Neyrinck13, Ricciardelli2013}. 
-Our work is based on the second kind of schemes.
+Our work follows the tradition of the second kind of schemes.
 
@@
 The tidal and the shear tensors encode more information than the
-density field as they trace the collapsing or expanding
+density/velocity fields as they trace the collapsing or expanding
 nature of the matter field, which defines the dynamics of the Cosmic
@@
 Both schemes depend on the construction of tensors based on the
-hessian of the potential (T-Web scheme) and the shear of the velocity
+Hessian of the potential (T-Web scheme) and the shear of the velocity
 (V-Web scheme). 
@@
 
-  \captionof{figure}{\small Spherically averaged radial density profile for
-    voids. The sample is split into subcompensated and overcompensated voids
-    (right and left) for the web schemes T-Web and V-Web (top and
-    bottom).}
+  \captionof{figure}{\small Spherically averaged radial density profiles for
+    stacked voids with different effective radii. The sample is split
+    into subcompensated and overcompensated voids (right and left) for
+    the web schemes T-Web and V-Web (top and bottom).}
   \label{fig:density_profile}
@@
   width=0.35\textheight]{voids_velocity_VwebFAG1.pdf}
-  \captionof{figure}{\small Spherically averaged radial velocity profile for
-    voids. The sample is split into subcompensated and overcompensated voids
+  \captionof{figure}{\small Spherically averaged radial velocity
+    profiles for stacked voids with different effective radii. The
+    sample is split into subcompensated and overcompensated voids
     (right and left) for the web schemes T-Web and V-Web (top and
@@
   \captionof{figure}{\small Spherically averaged Fractional Anisotropy
-    profile for voids. The sample is split into subcompensated and
-    overcompensated voids  (right and left) for the web schemes T-Web and V-Web (top and  bottom).}
+    profiles for stacked voids with different effective radii. The
+    sample is split into subcompensated andovercompensated voids
+    (right and left) for the web schemes T-Web and V-Web (top and
+    bottom).} 
   \label{fig:FA_profile}
@@
 %\midrule
-\textbf{bin [\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
+\textbf{${\bf r_{\rm eff}}$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
 %\midrule

### 2015-03-18 cosmic_voids.tex
last changes

@@
 \citep{Libeskind13,Forero2014}. 
-Here we summarize the most relevant aspects of each scheme, we refer
-the reader to the papers of \cite{Forero09} (T-Web) and
+Here we summarize the most relevant aspects of each scheme. 
+We refer the reader to the papers of \cite{Forero09} (T-Web) and
 \cite{Hoffman12} (V-Web) for detailed descriptions.
@@
 defined as the Hessian matrix of the normalized gravitational
-potential.
+potential
 
@@
 In this paper we take a different approach.
-We find the optimal value of the threshold based on the maximization
-of the fractional anisotropy field in the locations label as filaments
-and walls. 
-This is described in detailed in the next Section.
+In this work we propose an optimal value of the threshold based on the
+maximization of the fractional anisotropy field in the locations label
+as filaments and walls. 
+This threshold does not enter into our computations. 
+We simply offer this estimate as a guide to readers familiar with the
+meaning of this threshold.
 
@@
 
-In the left and middle panels of Figure \ref{fig:FA_field} we show the
+In the left and middle panels of Fig. \ref{fig:FA_field} we show the
 FA field and web classification for both  web schemes over a slice of
@@
 Comparing these two panels we see that voids and knots (white
-and black in the middle panel of Figure 1) display low FA values at
+and black in the middle panel of Fig. 1) display low FA values at
 their  centres, becoming gradually more anisotropic at outer regions.  
 On the other hand the filamentary structure (grey in the middle panel
-of Figure 1) is traced by high FA values.  
+of Fig. 1) is traced by high FA values.  
 This characteristic is the  key to use the FA as a tracer of cosmic
@@
 all the cells FA$<0.95$.   
-The middle panels in Figure \ref{fig:FA_field} show the web
+The middle panels in Fig. \ref{fig:FA_field} show the web
 classification for this choice of $\lambda_{th}$, demonstrating that
@@
 However, from the analysis of our results the choice of a fixed
-Cartesian mesh does not induce wrong results, at least with
+Cartesian mesh does not induce spurious results, at least with
 the mass resolution we have in the N-body simulation.
@@
 
-In Figure \ref{fig:L1_correlations} we find the correlations of
+In Fig. \ref{fig:L1_correlations} we find the correlations of
 the eigenvalue $\lambda_1$ with the matter overdensity (left panel) and
@@
 FA=$0.65$ which is the value that we choose to remove ridges. 
-The right column in Figure \ref{fig:FA_field} shows all the individual
+The right column in Fig. \ref{fig:FA_field} shows all the individual
 voids that have been identified using the watershed algorithm on the
@@
 Here we briefly describe the process to obtain the data. 
-For details see \cite{Forero09} (T-Web) and
+For details see \cite{Forero09} (T-Web);
 \cite{Hoffman12,Forero2014} (V-Web). 
@@
 Below that scale numerical resolution effects become important. 
-With that choice we find a volume filling fraction $54.88\%$ and
-$47.06\%$ for the FA-Vweb.
+With that choice we find a void volume filling fraction $54.88\%$ and
+$47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.
 
@@
 assigned to the void.   
-In Figure \ref{fig:volume_function} we show the void size
+In Fig. \ref{fig:volume_function} we show the void size
 distributions for the T-Web and the V-Web.
@@
 The formation of large voids is limited by the \textit{void-in-void}
-mechanism (first barrier), where large voids are constituted
+mechanism (first barrier) where large voids are constituted
 hierarchically of smaller ones. 
@@
 A large number of these small voids are embedded in overdense regions. 
-They are visible in the middle panel of Figure \ref{fig:FA_field} as
+They are already visible in the middle panel of Fig. \ref{fig:FA_field} as
 tiny white bubbles located inside sheets.
@@
 Comparing the abundance of large voids in the two web schemes, we find
-that the V-Web is limited to have voids on the scale of $\sim 10$\hMpc,
-while the T-Web scheme includes voids as large as $\sim 15$\hMpc. 
-Large voids in the T-Web scheme have a velocity structure that
-induces a split by the watershed algorithm in the V-Web. 
+that the largest voids in the V-Web have $r_{\rm eff}\sim 10$\hMpc,
+while the T-Web scheme includes voids as large as $r_{\rm eff}\sim 15$\hMpc. 
+This suggests that large voids in the T-Web scheme have a velocity
+structure that splits them in the V-Web. 
 This increased granularity in the velocity structure of voids is
-evident in the left and right panels of Figure \ref{fig:FA_field}.
+evident in the left and right panels of Fig. \ref{fig:FA_field}.
 
@@
 presence/absence of an overdense matter ridge in their density
-profiles. This result was also found by \citet{Ceccarelli13} when analysing
-voids in the SDSS.
+profiles. 
 To discriminate each void in one of the families we use the
@@
 
-In Figure \ref{fig:density_profile} we show the density and velocity profiles
+In Fig. \ref{fig:density_profile} we show the density and velocity profiles
 of voids splitted in these two families. 
@@
 We calculate the contrast density, radial-projected velocity and 
-FA profiles. For this purpose we catalogue all the voids in several radial 
-bins in order to capture possible size effects; moreover we show profiles 
-for both, subcompensated and overcompensated voids. Then, for each void, 
+FA profiles. 
+For this purpose we stack voids with similar effective radius.
+We also compute the profiles separately  for subcompensated and
+overcompensated voids. 
+For each void,  
 we take the distance of each member cell to the void centre along with the 
-properties of interest. Normalizing these distances with the effective 
-radius, we stack all the voids of a radial bin in order to compute the 
-radial profiles.
-
-Figure \ref{fig:density_profile} shows the results of stacked density
+properties of interest. 
+We normalize the radial distance with the effective radius and add the
+result to the stack.
+
+Fig. \ref{fig:density_profile} shows the results of stacked density
 profiles for different void sizes.  
-We normalize the radial coordinate with the effective radius to check
-for possible universal features among voids. 
 We calculate the profile out to a radius $8\ \reff$  to capture the
@@
 
-A first interesting result is the overdensity value at the void's
+The first interesting result is the overdensity value at the void's
 center.
@@
 The largest voids ($8.3-12\ \hMpc$) have an underdensity
-$\approx-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\approx 
+$\sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
 -0.8$ at their centers.
 This holds for both web schemes. 
-
 These values are consistent with most of the void finding schemes
@@
 This suggests that smaller subcompensated voids are embedded into low
-density structures like voids or walls, while large subcompensated
-voids are surrounded  by dense structures, reaching the mean density
-at lower effective radii than smaller voids.
-In overcompensated voids larger voids reach first  both the
+density structures, while large subcompensated voids are surrounded
+by dense structures, reaching the mean density at lower effective
+radii than smaller voids. 
+In the overcompensated case larger voids reach first  both the
 compensation ridge and then the mean density value.
@@
 
-In Figure \ref{fig:velocity_profile} we present the radial velocity
+In Fig. \ref{fig:velocity_profile} we present the radial velocity
 profiles. 
@@
 
-Figure \ref{fig:FA_profile} shows the results for the FA profiles.
+Fig. \ref{fig:FA_profile} shows the results for the FA profiles.
 We find that the FA clearly magnifies the difference between the
@@
 The central FA values also show a magnified trend with the void size. 
-Larger voids have lower FA values, more clearly than the same trend
+Large voids have lower FA values, amplifying the same trend
 observed with the central density value. 
-The voids in the V-Web scheme span a larger range of central FA values
-than in the T-Web scheme.
+Finally, we observe that voids in the V-Web scheme span a larger range
+of central FA values than in the T-Web scheme.
 
@@
 we present in sub-section \ref{subsec:watershed} to define void boundaries in
-our method.  Namely that as we increase the void boundary, we reach
+our method.  
+Namely that as we increase the void boundary, we reach
 first middle density walls, before reashing high density structures
-associated with high anisotropy, making the FA  ridge a  natural voids
-boundary instead of the density ridge.
+associated with high anisotropy. 
+This makes the FA ridge a reasonable
+boundary for voids compared to the traditional definition that puts
+the boundary at the density ridge.
 
 We recognize that our choice produces smaller voids as compared with
-other voids finding methods, however this has the advantage of
+other voids finding methods. 
+We consider that this has the advantage of
 avoiding the contamination from external structures.

### 2015-05-05 RefereeResponse.md
Format for the response to the Referee

Conceptual:
==

1. **It seems that part of the motivation for using FA is that it is very well correlated with lambda_1, at low lambda_1. FA is a rather interesting quantity in itself, differentiating haloes and voids from filaments and walls, but it is not clear why it should be superior to lambda_1 for void finding. The authors should more clearly articulate why this might be, if there is a reason. The FA being "conceived to quantify the anisotropy of the diffusivity of water molecules through cerebral tissue in nuclear magnetic resonance imaging" should be elaborated on; this does not clarify the usefulness of the FA for cosmologists. Conceptually, I also wonder: do filaments and walls behave differently from each other in FA, or do they both have FA ~ 1?**

2. **I did not understand the sentence at the end of Sect 2, "In this work we propose an optimal value of the threshold based on the maximization of the fractional anisotropy field in the locations label[ed] as filaments and walls," and this seems to be an important point. Is the threshold mentioned in this sentence a threshold in lambda_1, or FA? Is this the 0.95 threshold in FA? It seems to be a reasonable choice, but I do not see a sense in which it is "optimal," except that it seems to be the boundary between the FA being well-correlated with lambda_1 and not-so-well. Also, if this sentence is about the 0.95 threshold, I do not see why it "does not enter into our computations," since the boundary of many voids will depend on this threshold. It would be useful to know for what fraction of voids the limit FA = 0.95 actually affects the boundary (in the case of the largest voids, I suppose).**

3. **I do not see how the value of FA=0.65 (corresponding to lambda_1 = 0) is used "to remove ridges."**

4. **In Fig. 6, I only see a clear ridge in FA at r~r_eff in a few cases. the sentence in Sect. 5.5 "The difference between the radius where the density ridge is reached ([r/]reff = 3) and the radius of the FA ridge ([r/]reff = 1 ) ..." implies that I should see a ridge in FA at r~r_eff. Is this because the ridge is actually a 2D surface that is spherically averaged? It would be helpful to point this (or any other reasons) out. Also, the statement "This makes the FA ridge a reasonable boundary for voids compared to the traditional definition that puts the boundary at the density ridge" implies (perhaps unintentionally) that the FA ridge is a superior marker of the edge of a void than a density ridge. It is a physically different sort of ridge, and I agree that it is reasonable, but I do not see why it should be superior.**

5. **I am not convinced that the "tiny white bubbles located inside sheets" are embedded in overdense regions. Based just on Fig. 1, they could be physical, but small, voids. We also no nothing of their extent perpendicular to the plane of Fig. 1; we could just be looking of corners of much larger objects.**

6. **2D histograms of (lambda_1, delta) and (lambda_1, FA) are shown in Fig. 2, and I would appreciate also seeing a (FA, delta) 2D histogram, maybe with 1+delta on a log scale, which would help to clarify the physical meaning of FA.**

More minor things:
==

7. **I'm confused a bit about the middle panels of Fig. 1. The title, "Visual impresion for lambda_th=..." is strange. Aren't there several thresholds here? Also, what are the blue dots? Also "impresion" is misspelled.**

8. **Sect 3.3, 2nd paragraph: I do not see why "the analysis of [y]our results" shows that a fixed Cartesian mesh does not induce spurious results". It's true, that the results look reasonable, but I think it would be better to state something about the level of discreteness noise, e.g. the number of zero-density cells, or the minimum if there are none.**

9. **Sect. 5.4: The sentence "subcompensated voids have outflowing ve- locity profiles all the way up to the effective radius where the average radial density reaches the average value" is a bit confusing; this is not r_eff, right? If so, this statement seems to be an understatement (v_r >0 out to several r_eff, typically). If not, "effective" should be removed for clarity.**

10. **In Sect. 5.5, there are a few instances where I think you meant "r/r_eff =" instead of "r_eff =".**

11. **All quantities are computed at the pixel scale, ~1 Mpc/h, correct? If the authors have any insights about how the results would change if this scale were changed, it would be helpful to state them. A quantitative discussion of how some results would change with a different scale would be great, but not necessary.**

12. **Finally, about the necessity of color: Figs 4-6, as they currently are, require color, but it would be easy for the authors to use different linestyles, as well, to make color unnecessary.**

### 2015-05-13 cosmic_voids.tex
Slide of voids colored according to their effective radius instead of a random color. Little typo.

@@
 \setlength{\abovetopsep}{4pt}
+\pdfminorversion=5
 
@@
 \newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
+\newcommand{\before}[1]{\textcolor{red}{ #1}}
+\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
 
@@
 
-The tracer that we use to define the voids is the fractional
+% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+
+\before{ The tracer that we use to define the 
+voids is the fractional anisotropy (FA) computed from the set of 
+eigenvalues of the tensor under consideration. 
+The FA was initially introduced by \citet{Basser95} to quantify the
+anisotropy degree of the diffusivity of water molecules through
+cerebral tissue in nuclear magnetic resonance
+imaging and \citet{Libeskind13} introduced this concept in the context
+of Cosmic Web classification schemes.}
+
+\after{The tracer that we use to define the voids is the fractional
 anisotropy (FA) computed from the set of eigenvalues of the tensor
@@
 anisotropy degree of the diffusivity of water molecules through
-cerebral tissue in nuclear magnetic resonance
-imaging and \citet{Libeskind13} introduced this concept in the context
-of Cosmic Web classification schemes.
+cerebral tissue in nuclear magnetic resonance imaging, thereby allowing to 
+detect structures that restrict the otherwise isotropic Brownian movement 
+of water molecules. Taking into account that this process is identical to 
+the velocity shear in the large-scale matter distribution, 
+\citet{Libeskind13} introduced the concept of the FA in the context of 
+Cosmic Web classification schemes.}
+
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
   width=0.35\textheight]{delta_L1.pdf}  
-  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
   width=0.35\textheight]{FA_L1.pdf}
-
-  \captionof{figure}{\small Overdensity (left) and Fractional
-    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
-    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
-    over all grid cells in the Bolshoi simulation. 
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{FA_delta.pdf}
+
+  \captionof{figure}{\small Overdensity (upper left) and Fractional
+    Anisotropy (upper right) with respect to the eigenvalue $\lambda_1$ 
+    for each web scheme (T-Web, continous lines. V-Web, dashed lines) 
+    calculated over all grid cells in the Bolshoi simulation. 
     Thick central lines are the median and filled regions include
-    $50\%$ of the cells in each bin.
-    This information is necesary to define void boundaries in
-    the watershed algorithm. 
-    The vertical lines show the equivalent threshold values for the
-    T-Web and V-web in order to have voids composed by cells with
-    Fractional Anisotrop equal or less than $0.95$. 
-   This threshold on the eigenvalues does not influence our
-   computations. 
-   We show it as a guide to readers familiar with the
+    $50\%$ of the cells in each bin. This information is necessary to 
+    define void boundaries in the watershed algorithm. The vertical lines 
+    show the equivalent threshold values for the T-Web and V-web in order 
+    to have voids composed by cells with Fractional Anisotrop equal or 
+    less than $0.95$. This threshold on the eigenvalues does not influence 
+    our computations. We show it as a guide to readers familiar with the
     order of magnitude expectation for this threshold.}
@@
 
-The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
+% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+
+\before{The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
 conceived to quantify the anisotropy of the diffusivity of water
@@
 Here we present the FA, much in the same way as \citet{Libeskind13},
-to use it as a tracer of cosmic voids.
+to use it as a tracer of cosmic voids.}
+
+\after{The fractional anisotropy (FA), as developed by \citet{Basser95}, 
+was conceived to quantify the anisotropy of the diffusivity of water
+molecules through cerebral tissue in nuclear magnetic resonance imaging. 
+In this manner, barriers such as microtubules and cell membranes, that 
+restrict the otherwise isotropic Brownian motion of water molecules, can 
+be detected. In a cosmological context, the problem of finding structures 
+is very similar, where filaments and sheets restrict the otherwise 
+isotropic collapsing/expanding dynamics of the matter. Taking this into 
+account, we present here the FA, much in the same way as \citet{Libeskind13}, 
+to use it as a tracer of cosmic voids.}
+
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 overdensity has a large scatter at fixed $\lambda_1$.
+
+% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+\after{At this point, the eigenvalue $\lambda_1$ and the FA appear to be
+equally potential candidates for tracing cosmic voids, however, }
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 Namely that as we increase the void boundary, we reach
-first middle density walls, before reashing high density structures
+first middle density walls, before reaching high density structures
 associated with high anisotropy. 

### 2015-05-13 bench/codes_analysis/FA_histograms.py
New figure with histograms of FA for each environment

@@ -1,0 +1,65 @@
+#FA_histograms.py
+#
+#This code builds an histogram of all cells in the simulation classified into four different regions
+#and store the abundances for each range of FA
+#Usage: FA_histograms.py <Tweb or Vweb>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Web Scheme
+web = sys.argv[1]
+#Smooth parameter
+smooth = '_s1'
+#Range of FA
+FA_min = 0
+FA_max = 1.05
+#Number of bins
+N_FA = 200
+FAs = np.linspace( FA_min, FA_max, N_FA + 1 )
+
+#Values to evaluate lambda_th
+if web == 'Tweb':
+    Lambda = 0.265
+if web == 'Vweb':
+    Lambda = 0.175
+    
+#==================================================================================================
+#			CONSTRUCTING MEDIANS OF DENSITY REGARDING LAMBDA_1
+#==================================================================================================
+
+print simulation
+
+#Eigenvector web filename
+eig_filename = '%s%s%s/%d/Eigen%s'%(foldglobal,simulation,web,N_sec,smooth)
+
+#Loading eigenvectors
+eig1 = read_CIC_scalar( eig_filename+"_1" )
+eig1 = eig1.flatten()
+eig2 = read_CIC_scalar( eig_filename+"_2" )
+eig2 = eig2.flatten()
+eig3 = read_CIC_scalar( eig_filename+"_3" )
+eig3 = eig3.flatten()
+
+#Calculating FA
+FA = Fractional_Anisotropy( eig1, eig2, eig3 )
+
+#Calculating scheme
+scheme = Scheme_flatten( eig1, eig2, eig3, Lambda )
+
+#Initializing histograms
+FA_hist = np.zeros( (N_FA,5) )
+FA_hist[:,0] = FAs[:-1]
+for i_fa in xrange(N_FA):
+    for env in xrange(4):
+	FA_hist[i_fa,env+1] = (( FA[scheme==env]>=FAs[i_fa] )&( FA[scheme==env]<FAs[i_fa+1] )).sum()
+
+np.savetxt( '%sFA_Environment_%s.dat'%(data_figures_fold,web), FA_hist )

### 2015-05-13 bench/codes_analysis/_Head.py

@@ -36,6 +36,51 @@ figures_fold = '../../figures/'
 #==================================================================================================
 
 #..................................................................................................
+#Read a scalar binary field
+#..................................................................................................
+def read_CIC_scalar(filename):
+    f = open(filename, "rb")
+    dumb = f.read(38)
+
+    dumb = f.read(4)
+    n_x = f.read(4)
+    n_y = f.read(4)
+    n_z = f.read(4)
+    nodes = f.read(4)
+    x0 = f.read(4)
+    y0 = f.read(4)
+    z0 = f.read(4)
+    dx = f.read(4)
+    dy = f.read(4)
+    dz = f.read(4)
+    dumb = f.read(4)
+
+    n_x = (unpack('i', n_x))[0]
+    n_y = (unpack('i', n_y))[0]
+    n_z = (unpack('i', n_z))[0]
+    nodes = (unpack('i', nodes))[0]
+    dx = (unpack('f', dx))[0]
+    dy = (unpack('f', dy))[0]
+    dz = (unpack('f', dz))[0]
+    x0 = (unpack('f', x0))[0]
+    y0 = (unpack('f', y0))[0]
+    z0 = (unpack('f', z0))[0]
+    print n_x, n_y, n_z, nodes, dx, dy, dz
+
+    total_nodes = n_x * n_y *n_z
+    dumb = f.read(4)
+    array_data = f.read(total_nodes*4)
+    dumb = f.read(4)
+    format_s = str(total_nodes)+'f'
+    array_data = unpack(format_s, array_data)
+    f.close()
+    array_data  = np.array(array_data)
+    array_data.resize(n_z,n_y,n_x)
+    array_data = array_data.transpose()
+    return array_data
+  
+  
+#..................................................................................................
 #Cutting Halos in X axe
 #..................................................................................................
 def CutHaloX( X, thick, catalogue, plot=True, color='black' ):
@@ -257,6 +302,14 @@ def Scheme( eig1, eig2, eig3, Lamb ):
 		sch[i,j] += 1
 	    if eig3[i,j] > Lamb:
 		sch[i,j] += 1
+    return sch
+    
+    
+#..................................................................................................
+#Classification Scheme Flatten
+#..................................................................................................
+def Scheme_flatten( eig1, eig2, eig3, Lamb ):
+    sch = (eig1 > Lamb).astype(int) + (eig2 > Lamb).astype(int) + (eig3 > Lamb).astype(int)
     return sch
     
     

### 2015-05-13 bench/codes_figures/FA_environment_histogram.py

@@ -1,0 +1,69 @@
+#FA_environment_histogram.py
+#
+#This code plots histograms for each environment according to different ranges of FA
+#Usage: FA_environment_histogram.py <show(0) or save(1)>
+#
+#by: Sebastian Bustamante
+
+execfile('_Head.py')
+
+#==================================================================================================
+#			PARAMETERS
+#==================================================================================================
+#Simulation
+simulation = "BOLSHOI/"
+#Number of sections
+N_sec = 256
+#Smooth parameter
+smooth = '_s1'
+#Web Scheme
+webs = ['Tweb', 'Vweb']
+#Colors and labels
+colors = [ 'black', 'blue', 'red', 'green' ]
+#Linestyles
+linestyles = ["-", "--", "-.", ":"]
+linewidths = [2,2,2,3]
+#Labels
+labels = ["voids", "sheets", "filaments", "knots"]
+
+#==================================================================================================
+#Typical halo mass for each environment
+#==================================================================================================
+#Colors
+plt.figure( figsize=(5.8,5) )
+
+i_web = 0
+for web in webs:
+    #Loading files with quartiles
+    histogram = np.loadtxt( '%sFA_Environment_%s.dat'%(data_figures_fold,web) )
+
+    for env in xrange(4):
+	  plt.subplot(2,1,i_web+1)
+	  hist, bins = np.histogram( histogram[:,0], bins = 50, weights = histogram[:,env+1], density=True )
+	  if env == 0:
+	      hist[bins[:-1]>0.95]=0
+	  plt.plot( bins[:-1], hist, ls = linestyles[env], lw = linewidths[env],\
+	  label = labels[env], color=colors[env] )
+	
+    i_web += 1
+
+plt.subplot(2,1,1)
+plt.legend( loc="upper left", fancybox=True, shadow=True, fontsize=12, ncol=2 )
+plt.grid()
+plt.xlim((0,1))
+plt.ylim((0,25))
+plt.ylabel("Probability Density $P(FA)$", fontsize = 11)
+plt.text( 0.02, 6, "Tweb" )
+
+plt.subplot(2,1,2)
+plt.grid()
+plt.xlim((0,1))
+plt.ylim((0,25))
+plt.xlabel("FA")
+plt.ylabel("Probability Density $P(FA)$", fontsize = 11)
+plt.text( 0.02, 6, "Vweb" )
+
+if sys.argv[1] == '1':
+    plt.savefig( '%sFA_environment.pdf'%(figures_fold) )
+else:
+    plt.show()

### 2015-05-13 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -56,6 +56,10 @@ alphas = np.ones( cmap2.N+3)
 alphas[0] = 0
 cmap2._lut[:,-1] = alphas
 
+#Effective radius function
+def r_eff(X):
+    return ((10**np.log10(X)*(0.9765625)**3)/( 4*np.pi/3. ))**(1/3.)
+
 #==================================================================================================
 #			PLOTING WEB SCHEME AND DENSITY FIELD FOR SIMULATION
 #==================================================================================================
@@ -85,6 +89,8 @@ GH = np.loadtxt('%s%sC_GH_%s.dat'%(foldglobal,simulation,catalog))
 #Catalogue of voids
 voids = CutFieldZ( "%s/%s/%s/%d/voids%s/voids_%s/void_index.dat"%\
 (foldglobal, simulation, web, N_sec, void_scheme, config ), Cut, 'plain', Coor = axe )
+sizes = r_eff( np.loadtxt( "%s/%s/%s/%d/voids%s/voids_%s/void_regions.dat"%\
+(foldglobal, simulation, web, N_sec, void_scheme, config ), usecols=(1,) ) )
 
 #Loading Fields
 #delta = CutFieldZ( delta_filename, Cut, 32, Coor = axe )
@@ -111,7 +117,7 @@ for i in xrange(N_sec):
 		if j + jc >= N_sec: jt = 0
 		if j + jc < 0: jt = N_sec-1
 		#Marking contours
-		if( voids[i,j] != voids[it,jt] ):
+		if( voids[i,j] != voids[it,jt] and contours[it,jt] == 0 ):
 		    contours[i,j] = 1
 
 #FA field
@@ -123,9 +129,10 @@ plt.imshow( np.transpose(Fractional_Anisotropy( eig1, eig2, eig3 )[::,::-1]), ex
 plt.title( "Fractional Anisotropy (%s)"%web )
 plt.yticks( (),() )
 plt.xticks( (0,Box_L) )
-plt.xlabel( "[	$h^{-1}$ Mpc]" )
+#plt.xlabel( "[$h^{-1}$ Mpc]" )
 
-#plt.colorbar( orientation = "horizontal", fraction = 0.03, pad = 0.025 )
+#COLOR BAR
+plt.colorbar( orientation = "horizontal", fraction = 0.03, pad = 0.025 )
 
 
 #Visual impression
[…]

### 2015-05-13 cosmic_voids.tex
New figure with histograms of FA for each environment
Removing halos from visual impression. New caption of figure 1

@@
     (middle) where voids are white, sheets are light gray, filaments
-    are dark gray and knots are black; colored individual
-    voids (right) found by the a watershed algorithm on the Fractional
-    Anisotropy field. Top/bottom corresponds to the T-Web/V-Web.}
+    are dark gray and knots are black; individual voids (right) found by 
+    the a watershed algorithm on the Fractional Anisotropy field. Colours
+    correspond with the effective radius of each void. Top/bottom
+    corresponds to the T-Web/V-Web.}
   \label{fig:FA_field}
@@
   width=0.35\textheight]{FA_delta.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{FA_environment.pdf}
 

### 2015-05-13 bench/codes_figures/FA_delta_correlation.py

@@ -46,7 +46,7 @@ for web in webs:
     
     plt.grid(1)
     plt.ylabel( 'FA', fontsize = 12 )
-    plt.xlabel( '$\log_{10}(\delta+1)$', fontsize = 12)
+    plt.xlabel( '$\delta+1$', fontsize = 12)
     plt.xlim( (0.025,10) )
     plt.ylim( (0,1) )
     plt.legend( loc='lower right', fancybox = True, shadow = True, ncol = 1, prop={'size':10} )

### 2015-05-13 bench/codes_figures/cosmicweb_fractional_anisotropy.py

@@ -138,7 +138,7 @@ plt.colorbar( orientation = "horizontal", fraction = 0.03, pad = 0.025 )
 #Visual impression
 plt.subplot( 1, 3, 2 )
 Coor, X = CutHaloZ( Cut*Box_L/(1.0*N_sec)-dx/2.0, dx, GH, plot = False )
-plt.plot( Coor[0], Coor[1], '.', color = 'blue', markersize = 1 )
+#plt.plot( Coor[0], Coor[1], '.', color = 'blue', markersize = 1 )
 plt.imshow( -np.transpose(Scheme( eig1, eig2, eig3, Lambda_opt )[::,::-1]), extent = extent, vmin=-3, vmax=0, cmap = my_cmap4 )
 plt.title( "Visual impression for $\lambda_{th} = %1.3f$"%(Lambda_opt) )
 plt.yticks( (),() )

### 2015-05-19 RefereeResponse.md
Response of the first issue. New figure and explanations

@@
 Conceptually, I also wonder: do filaments and walls behave differently from each other in FA, or do they both have FA ~ 1?**
+
+      Response: 
+      - Although lambda_1 is the defining property of voids when using the T-web/V-web (1st paragraph of subsec 3.2.), the FA exihibit a key advantage that makes it a better void tracer (please refer to 3rd paragraph of subsec.
+3.2 of the new version).
+      - Now it is explicitly explained why the FA, as defined in the context of MRI, is useful to cosmologist (6th paragraph of introduction and 1st paragraph of subsec 3.1).
+      - A new figure (Fig 3.) was prepared. Histograms of the volume contribution of each environment for each value of the FA (3rd paragraph of subsec. 3.2).
 

### 2015-05-19 cosmic_voids.tex
Response of the first issue. New figure and explanations

@@
 %FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{figure*}
+\begin{figure}
 \centering
@@
   \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{delta_L1.pdf}  
+  width=0.30\textheight]{delta_L1.pdf}
   \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{FA_L1.pdf}
+  width=0.30\textheight]{FA_L1.pdf}  
   \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{FA_delta.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{FA_environment.pdf}
-
-  \captionof{figure}{\small Overdensity (upper left) and Fractional
-    Anisotropy (upper right) with respect to the eigenvalue $\lambda_1$ 
-    for each web scheme (T-Web, continous lines. V-Web, dashed lines) 
-    calculated over all grid cells in the Bolshoi simulation. 
+  width=0.30\textheight]{FA_delta.pdf}
+
+  \captionof{figure}{\small Density contrast (top) and Fractional
+    Anisotropy (middle) with respect to the eigenvalue $\lambda_1$ 
+    and with respect to each other (bottom) for each web scheme (T-Web, 
+    continous lines. V-Web, dashed lines) calculated over all grid cells 
+    in the Bolshoi simulation. 
     Thick central lines are the median and filled regions include
@@
 
-\end{figure*}
+\end{figure}
+%.........................................................................
+
+%-------------------------------------------------------------------------
+%FIGURE 3: Histograms for each environment regarding the FA value
+\begin{figure}
+\centering
+
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{FA_environment.pdf}
+
+  \captionof{figure}{\small Volume of each environment per FA 
+  ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA ($dV/dFA$).
+  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
+  each line represents the volume contribution of the respective 
+  environment to the total volume with the same FA value. Above FA=0.95,
+  only sheets and filaments contribute to all the volume of the simulation
+  within that range of FA.}
+  \label{fig:FA_environment}
+
+\end{figure}
 %.........................................................................
@@
 
-In Fig. \ref{fig:L1_correlations} we show that the these two values
+% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+\before{In Fig. \ref{fig:L1_correlations} we show that the these two values
 are indeed closely correlated.  
@@
 correlation between $\lambda_1$ and the FA. This shows that the
-overdensity has a large scatter at fixed $\lambda_1$.
-
-% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+overdensity has a large scatter at fixed $\lambda_1$.}
+
+\after{In Fig. \ref{fig:L1_correlations} we show that the these two values
+are indeed closely correlated.  The top panel shows the correlation between 
+$\lambda_1$ and $\delta$ for all the grid cells in the simulation while the 
+bottom panel shows the correlation between $\lambda_1$ and the FA. The middle 
+panel shows the correlation between $\delta$ and the FA. This shows that the 
+density has a larger scatter at fixed $\lambda_1$ than the FA, yet large and 
+small values of the density remain still associated to low values of the FA.}
+
 \after{At this point, the eigenvalue $\lambda_1$ and the FA appear to be
-equally potential candidates for tracing cosmic voids, however, }
+equally potential candidates for tracing cosmic voids, however, the 
+eigenvalue $\lambda_1$ presents, along with the density, an undesirable 
+feature for a void tracer. As we move out from inner parts of voids to outer 
+parts, $\lambda_1$ and the density increase monotonically, making unclear 
+where to set the frontier of voids. On the other hand, the FA naturally 
+indicates the real frontier as regions where anisotropic collapse begin to 
+dominate, which, according to Fig. \ref{fig:FA_environment}, are associated
+mainly to sheets and, to a lesser extent, to filaments.}
 %!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
@@
 %.........................................................................
-%FIGURE 3: volume functions
+%FIGURE 4: volume functions
 \begin{figure*}
@@
 %.........................................................................
-%FIGURE 4: Density profile of voids for each defined scheme
+%FIGURE 5: Density profile of voids for each defined scheme
 \begin{figure*}

### 2015-05-20 RefereeResponse.md
New issues solved

@@
 
-1.
-**It seems that part of the motivation for using FA is that it is very well correlated with lambda_1, at low lambda_1.
-FA is a rather interesting quantity in itself, differentiating haloes and voids from filaments and walls, but it is not clear why it should be superior to lambda_1 for void finding.
-The authors should more clearly articulate why this might be, if there is a reason.
-The FA being "conceived to quantify the anisotropy of the diffusivity of water molecules through cerebral tissue in nuclear magnetic resonance imaging" should be elaborated on; this does not clarify the usefulness of the FA for cosmologists.
-Conceptually, I also wonder: do filaments and walls behave differently from each other in FA, or do they both have FA ~ 1?**
+1. **It seems that part of the motivation for using FA is that it is very well correlated with lambda_1, 
+    at low lambda_1. FA is a rather interesting quantity in itself, differentiating haloes and voids from 
+    filaments and walls, but it is not clear why it should be superior to lambda_1 for void finding. The 
+    authors should more clearly articulate why this might be, if there is a reason. The FA being "conceived 
+    to quantify the anisotropy of the diffusivity of water molecules through cerebral tissue in nuclear 
+    magnetic resonance imaging" should be elaborated on; this does not clarify the usefulness of the FA for 
+    cosmologists. Conceptually, I also wonder: do filaments and walls behave differently from each other in 
+    FA, or do they both have FA ~ 1?**
 
       Response: 
-      - Although lambda_1 is the defining property of voids when using the T-web/V-web (1st paragraph of subsec 3.2.), the FA exihibit a key advantage that makes it a better void tracer (please refer to 3rd paragraph of subsec.
-3.2 of the new version).
-      - Now it is explicitly explained why the FA, as defined in the context of MRI, is useful to cosmologist (6th paragraph of introduction and 1st paragraph of subsec 3.1).
-      - A new figure (Fig 3.) was prepared. Histograms of the volume contribution of each environment for each value of the FA (3rd paragraph of subsec. 3.2).
+      - Although lambda_1 is the defining property of voids when using the T-web/V-web (1st paragraph of 
+	subsec 3.2), the FA exihibit a key advantage that makes it a better void tracer (please refer to 
+	3rd paragraph of subsec. 3.2 of the new version).
+      - Now it is explicitly explained why the FA, as defined in the context of MRI, is useful to cosmologist 
+	(6th paragraph of introduction and 1st paragraph of subsec 3.1).
+      - A new figure (Fig 3.) was prepared. Histograms of the volume contribution of each environment for 
+	each value of the FA (3rd paragraph of subsec. 3.2). Sheets (mainly) and filaments are clearly 
+	associated with high values of the FA.
 
-2.
-**I did not understand the sentence at the end of Sect 2, "In this work we propose an optimal value of the threshold based on the maximization of the fractional anisotropy field in the locations label[ed] as filaments and walls," and this seems to be an important point.
-Is the threshold mentioned in this sentence a threshold in lambda_1, or FA?
-Is this the 0.95 threshold in FA?
-It seems to be a reasonable choice, but I do not see a sense in which it is "optimal," except that it seems to be the boundary between the FA being well-correlated with lambda_1 and not-so-well.
-Also, if this sentence is about the 0.95 threshold, I do not see why it "does not enter into our computations," since the boundary of many voids will depend on this threshold.
-It would be useful to know for what fraction of voids the limit FA = 0.95 actually affects the boundary (in the case of the largest voids, I suppose).**
+2. **I did not understand the sentence at the end of Sect 2, "In this work we propose an optimal value of 
+    the threshold based on the maximization of the fractional anisotropy field in the locations label[ed] 
+    as filaments and walls," and this seems to be an important point. Is the threshold mentioned in this 
+    sentence a threshold in lambda_1, or FA? Is this the 0.95 threshold in FA? It seems to be a reasonable 
+    choice, but I do not see a sense in which it is "optimal," except that it seems to be the boundary 
+    between the FA being well-correlated with lambda_1 and not-so-well. Also, if this sentence is about the 
+    0.95 threshold, I do not see why it "does not enter into our computations," since the boundary of many 
+    voids will depend on this threshold. It would be useful to know for what fraction of voids the limit 
+    FA = 0.95 actually affects the boundary (in the case of the largest voids, I suppose).**
 
@@
 
-4.
-**In Fig.
-6, I only see a clear ridge in FA at r~r_eff in a few cases.
-the sentence in Sect.
-5.5 "The difference between the radius where the density ridge is reached ([r/]reff = 3) and the radius of the FA ridge ([r/]reff = 1 ) ..." implies that I should see a ridge in FA at r~r_eff.
-Is this because the ridge is actually a 2D surface that is spherically averaged?
-It would be helpful to point this (or any other reasons) out.
-Also, the statement "This makes the FA ridge a reasonable boundary for voids compared to the traditional definition that puts the boundary at the density ridge" implies (perhaps unintentionally) that the FA ridge is a superior marker of the edge of a void than a density ridge.
-It is a physically different sort of ridge, and I agree that it is reasonable, but I do not see why it should be superior.**
+    Response: 
+    - We have added a clearer explanation of the ridge removing procedure (3rd paragraph of subsec. 3.3).
 
-5.
-**I am not convinced that the "tiny white bubbles located inside sheets" are embedded in overdense regions.
-Based just on Fig.
-1, they could be physical, but small, voids.
-We also no nothing of their extent perpendicular to the plane of Fig.
-1; we could just be looking of corners of much larger objects.**
+4. **In Fig. 6, I only see a clear ridge in FA at r~r_eff in a few cases. the sentence in Sect. 5.5 "The 
+    difference between the radius where the density ridge is reached ([r/]reff = 3) and the radius of the 
+    FA ridge ([r/]reff = 1 ) ..." implies that I should see a ridge in FA at r~r_eff. Is this because the 
+    ridge is actually a 2D surface that is spherically averaged? It would be helpful to point this (or any 
+    other reasons) out. Also, the statement "This makes the FA ridge a reasonable boundary for voids compared 
+    to the traditional definition that puts the boundary at the density ridge" implies (perhaps 
+    unintentionally) that the FA ridge is a superior marker of the edge of a void than a density ridge. It is 
+    a physically different sort of ridge, and I agree that it is reasonable, but I do not see why it should 
+    be superior.**
 
-6.
-**2D histograms of (lambda_1, delta) and (lambda_1, FA) are shown in Fig.
-2, and I would appreciate also seeing a (FA, delta) 2D histogram, maybe with 1+delta on a log scale, which would help to clarify the physical meaning of FA.**
+5. **I am not convinced that the "tiny white bubbles located inside sheets" are embedded in overdense regions. 
+    Based just on Fig. 1, they could be physical, but small, voids. We also no nothing of their extent 
+    perpendicular to the plane of Fig. 1; we could just be looking of corners of much larger objects.**
+
+    Response:
+    - In Right panels of Fig. 1, the color of each void refers now the effective radius. The size can now be
+      inferred from the figure. Small voids are indeed located inside sheets and filaments.
+
+6. **2D histograms of (lambda_1, delta) and (lambda_1, FA) are shown in Fig. 2, and I would appreciate also 
+    seeing a (FA, delta) 2D histogram, maybe with 1+delta on a log scale, which would help to clarify the 
+    physical meaning of FA.**
+
+    Response: 
+    - The requested histogram has been added as the bottom panel of Fig. 2. This shows that lower values of
+      the FA are associated to small (voids) and large values (clusters) of the density.
 
@@
 
-7.
-**I'm confused a bit about the middle panels of Fig.
-1.
-The title, "Visual impresion for lambda_th=..." is strange.
-Aren't there several thresholds here?
-Also, what are the blue dots?
-Also "impresion" is misspelled.**
+7. **I'm confused a bit about the middle panels of Fig. 1. The title, "Visual impresion for lambda_th=..." 
+    is strange. Aren't there several thresholds here? Also, what are the blue dots? Also "impresion" is 
+    misspelled.**
 
-8.
-**Sect 3.3, 2nd paragraph: I do not see why "the analysis of [y]our results" shows that a fixed Cartesian mesh does not induce spurious results".
-It's true, that the results look reasonable, but I think it would be better to state something about the level of discreteness noise, e.g.
-the number of zero-density cells, or the minimum if there are none.**
+    Response:
+    - For each cell, the environment is determined according the relative strenght of each eigenvalue with
+      respect to the lambda_th value, so only a threshold is required (please refer to 2nd paragraph of subsec. 
+      2.1). Blue dots were dark matter halos (FOF), but we have deleted them for clarity. Typo "impresion" 
+      also corrected.
 
-9.
-**Sect.
-5.4: The sentence "subcompensated voids have outflowing ve- locity profiles all the way up to the effective radius where the average radial density reaches the average value" is a bit confusing; this is not r_eff, right?
-If so, this statement seems to be an understatement (v_r >0 out to several r_eff, typically).
-If not, "effective" should be removed for clarity.**
+8. **Sect 3.3, 2nd paragraph: I do not see why "the analysis of [y]our results" shows that a fixed Cartesian 
+    mesh does not induce spurious results". It's true, that the results look reasonable, but I think it would 
+    be better to state something about the level of discreteness noise, e.g. the number of zero-density cells, 
+    or the minimum if there are none.**
+
+9. **Sect. 5.4: The sentence "subcompensated voids have outflowing ve- locity profiles all the way up to the 
+    effective radius where the average radial density reaches the average value" is a bit confusing; this is 
+    not r_eff, right? If so, this statement seems to be an understatement (v_r >0 out to several r_eff, 
+    typically). If not, "effective" should be removed for clarity.**
 
@@
 
-11.
-**All quantities are computed at the pixel scale, ~1 Mpc/h, correct?
-If the authors have any insights about how the results would change if this scale were changed, it would be helpful to state them.
-A quantitative discussion of how some results would change with a different scale would be great, but not necessary.**
+11. **All quantities are computed at the pixel scale, ~1 Mpc/h, correct? If the authors have any insights about 
+    how the results would change if this scale were changed, it would be helpful to state them. A quantitative 
+    discussion of how some results would change with a different scale would be great, but not necessary.**
 
-12. **Finally, about the necessity of color: Figs 4-6, as they currently are, require color, but it would be easy for the authors to use different linestyles, as well, to make color unnecessary.**
+12. **Finally, about the necessity of color: Figs 4-6, as they currently are, require color, but it would be 
+    easy for the authors to use different linestyles, as well, to make color unnecessary.**
+
+    Response:
+    - These figures have already different linewidths for each bin. We think it might be easier to have 6 
+      different widths than 6 different linestyles.

### 2015-05-20 cosmic_voids.tex
New issues solved

@@
 
-% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 
-% CORRECTION: ISSUE 1 !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 \before{In Fig. \ref{fig:L1_correlations} we show that the these two values
@@
 
-The watershed algorithm also needs a threshold value to reduce
+% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+\before{The watershed algorithm also needs a threshold value to reduce
 spurious features and prevent void hierarchization.  
@@
 In our case we have to find a corresponding FA value
-to define this threshold.
+to define this threshold.}
+
+\after{The watershed algorithm also needs a threshold value to reduce
+spurious features and prevent void hierarchization.  
+If the density field is used, a typical threshold is
+$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbour 
+voids, if the mean value of the density across their common boundary is 
+below that threshold, both voids are taken as just one void.
+In our case we have to find a corresponding FA value
+to define this threshold.}
+%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 

### 2015-05-26 RefereeResponse.md
solved issue #17, caption in Figure 1

@@
 
-7. **I'm confused a bit about the middle panels of Fig. 1. The title, "Visual impresion for lambda_th=..." 
-    is strange. Aren't there several thresholds here? Also, what are the blue dots? Also "impresion" is 
-    misspelled.**
+7. **I'm confused a bit about the middle panels of Fig. 1. The title,
+    "Visual impresion for lambda_th=..."  is strange. Aren't there
+    several thresholds here? Also, what are the blue dots? Also
+    "impresion" is  misspelled.**
 
     Response:
-    - For each cell, the environment is determined according the relative strenght of each eigenvalue with
-      respect to the lambda_th value, so only a threshold is required (please refer to 2nd paragraph of subsec. 
-      2.1). Blue dots were dark matter halos (FOF), but we have deleted them for clarity. Typo "impresion" 
-      also corrected.
+    - We have rewritten the caption. There are two different
+    thresholds, one for each web finder. Blue dots were dark matter
+    halos (FOF). We removed them for clarity. The typo ("impresion")
+    is  also corrected.
 

### 2015-05-26 cosmic_voids.tex
solved issue #17, caption in Figure 1

@@
   width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
-  \caption{Visual impression of different fields in a slice of
-    $1\hMpc$ width in the Bolshoi simulation.   
+  \caption{Different fields in a slice of
+    $1\hMpc$ width in the Bolshoi simulation. Top/bottom panels correspond
+    to the T-Web/V-Web.      
     Fractional Anisotropy field (left); cosmic web classification
-    (middle) where voids are white, sheets are light gray, filaments
-    are dark gray and knots are black; individual voids (right) found by 
+    (middle) for a given value of the threhold eigenvalue
+    $\lambda_{\rm th}$ where voids are white, sheets are light gray,
+    filaments are dark gray and knots are black; individual voids (right) found by 
     the a watershed algorithm on the Fractional Anisotropy field. Colours
-    correspond with the effective radius of each void. Top/bottom
-    corresponds to the T-Web/V-Web.}
+    in the right panels correspond with the effective radius of each void. }
   \label{fig:FA_field}

### 2015-05-26 cosmic_voids.tex
resuelto issue #18 sobre la seccion 3.3 y el sampleo en grid cartesiana

@@
 \citep{Schaap00}.
-However, from the analysis of our results the choice of a fixed
+\before{However, from the analysis of our results the choice of a fixed
 Cartesian mesh does not induce spurious results, at least with
-the mass resolution we have in the N-body simulation.
+the mass resolution we have in the N-body simulation. }
+\after{Nevertheless, in our case the average number of particles per cell
+  is large enough ($512$ particles/cell) ensuring that the lowest
+  density regions are sampled with at least $\sim 10$ particles
+  ($\delta \sim-0.98$), which seems to avoid spurious results from a
+  noisy density field sampling.}
 

### 2015-05-26 cosmic_voids.tex
solved minor issue #19. statement about subcompemsated voids

@@
 
-We find that subcompensated voids have outflowing velocity profiles
+\before{We find that subcompensated voids have outflowing velocity profiles
 all the way up to the effective radius where the average radial
-density reaches the average value.
+density reaches the average value.}
+\after{We find that subcompensated voids have outflowing velocity profiles
+all the way up to the radius where the average radial
+density reaches the average value.}
 For voids with sizes $r_{\rm eff}<8\hMpc$ the outflow is always

### 2015-05-26 cosmic_voids.tex
solved minor issue #20. replaced r_eff by r/r_eff

@@
     curves correspond to the T-Web (V-Web).
-    The abundance for small ($r_{eff}<2.0\hMpc$) overcompensated voids
+    The abundance for small ($\reff <2.0\hMpc$) overcompensated voids
     shoots up in the V-Web scheme.
@@
 Comparing the abundance of large voids in the two web schemes, we find
-that the largest voids in the V-Web have $r_{\rm eff}\sim 10$\hMpc,
-while the T-Web scheme includes voids as large as $r_{\rm eff}\sim 15$\hMpc. 
+that the largest voids in the V-Web have $\reff \sim 10$\hMpc,
+while the T-Web scheme includes voids as large as $\reff \sim 15$\hMpc. 
 This suggests that large voids in the T-Web scheme have a velocity
@@
 %\midrule
-\textbf{${\bf r_{\rm eff}}$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
+\textbf{${\bf \reff }$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
 %\midrule
@@
 The largest voids ($8.3-12\ \hMpc$) have an underdensity
-$\sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
+$\delta \sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
 -0.8$ at their centers.
@@
 Our results extend the findings of \cite{Hamaus14} into the range of
-voids with size $r_{\rm eff}<10$\hMpc.
+voids with size $\reff <10$\hMpc.
 
@@
 density reaches the average value.}
-For voids with sizes $r_{\rm eff}<8\hMpc$ the outflow is always
+For voids with sizes $\reff <8\hMpc$ the outflow is always
 positive, consistent with the fact that their density profiles do not
@@
 We find that the FA clearly magnifies the difference between the
-internal profile $r_{\rm eff}<1$ and the external profile $r_{\rm
-  eff}>1$. 
+internal profile $r/\reff <1$ and the external profile $r/\reff >1$. 
 Subcompensanted voids in the T-Web reach an asymptotic background
-value of F=$0.8$ almost right at $r_{\rm eff}=2$. 
+value of F=$0.8$ almost right at $r/\reff =2$. 
 For the V-Web the results are similar, albeit rather slowly with the
@@
 Overcompensated voids reach a maximum FA at the same effective radiuus
-$r_{\rm eff}=1$ and decline to reach an asymptotic value of FA=$0.85$
+$r/\reff =1$ and decline to reach an asymptotic value of FA=$0.85$
 at larger radii.
@@
 The difference between the radius where the density ridge is reached 
-($r_{\rm eff}=3$) and the radius of the FA  ridge ($r_{\rm eff}=1$ )
+($r/\reff =3$) and the radius of the FA  ridge ($r/\reff =1$ )
 justifies in a more quantiative way the qualitative argument
@@
 In these profiles it is evident the presence of an overdense ridge
-around $2<r/r_{\rm eff}<3$ for the overcompensated voids.
+around $2<r/\reff <3$ for the overcompensated voids.
 Subcompensated voids do not show such a ridge keeping its density
-lower than the average value up to $r/r_{\rm eff}\sim 8$.
+lower than the average value up to $r/\reff \sim 8$.
 
@@
 density fields the ridge is, almost by definition, located around
-$r/r_{\rm eff}\sim 1$ and the subcompensated voids reach average
-density around $r/r_{\rm eff}\sim 3$. 
+$r/\reff \sim 1$ and the subcompensated voids reach average
+density around $r/\reff \sim 3$. 
 This indicates that voids defined by FA boundaries are smaller  than
@@
 For the subcompensated voids the FA quickly increases to FA values of 
-$\sim 0.7-0.8$ at $r/r_{\rm eff}\sim 1$ to find a plateau, which is
+$\sim 0.7-0.8$ at $r/\reff \sim 1$ to find a plateau, which is
 quite far from the limiting FA$=0.95$ suggesting that these voids are

### 2015-05-26 RefereeResponse.md
resuelto issue #18 sobre la seccion 3.3 y el sampleo en grid cartesiana
solved minor issue #19. statement about subcompemsated voids
solved minor issue #20. replaced r_eff by r/r_eff
solved minor issue #21 sobre lo que pasaria con otra smoothing scale

@@
 
-8. **Sect 3.3, 2nd paragraph: I do not see why "the analysis of [y]our results" shows that a fixed Cartesian 
-    mesh does not induce spurious results". It's true, that the results look reasonable, but I think it would 
-    be better to state something about the level of discreteness noise, e.g. the number of zero-density cells, 
-    or the minimum if there are none.**
+8. **Sect 3.3, 2nd paragraph: I do not see why "the analysis of [y]our
+    results" shows that a fixed Cartesian  mesh does not induce
+    spurious results". It's true, that the results look reasonable,
+    but I think it would  be better to state something about the level
+    of discreteness noise, e.g. the number of zero-density cells,  or
+    the minimum if there are none.**
 
-9. **Sect. 5.4: The sentence "subcompensated voids have outflowing ve- locity profiles all the way up to the 
-    effective radius where the average radial density reaches the average value" is a bit confusing; this is 
-    not r_eff, right? If so, this statement seems to be an understatement (v_r >0 out to several r_eff, 
+    Response:
+    We have rephrased this in terms of the number of particles per
+    cell in the lowest density regions.
+
+9. **Sect. 5.4: The sentence "subcompensated voids have outflowing ve-
+    locity profiles all the way up to the effective radius where the
+    average radial density reaches the average value" is a bit
+    confusing; this is not r_eff, right? If so, this statement seems
+    to be an understatement (v_r >0 out to several r_eff,
     typically). If not, "effective" should be removed for clarity.**
+
+    Response:
+    We removed "effective" for clarity.
 
@@
 
-11. **All quantities are computed at the pixel scale, ~1 Mpc/h, correct? If the authors have any insights about 
-    how the results would change if this scale were changed, it would be helpful to state them. A quantitative 
-    discussion of how some results would change with a different scale would be great, but not necessary.**
+    Response:
+    We have revised all the instances and replaced r_eff by r/r_eff
+    wherever it was appropriate.
 
-12. **Finally, about the necessity of color: Figs 4-6, as they currently are, require color, but it would be 
-    easy for the authors to use different linestyles, as well, to make color unnecessary.**
+11. **All quantities are computed at the pixel scale, ~1 Mpc/h,
+    correct? If the authors have any insights about  how the results
+    would change if this scale were changed, it would be helpful to
+    state them. A quantitative  discussion of how some results would
+    change with a different scale would be great, but not necessary.**
 
     Response:
-    - These figures have already different linewidths for each bin. We think it might be easier to have 6 
+    We now mention in the first paragraph of the Results section the
+    expected results for larger smoothing scales. Namely, that the
+    statistics for the cosmci web tend to be those of a random
+    Gaussian field.
+
+12. **Finally, about the necessity of color: Figs 4-6, as they
+currently are, require color, but it would be  easy for the authors to
+use different linestyles, as well, to make color unnecessary.**
+
+    Response:
+    - These figures have already different linewidths for each bin. We
+    think it might be easier to have 6  
       different widths than 6 different linestyles.

### 2015-05-26 cosmic_voids.tex
solved minor issue #21 sobre lo que pasaria con otra smoothing scale

@@
 smoothing length of the density field, i.e. $\sim 1$\hMpc.  
-Below that scale numerical resolution effects become important. 
+\before{Below that scale numerical resolution effects become
+  important. }
+\after{For smaller interpolation/smoothing scales the shot noise in
+  the low density regions starts to be noticeable.}
 With that choice we find a void volume filling fraction $54.88\%$ and
 $47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.  
+\after{For larger smoothing scales ($>5\hMpc$) the density and shear fields
+  tend to be Gaussian and therefore follow closely the analytical environment abundance
+  predictions for Gaussian random fields \citep{Forero09,Alonso2015}. }
 

### 2015-06-03 RefereeResponse.md
solving issue #16 (major issue)

@@
 
-1. **It seems that part of the motivation for using FA is that it is very well correlated with lambda_1, 
-    at low lambda_1. FA is a rather interesting quantity in itself, differentiating haloes and voids from 
+1. **It seems that part of the motivation for using FA is that it is
+    very well correlated with lambda_1,  at low lambda_1. FA is a
+    rather interesting quantity in itself, differentiating haloes and
+    voids from  
     filaments and walls, but it is not clear why it should be superior to lambda_1 for void finding. The 
-    authors should more clearly articulate why this might be, if there is a reason. The FA being "conceived 
-    to quantify the anisotropy of the diffusivity of water molecules through cerebral tissue in nuclear 
-    magnetic resonance imaging" should be elaborated on; this does not clarify the usefulness of the FA for 
-    cosmologists. Conceptually, I also wonder: do filaments and walls behave differently from each other in 
-    FA, or do they both have FA ~ 1?**
+    authors should more clearly articulate why this might be, if there
+    is a reason. The FA being "conceived  to quantify the anisotropy
+    of the diffusivity of water molecules through cerebral tissue in
+    nuclear  magnetic resonance imaging" should be elaborated on; this
+    does not clarify the usefulness of the FA for
+    cosmologists. Conceptually, I also wonder: do filaments and walls
+    behave differently from each other in  FA, or do they both have FA
+    ~ 1?**
 
@@
 
-6. **2D histograms of (lambda_1, delta) and (lambda_1, FA) are shown in Fig. 2, and I would appreciate also 
-    seeing a (FA, delta) 2D histogram, maybe with 1+delta on a log scale, which would help to clarify the 
-    physical meaning of FA.**
+6. **2D histograms of (lambda_1, delta) and (lambda_1, FA) are shown
+    in Fig. 2, and I would appreciate also  seeing a (FA, delta) 2D
+    histogram, maybe with 1+delta on a log scale, which would help to
+    clarify the  physical meaning of FA.**
 
     Response: 
-    - The requested histogram has been added as the bottom panel of Fig. 2. This shows that lower values of
-      the FA are associated to small (voids) and large values (clusters) of the density.
+    - We have included the new plot in Fig. 2. This shows that indeed
+    the overdensity of zero is found at the highest Fractional Anisotropy.
 

### 2015-06-03 cosmic_voids.tex
solving issue #16 (major issue)

@@
 %FIGURE 2: Distributions of FA and density regarding the Lambda_1 eigenvalue
-\begin{figure}
+\begin{figure*}
 \centering
 
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.30\textheight]{delta_L1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.30\textheight]{FA_L1.pdf}  
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.30\textheight]{FA_delta.pdf}
-
-  \captionof{figure}{\small Density contrast (top) and Fractional
-    Anisotropy (middle) with respect to the eigenvalue $\lambda_1$ 
-    and with respect to each other (bottom) for each web scheme (T-Web, 
-    continous lines. V-Web, dashed lines) calculated over all grid cells 
-    in the Bolshoi simulation. 
-    Thick central lines are the median and filled regions include
-    $50\%$ of the cells in each bin. This information is necessary to 
-    define void boundaries in the watershed algorithm. The vertical lines 
-    show the equivalent threshold values for the T-Web and V-web in order 
-    to have voids composed by cells with Fractional Anisotrop equal or 
-    less than $0.95$. This threshold on the eigenvalues does not influence 
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
+  width=0.33\textwidth]{FA_delta.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
+  width=0.33\textwidth]{delta_L1.pdf}
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
+  width=0.33\textwidth]{FA_L1.pdf}
+
+  \captionof{figure}{\small Fractional Anisotropy  as a function of
+    the overdensity (left) and the eigenvalue $\lambda_1$ (middle), and
+    density contrast (right) as a function of the
+    eigenvalue $\lambda_1$ for each web scheme (T-Web,  continous
+    lines. V-Web, dashed lines). Thick central lines are the median
+    and filled regions include $50\%$ of the cells in each bin. 
+    The left panel we confirms that underdense regions can be
+    identified with Fractional Anisotropy values less than $0.95$.
+    For this reason we define voids to be composed by cells with
+    Fractional Anisotropy equal or less than this value.
+    In the middle and right panel we show the equivalent eigenvalue
+    threshold for the T-Web and V-web corresponding to that
+    Fractional Anisotropy. 
+    This threshold on the eigenvalues does not influence 
     our computations. We show it as a guide to readers familiar with the
-    order of magnitude expectation for this threshold.}
+    order of magnitude expectation for this quantity.}
   \label{fig:L1_correlations}
 
-\end{figure}
+\end{figure*}
 %.........................................................................

### 2015-06-11 RefereeResponse.md
solved issue #15

@@
 
-5. **I am not convinced that the "tiny white bubbles located inside sheets" are embedded in overdense regions. 
-    Based just on Fig. 1, they could be physical, but small, voids. We also no nothing of their extent 
-    perpendicular to the plane of Fig. 1; we could just be looking of corners of much larger objects.**
+5. **I am not convinced that the "tiny white bubbles located inside
+sheets" are embedded in overdense regions.  Based just on Fig. 1, they
+could be physical, but small, voids. We also no nothing of their
+extent  perpendicular to the plane of Fig. 1; we could just be looking
+of corners of much larger objects.**
 
     Response:
-    - In Right panels of Fig. 1, the color of each void refers now the effective radius. The size can now be
-      inferred from the figure. Small voids are indeed located inside sheets and filaments.
+    - In the right panels of Fig. 1, the color of each void refers now
+    the effective radius. The size could be inferred from the
+    figure. We have checked by visual inspection some cases and small
+    voids are indeed located inside sheets and filaments. This was
+    already found and explained in Hoffman et al. 2012.
 

### 2015-06-11 cosmic_voids.tex
solved issue #14

@@
 The difference between the radius where the density ridge is reached 
-($r/\reff =3$) and the radius of the FA  ridge ($r/\reff =1$ )
-justifies in a more quantiative way the qualitative argument
-we present in sub-section \ref{subsec:watershed} to define void boundaries in
-our method.  
-Namely that as we increase the void boundary, we reach
-first middle density walls, before reaching high density structures
-associated with high anisotropy. 
-This makes the FA ridge a reasonable
-boundary for voids compared to the traditional definition that puts
-the boundary at the density ridge.
+($r/\reff =3$) and the radius of the FA maxima ($r/\reff =1$, most
+manifest in the T-Web voids) justifies in a more quantiative way the
+qualitative argument we present in sub-section \ref{subsec:watershed}
+to define void boundaries in our method.  
+Namely that as we increase the void boundary moving away from the
+center, we reach first middle density walls, before reaching high
+density structures associated with high anisotropy.  
+This implies that voids defined with the FA never present positive
+overdensities, making the FA maximum a reasonable boundary for voids
+compared to the traditional definition that puts the boundary at the
+densityridge.
 

### 2015-06-16 RefereeResponse.md
solved issue #14
issue #16 solved

@@
     Response: 
-    - We have added a clearer explanation of the ridge removing procedure (3rd paragraph of subsec. 3.3).
+    - We have improved our explanation about the ridge removing
+    procedure in the 3rd paragraph of subsection 3.3.
 
-4. **In Fig. 6, I only see a clear ridge in FA at r~r_eff in a few cases. the sentence in Sect. 5.5 "The 
-    difference between the radius where the density ridge is reached ([r/]reff = 3) and the radius of the 
-    FA ridge ([r/]reff = 1 ) ..." implies that I should see a ridge in FA at r~r_eff. Is this because the 
-    ridge is actually a 2D surface that is spherically averaged? It would be helpful to point this (or any 
-    other reasons) out. Also, the statement "This makes the FA ridge a reasonable boundary for voids compared 
-    to the traditional definition that puts the boundary at the density ridge" implies (perhaps 
-    unintentionally) that the FA ridge is a superior marker of the edge of a void than a density ridge. It is 
-    a physically different sort of ridge, and I agree that it is reasonable, but I do not see why it should 
-    be superior.**
+4. **In Fig. 6, I only see a clear ridge in FA at r~r_eff in a few
+    cases. the sentence in Sect. 5.5 "The  difference between the
+    radius where the density ridge is reached ([r/]reff = 3) and the
+    radius of the  FA ridge ([r/]reff = 1 ) ..." implies that I should
+    see a ridge in FA at r~r_eff. Is this because the ridge is
+    actually a 2D surface that is spherically averaged? It would be
+    helpful to point this (or any  other reasons) out. Also, the
+    statement "This makes the FA ridge a reasonable boundary for voids
+    compared  to the traditional definition that puts the boundary at
+    the density ridge" implies (perhaps  unintentionally) that the FA
+    ridge is a superior marker of the edge of a void than a density
+    ridge. It is  a physically different sort of ridge, and I agree
+    that it is reasonable, but I do not see why it should  be
+    superior.**
+
+    Response:
+    - We now talk about "maxima" instead of "ridge" in the TA
+    profiles. We have also removed the references of the TA as a
+    "superior" characterization.
 

### 2015-06-16 cosmic_voids.tex
issue #16 solved

@@
 If the density field is used, a typical threshold is
-$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbour 
+$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbouring 
 voids, if the mean value of the density across their common boundary is 
-below that threshold, both voids are taken as just one void.
+below that threshold, the two voids are merged.
 In our case we have to find a corresponding FA value
@@
 
-In Fig. \ref{fig:L1_correlations} we find the correlations of
-the eigenvalue $\lambda_1$ with the matter overdensity (left panel) and
-the FA (right panel).
-We can use this information to find the equivalent FA threshold. 
-From the left panel we see that an underdensity of $\delta=-0.8$ 
-corresponds to $\lambda_1=0.0$, regardless of the web-finding
-scheme.
-From the second panel we have a very tight correlation of $\lambda_1$
-with the FA, indicating that in turn $\lambda_1=0.0$ corresponds to a
-FA=$0.65$ which is the value that we choose to remove ridges. 
+\after{In the left panel of Fig. \ref{fig:L1_correlations} we see how 
+the FA correlates with the matter overdensity. 
+A value of $\delta=-0.8$ corresponds to a value of $FA\sim 0.65$ regardless of
+the web-finding scheme. 
+This is the value we choose to remove ridges between two watershed
+voids. 
 The right column in Fig. \ref{fig:FA_field} shows all the individual
 voids that have been identified using the watershed algorithm on the
-FA field.
+FA field.}
 

### 2015-06-16 cosmic_voids.tex
closed issue #12

@@
 
-Usually, the threshold is a free parameter that is tuned to reproduce
-the visual appearence of the comic web. 
-In this paper we take a different approach.
-In this work we propose an optimal value of the threshold based on the
-maximization of the fractional anisotropy field in the locations label
-as filaments and walls. 
-This threshold does not enter into our computations. 
-We simply offer this estimate as a guide to readers familiar with the
-meaning of this threshold.
+Usually, the threshold $\lambda_{th}$ is a free parameter that is
+tuned to reproduce the visual appearence of the comic web. 
+However, in this paper this threshold does not play any role in our
+computations.
+In Figure \ref{fig:L1_correlations} we offer a threshold estimate
+(from the FA=$0.95$ as a function of $\lambda_1$, this choice is
+explained in the next section) only as a guide to readers familiar
+with its meaning.
 

### 2015-06-19 RefereeResponse.md
closed issue #12
issue #11

@@
       Response: 
-      - Although lambda_1 is the defining property of voids when using the T-web/V-web (1st paragraph of 
-	subsec 3.2), the FA exihibit a key advantage that makes it a better void tracer (please refer to 
-	3rd paragraph of subsec. 3.2 of the new version).
-      - Now it is explicitly explained why the FA, as defined in the context of MRI, is useful to cosmologist 
+      - Although lambda_1 is the defining property of voids when using
+      the FA has a key advantage that makes it a better void tracer,
+      namely that it is possible to define a boundary in regions with
+      FA~1. The boudary setting is more arbitrary in the case of using
+      lambda_1 as a tracer. We make this clarification in the 
+	3rd paragraph of subsec. 3.2 of the new version.
+      - Now it is explicitly explained why the FA, as defined in the
+      context of MRI, is useful to cosmologist  
 	(6th paragraph of introduction and 1st paragraph of subsec 3.1).
-      - A new figure (Fig 3.) was prepared. Histograms of the volume contribution of each environment for 
-	each value of the FA (3rd paragraph of subsec. 3.2). Sheets (mainly) and filaments are clearly 
+      - A new figure (Fig 3.) was prepared. Histograms of the volume
+      contribution of each environment for  
+	each value of the FA (3rd paragraph of subsec. 3.2). Sheets
+      (mainly) and filaments are clearly  
 	associated with high values of the FA.
 
-2. **I did not understand the sentence at the end of Sect 2, "In this work we propose an optimal value of 
-    the threshold based on the maximization of the fractional anisotropy field in the locations label[ed] 
-    as filaments and walls," and this seems to be an important point. Is the threshold mentioned in this 
-    sentence a threshold in lambda_1, or FA? Is this the 0.95 threshold in FA? It seems to be a reasonable 
-    choice, but I do not see a sense in which it is "optimal," except that it seems to be the boundary 
-    between the FA being well-correlated with lambda_1 and not-so-well. Also, if this sentence is about the 
-    0.95 threshold, I do not see why it "does not enter into our computations," since the boundary of many 
-    voids will depend on this threshold. It would be useful to know for what fraction of voids the limit 
-    FA = 0.95 actually affects the boundary (in the case of the largest voids, I suppose).**
+2. **I did not understand the sentence at the end of Sect 2, "In this
+    work we propose an optimal value of  the threshold based on the
+    maximization of the fractional anisotropy field in the locations
+    label[ed]  as filaments and walls," and this seems to be an important point. Is the threshold mentioned in this 
+    sentence a threshold in lambda_1, or FA? Is this the 0.95
+    threshold in FA? It seems to be a reasonable choice, but I do not
+    see a sense in which it is "optimal," except that it seems to be
+    the boundary  between the FA being well-correlated with lambda_1
+    and not-so-well. Also, if this sentence is about the     0.95
+    threshold, I do not see why it "does not enter into our
+    computations," since the boundary of many    voids will depend on
+    this threshold. It would be useful to know for what fraction of
+    voids the limit    FA = 0.95 actually affects the boundary (in the
+    case of the largest voids, I suppose).**
+
+    Response:
+    We have rewritten this paragraph. The threshold that is not
+    relevant to our computations is lambda_th, not FA=0.95.
 

### 2015-06-19 cosmic_voids.tex
removed new figure 3, removed before-after

@@
 
-\before{ The tracer that we use to define the 
-voids is the fractional anisotropy (FA) computed from the set of 
-eigenvalues of the tensor under consideration. 
-The FA was initially introduced by \citet{Basser95} to quantify the
-anisotropy degree of the diffusivity of water molecules through
-cerebral tissue in nuclear magnetic resonance
-imaging and \citet{Libeskind13} introduced this concept in the context
-of Cosmic Web classification schemes.}
-
-\after{The tracer that we use to define the voids is the fractional
+The tracer that we use to define the voids is the fractional
 anisotropy (FA) computed from the set of eigenvalues of the tensor
@@
 \citet{Libeskind13} introduced the concept of the FA in the context of 
-Cosmic Web classification schemes.}
+Cosmic Web classification schemes.
 
@@
 %FIGURE 3: Histograms for each environment regarding the FA value
-\begin{figure}
-\centering
-
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-  width=0.35\textheight]{FA_environment.pdf}
-
-  \captionof{figure}{\small Volume of each environment per FA 
-  ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA ($dV/dFA$).
-  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
-  each line represents the volume contribution of the respective 
-  environment to the total volume with the same FA value. Above FA=0.95,
-  only sheets and filaments contribute to all the volume of the simulation
-  within that range of FA.}
-  \label{fig:FA_environment}
-
-\end{figure}
+%\begin{figure}
+%\centering
+%  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
+%  width=0.35\textheight]{FA_environment.pdf}
+%   \captionof{figure}{\small Volume of each environment per FA
+%   ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA
+%   ($dV/dFA$). 
+%  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
+%  each line represents the volume contribution of the respective 
+%  environment to the total volume with the same FA value. Above FA=0.95,
+%  only sheets and filaments contribute to all the volume of the simulation
+%  within that range of FA.}
+%  \label{fig:FA_environment}
+%\end{figure}
 %.........................................................................
@@
 
-\before{The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
-conceived to quantify the anisotropy of the diffusivity of water
-molecules through cerebral tissue in nuclear magnetic resonance imaging. 
-Here we present the FA, much in the same way as \citet{Libeskind13},
-to use it as a tracer of cosmic voids.}
-
-\after{The fractional anisotropy (FA), as developed by \citet{Basser95}, 
+The fractional anisotropy (FA), as developed by \citet{Basser95}, 
 was conceived to quantify the anisotropy of the diffusivity of water
@@
 account, we present here the FA, much in the same way as \citet{Libeskind13}, 
-to use it as a tracer of cosmic voids.}
+to use it as a tracer of cosmic voids.
 
@@
 % CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-\before{In Fig. \ref{fig:L1_correlations} we show that the these two values
-are indeed closely correlated.  
-The right panel shows the correlation between $\lambda_1$ and $\delta$ for
-all the grid cells in the simulation while the right panel shows the
-correlation between $\lambda_1$ and the FA. This shows that the
-overdensity has a large scatter at fixed $\lambda_1$.}
-
-\after{In Fig. \ref{fig:L1_correlations} we show that the these two values
+
+In Fig. \ref{fig:L1_correlations} we show that the these two values
 are indeed closely correlated.  The top panel shows the correlation between 
@@
 density has a larger scatter at fixed $\lambda_1$ than the FA, yet large and 
-small values of the density remain still associated to low values of the FA.}
-
-\after{At this point, the eigenvalue $\lambda_1$ and the FA appear to be
+small values of the density remain still associated to low values of the FA.
+
+At this point, the eigenvalue $\lambda_1$ and the FA appear to be
 equally potential candidates for tracing cosmic voids, however, the 
@@
 dominate, which, according to Fig. \ref{fig:FA_environment}, are associated
-mainly to sheets and, to a lesser extent, to filaments.}
+mainly to sheets and, to a lesser extent, to filaments.
 %!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
@@
 \citep{Schaap00}.
-\before{However, from the analysis of our results the choice of a fixed
-Cartesian mesh does not induce spurious results, at least with
-the mass resolution we have in the N-body simulation. }
-\after{Nevertheless, in our case the average number of particles per cell
+Nevertheless, in our case the average number of particles per cell
   is large enough ($512$ particles/cell) ensuring that the lowest
@@
   ($\delta \sim-0.98$), which seems to avoid spurious results from a
-  noisy density field sampling.}
+  noisy density field sampling.
 
 % CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-\before{The watershed algorithm also needs a threshold value to reduce
-spurious features and prevent void hierarchization.  
-If the density field is used, a typical threshold is
-$\delta = -0.8$ \citep{Platen07},  which means that any ridge between
-two voids with overdensity below that value is removed to merge the
-respective voids. 
-In our case we have to find a corresponding FA value
-to define this threshold.}
-
-\after{The watershed algorithm also needs a threshold value to reduce
+
+The watershed algorithm also needs a threshold value to reduce
 spurious features and prevent void hierarchization.  
@@
 In our case we have to find a corresponding FA value
-to define this threshold.}
+to define this threshold.
 %!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
@@
 smoothing length of the density field, i.e. $\sim 1$\hMpc.  
-\before{Below that scale numerical resolution effects become
-  important. }
-\after{For smaller interpolation/smoothing scales the shot noise in
-  the low density regions starts to be noticeable.}
+For smaller interpolation/smoothing scales the shot noise in
+  the low density regions starts to be noticeable.
 With that choice we find a void volume filling fraction $54.88\%$ and
 $47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.  
-\after{For larger smoothing scales ($>5\hMpc$) the density and shear fields
+For larger smoothing scales ($>5\hMpc$) the density and shear fields
   tend to be Gaussian and therefore follow closely the analytical environment abundance
-  predictions for Gaussian random fields \citep{Forero09,Alonso2015}. }
+  predictions for Gaussian random fields \citep{Forero09,Alonso2015}.
 
@@
 
-\before{We find that subcompensated voids have outflowing velocity profiles
-all the way up to the effective radius where the average radial
-density reaches the average value.}
-\after{We find that subcompensated voids have outflowing velocity profiles
+We find that subcompensated voids have outflowing velocity profiles
 all the way up to the radius where the average radial
-density reaches the average value.}
+density reaches the average value.
 For voids with sizes $\reff <8\hMpc$ the outflow is always

### 2015-06-19 RefereeResponse.md
respuesta

@@
+Dear Editor,
+
+We thank the referee for a very detailed report. We feel that his/her
+comments have dramatically improved the clarity and readability of our
+paper.
+
+We have addressed all the points raised by the referee. We include in
+this reply an answer to each comment. We have included the file main_diff.pdf
+showing the differences in the body of the paper.
+
+The Authors.
+
 Conceptual:
@@
     rather interesting quantity in itself, differentiating haloes and
-    voids from  
-    filaments and walls, but it is not clear why it should be superior to lambda_1 for void finding. The 
-    authors should more clearly articulate why this might be, if there
-    is a reason. The FA being "conceived  to quantify the anisotropy
-    of the diffusivity of water molecules through cerebral tissue in
-    nuclear  magnetic resonance imaging" should be elaborated on; this
-    does not clarify the usefulness of the FA for
-    cosmologists. Conceptually, I also wonder: do filaments and walls
-    behave differently from each other in  FA, or do they both have FA
-    ~ 1?**
+    voids from  filaments and walls, but it is not clear why it should
+    be superior to lambda_1 for void finding. The authors should more
+    clearly articulate why this might be, if there is a reason. The FA
+    being "conceived  to quantify the anisotropy of the diffusivity of
+    water molecules through cerebral tissue in nuclear  magnetic
+    resonance imaging" should be elaborated on; this does not clarify
+    the usefulness of the FA for cosmologists. Conceptually, I also
+    wonder: do filaments and walls behave differently from each other
+    in  FA, or do they both have FA ~ 1?**
 
       Response:   
-      - Although lambda_1 is the defining property of voids when using
+      - Although lambda_1 is the defining property of voids, 
       the FA has a key advantage that makes it a better void tracer,
       namely that it is possible to define a boundary in regions with
-      FA~1. The boudary setting is more arbitrary in the case of using
-      lambda_1 as a tracer. We make this clarification in the 
-	3rd paragraph of subsec. 3.2 of the new version.
+      FA~1. Boudary setting becomes arbitrary in the case of using
+      lambda_1 as a tracer because lambda_1 is not bound. 
+      We make this clarification in the  3rd paragraph of subsec. 3.2
+      of the new version. 
       - Now it is explicitly explained why the FA, as defined in the
@@
 	(6th paragraph of introduction and 1st paragraph of subsec 3.1).
-      - A new figure (Fig 3.) was prepared. Histograms of the volume
-      contribution of each environment for  
-	each value of the FA (3rd paragraph of subsec. 3.2). Sheets
-      (mainly) and filaments are clearly  
-	associated with high values of the FA.
+      - We prepare a new Figure (Fig. 3) to shows that filaments and
+      sheets have different behaviour in FA. Only sheets are
+      associated with high values of FA~1.
 
@@
     maximization of the fractional anisotropy field in the locations
-    label[ed]  as filaments and walls," and this seems to be an important point. Is the threshold mentioned in this 
-    sentence a threshold in lambda_1, or FA? Is this the 0.95
-    threshold in FA? It seems to be a reasonable choice, but I do not
-    see a sense in which it is "optimal," except that it seems to be
-    the boundary  between the FA being well-correlated with lambda_1
-    and not-so-well. Also, if this sentence is about the     0.95
+    label[ed]  as filaments and walls," and this seems to be an
+    important point. Is the threshold mentioned in this  sentence a
+    threshold in lambda_1, or FA? Is this the 0.95 threshold in FA? It
+    seems to be a reasonable choice, but I do not see a sense in which
+    it is "optimal," except that it seems to be the boundary  between
+    the FA being well-correlated with lambda_1 and not-so-well. 
+    Also, if this sentence is about the     0.95   
     threshold, I do not see why it "does not enter into our
@@
     Response:
-    We have rewritten this paragraph. The threshold that is not
-    relevant to our computations is lambda_th, not FA=0.95.
+    We have rewritten this paragraph. The threshold that is 
+    irrrelevant to our computations is lambda_th, not FA=0.95.
 
-3. **I do not see how the value of FA=0.65 (corresponding to lambda_1 = 0) is used "to remove ridges."**
+3. **I do not see how the value of FA=0.65 (corresponding to lambda_1
+= 0) is used "to remove ridges."**
 
@@
 
-10. **In Sect. 5.5, there are a few instances where I think you meant "r/r_eff =" instead of "r_eff =".**
+10. **In Sect. 5.5, there are a few instances where I think you meant
+"r/r_eff =" instead of "r_eff =".**
 
     Response:
-    We have revised all the instances and replaced r_eff by r/r_eff
+    Indeed. We have revised all the instances and replaced r_eff by r/r_eff
     wherever it was appropriate.
@@
     - These figures have already different linewidths for each bin. We
-    think it might be easier to have 6  
-      different widths than 6 different linestyles.
+    think it might be easier to have 6 different widths than 6
+    different linestyles.

### 2015-06-20 RefereeResponse.md
Little typos

@@
     Response:
-    - We now talk about "maxima" instead of "ridge" in the TA
-    profiles. We have also removed the references of the TA as a
+    - We now talk about "maxima" instead of "ridge" in the FA
+    profiles. We have also removed the references of the FA as a
     "superior" characterization.
@@
     Response:
-    We have rephrased this in terms of the number of particles per
+    - We have rephrased this in terms of the number of particles per
     cell in the lowest density regions.
@@
     Response:
-    We removed "effective" for clarity.
+    - We removed "effective" for clarity.
 
@@
     Response:
-    Indeed. We have revised all the instances and replaced r_eff by r/r_eff
+    - Indeed. We have revised all the instances and replaced r_eff by r/r_eff
     wherever it was appropriate.
@@
     Response:
-    We now mention in the first paragraph of the Results section the
+    - We now mention in the first paragraph of the Results section the
     expected results for larger smoothing scales. Namely, that the

### 2015-06-20 cosmic_voids.tex
more typos fixed

@@
 \citep{Hoffman12}. 
-Our procedure allows for a description of the internal structure
-of voids that goes beyond a simple definition of a void as an
-underdense region in the large-scale matter distribution.
-The tidal and the shear tensors encode more information than the
-density/velocity fields as they trace the collapsing or expanding
-nature of the matter field, which defines the dynamics of the Cosmic
-Web.
-
-% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+Our procedure allows for a description of a void internal structure
+beyond a simple definition of a void as an underdense region in the
+large-scale matter distribution. 
+The tidal and the shear tensors
+encode more information than the density/velocity fields as they trace
+the collapsing or expanding nature of the matter field, which defines
+the dynamics of the Cosmic Web.
 
@@
     the a watershed algorithm on the Fractional Anisotropy field. Colours
-    in the right panels correspond with the effective radius of each void. }
+    in the right panel correspond with the effective radius of each void. }
   \label{fig:FA_field}
@@
 \centering
-
   \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
-  width=0.33\textwidth]{FA_delta.pdf}
+  width=0.33\textwidth]{FA_L1.pdf}  
   \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
@@
   \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
-  width=0.33\textwidth]{FA_L1.pdf}
-
-  \captionof{figure}{\small Fractional Anisotropy  as a function of
+  width=0.33\textwidth]{FA_delta.pdf}
+  \captionof{figure}{
+    Fractional Anisotropy  as a function of
     the overdensity (left) and the eigenvalue $\lambda_1$ (middle), and
@@
     eigenvalue $\lambda_1$ for each web scheme (T-Web,  continous
-    lines. V-Web, dashed lines). Thick central lines are the median
+    lines. V-Web, dashed lines).     
+    Fractional Anisotropy  as a function of $\lambda_1$ (left),
+    overdensity as a function of $\lambda_1$ (middle) and Fractional
+    Anisotropy as a function of the overdensity (right).
+    Thick central lines are the median
     and filled regions include $50\%$ of the cells in each bin. 
-    The left panel we confirms that underdense regions can be
+    The left panel shows the tigth correlation between FA and
+    $\lambda_1$ in voids.
+    In the middle and right panel we show the equivalent eigenvalue
+    threshold for the T-Web and V-web corresponding to FA=$0.95$. 
+    The right panel confirms that underdense regions can be
     identified with Fractional Anisotropy values less than $0.95$.
@@
     Fractional Anisotropy equal or less than this value.
-    In the middle and right panel we show the equivalent eigenvalue
-    threshold for the T-Web and V-web corresponding to that
-    Fractional Anisotropy. 
-    This threshold on the eigenvalues does not influence 
-    our computations. We show it as a guide to readers familiar with the
+    The threshold $\lambda_{\rm th}$ on the eigenvalues does not
+    influence our results. 
+    We show it as a guide to readers familiar with the
     order of magnitude expectation for this quantity.}
@@
 %FIGURE 3: Histograms for each environment regarding the FA value
-%\begin{figure}
-%\centering
-%  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-%  width=0.35\textheight]{FA_environment.pdf}
-%   \captionof{figure}{\small Volume of each environment per FA
-%   ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA
-%   ($dV/dFA$). 
-%  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
-%  each line represents the volume contribution of the respective 
-%  environment to the total volume with the same FA value. Above FA=0.95,
-%  only sheets and filaments contribute to all the volume of the simulation
-%  within that range of FA.}
-%  \label{fig:FA_environment}
-%\end{figure}
+\begin{figure}
+\centering
+  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{FA_environment.pdf}
+   \captionof{figure}{\small Volume of each environment per FA
+   ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA
+   ($dV/dFA$). 
+  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
+  each line represents the volume contribution of the respective 
+  environment to the total volume with the same FA value. Above FA=0.95,
+  only sheets and filaments contribute to all the volume of the simulation
+  within that range of FA.}
+  \label{fig:FA_environment}
+\end{figure}
 %.........................................................................
@@
 On the other hand the filamentary structure (grey in the middle panel
-of Fig. 1) is traced by high FA values.  
+of Fig. 1) is traced by middle to high FA values.  
 This characteristic is the  key to use the FA as a tracer of cosmic
@@
 Voids are regions where $\lambda_3\leq\lambda_2\leq
-\lambda_1\leq\lambda_{th}$. 
+\lambda_1\leq\lambda_{\rm th}$. 
 This implies that a void is completely fixed by the relative strength
 of the $\lambda_1$ eigenvalue with respect to the threshold.   
-As we increase/decrease the threshold value $\lambda_{th}$, voids
+As we increase/decrease the threshold value $\lambda_{\rm th}$, voids
 increase/decrease progressively through contours of
@@
 
-% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
 In Fig. \ref{fig:L1_correlations}  we show that the these two values
-are indeed closely correlated.  The top panel shows the correlation between 
-$\lambda_1$ and $\delta$ for all the grid cells in the simulation while the 
-bottom panel shows the correlation between $\lambda_1$ and the FA. The middle 
-panel shows the correlation between $\delta$ and the FA. This shows that the 
-density has a larger scatter at fixed $\lambda_1$ than the FA, yet large and 
-small values of the density remain still associated to low values of the FA.
+are correlated. 
+The left panel shows the correlation between the FA and $\lambda_1$
+and the middle panel between the overdensity $\delta$ and $\lambda_1$.
+The right panel shows the correlation between $\delta$ and the
+FA. 
+This shows that the  density has a larger scatter at fixed
+$\lambda_1$ than the FA, yet large and  small values of the density
+remain still associated to low values of the FA.
 
@@
 equally potential candidates for tracing cosmic voids, however, the 
-eigenvalue $\lambda_1$ presents, along with the density, an undesirable 
-feature for a void tracer. As we move out from inner parts of voids to outer 
-parts, $\lambda_1$ and the density increase monotonically, making unclear 
-where to set the frontier of voids. On the other hand, the FA naturally 
-indicates the real frontier as regions where anisotropic collapse begin to 
-dominate, which, according to Fig. \ref{fig:FA_environment}, are associated
-mainly to sheets and, to a lesser extent, to filaments.
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+eigenvalue $\lambda_1$ presents, along with the overdensity, an undesirable 
+feature for a void tracer. 
+As we move out from inner parts of voids to outer parts, $\lambda_1$
+and $\delta$ increase monotonically making unclear where to set the
+void boudary, while for low density regions ($\delta<1$) the FA traces
+the boundary where anisotropic collapse regions begin to 
+dominate.
+According to Fig. \ref{fig:FA_environment} these anisotropic areas are
+mainly associated to sheets and, to a lesser extent, filaments.
 
@@
 classification for this choice of $\lambda_{th}$, demonstrating that
-this FA level is a sensitive choice to define voids.
+this FA level is a reasonable choice to define voids.
 
@@
 
-% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
 The watershed algorithm also needs a threshold value to reduce
@@
 to define this threshold.
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
-\after{In the left panel of Fig. \ref{fig:L1_correlations} we see how 
+
+In the right panel of Fig. \ref{fig:L1_correlations} we see how 
 the FA correlates with the matter overdensity. 
-A value of $\delta=-0.8$ corresponds to a value of $FA\sim 0.65$ regardless of
-the web-finding scheme. 
+A value of $\delta=-0.8$ corresponds to a value of FA$\sim 0.65$
+regardless of the web-finding scheme. 
 This is the value we choose to remove ridges between two watershed
@@
 voids that have been identified using the watershed algorithm on the
-FA field.}
+FA field.
 
@@
 For larger smoothing scales ($>5\hMpc$) the density and shear fields
-  tend to be Gaussian and therefore follow closely the analytical environment abundance
-  predictions for Gaussian random fields \citep{Forero09,Alonso2015}.
+  tend to be Gaussian and therefore follow closely the analytical
+  environment abundance predictions for Gaussian random fields
+  \citep{Forero09,Alonso2015}.  
+In this paper we limit ourselves to a smoothing scale $\sim 1$ \hMpc.
 
@@
 To discriminate each void in one of the families we use the
-compensation  index $\mathcal{C}$.
+compensation  index $C$
 It is defined as the mass of a void enclosed in a spherical volume of
@@
 \eq{compensation}
-{\mathcal{C} = \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}
+{C= \frac{M_v}{\overline{M}} = \frac{3}{2R^{3}} \int_0^{R} [\delta(r) + 1] r^2 dr}
 
@@
 enclose the compensation ridge for a typical void in case there is one. 
-This leads us to voids with $\mathcal{C}>1$ having more mass than expected, 
+This leads us to voids with $C>1$ having more mass than expected, 
 constituting the family of overcompensated voids. 
@@
 dense nearby structures. 
-In the same fashion, voids with $\mathcal{C}<1$ constitute the family
+In the same fashion, voids with $C<1$ constitute the family
 of  subcompensated voids.
@@
 overcompensated voids. 
+Table \ref{tab:number_voids} lists the number of voids in 
+each effective radius bin for the two web finding methods.
 
@@
 
-Table \ref{tab:number_voids} lists the number of voids in 
-each effective radius bin for the two web finding methods.
-
 %.........................................................................
@@
 larger radii than larger voids.
-This suggests that smaller subcompensated voids are embedded into low
+This suggests that small subcompensated voids are embedded into low
 density structures, while large subcompensated voids are surrounded
@@
 \citep{Lavaux12, Ceccarelli13, Paz13, Hamaus14}. 
-Our results extend the findings of \cite{Hamaus14} into the range of
-voids with size $\reff <10$\hMpc.
+Indeed, our results extend the findings of \cite{Hamaus14} into the
+range of voids with size $\reff <10$\hMpc.
 
@@
 all the way up to the radius where the average radial
-density reaches the average value.
-For voids with sizes $\reff <8\hMpc$ the outflow is always
+density reaches zero.
+In voids with sizes $\reff <8\hMpc$ the outflow is always
 positive, consistent with the fact that their density profiles do not
@@
 value of F=$0.8$ almost right at $r/\reff =2$. 
-For the V-Web the results are similar, albeit rather slowly with the
-effective radius.
+For the V-Web the results are similar, albeit with a slower trend with
+the effective radius. 
 Overcompensated voids reach a maximum FA at the same effective radiuus
@@
 is the separation into subcompensated and overcompensated samples. 
-In the T-Web $35\%$ of the voids are overcompensated ($65\%$
-subcompensated), meaning that they are located in denser regions with
+In the T-Web $35\%$ of the voids are overcompensated and $65\%$
+subcompensated, meaning that they are located in denser regions with
 a clear delimiting ridge.   
-For the V-web the subcompensated fraction rises from $65\%$ to $85\%$ as the
+For the V-web the subcompensated fraction rises to $85\%$ as the
 void size decreases, supporting the picture of smaller spurious voids
@@
 
-Finally we proceed with an more detailed void characterization
+Finally we proceed with a more detailed void characterization
 through the radially averaged profiles of density, radial velocity and
@@
 
-The Fractional Anisotropy profiles also show remarkable similarities
+The FA profiles also show remarkable similarities
 inside each class of subcompensated and overcompensated voids
@@
 quite far from the limiting FA$=0.95$ suggesting that these voids are
-far from spherical.
+ellipsoidal.
 
@@
 evidence for a universal density profile.  
-Our results extends to smaller void sizes the work done by
+Our results extend to smaller void sizes the work done by
 \cite{Hamaus14} on simulations and by \cite{Ceccarelli13} on SDSS data.

### 2015-06-20 cosmic_voids.tex
including references

@@
 \bibliographystyle{mn2e}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{}
+
+\bibitem[\protect\citeauthoryear{{Abazajian}, et al. \& {(the SDSS
+  Collaboration)}}{{Abazajian} et~al.}{2003}]{Abazajian03}
+{Abazajian} K.,  et al.   {(the SDSS Collaboration)} 2003, \aj, 126, 2081
+
+\bibitem[\protect\citeauthoryear{{Alonso}, {Eardley} \& {Peacock}}{{Alonso}
+  et~al.}{2015}]{Alonso2015}
+{Alonso} D.,  {Eardley} E.,    {Peacock} J.~A.,  2015, \mnras, 447, 2683
+
+\bibitem[\protect\citeauthoryear{{Basser}}{{Basser}}{1995}]{Basser95}
+{Basser} P.,  1995, NMR in Biomedical Imaging, 8, 333
+
+\bibitem[\protect\citeauthoryear{{Bertschinger}}{{Bertschinger}}{1985}]{Bertschinger85}
+{Bertschinger} E.,  1985, \apjs, 58, 1
+
+\bibitem[\protect\citeauthoryear{{Beucher} \& {Lantuejoul}}{{Beucher} \&
+  {Lantuejoul}}{1979}]{Beucher79}
+{Beucher} S.,  {Lantuejoul} C.,  1979, in Proceedings Interna- tional Workshop
+  on Image Processing, CCETT/IRISA, Rennes, France
+
+\bibitem[\protect\citeauthoryear{{Beucher} \& {Meyer}}{{Beucher} \&
+  {Meyer}}{1993}]{Beucher93}
+{Beucher} S.,  {Meyer} F.,  1993, {Mathematical Morphology in Image
+  Processing}.
+Marcel Deker, New York
+
+\bibitem[\protect\citeauthoryear{{Blumenthal}, {da Costa}, {Goldwirth}, {Lecar}
+  \& {Piran}}{{Blumenthal} et~al.}{1992}]{Blumenthal92}
+{Blumenthal} G.~R.,  {da Costa} L.~N.,  {Goldwirth} D.~S.,  {Lecar} M.,
+  {Piran} T.,  1992, \apj, 388, 234
+
+\bibitem[\protect\citeauthoryear{{Bond}, {Kofman} \& {Pogosyan}}{{Bond}
+  et~al.}{1996}]{Bond96}
+{Bond} J.~R.,  {Kofman} L.,    {Pogosyan} D.,  1996, \nat, 380, 603
+
+\bibitem[\protect\citeauthoryear{{Brunino}, {Trujillo}, {Pearce} \&
+  {Thomas}}{{Brunino} et~al.}{2007}]{Brunino07}
+{Brunino} R.,  {Trujillo} I.,  {Pearce} F.~R.,    {Thomas} P.~A.,  2007,
+  \mnras, 375, 184
+
+\bibitem[\protect\citeauthoryear{{Ceccarelli}, {Padilla}, {Valotto} \&
+  {Lambas}}{{Ceccarelli} et~al.}{2006}]{Ceccarelli06}
+{Ceccarelli} L.,  {Padilla} N.~D.,  {Valotto} C.,    {Lambas} D.~G.,  2006,
+  \mnras, 373, 1440
+
+\bibitem[\protect\citeauthoryear{{Ceccarelli}, {Paz}, {Lares}, {Padilla} \&
+  {Lambas}}{{Ceccarelli} et~al.}{2013}]{Ceccarelli13}
+{Ceccarelli} L.,  {Paz} D.,  {Lares} M.,  {Padilla} N.,    {Lambas} D.~G.,
+  2013, \mnras, 434, 1435
+
+\bibitem[\protect\citeauthoryear{{Chincarini} \& {Rood}}{{Chincarini} \&
+  {Rood}}{1975}]{Chincarini75}
+{Chincarini} G.,  {Rood} H.~J.,  1975, \nat, 257, 294
+
+\bibitem[\protect\citeauthoryear{{Colberg}, {Pearce} \& et al.}{{Colberg}
+  et~al.}{2008}]{Colberg08}
+{Colberg} J.~M.,  {Pearce} F.,    et al. 2008, \mnras, 387, 933
+
+\bibitem[\protect\citeauthoryear{{Colberg}, {Sheth}, {Diaferio}, {Gao} \&
+  {Yoshida}}{{Colberg} et~al.}{2005}]{Colberg05}
+{Colberg} J.~M.,  {Sheth} R.~K.,  {Diaferio} A.,  {Gao} L.,    {Yoshida} N.,
+  2005, \mnras, 360, 216
+
+\bibitem[\protect\citeauthoryear{{Colless}, et al. \& {(the 2dFGRS
+  Team),}}{{Colless} et~al.}{2001}]{Colless01}
+{Colless} M.,  et al.   {(the 2dFGRS Team),} 2001, \mnras, 328, 1039
+
+\bibitem[\protect\citeauthoryear{{Colless}, et al. \& {(the 2dFGRS
+  Team),}}{{Colless} et~al.}{2003}]{Colless03}
+{Colless} M.,  et al.   {(the 2dFGRS Team),} 2003, VizieR Online Data Catalog,
+  7226
+
+\bibitem[\protect\citeauthoryear{{Croton} \& et al.}{{Croton} \&
+  et~al.}{2004}]{Croton04}
+{Croton} D.~J.,  et al. 2004, \mnras, 352, 828
+
+\bibitem[\protect\citeauthoryear{{Dubinski}, {da Costa}, {Goldwirth}, {Lecar}
+  \& {Piran}}{{Dubinski} et~al.}{1993}]{Dubinski93}
+{Dubinski} J.,  {da Costa} L.~N.,  {Goldwirth} D.~S.,  {Lecar} M.,    {Piran}
+  T.,  1993, \apj, 410, 458
+
+\bibitem[\protect\citeauthoryear{{Einasto}, {Joeveer} \& {Saar}}{{Einasto}
+  et~al.}{1980a}]{Einasto80M}
+{Einasto} J.,  {Joeveer} M.,    {Saar} E.,  1980a, \mnras, 193, 353
+
+\bibitem[\protect\citeauthoryear{{Einasto}, {Joeveer} \& {Saar}}{{Einasto}
+  et~al.}{1980b}]{Einasto80N}
+{Einasto} J.,  {Joeveer} M.,    {Saar} E.,  1980b, \nat, 283, 47
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Contreras} \&
+  {Padilla}}{{Forero-Romero} et~al.}{2014}]{Forero2014}
+{Forero-Romero} J.~E.,  {Contreras} S.,    {Padilla} N.,  2014, \mnras, 443,
+  1090
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Hoffman}, {Gottl{\"o}ber},
+  {Klypin} \& {Yepes}}{{Forero-Romero} et~al.}{2009}]{Forero09}
+{Forero-Romero} J.~E.,  {Hoffman} Y.,  {Gottl{\"o}ber} S.,  {Klypin} A.,
+  {Yepes} G.,  2009, \mnras, 396, 1815
+
+\bibitem[\protect\citeauthoryear{{Foster} \& {Nelson}}{{Foster} \&
+  {Nelson}}{2009}]{Foster09}
+{Foster} C.,  {Nelson} L.~A.,  2009, \apj, 699, 1252
+
+\bibitem[\protect\citeauthoryear{{Gottl{\"o}ber}, {{\L}okas}, {Klypin} \&
+  {Hoffman}}{{Gottl{\"o}ber} et~al.}{2003}]{Gottlober03}
+{Gottl{\"o}ber} S.,  {{\L}okas} E.~L.,  {Klypin} A.,    {Hoffman} Y.,  2003,
+  \mnras, 344, 715
+
+\bibitem[\protect\citeauthoryear{{Gregory} \& {Thompson}}{{Gregory} \&
+  {Thompson}}{1978}]{Gregory78}
+{Gregory} S.~A.,  {Thompson} L.~A.,  1978, \apj, 222, 784
+
+\bibitem[\protect\citeauthoryear{{Hahn}, {Porciani}, {Carollo} \&
+  {Dekel}}{{Hahn} et~al.}{2007}]{Hahn07}
+{Hahn} O.,  {Porciani} C.,  {Carollo} C.~M.,    {Dekel} A.,  2007, \mnras, 375,
+  489
+
+\bibitem[\protect\citeauthoryear{{Hamaus}, {Sutter} \& {Wandelt}}{{Hamaus}
+  et~al.}{2014}]{Hamaus14}
+{Hamaus} N.,  {Sutter} P.~M.,    {Wandelt} B.~D.,  2014, Physical Review
+  Letters, 112, 251302
+
+\bibitem[\protect\citeauthoryear{{Hinshaw} et~al.,}{{Hinshaw}
+  et~al.}{2013}]{Hinshaw2013}
+{Hinshaw} G.  et~al., 2013, \apjs, 208, 19
+
+\bibitem[\protect\citeauthoryear{{Hoffman}, {Metuki}, {Yepes}, {Gottl{\"o}ber},
+  {Forero-Romero}, {Libeskind} \& {Knebe}}{{Hoffman} et~al.}{2012}]{Hoffman12}
+{Hoffman} Y.,  {Metuki} O.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Forero-Romero}
+  J.~E.,  {Libeskind} N.~I.,    {Knebe} A.,  2012, \mnras, 425, 2049
+
+\bibitem[\protect\citeauthoryear{{Hoffman} \& {Shaham}}{{Hoffman} \&
+  {Shaham}}{1982}]{Hoffman82}
+{Hoffman} Y.,  {Shaham} J.,  1982, \apjl, 262, L23
+
+\bibitem[\protect\citeauthoryear{{Hoyle} \& {Vogeley}}{{Hoyle} \&
+  {Vogeley}}{2004}]{Hoyle04}
+{Hoyle} F.,  {Vogeley} M.~S.,  2004, \apj, 607, 751
+
+\bibitem[\protect\citeauthoryear{{Icke}}{{Icke}}{1984}]{Icke84}
+{Icke} V.,  1984, \mnras, 206, 1P
+
+\bibitem[\protect\citeauthoryear{{Kauffmann} \& {Fairall}}{{Kauffmann} \&
+  {Fairall}}{1991}]{Kauffmann91}
+{Kauffmann} G.,  {Fairall} A.~P.,  1991, \mnras, 248, 313
+
+\bibitem[\protect\citeauthoryear{{Kirshner}, {Oemler} Jr., {Schechter} \&
+  {Shectman}}{{Kirshner} et~al.}{1981}]{Kirshner81}
+{Kirshner} R.~P.,  {Oemler} Jr. A.,  {Schechter} P.~L.,    {Shectman} S.~A.,
+  1981, \apjl, 248, L57
+
+\bibitem[\protect\citeauthoryear{{Kirshner}, {Oemler} Jr., {Schechter} \&
+  {Shectman}}{{Kirshner} et~al.}{1987}]{Kirshner87}
+{Kirshner} R.~P.,  {Oemler} Jr. A.,  {Schechter} P.~L.,    {Shectman} S.~A.,
+  1987, \apj, 314, 493
+
+\bibitem[\protect\citeauthoryear{{Klypin}, {Trujillo-Gomez} \&
+  {Primack}}{{Klypin} et~al.}{2011}]{Klypin11}
+{Klypin} A.~A.,  {Trujillo-Gomez} S.,    {Primack} J.,  2011, \apj, 740, 102
+
+\bibitem[\protect\citeauthoryear{{Lavaux} \& {Wandelt}}{{Lavaux} \&
+  {Wandelt}}{2012}]{Lavaux12}
+{Lavaux} G.,  {Wandelt} B.~D.,  2012, \apj, 754, 109
+
+\bibitem[\protect\citeauthoryear{{Libeskind}, {Hoffman}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Knebe}, {Steinmetz} \& {Klypin}}{{Libeskind}
+  et~al.}{2013}]{Libeskind13}
+{Libeskind} N.~I.,  {Hoffman} Y.,  {Forero-Romero} J.,  {Gottl{\"o}ber} S.,
+  {Knebe} A.,  {Steinmetz} M.,    {Klypin} A.,  2013, \mnras, 428, 2489
+
+\bibitem[\protect\citeauthoryear{{Martel} \& {Wasserman}}{{Martel} \&
+  {Wasserman}}{1990}]{Martel90}
+{Martel} H.,  {Wasserman} I.,  1990, \apj, 348, 1
+
+\bibitem[\protect\citeauthoryear{{Micheletti} et~al.,}{{Micheletti}
+  et~al.}{2014}]{Micheletti14}
+{Micheletti} D.  et~al., 2014, \aap, 570, A106
+
+\bibitem[\protect\citeauthoryear{{Mu{\~n}oz-Cuartas}, {M{\"u}ller} \&
+  {Forero-Romero}}{{Mu{\~n}oz-Cuartas} et~al.}{2011}]{MunozCuartas11}
+{Mu{\~n}oz-Cuartas} J.~C.,  {M{\"u}ller} V.,    {Forero-Romero} J.~E.,  2011,
+  \mnras, 417, 1303
+
+\bibitem[\protect\citeauthoryear{{M{\"u}ller}, {Arbabi-Bidgoli}, {Einasto} \&
+  {Tucker}}{{M{\"u}ller} et~al.}{2000}]{Muller00}
+{M{\"u}ller} V.,  {Arbabi-Bidgoli} S.,  {Einasto} J.,    {Tucker} D.,  2000,
+  \mnras, 318, 280
+
+\bibitem[\protect\citeauthoryear{{Nadathur} \& {Hotchkiss}}{{Nadathur} \&
+  {Hotchkiss}}{2014}]{Nadathur14}
+{Nadathur} S.,  {Hotchkiss} S.,  2014, \mnras, 440, 1248
+
+\bibitem[\protect\citeauthoryear{{Neyrinck}}{{Neyrinck}}{2008}]{Neyrinck08}
+{Neyrinck} M.~C.,  2008, \mnras, 386, 2101
+
+\bibitem[\protect\citeauthoryear{{Neyrinck}, {Falck} \& {Szalay}}{{Neyrinck}
+  et~al.}{2013}]{Neyrinck13}
+{Neyrinck} M.~C.,  {Falck} B.~L.,    {Szalay} A.~S.,  2013, ArXiv e-prints
+
+\bibitem[\protect\citeauthoryear{{Padilla}, {Ceccarelli} \& {Lambas}}{{Padilla}
+  et~al.}{2005}]{Padilla05}
+{Padilla} N.~D.,  {Ceccarelli} L.,    {Lambas} D.~G.,  2005, \mnras, 363, 977
+
+\bibitem[\protect\citeauthoryear{{Pan}, {Vogeley}, {Hoyle}, {Choi} \&
+  {Park}}{{Pan} et~al.}{2012}]{Pan10}
+{Pan} D.~C.,  {Vogeley} M.~S.,  {Hoyle} F.,  {Choi} Y.-Y.,    {Park} C.,  2012,
+  \mnras, 421, 926
+
+\bibitem[\protect\citeauthoryear{{Patiri}, {Betancort-Rijo} \&
+  {Prada}}{{Patiri} et~al.}{2006}]{Patiri06a}
+{Patiri} S.~G.,  {Betancort-Rijo} J.,    {Prada} F.,  2006, \mnras, 368, 1132
+
+\bibitem[\protect\citeauthoryear{{Patiri}, {Prada}, {Holtzman}, {Klypin} \&
+  {Betancort-Rijo}}{{Patiri} et~al.}{2006}]{Patiri06b}
+{Patiri} S.~G.,  {Prada} F.,  {Holtzman} J.,  {Klypin} A.,    {Betancort-Rijo}
+  J.,  2006, \mnras, 372, 1710
+
+\bibitem[\protect\citeauthoryear{{Paz}, {Lares}, {Ceccarelli}, {Padilla} \&
+  {Lambas}}{{Paz} et~al.}{2013}]{Paz13}
+{Paz} D.,  {Lares} M.,  {Ceccarelli} L.,  {Padilla} N.,    {Lambas} D.~G.,
+  2013, \mnras, 436, 3480
+
+\bibitem[\protect\citeauthoryear{{Platen}, {van de Weygaert} \&
+  {Jones}}{{Platen} et~al.}{2007}]{Platen07}
+{Platen} E.,  {van de Weygaert} R.,    {Jones} B.~J.~T.,  2007, \mnras, 380,
+  551
+
+\bibitem[\protect\citeauthoryear{{Plionis} \& {Basilakos}}{{Plionis} \&
+  {Basilakos}}{2002}]{Plionis02}
+{Plionis} M.,  {Basilakos} S.,  2002, \mnras, 330, 399
+
+\bibitem[\protect\citeauthoryear{{Regos} \& {Geller}}{{Regos} \&
+  {Geller}}{1991}]{Regos91}
+{Regos} E.,  {Geller} M.~J.,  1991, \apj, 377, 14
+
+\bibitem[\protect\citeauthoryear{{Ricciardelli}, {Quilis} \&
+  {Planelles}}{{Ricciardelli} et~al.}{2013}]{Ricciardelli2013}
+{Ricciardelli} E.,  {Quilis} V.,    {Planelles} S.,  2013, \mnras, 434, 1192
+
+\bibitem[\protect\citeauthoryear{{Riebe} et~al.,}{{Riebe}
+  et~al.}{2013}]{Riebe11}
+{Riebe} K.  et~al., 2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[\protect\citeauthoryear{{Rojas}, {Vogeley}, {Hoyle} \&
+  {Brinkmann}}{{Rojas} et~al.}{2005}]{Rojas05}
+{Rojas} R.~R.,  {Vogeley} M.~S.,  {Hoyle} F.,    {Brinkmann} J.,  2005, \apj,
+  624, 571
+
+\bibitem[\protect\citeauthoryear{{Schaap} \& {van de Weygaert}}{{Schaap} \&
+  {van de Weygaert}}{2000}]{Schaap00}
+{Schaap} W.~E.,  {van de Weygaert} R.,  2000, \aap, 363, L29
+
+\bibitem[\protect\citeauthoryear{{Shandarin}, {Feldman}, {Heitmann} \&
+  {Habib}}{{Shandarin} et~al.}{2006}]{Shandarin06}
+{Shandarin} S.,  {Feldman} H.~A.,  {Heitmann} K.,    {Habib} S.,  2006, \mnras,
+  367, 1629
+
+\bibitem[\protect\citeauthoryear{{Sheth} \& {van de Weygaert}}{{Sheth} \& {van
+  de Weygaert}}{2004}]{Sheth04}
+{Sheth} R.~K.,  {van de Weygaert} R.,  2004, \mnras, 350, 517
+
+\bibitem[\protect\citeauthoryear{{Sutter} et~al.,}{{Sutter}
+  et~al.}{2015}]{Sutter14}
+{Sutter} P.~M.  et~al., 2015, Astronomy and Computing, 9, 1
+
+\bibitem[\protect\citeauthoryear{{Sutter}, {Lavaux}, {Wandelt} \&
+  {Weinberg}}{{Sutter} et~al.}{2012}]{Sutter12b}
+{Sutter} P.~M.,  {Lavaux} G.,  {Wandelt} B.~D.,    {Weinberg} D.~H.,  2012,
+  \apj, 761, 44
+
+\bibitem[\protect\citeauthoryear{{Sutter}, {Lavaux}, {Wandelt}, {Weinberg} \&
+  {Warren}}{{Sutter} et~al.}{2014}]{Sutter14a}
+{Sutter} P.~M.,  {Lavaux} G.,  {Wandelt} B.~D.,  {Weinberg} D.~H.,    {Warren}
+  M.~S.,  2014, \mnras, 438, 3177
+
+\bibitem[\protect\citeauthoryear{{Tikhonov}}{{Tikhonov}}{2006}]{Tikhonov06}
+{Tikhonov} A.~V.,  2006, Astronomy Letters, 32, 727
+
+\bibitem[\protect\citeauthoryear{{Tikhonov}}{{Tikhonov}}{2007}]{Tikhonov07}
+{Tikhonov} A.~V.,  2007, Astronomy Letters, 33, 499
+
+\bibitem[\protect\citeauthoryear{{van de Weygaert} \& {van Kampen}}{{van de
+  Weygaert} \& {van Kampen}}{1993}]{Weygaert93}
+{van de Weygaert} R.,  {van Kampen} E.,  1993, \mnras, 263, 481
+
+\bibitem[\protect\citeauthoryear{{von Benda-Beckmann} \& {M{\"u}ller}}{{von
+  Benda-Beckmann} \& {M{\"u}ller}}{2008}]{BendaBeckmann08}
+{von Benda-Beckmann} A.~M.,  {M{\"u}ller} V.,  2008, \mnras, 384, 1189
+
+\bibitem[\protect\citeauthoryear{{York}, et al. \& {(the SDSS
+  Collaboration),}}{{York} et~al.}{2000}]{York00}
+{York} D.~G.,  et al.   {(the SDSS Collaboration),} 2000, \aj, 120, 1579
+
+\bibitem[\protect\citeauthoryear{{Zeldovich}, {Einasto} \&
+  {Shandarin}}{{Zeldovich} et~al.}{1982}]{Zeldovich82}
+{Zeldovich} I.~B.,  {Einasto} J.,    {Shandarin} S.~F.,  1982, \nat, 300, 407
+
+\bibitem[\protect\citeauthoryear{{Zel'dovich}}{{Zel'dovich}}{1970}]{Zeldovich70}
+{Zel'dovich} Y.~B.,  1970, \aap, 5, 84
+
+\end{thebibliography}
 

### 2015-06-20 first_cosmic_voids.tex
latex first submitted version

--- 2015-06-19 cosmic_voids.tex
@@
 \newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
-\newcommand{\before}[1]{\textcolor{red}{ #1}}
-\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
 
@@
 
-% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
 The tracer that we use to define the voids is the fractional
@@
 anisotropy degree of the diffusivity of water molecules through
-cerebral tissue in nuclear magnetic resonance imaging, thereby allowing to 
-detect structures that restrict the otherwise isotropic Brownian movement 
-of water molecules. Taking into account that this process is identical to 
-the velocity shear in the large-scale matter distribution, 
-\citet{Libeskind13} introduced the concept of the FA in the context of 
-Cosmic Web classification schemes.
-
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+cerebral tissue in nuclear magnetic resonance
+imaging and \citet{Libeskind13} introduced this concept in the context
+of Cosmic Web classification schemes.
 
@@
   width=0.73\textheight]{cosmicweb_FA_Vweb.pdf}
-  \caption{Different fields in a slice of
-    $1\hMpc$ width in the Bolshoi simulation. Top/bottom panels correspond
-    to the T-Web/V-Web.      
+  \caption{Visual impression of different fields in a slice of
+    $1\hMpc$ width in the Bolshoi simulation.   
     Fractional Anisotropy field (left); cosmic web classification
-    (middle) for a given value of the threhold eigenvalue
-    $\lambda_{\rm th}$ where voids are white, sheets are light gray,
-    filaments are dark gray and knots are black; individual voids (right) found by 
-    the a watershed algorithm on the Fractional Anisotropy field. Colours
-    in the right panels correspond with the effective radius of each void. }
+    (middle) where voids are white, sheets are light gray, filaments
+    are dark gray and knots are black; colored individual
+    voids (right) found by the a watershed algorithm on the Fractional
+    Anisotropy field. Top/bottom corresponds to the T-Web/V-Web.}
   \label{fig:FA_field}
@@
 
-Usually, the threshold $\lambda_{th}$ is a free parameter that is
-tuned to reproduce the visual appearence of the comic web. 
-However, in this paper this threshold does not play any role in our
-computations.
-In Figure \ref{fig:L1_correlations} we offer a threshold estimate
-(from the FA=$0.95$ as a function of $\lambda_1$, this choice is
-explained in the next section) only as a guide to readers familiar
-with its meaning.
+Usually, the threshold is a free parameter that is tuned to reproduce
+the visual appearence of the comic web. 
+In this paper we take a different approach.
+In this work we propose an optimal value of the threshold based on the
+maximization of the fractional anisotropy field in the locations label
+as filaments and walls. 
+This threshold does not enter into our computations. 
+We simply offer this estimate as a guide to readers familiar with the
+meaning of this threshold.
 
@@
 
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
-  width=0.33\textwidth]{FA_delta.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
-  width=0.33\textwidth]{delta_L1.pdf}
-  \includegraphics[trim = 1mm 0mm 5mm 10mm, keepaspectratio=true,
-  width=0.33\textwidth]{FA_L1.pdf}
-
-  \captionof{figure}{\small Fractional Anisotropy  as a function of
-    the overdensity (left) and the eigenvalue $\lambda_1$ (middle), and
-    density contrast (right) as a function of the
-    eigenvalue $\lambda_1$ for each web scheme (T-Web,  continous
-    lines. V-Web, dashed lines). Thick central lines are the median
-    and filled regions include $50\%$ of the cells in each bin. 
-    The left panel we confirms that underdense regions can be
-    identified with Fractional Anisotropy values less than $0.95$.
-    For this reason we define voids to be composed by cells with
-    Fractional Anisotropy equal or less than this value.
-    In the middle and right panel we show the equivalent eigenvalue
-    threshold for the T-Web and V-web corresponding to that
-    Fractional Anisotropy. 
-    This threshold on the eigenvalues does not influence 
-    our computations. We show it as a guide to readers familiar with the
-    order of magnitude expectation for this quantity.}
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{delta_L1.pdf}  
+  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
+  width=0.35\textheight]{FA_L1.pdf}
+
+  \captionof{figure}{\small Overdensity (left) and Fractional
+    Anisotropy (right) with respect to the eigenvalue $\lambda_1$ 
+    for each web scheme (T-Web, continous lines. V-Web, dashed lines) calculated 
+    over all grid cells in the Bolshoi simulation. 
+    Thick central lines are the median and filled regions include
+    $50\%$ of the cells in each bin.
+    This information is necesary to define void boundaries in
+    the watershed algorithm. 
+    The vertical lines show the equivalent threshold values for the
+    T-Web and V-web in order to have voids composed by cells with
+    Fractional Anisotrop equal or less than $0.95$. 
+   This threshold on the eigenvalues does not influence our
+   computations. 
+   We show it as a guide to readers familiar with the
+   order of magnitude expectation for this threshold.}
   \label{fig:L1_correlations}
@@
 \end{figure*}
-%.........................................................................
-
-%-------------------------------------------------------------------------
-%FIGURE 3: Histograms for each environment regarding the FA value
-%\begin{figure}
-%\centering
-%  \includegraphics[trim = 1mm 0mm 5mm 10mm, clip, keepaspectratio=true,
-%  width=0.35\textheight]{FA_environment.pdf}
-%   \captionof{figure}{\small Volume of each environment per FA
-%   ($dV_i/dFA,\ \ i=v,s,f,k$) normalized by the total volume per FA
-%   ($dV/dFA$). 
-%  Top/bottom corresponds to the T-Web/V-Web. For a given value of the FA, 
-%  each line represents the volume contribution of the respective 
-%  environment to the total volume with the same FA value. Above FA=0.95,
-%  only sheets and filaments contribute to all the volume of the simulation
-%  within that range of FA.}
-%  \label{fig:FA_environment}
-%\end{figure}
 %.........................................................................
@@
 
-% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
-The fractional anisotropy (FA), as developed by \citet{Basser95}, 
-was conceived to quantify the anisotropy of the diffusivity of water
+The fractional anisotropy (FA), as developed by \citet{Basser95}, was 
+conceived to quantify the anisotropy of the diffusivity of water
 molecules through cerebral tissue in nuclear magnetic resonance imaging. 
-In this manner, barriers such as microtubules and cell membranes, that 
-restrict the otherwise isotropic Brownian motion of water molecules, can 
-be detected. In a cosmological context, the problem of finding structures 
-is very similar, where filaments and sheets restrict the otherwise 
-isotropic collapsing/expanding dynamics of the matter. Taking this into 
-account, we present here the FA, much in the same way as \citet{Libeskind13}, 
+Here we present the FA, much in the same way as \citet{Libeskind13},
 to use it as a tracer of cosmic voids.
-
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
 
@@
 
-% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
 In Fig. \ref{fig:L1_correlations} we show that the these two values
-are indeed closely correlated.  The top panel shows the correlation between 
-$\lambda_1$ and $\delta$ for all the grid cells in the simulation while the 
-bottom panel shows the correlation between $\lambda_1$ and the FA. The middle 
-panel shows the correlation between $\delta$ and the FA. This shows that the 
-density has a larger scatter at fixed $\lambda_1$ than the FA, yet large and 
-small values of the density remain still associated to low values of the FA.
-
-At this point, the eigenvalue $\lambda_1$ and the FA appear to be
-equally potential candidates for tracing cosmic voids, however, the 
-eigenvalue $\lambda_1$ presents, along with the density, an undesirable 
-feature for a void tracer. As we move out from inner parts of voids to outer 
-parts, $\lambda_1$ and the density increase monotonically, making unclear 
-where to set the frontier of voids. On the other hand, the FA naturally 
-indicates the real frontier as regions where anisotropic collapse begin to 
-dominate, which, according to Fig. \ref{fig:FA_environment}, are associated
-mainly to sheets and, to a lesser extent, to filaments.
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+are indeed closely correlated.  
+The right panel shows the correlation between $\lambda_1$ and $\delta$ for
+all the grid cells in the simulation while the right panel shows the
+correlation between $\lambda_1$ and the FA. This shows that the
+overdensity has a large scatter at fixed $\lambda_1$.
 
@@
 \citep{Schaap00}.
-Nevertheless, in our case the average number of particles per cell
-  is large enough ($512$ particles/cell) ensuring that the lowest
-  density regions are sampled with at least $\sim 10$ particles
-  ($\delta \sim-0.98$), which seems to avoid spurious results from a
-  noisy density field sampling.
-
-% CORRECTION !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
+However, from the analysis of our results the choice of a fixed
+Cartesian mesh does not induce spurious results, at least with
+the mass resolution we have in the N-body simulation.
 
@@
 If the density field is used, a typical threshold is
-$\delta = -0.8$ \citep{Platen07},  which means that, given two neighbouring 
-voids, if the mean value of the density across their common boundary is 
-below that threshold, the two voids are merged.
+$\delta = -0.8$ \citep{Platen07},  which means that any ridge between
+two voids with overdensity below that value is removed to merge the
+respective voids. 
 In our case we have to find a corresponding FA value
 to define this threshold.
-%!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
-
-\after{In the left panel of Fig. \ref{fig:L1_correlations} we see how 
-the FA correlates with the matter overdensity. 
-A value of $\delta=-0.8$ corresponds to a value of $FA\sim 0.65$ regardless of
-the web-finding scheme. 
-This is the value we choose to remove ridges between two watershed
-voids. 
+
+In Fig. \ref{fig:L1_correlations} we find the correlations of
+the eigenvalue $\lambda_1$ with the matter overdensity (left panel) and
+the FA (right panel).
+We can use this information to find the equivalent FA threshold. 
+From the left panel we see that an underdensity of $\delta=-0.8$ 
+corresponds to $\lambda_1=0.0$, regardless of the web-finding
+scheme.
+From the second panel we have a very tight correlation of $\lambda_1$
+with the FA, indicating that in turn $\lambda_1=0.0$ corresponds to a
+FA=$0.65$ which is the value that we choose to remove ridges. 
 The right column in Fig. \ref{fig:FA_field} shows all the individual
 voids that have been identified using the watershed algorithm on the
-FA field.}
-
-%.........................................................................
-%FIGURE 4: volume functions
+FA field.
+
+%.........................................................................
+%FIGURE 3: volume functions
 \begin{figure*}
@@
     curves correspond to the T-Web (V-Web).
-    The abundance for small ($\reff <2.0\hMpc$) overcompensated voids
+    The abundance for small ($r_{eff}<2.0\hMpc$) overcompensated voids
     shoots up in the V-Web scheme.
@@
 smoothing length of the density field, i.e. $\sim 1$\hMpc.  
-For smaller interpolation/smoothing scales the shot noise in
-  the low density regions starts to be noticeable.
+Below that scale numerical resolution effects become important. 
 With that choice we find a void volume filling fraction $54.88\%$ and
 $47.06\%$ for the FA-Vweb and the FA-Tweb, respectively.
-For larger smoothing scales ($>5\hMpc$) the density and shear fields
-  tend to be Gaussian and therefore follow closely the analytical environment abundance
-  predictions for Gaussian random fields \citep{Forero09,Alonso2015}.
 
@@
 Comparing the abundance of large voids in the two web schemes, we find
-that the largest voids in the V-Web have $\reff \sim 10$\hMpc,
-while the T-Web scheme includes voids as large as $\reff \sim 15$\hMpc. 
+that the largest voids in the V-Web have $r_{\rm eff}\sim 10$\hMpc,
+while the T-Web scheme includes voids as large as $r_{\rm eff}\sim 15$\hMpc. 
 This suggests that large voids in the T-Web scheme have a velocity
@@
 %.........................................................................
-%FIGURE 5: Density profile of voids for each defined scheme
+%FIGURE 4: Density profile of voids for each defined scheme
 \begin{figure*}
@@
 %\midrule
-\textbf{${\bf \reff }$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
+\textbf{${\bf r_{\rm eff}}$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
 %\midrule
@@
 The largest voids ($8.3-12\ \hMpc$) have an underdensity
-$\delta \sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
+$\sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
 -0.8$ at their centers.
@@
 Our results extend the findings of \cite{Hamaus14} into the range of
-voids with size $\reff <10$\hMpc.
+voids with size $r_{\rm eff}<10$\hMpc.
 
@@
 We find that subcompensated voids have outflowing velocity profiles
-all the way up to the radius where the average radial
+all the way up to the effective radius where the average radial
 density reaches the average value.
-For voids with sizes $\reff <8\hMpc$ the outflow is always
+For voids with sizes $r_{\rm eff}<8\hMpc$ the outflow is always
 positive, consistent with the fact that their density profiles do not
@@
 We find that the FA clearly magnifies the difference between the
-internal profile $r/\reff <1$ and the external profile $r/\reff >1$. 
+internal profile $r_{\rm eff}<1$ and the external profile $r_{\rm
+  eff}>1$. 
 Subcompensanted voids in the T-Web reach an asymptotic background
-value of F=$0.8$ almost right at $r/\reff =2$. 
+value of F=$0.8$ almost right at $r_{\rm eff}=2$. 
 For the V-Web the results are similar, albeit rather slowly with the
@@
 Overcompensated voids reach a maximum FA at the same effective radiuus
-$r/\reff =1$ and decline to reach an asymptotic value of FA=$0.85$
+$r_{\rm eff}=1$ and decline to reach an asymptotic value of FA=$0.85$
 at larger radii.
@@
 The difference between the radius where the density ridge is reached 
-($r/\reff =3$) and the radius of the FA maxima ($r/\reff =1$, most
-manifest in the T-Web voids) justifies in a more quantiative way the
-qualitative argument we present in sub-section \ref{subsec:watershed}
-to define void boundaries in our method.  
-Namely that as we increase the void boundary moving away from the
-center, we reach first middle density walls, before reaching high
-density structures associated with high anisotropy.  
-This implies that voids defined with the FA never present positive
-overdensities, making the FA maximum a reasonable boundary for voids
-compared to the traditional definition that puts the boundary at the
-densityridge.
+($r_{\rm eff}=3$) and the radius of the FA  ridge ($r_{\rm eff}=1$ )
+justifies in a more quantiative way the qualitative argument
+we present in sub-section \ref{subsec:watershed} to define void boundaries in
+our method.  
+Namely that as we increase the void boundary, we reach
+first middle density walls, before reaching high density structures
+associated with high anisotropy. 
+This makes the FA ridge a reasonable
+boundary for voids compared to the traditional definition that puts
+the boundary at the density ridge.
 
@@
 In these profiles it is evident the presence of an overdense ridge
-around $2<r/\reff <3$ for the overcompensated voids.
+around $2<r/r_{\rm eff}<3$ for the overcompensated voids.
 Subcompensated voids do not show such a ridge keeping its density
-lower than the average value up to $r/\reff \sim 8$.
+lower than the average value up to $r/r_{\rm eff}\sim 8$.
 
@@
 density fields the ridge is, almost by definition, located around
-$r/\reff \sim 1$ and the subcompensated voids reach average
-density around $r/\reff \sim 3$. 
+$r/r_{\rm eff}\sim 1$ and the subcompensated voids reach average
+density around $r/r_{\rm eff}\sim 3$. 
 This indicates that voids defined by FA boundaries are smaller  than
@@
 For the subcompensated voids the FA quickly increases to FA values of 
-$\sim 0.7-0.8$ at $r/\reff \sim 1$ to find a plateau, which is
+$\sim 0.7-0.8$ at $r/r_{\rm eff}\sim 1$ to find a plateau, which is
 quite far from the limiting FA$=0.95$ suggesting that these voids are

### 2015-06-20 RefereeResponse.md
changed filename in referee response
fixed few typos in referee reply

@@
 We have addressed all the points raised by the referee. We include in
-this reply an answer to each comment. We have included the file main_diff.pdf
+this reply an answer to each comment. We have included the file diff_cosmic_voids.pdf
 showing the differences in the body of the paper.
@@
       - We prepare a new Figure (Fig. 3) to shows that filaments and
-      sheets have different behaviour in FA. Only sheets are
+      sheets have different behavior in FA. Only sheets are
       associated with high values of FA~1.
@@
     We have rewritten this paragraph. The threshold that is 
-    irrrelevant to our computations is lambda_th, not FA=0.95.
+    irrelevant to our computations is lambda_th, not FA=0.95.
 
@@
 7. **I'm confused a bit about the middle panels of Fig. 1. The title,
-    "Visual impresion for lambda_th=..."  is strange. Aren't there
+    "Visual impression for lambda_th=..."  is strange. Aren't there
     several thresholds here? Also, what are the blue dots? Also
@@
     expected results for larger smoothing scales. Namely, that the
-    statistics for the cosmci web tend to be those of a random
+    statistics for the cosmic web tend to be those of a random
     Gaussian field.

### 2015-07-19 cosmic_voids.tex
Final accepted version in MNRAS

@@
 abundance and radial averaged profiles for the density, velocity and
-fractional anistropy.
+fractional anisotropy.
 We find that voids in the velocity shear web are smaller than voids in
@@
 the inner region of filaments/sheets.
-We clasify voids as subcompensated/overcompansated depending on the
+We classify voids as subcompensated/overcompansated depending on the
 absence/presence of an overdense matter ridge in their density
@@
 Cosmic voids are regarded as one of the most striking features of the
-Universe on its larges scales ever since they were found in the first
+Universe on its larger scales ever since they were found in the first
 galaxy surveys \citep{Chincarini75, Gregory78, Einasto80M, Einasto80N,
@@
   Brunino07,  Foster09, Micheletti14, Sutter14}. 
-While other chemes are based on the smooth and continuous matter density
+While other schemes are based on the smooth and continuous matter density
 field either from simulations or from reconstruction procedures on
@@
 
-Here we introduce a new algorithm to define voids over the continous
+Here we introduce a new algorithm to define voids over the continuous
 matter density or velocity distribution defined on a fixed and
@@
     Fractional Anisotropy field (left); cosmic web classification
-    (middle) for a given value of the threhold eigenvalue
+    (middle) for a given value of the threshold eigenvalue
     $\lambda_{\rm th}$ where voids are white, sheets are light gray,
@@
 Our new void finding method is based on two existing cosmic web
-classification schemes that work on cosmological N-body simularions.
+classification schemes that work on cosmological N-body simulations.
 Both schemes depend on the construction of tensors based on the
@@
 The tidal tensor allows a classification in terms of the orbital
-dinamics of the matter field.
+dynamics of the matter field.
 This approach extends to second-order the equations of motion around 
@@
 Usually, the threshold $\lambda_{th}$ is a free parameter that is
-tuned to reproduce the visual appearence of the comic web. 
+tuned to reproduce the visual appearance of the comic web. 
 However, in this paper this threshold does not play any role in our
@@
     density contrast (right) as a function of the
-    eigenvalue $\lambda_1$ for each web scheme (T-Web,  continous
+    eigenvalue $\lambda_1$ for each web scheme (T-Web,  continuous
     lines. V-Web, dashed lines).     
@@
     and filled regions include $50\%$ of the cells in each bin. 
-    The left panel shows the tigth correlation between FA and
+    The left panel shows the tight correlation between FA and
     $\lambda_1$ in voids.
@@
 and $\delta$ increase monotonically making unclear where to set the
-void boudary, while for low density regions ($\delta<1$) the FA traces
-the boundary where anisotropic collapse regions begin to 
-dominate.
+void boundary, while for low density regions ($\delta<1$) the FA traces
+the boundary where anisotropic collapsing regions begin to 
+dominate, i.e. at the ridge reached around $\delta = 0$ as shown in the 
+right panel of Fig. \ref{fig:L1_correlations}.
 According to Fig. \ref{fig:FA_environment} these anisotropic areas are
@@
     panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
-    function of the effective radius. The continous (dashed)
+    function of the effective radius. The continuous (dashed)
     curves correspond to the T-Web (V-Web).
@@
 \citet{Hoffman12}.    
-The main argument is that as matter colides into a pancake-like
+The main argument is that as matter collides into a pancake-like
 fashion crossing sheets encounter each other at the symmetry plane.
@@
     profiles for stacked voids with different effective radii. The
-    sample is split into subcompensated andovercompensated voids
+    sample is split into subcompensated and overcompensated voids
     (right and left) for the web schemes T-Web and V-Web (top and
@@
 In Fig. \ref{fig:density_profile} we show the density and velocity profiles
-of voids splitted in these two families. 
+of voids split in these two families. 
 In the left column it becomes clear the difference between sub- and
@@
 The first interesting result is the overdensity value at the void's
-center.
+centre.
 We find that larger voids have a lower overdensity value.
@@
 $\delta \sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
--0.8$ at their centers.
+-0.8$ at their centres.
 This holds for both web schemes. 
@@
 
-A second feature about these profiles is their steepnes at inner
+A second feature about these profiles is their steepness at inner
 regions.  
@@
 profiles. 
-Positive values correspond to outflows with respect to the center.
+Positive values correspond to outflows with respect to the centre.
 
@@
 the effective radius. 
-Overcompensated voids reach a maximum FA at the same effective radiuus
+Overcompensated voids reach a maximum FA at the same effective radius
 $r/\reff =1$ and decline to reach an asymptotic value of FA=$0.85$
@@
 ($r/\reff =3$) and the radius of the FA maxima ($r/\reff =1$, most
-manifest in the T-Web voids) justifies in a more quantiative way the
+manifest in the T-Web voids) justifies in a more quantitative way the
 qualitative argument we present in sub-section \ref{subsec:watershed}
@@
 Namely that as we increase the void boundary moving away from the
-center, we reach first middle density walls, before reaching high
+centre, we reach first middle density walls, before reaching high
 density structures associated with high anisotropy.  
@@
 compared to the traditional definition that puts the boundary at the
-densityridge.
+density ridge.
 
@@
 This is due to two reasons. 
-First, there are artifacts in the web
+First, there are artefacts in the web
 finding scheme inside sheets. 
